### 2017-06-05 README.Rmd
initial commit

---
output:
  github_document:
    toc: true 
    toc_depth: 3
---

Infer: a grammar for statistical inference
---

The objective of this package is to perform statistical inference using a grammar that illustrates the underlying concepts and a format that coheres with the `tidyverse`.

### Hypothesis tests
![h-test diagram](figs/ht-diagram.png)

### Confidence intervals

### 2017-06-05 README.Rmd
point to issues
add examples

@@
 The objective of this package is to perform statistical inference using a grammar that illustrates the underlying concepts and a format that coheres with the `tidyverse`.
+To participate in the discussion surrounding the development of this package, please see the issues.
 
@@
 
+#### Examples
+
+One categorical (2 level) variable
+```
+mtcars %>%
+select(am) %>%
+hypothesis(null = “p = 25”) %>% # would require string parsing
+generate(repeat = 100) %>% # here it’d be doing simulation
+calculate(stat = “prop”) #
+```
+
+Two categorical (2 level) variables
+```
+mtcars %>%
+select(am, vs) %>%
+hypothesis(null = “independence”) %>% # 
+generate(repeat = 100) %>%
+calculate(stat = “diff in prop”) #
+```
+
+One categorical (>2 level) - GoF
+```
+mtcars %>%
+select(cyl) %>%
+hypothesis(null = “p1 = .33, p2 = .33, p3 = .33”) %>%
+generate(repeat = 100) %>%
+calculate(stat = “chisq”)
+```
+
+Two categorical (>2 level) variables
+```
+mtcars %>%
+select(cyl, am) %>%
+hypothesis(null = “independence”) %>%
+generate(repeat = 100) %>%
+calculate(stat = “chisq”)
+```
+
+One numerical variable one categorical (2 levels) (diff in means)
+```
+mtcars %>%
+select(mpg, am) %>%
+hypothesis(null = “equal means”) %>%
+generate(repeat = 100) %>%
+calculate(stat = “diff in means”)
+```
+
+One numerical one categorical (>2 levels) -  ANOVA
+```
+mtcars %>%
+select(mpg, cyl) %>%
+hypothesis(null = “equal means”) %>%
+generate(repeat = 100) %>%
+calculate(stat = “F”)
+```
+
+Two numerical vars - SLR
+```
+mtcars %>%
+select(mpg, hp) %>%
+hypothesis(null = “independence”) %>% # or “slope = 0”
+generate(repeat = 100) %>%
+calculate(stat = “lm(mpg ~ hp)”)
+```
+
 ### Confidence intervals

### 2017-06-05 README.Rmd

--- 2017-06-05 README.Rmd
@@
 
+#### Examples
+
+One categorical (2 level) variable
+```
+mtcars %>%
+  select(am) %>%
+  hypothesis(null = "p = 25") %>% # would require string parsing
+  generate(repeat = 100) %>% # here it’d be doing simulation
+  calculate(stat = "prop") #
+```
+
+Two categorical (2 level) variables
+```
+mtcars %>%
+  select(am, vs) %>%
+  hypothesis(null = "independence") %>% # 
+  generate(repeat = 100) %>%
+  calculate(stat = "diff in prop") #
+```
+
+One categorical (>2 level) - GoF
+```
+mtcars %>%
+  select(cyl) %>%
+  hypothesis(null = "p1 = .33, p2 = .33, p3 = .33") %>%
+  generate(repeat = 100) %>%
+  calculate(stat = "chisq")
+```
+
+Two categorical (>2 level) variables
+```
+mtcars %>%
+  select(cyl, am) %>%
+  hypothesis(null = "independence") %>%
+  generate(repeat = 100) %>%
+  calculate(stat = "chisq")
+```
+
+One numerical variable one categorical (2 levels) (diff in means)
+```
+mtcars %>%
+  select(mpg, am) %>%
+  hypothesis(null = "equal means") %>%
+  generate(repeat = 100) %>%
+  calculate(stat = "diff in means")
+```
+
+One numerical one categorical (>2 levels) -  ANOVA
+```
+mtcars %>%
+  select(mpg, cyl) %>%
+  hypothesis(null = "equal means") %>%
+  generate(repeat = 100) %>%
+  calculate(stat = "F")
+```
+
+Two numerical vars - SLR
+```
+mtcars %>%
+  select(mpg, hp) %>%
+  hypothesis(null = "independence") %>% # or "slope = 0"
+  generate(repeat = 100) %>%
+  calculate(stat = "lm(mpg ~ hp)")
+```
+
 ### Confidence intervals

### 2017-06-10 README.Rmd
Added Two Means example

--- 2017-06-05 README.Rmd
@@
 Infer: a grammar for statistical inference
+
 ---
@@
 
+#### Examples
+
+These examples assume that `mtcars` has been overwritten so that the variables
+`cyl`, `vs`, `am`, `gear`, and `carb` are `factor`s:
+
+```
+mtcars <- as.data.frame(mtcars) %>%
+  mutate(cyl = factor(cyl),
+         vs = factor(vs),
+         am = factor(am),
+         gear = factor(gear),
+         carb = factor(carb))
+```
+
+One categorical (2 level) variable
+```
+mtcars %>%
+  select(am) %>%
+  hypothesis(null = "p = 25") %>% # would require string parsing
+  generate(reps = 100, type = "permute") %>% # here it’d be doing simulation
+  calculate(stat = "prop") #
+```
+
+Two categorical (2 level) variables
+```
+mtcars %>%
+  select(am, vs) %>%
+  hypothesis(null = "independence") %>% # 
+  generate(reps = 100, type = "permute") %>%
+  calculate(stat = "diff in prop") #
+```
+
+One categorical (>2 level) - GoF
+```
+mtcars %>%
+  select(cyl) %>%
+  hypothesis(null = "p1 = .33, p2 = .33, p3 = .33") %>%
+  generate(reps = 100, type = "permute") %>%
+  calculate(stat = "chisq")
+```
+
+Two categorical (>2 level) variables
+```
+mtcars %>%
+  select(cyl, am) %>%
+  hypothesis(null = "independence") %>%
+  generate(reps = 100, type = "permute") %>%
+  calculate(stat = "chisq")
+```
+
+One numerical variable one categorical (2 levels) (diff in means)
+```
+mtcars %>%
+  select(mpg, am) %>%
+  hypothesis(null = "equal means") %>%
+  generate(reps = 100, type = "permute") %>%
+  calculate(stat = "diff in means")
+```
+
+One numerical one categorical (>2 levels) -  ANOVA
+```
+mtcars %>%
+  select(mpg, cyl) %>%
+  hypothesis(null = "equal means") %>%
+  generate(reps = 100, type = "permute") %>%
+  calculate(stat = "F")
+```
+
+Two numerical vars - SLR
+```
+mtcars %>%
+  select(mpg, hp) %>%
+  hypothesis(null = "independence") %>% # or "slope = 0"
+  generate(reps = 100, type = "permute") %>%
+  calculate(stat = "lm(mpg ~ hp)")
+```
+
 ### Confidence intervals
+
+One numerical (one mean)
+```
+mtcars %>%
+  select(mpg) %>%
+  generate(reps = 100, type = "bootstrap") %>%
+  calculate(stat = "mean")
+```

### 2017-06-12 README.Rmd
Change hypothesis to hypothesize and add Two Proportions example

@@
 
+***
+
 One categorical (2 level) variable
@@
   select(am) %>%
-  hypothesis(null = "p = 25") %>% # would require string parsing
+  hypothesize(null = "p = 25") %>% # would require string parsing
   generate(reps = 100, type = "permute") %>% # here it’d be doing simulation
@@
 Two categorical (2 level) variables
+
+- Implemented
+
 ```
@@
   select(am, vs) %>%
-  hypothesis(null = "independence") %>% # 
+  hypothesize(null = "independence") %>% # 
   generate(reps = 100, type = "permute") %>%
-  calculate(stat = "diff in prop") #
+  calculate(stat = "diff in props") #
 ```
@@
   select(cyl) %>%
-  hypothesis(null = "p1 = .33, p2 = .33, p3 = .33") %>%
+  hypothesize(null = "p1 = .33, p2 = .33, p3 = .33") %>%
   generate(reps = 100, type = "permute") %>%
@@
   select(cyl, am) %>%
-  hypothesis(null = "independence") %>%
+  hypothesize(null = "independence") %>%
   generate(reps = 100, type = "permute") %>%
@@
 One numerical variable one categorical (2 levels) (diff in means)
+
+- Implemented
+
 ```
@@
   select(mpg, am) %>%
-  hypothesis(null = "equal means") %>%
+  hypothesize(null = "equal means") %>%
   generate(reps = 100, type = "permute") %>%
@@
   select(mpg, cyl) %>%
-  hypothesis(null = "equal means") %>%
+  hypothesize(null = "equal means") %>%
   generate(reps = 100, type = "permute") %>%
@@
   select(mpg, hp) %>%
-  hypothesis(null = "independence") %>% # or "slope = 0"
+  hypothesize(null = "independence") %>% # or "slope = 0"
   generate(reps = 100, type = "permute") %>%

### 2017-06-12 R/infer.R

@@ -10,14 +10,14 @@
 #' # One binary variable
 #'   mtcars %>%
 #'     select(am) %>%
-#'     hypothesis(null = "p = 25") %>%
+#'     hypothesize(null = "p = 25") %>%
 #'     generate(reps = 100) %>%
 #'     calculate(stat = "prop")
 #'     
 #' # Permutation test
 #'   mtcars %>%
 #'     select(mpg, cyl) %>%
-#'     hypothesis(null = "rho = 0") %>%
+#'     hypothesize(null = "rho = 0") %>%
 #'     generate(reps = 100, type = "permute") %>%
 #'     calculate(stat = "cor")
 #' }
@@ -30,7 +30,7 @@
 #'     tidy()  
 #' }
 
-hypothesis <- function(x, null, ...) {
+hypothesize <- function(x, null, ...) {
   attr(x, "null") <- null
   return(as.tbl(x))
 }
@@ -60,16 +60,18 @@ bootstrap <- function(x, reps = 1, ...) {
 #' @importFrom dplyr bind_rows mutate_ group_by
 
 permute <- function(x, reps = 1, ...) {
-  replicate(reps, permute_once(x), simplify = FALSE) %>%
+  df_out <- replicate(reps, permute_once(x), simplify = FALSE) %>%
     dplyr::bind_rows() %>%
     dplyr::mutate_(replicate = ~rep(1:reps, each = nrow(x))) %>%
     dplyr::group_by(replicate)
+  attr(df_out, "null") <- attr(x, "null")
+  return(df_out)
 }
 
 permute_once <- function(x, ...) {
   dots <- list(...)
   
-#  if(attr(x, "null") == "equal means"){
+  if(attr(x, "null") == "equal means"){
     ## need to look for name of variable to permute...ugh
     ## by default, use the first column
     # y <- x[, 1]
@@ -81,35 +83,64 @@ permute_once <- function(x, ...) {
     y_prime <- y[ sample.int(length(y)) ]
     x[[num_name]] <- y_prime
     return(x)
-#  }
-  
+  }
+ 
+  if(attr(x, "null") == "independence"){
+    ## by default, permute the first column of the two selected
+    # Since dealing with tibble potentially, we need to force a
+    # vector here
+    y <- x[[1]]
+    
+    y_prime <- y[ sample.int(length(y)) ]
+    x[[1]] <- y_prime
+    return(x)
+  }  
+   
 }
 
 
-
-
[…]

### 2017-06-27 README.Rmd
Add "Implemented" tags in README
split hypotheses into null and parameters

@@
   select(am) %>%
-  hypothesize(null = "p = 25") %>% # would require string parsing
-  generate(reps = 100, type = "permute") %>% # here it’d be doing simulation
+  hypothesize(null = "point", p = .25) %>% 
+  generate(reps = 100, type = "simulation") %>% 
   calculate(stat = "prop") #
@@
   select(cyl) %>%
-  hypothesize(null = "p1 = .33, p2 = .33, p3 = .33") %>%
-  generate(reps = 100, type = "permute") %>%
+  hypothesize(null = "point", p1 = .25, p2 = .25, p3 = .50) %>% # call levels() to find order of p's
+  generate(reps = 100, type = "simulate") %>%
   calculate(stat = "chisq")
@@
   select(mpg, am) %>%
-  hypothesize(null = "equal means") %>%
+  hypothesize(null = "independence") %>%
   generate(reps = 100, type = "permute") %>%
@@
   select(mpg, cyl) %>%
-  hypothesize(null = "equal means") %>%
+  hypothesize(null = "independence") %>%
   generate(reps = 100, type = "permute") %>%
@@
 One numerical (one mean)
+
+- Implemented
+
 ```

### 2017-06-27 README.Rmd
fleshed out simulate, added examples, and added stat = "prop"

@@
   hypothesize(null = "point", p = .25) %>% 
-  generate(reps = 100, type = "simulation") %>% 
+  generate(reps = 100, type = "simulate") %>% 
   calculate(stat = "prop") #

### 2017-06-27 R/calculate.R

@@ -31,7 +31,7 @@
 
 calculate <- function(x, stat, ...) {
 
-  if(stat == "diff in means"){
+  if (stat == "diff in means") {
     num_cols <- sapply(x, is.numeric)
     non_num_name <- names(num_cols[num_cols != TRUE])
     col <- setdiff(names(x), "replicate")
@@ -45,7 +45,7 @@ calculate <- function(x, stat, ...) {
     return(df_out)
   }
 
-  if(stat == "diff in props"){
+  if (stat == "diff in props") {
     # Assume the first column is to be permuted and
     # the second column are the groups
     # Assumes the variables are factors and NOT chars here!
@@ -62,11 +62,20 @@ calculate <- function(x, stat, ...) {
     return(df_out)
   }
 
-  if(stat == "mean"){
+  if (stat == "mean") {
     col <- setdiff(names(x), "replicate")
     x %>%
       dplyr::group_by(replicate) %>%
       dplyr::summarize_(mean = lazyeval::interp(~mean(var),
+                                                var = as.name(col)))
+  }
+  
+  if (stat == "prop") {
+    col <- setdiff(names(x), "replicate")
+    x %>%
+      dplyr::group_by(replicate) %>%
+      dplyr::summarize_(N = ~n(),
+                        prop = lazyeval::interp(~mean(var == levels(var)[1]),
                                                 var = as.name(col)))
   }
 

### 2017-06-27 R/generate.R

@@ -5,6 +5,38 @@
 #' @param ... currently ignored
 #' @importFrom dplyr group_by
 #' @export
+#' @examples 
+#' 
+#' # bootstrap for one numerical variable
+#' if (require(dplyr)) {
+#'   mtcars %>%
+#'     select(mpg) %>%
+#'     generate(reps = 100, type = "bootstrap") %>%
+#'     calculate(stat = "mean")
+#'     
+#'  # permutation test for equal means
+#'   mtcars %>% 
+#'     select(mpg, am) %>%
+#'     hypothesize(null = "equal means") %>%
+#'     generate(reps = 100, type = "permute") %>%
+#'     calculate(stat = "diff in means")
+#'  
+#'  # simulate draws from a single categorical variable
+#'  mtcars %>% 
+#'    select(am) %>%
+#'    mutate(am = factor(am)) %>%
+#'    hypothesize(null = "point", p1 = 0.25, p2 = 0.75) %>%
+#'    generate(reps = 100, type = "simulate") %>%
+#'    calculate(stat = "prop")
+#'    
+#'  # goodness-of-fit for one categorical variable
+#'  mtcars %>%
+#'    select(cyl) %>%
+#'    hypothesize(null = "point", p1 = .25, p2 = .25, p3 = .50) %>%
+#'    generate(reps = 100, type = "simulate") %>%
+#'    calculate(stat = "chisq")
+#' }
+#' 
 
 generate <- function(x, reps = 1, type = "bootstrap", ...) {
   if (type == "bootstrap") {
@@ -37,7 +69,7 @@ permute <- function(x, reps = 1, ...) {
 permute_once <- function(x, ...) {
   dots <- list(...)
 
-  if(attr(x, "null") == "equal means"){
+  if (attr(x, "null") == "equal means") {
     ## need to look for name of variable to permute...ugh
     ## by default, use the first column
     # y <- x[, 1]
@@ -51,7 +83,7 @@ permute_once <- function(x, ...) {
     return(x)
   }
 
-  if(attr(x, "null") == "independence"){
+  if (attr(x, "null") == "independence") {
     ## by default, permute the first column of the two selected
     # Since dealing with tibble potentially, we need to force a
     # vector here
@@ -64,23 +96,36 @@ permute_once <- function(x, ...) {
 
 }
 
+#' @importFrom dplyr pull
+
 simulate <- function(x, reps = 1, ...) {
[…]

### 2017-06-27 R/hypothesize.R

@@ -11,7 +11,7 @@
 #'   mtcars %>%
 #'     select(am) %>%
 #'     hypothesize(null = "point", p = 0.25) %>%
-#'     generate(reps = 100) %>%
+#'     generate(reps = 100, type = "simulate") %>%
 #'     calculate(stat = "prop")
 #'
 #' # Permutation test
@@ -41,7 +41,7 @@ hypothesize <- function(x, null = c("independence", "point"), ...) {
 
   # error: too many columns
   if (ncol(x) > 2) {
-    stop("Too many columns. Use select() to narrow down your data.frame.")
+    stop("Too many columns. Use select() to narrow your data.frame.")
   }
 
   # error: null not found
@@ -58,10 +58,10 @@ hypothesize <- function(x, null = c("independence", "point"), ...) {
 
   dots <- list(...)
   params <- parse_params(dots)
-
-  # error: number of parameters exceeds number of columns
-  if(length(params) > ncol(x)) {
-    stop("The number of parameters exceeds the number of columns.")
+  
+  # error: number of parameters exceeds number of factor levels
+  if (length(params) != length(levels(x[,1]))) {
+    stop("The number of parameters must match the number of factor levels.")
   }
 
   attr(x, "params") <- params

### 2017-06-29 README.Rmd
change p to a named vector

@@
   select(am) %>%
-  hypothesize(null = "point", p = .25) %>% 
+  hypothesize(null = "point", p = c("manual" = .25)) %>% 
   generate(reps = 100, type = "simulate") %>% 
@@
   select(cyl) %>%
-  hypothesize(null = "point", p1 = .25, p2 = .25, p3 = .50) %>% # call levels() to find order of p's
+  hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25)) %>% # call levels() to find order of p's
   generate(reps = 100, type = "simulate") %>%

### 2017-06-29 README.Rmd
fi typo

@@
   select(am) %>%
-  hypothesize(null = "point", p = c("manual" = .25)) %>% 
+  hypothesize(null = "point", p = c("1" = .25)) %>% 
   generate(reps = 100, type = "simulate") %>% 

### 2017-07-09 README.Rmd
update with one prop

--- 2017-06-27 README.Rmd
@@
 One categorical (2 level) variable
+
 ```
@@
   select(am) %>%
-  hypothesize(null = "point", p = .25) %>% 
+  hypothesize(null = "point", p = c("1" = .25)) %>% 
   generate(reps = 100, type = "simulate") %>% 
@@
 
-Two categorical (2 level) variables
-
-- Implemented
+Two categorical (2 level) variables (not yet implemented)
 
@@
 
-One categorical (>2 level) - GoF
+One categorical (>2 level) - GoF  (not yet implemented)
 ```
@@
 
-Two categorical (>2 level) variables
+Two categorical (>2 level) variables  (not yet implemented)
 ```
@@
 
-- Implemented
-
 ```
@@
 
-One numerical one categorical (>2 levels) -  ANOVA
+One numerical one categorical (>2 levels) -  ANOVA  (not yet implemented)
+
 ```
@@
 
-Two numerical vars - SLR
+Two numerical vars - SLR  (not yet implemented)
 ```

### 2017-07-12 README.Rmd
implement diff in prop

@@
   generate(reps = 100, type = "simulate") %>% 
-  calculate(stat = "prop") #
+  calculate(stat = "prop")
 ```
 
-Two categorical (2 level) variables (not yet implemented)
+Two categorical (2 level) variables
 
@@
   select(am, vs) %>%
-  hypothesize(null = "independence") %>% # 
+  hypothesize(null = "independence") %>%
   generate(reps = 100, type = "permute") %>%
-  calculate(stat = "diff in props") #
+  calculate(stat = "diff in props")
 ```

### 2017-07-12 README.Rmd
replace select() with specify()

@@
 The objective of this package is to perform statistical inference using a grammar that illustrates the underlying concepts and a format that coheres with the `tidyverse`.
-To participate in the discussion surrounding the development of this package, please see the issues.
 
@@
 mtcars %>%
-  select(am) %>%
+  specify(response = am) %>% # alt: am ~ 1
   hypothesize(null = "point", p = c("1" = .25)) %>% 
@@
 mtcars %>%
-  select(am, vs) %>%
+  specify(am ~ vs) %>% # alt: response = am, explanatory = vs
   hypothesize(null = "independence") %>%
@@
 mtcars %>%
-  select(cyl) %>%
-  hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25)) %>% # call levels() to find order of p's
+  specify(response = cyl) %>% # alt: cyl ~ 1
+  hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25)) %>%
   generate(reps = 100, type = "simulate") %>%
@@
 mtcars %>%
-  select(cyl, am) %>%
+  specify(cyl ~ am) %>% # alt: response = cyl, explanatory = am
   hypothesize(null = "independence") %>%
@@
 mtcars %>%
-  select(mpg, am) %>%
+  specify(mpg ~ am) %>% alt: response = mpg, explanatory = am
   hypothesize(null = "independence") %>%
@@
 mtcars %>%
-  select(mpg, cyl) %>%
+  specify(mpg ~ cyl) %>% # alt: response = mpg, explanatory = cyl
   hypothesize(null = "independence") %>%
@@
 mtcars %>%
-  select(mpg, hp) %>%
+  specify(mpg ~ hp) %>% alt: response = mpg, explanatory = cyl
   hypothesize(null = "independence") %>% # or "slope = 0"
@@
 mtcars %>%
-  select(mpg) %>%
+  specify(response = mpg) %>%
   generate(reps = 100, type = "bootstrap") %>%
@@
 ```
+
+One numerical (one proportion)
+
+```
+mtcars %>%
+  specify(response = mpg) %>%
+  generate(reps = 100, type = "bootstrap") %>%
+  calculate(stat = "mean")
+```

### 2017-07-12 README.Rmd
Add tweaks

@@
 One categorical (>2 level) - GoF  (not yet implemented)
+
 ```
@@
 Two categorical (>2 level) variables  (not yet implemented)
+
 ```
@@
 mtcars %>%
-  specify(mpg ~ am) %>% alt: response = mpg, explanatory = am
+  specify(mpg ~ am) %>% # alt: response = mpg, explanatory = am
   hypothesize(null = "independence") %>%
@@
 Two numerical vars - SLR  (not yet implemented)
+
 ```
 mtcars %>%
-  specify(mpg ~ hp) %>% alt: response = mpg, explanatory = cyl
+  specify(mpg ~ hp) %>% # alt: response = mpg, explanatory = cyl
   hypothesize(null = "independence") %>% # or "slope = 0"
   generate(reps = 100, type = "permute") %>%
-  calculate(stat = "lm(mpg ~ hp)")
+  calculate(stat = "slope")
 ```
@@
 mtcars %>%
-  specify(response = mpg) %>%
+  specify(response = mpg) %>% # alt: mpg ~ 1
   generate(reps = 100, type = "bootstrap") %>%
@@
 
-One numerical (one proportion)
+One categorical (one proportion) (not yet implemented)
 
@@
 mtcars %>%
-  specify(response = mpg) %>%
+  specify(response = am) %>%
   generate(reps = 100, type = "bootstrap") %>%
-  calculate(stat = "mean")
+  calculate(stat = "prop")
 ```

### 2017-07-12 README.Rmd
finish up CIs

@@
 ```
+
+One numerical variable one categorical (2 levels) (diff in means)
+
+```
+mtcars %>%
+  specify(mpg ~ am) %>%
+  generate(reps = 100, type = "bootstrap") %>%
+  calculate(stat = "diff in means")
+```
+
+Two categorical variables (diff in proportions) (not yet implemented)
+
+```
+mtcars %>%
+  specify(am ~ vs) %>%
+  generate(reps = 100, type = "bootstrap") %>%
+  calculate(stat = "diff in prop")
+```

### 2017-07-13 README.Rmd
update implementation status
add ci for slope

@@
 
-One categorical (2 level) variable
+One categorical (2 level) variable (implemented up to calculate())
 
@@
 
-Two categorical (2 level) variables
+Two categorical (2 level) variables (implemented)
 
@@
 mtcars %>%
-  specify(response = mpg) %>% # alt: mpg ~ 1
+  specify(response = mpg) %>%
   generate(reps = 100, type = "bootstrap") %>%
@@
 ```
+
+Two numerical vars - SLR  (not yet implemented)
+
+```
+mtcars %>%
+  specify(mpg ~ hp) %>% 
+  generate(reps = 100, type = "bootstrap") %>%
+  calculate(stat = "slope")
+```

### 2017-07-14 README.Rmd
update implementation status

@@
 
-One categorical (>2 level) - GoF  (not yet implemented)
+One categorical (>2 level) - GoF  (implemented)
 
@@
 mtcars %>%
-  specify(response = cyl) %>% # alt: cyl ~ 1
+  specify(cyl ~ NULL) %>% # alt: response = cyl
   hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25)) %>%
   generate(reps = 100, type = "simulate") %>%
-  calculate(stat = "chisq")
+  calculate(stat = "Chisq")
 ```
 
-Two categorical (>2 level) variables  (not yet implemented)
+Two categorical (>2 level) variables  (implemented)
 
@@
   generate(reps = 100, type = "permute") %>%
-  calculate(stat = "chisq")
+  calculate(stat = "Chisq")
 ```
 
-One numerical variable one categorical (2 levels) (diff in means)
+One numerical variable one categorical (2 levels) (diff in means) (implemented)
 

### 2017-07-17 README.Rmd
update
Add difference in medians example to README

@@
 
-One categorical (2 level) variable (implemented up to calculate())
+One categorical (2 level) variable
 
@@
 mtcars %>%
-  specify(response = am) %>% # alt: am ~ 1
+  specify(response = am) %>% # alt: am ~ NULL (or am ~ 1)
   hypothesize(null = "point", p = c("1" = .25)) %>% 
@@
 
-Two categorical (2 level) variables (implemented)
+Two categorical (2 level) variables
 
@@
 
-One categorical (>2 level) - GoF  (implemented)
+One categorical (>2 level) - GoF
 
@@
 
-Two categorical (>2 level) variables  (implemented)
+Two categorical (>2 level) variables
 
@@
 
-One numerical variable one categorical (2 levels) (diff in means) (implemented)
+One numerical variable one categorical (2 levels) (diff in means)
 
@@
 
-One numerical one categorical (>2 levels) -  ANOVA  (not yet implemented)
+One numerical variable one categorical (2 levels) (diff in medians)
+
+```
+mtcars %>%
+  specify(mpg ~ am) %>% # alt: response = mpg, explanatory = am
+  hypothesize(null = "independence") %>%
+  generate(reps = 100, type = "permute") %>%
+  calculate(stat = "diff in medians")
+```
+
+One numerical one categorical (>2 levels) -  ANOVA
 
@@
 
-Two numerical vars - SLR  (not yet implemented)
+Two numerical vars - SLR
 

### 2017-07-18 R/generate.R
Implemented one mean hypothesis test

@@ -1,45 +1,16 @@
 #' Generate resamples
 #' @param x a data frame that can be coerced into a \code{\link[dplyr]{tbl_df}}
 #' @param reps the number of resamples to generate
-#' @param type currently either \code{bootstrap} or \code{permute}
+#' @param type currently either \code{bootstrap}, \code{permute}, or \code{simulate}
 #' @param ... currently ignored
 #' @importFrom dplyr group_by
 #' @export
 #' @examples
 #'
-#' # bootstrap for one numerical variable
-#' if (require(dplyr)) {
-#'   mtcars %>%
-#'     select(mpg) %>%
-#'     generate(reps = 100, type = "bootstrap") %>%
-#'     calculate(stat = "mean")
-#'
-#'  # permutation test for equal means
-#'   mtcars %>%
-#'     select(mpg, am) %>%
-#'     hypothesize(null = "equal means") %>%
-#'     generate(reps = 100, type = "permute") %>%
-#'     calculate(stat = "diff in means")
-#'
-#'  # simulate draws from a single categorical variable
-#'  mtcars %>%
-#'    select(am) %>%
-#'    mutate(am = factor(am)) %>%
-#'    hypothesize(null = "point", p1 = 0.25, p2 = 0.75) %>%
-#'    generate(reps = 100, type = "simulate") %>%
-#'    calculate(stat = "prop")
-#'
-#'  # goodness-of-fit for one categorical variable
-#'  mtcars %>%
-#'    select(cyl) %>%
-#'    hypothesize(null = "point", p1 = .25, p2 = .25, p3 = .50) %>%
-#'    generate(reps = 100, type = "simulate") %>%
-#'    calculate(stat = "chisq")
-#' }
 #'
 
 generate <- function(x, reps = 1, type = "bootstrap", ...) {
-  if (type == "bootstrap") {
+  if (type == "bootstrap"){
     return(bootstrap(x, reps, ...))
   }
   if (type == "permute") {
@@ -52,6 +23,14 @@ generate <- function(x, reps = 1, type = "bootstrap", ...) {
 }
 
 bootstrap <- function(x, reps = 1, ...) {
+  # Check if hypothesis test chosen
+  # If so, shift the variable chosen to have a mean corresponding
+  # to that specified in `hypothesize`
+  if(attr(attr(x, "params"), "names") == "mu"){
+    col <- as.character(attr(x, "response"))
[…]

### 2017-07-18 R/hypothesize.R

@@ -66,11 +66,13 @@ parse_params <- function(dots, x) {
   }
 
   # add in 1 - p if it's missing
-  if (length(dots[[p_ind]]) == 1) {
-    warning(paste0("Missing level, assuming proportion is 1 - ", dots$p, "."))    
+  if(length(p_ind)){
+    if(length(dots[[p_ind]]) == 1){
+    warning(paste0("Missing level, assuming proportion is 1 - ", dots$p, "."))
     missing_lev <- setdiff(levels(pull(x, !! attr(x, "response"))), names(dots$p))
     dots$p <- append(dots$p, 1 - dots$p)
     names(dots$p)[2] <- missing_lev
+    }
   }
   
   # if (sum(dots[[p_ind]]) != 1){

### 2017-07-18 README.Rmd
Implemented one mean hypothesis test
Add one median bootstrap CI and hypothesis test

@@
 ***
+
+One numerical variable (mean)
+
+```
+mtcars %>%
+  specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
+  hypothesize(null = "point", mu = 25) %>% 
+  generate(reps = 100, type = "bootstrap") %>% 
+  calculate(stat = "mean")
+```
+
+One numerical variable (median)
+
+```
+mtcars %>%
+  specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
+  hypothesize(null = "point", Med = 26) %>% 
+  generate(reps = 100, type = "bootstrap") %>% 
+  calculate(stat = "median")
+```
 
@@
 
+One numerical (one median)
+
+```
+mtcars %>%
+  specify(response = mpg) %>%
+  generate(reps = 100, type = "bootstrap") %>%
+  calculate(stat = "median")
+```
+
 One categorical (one proportion) (not yet implemented)

### 2017-07-19 profiles_examples.Rmd
Add another dataset to check

---
output:
  github_document:
    toc: true 
    toc_depth: 3
---

Infer: a grammar for statistical inference

Using a sample of profiles from the `okcupiddata` package

---

The objective of this package is to perform statistical inference using a grammar that illustrates the underlying concepts and a format that coheres with the `tidyverse`.

### Hypothesis tests
![h-test diagram](figs/ht-diagram.png)

#### Examples

```{r message=FALSE, warning=FALSE}
library(okcupiddata)
library(tidyverse)
library(stringr)
library(infer)
set.seed(2017)
prof_small <- profiles %>% sample_n(size = 500) %>% 
  mutate(frisco = case_when(
    str_detect(location, "san fran") ~ "san fran",
    !str_detect(location, "san fran") ~ "not san fran"
  )) %>% 
  select(age, sex, frisco, drugs, height, status)
```

- `height` and `age` are numerical variables.
- `sex` has two categories (`"m"`, `"f"`)
- `frisco` has two categories (`"san fran"`, `"not san fran"`)
- `drugs` has three categories (`"never"`, `"sometimes"`, `"often"`) - Also has missing values
- `status` has three categories (`"single"`, `"available"`, `"seeing someone"`)

***

One numerical variable (mean)

```{r}
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
  hypothesize(null = "point", mu = 50) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean") %>% 
  visualize()
```

One numerical variable (median)

```{r}
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
  hypothesize(null = "point", Med = 55) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "median") %>% 
  visualize()
```

One categorical (2 level) variable

```{r}
prof_small %>%
  specify(response = sex) %>% # alt: sex ~ NULL (or sex ~ 1)
  hypothesize(null = "point", p = c("m" = .65)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "prop") %>% 
  visualize()
```

Two categorical (2 level) variables

```{r}
prof_small %>%
  specify(sex ~ frisco) %>% # alt: response = sex, explanatory = vs
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in props") %>% 
  visualize()
```

One categorical (>2 level) - GoF

```{r}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = frisco
  hypothesize(null = "point", p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "Chisq") %>% 
  visualize()
```

Two categorical (>2 level) variables

```{r}
prof_small %>%
  specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "Chisq") %>% 
  visualize()
```

One numerical variable one categorical (2 levels) (diff in means)

```{r}
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means") %>% 
  visualize()
```

One numerical variable one categorical (2 levels) (diff in medians)

```{r}
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians") %>% 
  visualize()
```

One numerical one categorical (>2 levels) -  ANOVA

```{r}
prof_small %>%
  specify(age ~ status) %>% # alt: response = age, explanatory = frisco
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "F") %>% 
  visualize()
```

Two numerical vars - SLR

```{r}
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>% # or "slope = 0"
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "slope") %>% 
  visualize()
```

### Confidence intervals

One numerical (one mean)

```{r}
prof_small %>%
  specify(response = age) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean") %>% 
  visualize()
```

One numerical (one median)

```{r}
prof_small %>%
  specify(response = age) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "median") %>% 
  visualize()
```

One categorical (one proportion) (not yet implemented)

```
prof_small %>%
  specify(response = sex) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "prop")
```

One numerical variable one categorical (2 levels) (diff in means)

```{r}
prof_small %>%
  specify(age ~ sex) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means") %>% 
  visualize()
```

Two categorical variables (diff in proportions) (not yet implemented)

```
prof_small %>%
  specify(sex ~ frisco) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in prop")
```

Two numerical vars - SLR

```{r}
prof_small %>%
  specify(age ~ height) %>% 
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "slope") %>% 
  visualize()
```

### 2017-07-19 profiles_examples.Rmd
Re-export the pipe function for outside use (not just within the package development)

@@
 library(okcupiddata)
-library(tidyverse)
 library(stringr)
@@
 set.seed(2017)
-prof_small <- profiles %>% sample_n(size = 500) %>% 
-  mutate(frisco = case_when(
+prof_small <- profiles %>% dplyr::sample_n(size = 500) %>% 
+  dplyr::mutate(frisco = dplyr::case_when(
     str_detect(location, "san fran") ~ "san fran",
@@
   )) %>% 
-  select(age, sex, frisco, drugs, height, status)
+  dplyr::select(age, sex, frisco, drugs, height, status)
 ```

### 2017-07-19 R/calculate.R

@@ -3,7 +3,7 @@
 #' @param stat a string giving the type of the statistic to calculate. Current options include "mean", "prop", "diff in means", "diff in props", "chisq", and "F".
 #' or an equation in quotes
 #' @param ... currently ignored
-#' @importFrom dplyr %>% group_by summarize
+#' @importFrom dplyr group_by summarize
 #' @importFrom rlang !! sym quo enquo eval_tidy
 #' @export
 #' @examples

### 2017-07-19 README.Rmd
Implement success argument in calculate()

@@
 ---
+[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer)
 
@@
 
-One categorical (one proportion) (not yet implemented)
+One categorical (one proportion)
 
@@
   generate(reps = 100, type = "bootstrap") %>%
-  calculate(stat = "prop")
+  calculate(stat = "prop", success = "1")
 ```

### 2017-07-19 R/calculate.R

@@ -1,7 +1,10 @@
 #' Calculate summary statistics
 #' @param x the output from \code{\link{hypothesize}} or \code{\link{generate}}
-#' @param stat a string giving the type of the statistic to calculate. Current options include "mean", "prop", "diff in means", "diff in props", "chisq", and "F".
-#' or an equation in quotes
+#' @param stat a string giving the type of the statistic to calculate. Current 
+#' options include "mean", "median", "prop", "diff in means", "diff in medians",
+#' "diff in props", "Chisq", "F", and "slope".
+#' @param success a string specifying which level of the response variable should be
+#' used as a success in bootstrapping a one proportion confidence interval
 #' @param ... currently ignored
 #' @importFrom dplyr group_by summarize
 #' @importFrom rlang !! sym quo enquo eval_tidy
@@ -19,7 +22,7 @@
 #'     visualize()
 #' }
 
-calculate <- function(x, stat, ...) {
+calculate <- function(x, stat, success = NULL, ...) {
 
   # TODO: Check to see if dplyr::group_by(replicate) is needed since
   # generate() does a grouping of replicate
@@ -40,7 +43,8 @@ calculate <- function(x, stat, ...) {
 
   if (stat == "prop") {
     col <- attr(x, "response")
-    success <- quo(get_par_levels(x)[1])
+    if(is.null(success))
+      success <- quo(get_par_levels(x)[1])
     df_out <- x %>%
      # dplyr::summarize(stat = mean(!! col == rlang::eval_tidy(success))) # This doesn't appear to be working
       dplyr::group_by(replicate) %>% 

### 2017-07-19 profiles_examples.Rmd
stubbed out print method; #14
Fix spacing
Add one prop bootstrap implementation to profiles example

@@
 set.seed(2017)
-prof_small <- profiles %>% dplyr::sample_n(size = 500) %>% 
+prof_small <- profiles %>% 
+  dplyr::sample_n(size = 500) %>% 
   dplyr::mutate(frisco = dplyr::case_when(
@@
   specify(drugs ~ NULL) %>% # alt: response = frisco
-  hypothesize(null = "point", p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
+  hypothesize(null = "point", 
+              p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
   generate(reps = 1000, type = "simulate") %>%
@@
 
-One categorical (one proportion) (not yet implemented)
+One categorical (one proportion)
 
-```
+```{r}
 prof_small %>%
@@
   generate(reps = 1000, type = "bootstrap") %>%
-  calculate(stat = "prop")
+  calculate(stat = "prop", success = "f") %>% 
+  visualize()
 ```

### 2017-07-19 profiles_examples.Rmd
Diff in props is working (All examples in README working)

@@
 ---
-
-Infer: a grammar for statistical inference
-
-Using a sample of profiles from the `okcupiddata` package
-
----
-
-The objective of this package is to perform statistical inference using a grammar that illustrates the underlying concepts and a format that coheres with the `tidyverse`.
 
@@
 
-Two categorical variables (diff in proportions) (not yet implemented)
+Two categorical variables (diff in proportions)
 
-```
+```{r}
 prof_small %>%
@@
   generate(reps = 1000, type = "bootstrap") %>%
-  calculate(stat = "diff in prop")
+  calculate(stat = "diff in props") %>% 
+  visualize()
 ```

### 2017-07-19 README.Rmd

@@
 
-Two categorical variables (diff in proportions) (not yet implemented)
+Two categorical variables (diff in proportions)
 
@@
   generate(reps = 100, type = "bootstrap") %>%
-  calculate(stat = "diff in prop")
+  calculate(stat = "diff in props")
 ```

### 2017-07-19 README.Rmd
Add timing examples for flights data

@@
   specify(mpg ~ hp) %>% # alt: response = mpg, explanatory = cyl
-  hypothesize(null = "independence") %>% # or "slope = 0"
+  hypothesize(null = "independence") %>%
   generate(reps = 100, type = "permute") %>%

### 2017-07-19 examples/profiles_examples.Rmd
Add timing examples for flights data

--- 2017-07-19 profiles_examples.Rmd
@@
 ### Hypothesis tests
-![h-test diagram](figs/ht-diagram.png)
+![h-test diagram](../figs/ht-diagram.png)
 
@@
   dplyr::sample_n(size = 500) %>% 
-  dplyr::mutate(frisco = dplyr::case_when(
+  dplyr::mutate(city = dplyr::case_when(
     str_detect(location, "san fran") ~ "san fran",
@@
   )) %>% 
-  dplyr::select(age, sex, frisco, drugs, height, status)
+  dplyr::select(age, sex, city, drugs, height, status)
 ```
@@
 - `sex` has two categories (`"m"`, `"f"`)
-- `frisco` has two categories (`"san fran"`, `"not san fran"`)
+- `city` has two categories (`"san fran"`, `"not san fran"`)
 - `drugs` has three categories (`"never"`, `"sometimes"`, `"often"`) - Also has missing values
@@
 prof_small %>%
-  specify(sex ~ frisco) %>% # alt: response = sex, explanatory = vs
+  specify(sex ~ city) %>% # alt: response = sex, explanatory = vs
   hypothesize(null = "independence") %>%
@@
 prof_small %>%
-  specify(drugs ~ NULL) %>% # alt: response = frisco
+  specify(drugs ~ NULL) %>% # alt: response = drugs
   hypothesize(null = "point", 
@@
 prof_small %>%
-  specify(age ~ status) %>% # alt: response = age, explanatory = frisco
+  specify(age ~ status) %>% # alt: response = age, explanatory = status
   hypothesize(null = "independence") %>%
@@
   specify(age ~ height) %>% # alt: response = age, explanatory = height
-  hypothesize(null = "independence") %>% # or "slope = 0"
+  hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
@@
 prof_small %>%
-  specify(sex ~ frisco) %>%
+  specify(sex ~ city) %>%
   generate(reps = 1000, type = "bootstrap") %>%

### 2017-07-19 examples/timing_flights.Rmd
Add timing examples for flights data

---
output:
  github_document
params:
  num_rows: 10000
  rep_times: 1000
---

# Timing analysis

This analysis is for `r params$num_rows` flights with `reps =` ``r params$rep_times``.

```{r}
devtools::session_info()
```

```{r message=FALSE, warning=FALSE}
library(nycflights13)
library(tidyverse)
library(stringr)
library(infer)
set.seed(2017)
fli_small <- flights %>% 
  sample_n(size = params$num_rows) %>% 
  mutate(half_year = case_when(
    between(month, 1, 6) ~ "h1",
    between(month, 7, 12) ~ "h2"
  )) %>% 
  mutate(day_hour = case_when(
    between(hour, 1, 12) ~ "morning",
    between(hour, 13, 24) ~ "not morning"
  )) %>% 
  select(arr_delay, dep_delay, half_year, 
         day_hour, origin, carrier)
```

* Two numeric - `arr_delay`, `dep_delay`
* Two categories 
    - `half_year` (`"h1"`, `"h2"`), 
    - `day_hour` (`"morning"`, `"not morning"`)
* Three categories - `origin` (`"EWR"`, `"JFK"`, `"LGA"`)
* Sixteen categories - `carrier`

***

```{r}
library(rbenchmark)
```

One numerical variable (mean)

```{r}
benchmark(
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", mu = 50) %>% 
  generate(reps = params$rep_times, type = "bootstrap") %>% 
  calculate(stat = "mean"),
replications = 1, columns = "elapsed"
)
```

One numerical variable (median)

```{r}
benchmark(
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", Med = 55) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "median"),
replications = 1, columns = "elapsed"
)
```

One categorical (2 level) variable

```{r}
benchmark(
fli_small %>%
  specify(response = half_year) %>% # alt: half_year ~ NULL (or half_year ~ 1)
  hypothesize(null = "point", p = c("h1" = .45)) %>% 
  generate(reps = params$rep_times, type = "simulate") %>% 
  calculate(stat = "prop"),
replications = 1, columns = "elapsed"
)
```

Two categorical (2 level) variables

```{r}
benchmark(
fli_small %>%
  specify(half_year ~ day_hour) %>% # alt: response = half_year, explanatory = vs
  hypothesize(null = "independence") %>%
  generate(reps = params$rep_times, type = "permute") %>%
  calculate(stat = "diff in props"),
replications = 1, columns = "elapsed"
)
```

One categorical (>2 level) - GoF

```{r}
benchmark(
fli_small %>%
  specify(origin ~ NULL) %>% # alt: response = day_hour
  hypothesize(null = "point", 
              p = c("EWR" = .3, "JFK" = .4, "LGA" = .3)) %>%
  generate(reps = params$rep_times, type = "simulate") %>%
  calculate(stat = "Chisq"),
replications = 1, columns = "elapsed"
)
```

Two categorical (>2 level) variables

```{r}
benchmark(
fli_small %>%
  specify(origin ~ carrier) %>% # alt: response = origin, explanatory = carrier
  hypothesize(null = "independence") %>%
  generate(reps = params$rep_times, type = "permute") %>%
  calculate(stat = "Chisq"),
replications = 1, columns = "elapsed"
)
```

One numerical variable one categorical (2 levels) (diff in means)

```{r}
benchmark(
fli_small %>%
  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
  hypothesize(null = "independence") %>%
  generate(reps = params$rep_times, type = "permute") %>%
  calculate(stat = "diff in means"),
replications = 1, columns = "elapsed"
)
```

One numerical variable one categorical (2 levels) (diff in medians)

```{r}
benchmark(
fli_small %>%
  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
  hypothesize(null = "independence") %>%
  generate(reps = params$rep_times, type = "permute") %>%
  calculate(stat = "diff in medians"),
replications = 1, columns = "elapsed"
)
```

One numerical one categorical (>2 levels) -  ANOVA

```{r}
benchmark(
fli_small %>%
  specify(arr_delay ~ origin) %>% # alt: response = arr_delay, explanatory = day_hour
  hypothesize(null = "independence") %>%
  generate(reps = params$rep_times, type = "permute") %>%
  calculate(stat = "F"),
replications = 1, columns = "elapsed"
)
```

Two numerical vars - SLR

```{r}
benchmark(
fli_small %>%
  specify(arr_delay ~ dep_delay) %>% # alt: response = arr_delay, explanatory = dep_delay
  hypothesize(null = "independence") %>%
  generate(reps = params$rep_times, type = "permute") %>%
  calculate(stat = "slope"),
replications = 1, columns = "elapsed"
)
```

### Confidence intervals

One numerical (one mean)

```{r}
benchmark(
fli_small %>%
  specify(response = arr_delay) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "mean"),
replications = 1, columns = "elapsed"
)
```

One numerical (one median)

```{r}
benchmark(
fli_small %>%
  specify(response = arr_delay) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "median"),
replications = 1, columns = "elapsed"
)
```

One categorical (one proportion)

```{r}
benchmark(
fli_small %>%
  specify(response = half_year) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "prop", success = "f"),
replications = 1, columns = "elapsed"
)
```

One numerical variable one categorical (2 levels) (diff in means)

```{r}
benchmark(
fli_small %>%
  specify(arr_delay ~ half_year) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "diff in means"),
replications = 1, columns = "elapsed"
)
```

Two categorical variables (diff in proportions)

```{r}
benchmark(
fli_small %>%
  specify(half_year ~ day_hour) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "diff in props"),
replications = 1, columns = "elapsed"
)
```

Two numerical vars - SLR

```{r}
benchmark(
fli_small %>%
  specify(arr_delay ~ dep_delay) %>% 
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "slope"),
replications = 1, columns = "elapsed"
)

```

### 2017-07-19 examples/timing_flights_5k.Rmd
Add timing examples for flights data

--- 2017-07-19 examples/timing_flights.Rmd
@@
 output:
-  github_document
+  github_document:
+    toc: true 
+    toc_depth: 3
 params:
-  num_rows: 10000
-  rep_times: 1000
+  num_rows: 5000
+  rep_times: 5000
 ---
@@
 
-This analysis is for `r params$num_rows` flights with `reps =` ``r params$rep_times``.
+This analysis is for `r params$num_rows` flights with `reps =```r params$rep_times``.
 

### 2017-07-19 examples/timing_flights_5k.Rmd
Remove missing values

--- 2017-07-19 examples/timing_flights.Rmd
@@
 ---
-output:
-  github_document
+output: github_document
 params:
-  num_rows: 10000
-  rep_times: 1000
+  num_rows: 5000
+  rep_times: 5000
 ---
@@
 fli_small <- flights %>% 
+  na.omit() %>% 
   sample_n(size = params$num_rows) %>% 

### 2017-07-20 examples/flights_examples.Rmd
Add example with missing numeric data

---
output: github_document
params:
  num_rows: 200
  rep_times: 5000
---

```{r message=FALSE, warning=FALSE}
library(nycflights13)
library(tidyverse)
library(stringr)
library(infer)
set.seed(2017)
fli_small <- flights %>% 
  sample_n(size = params$num_rows) %>% 
  mutate(half_year = case_when(
    between(month, 1, 6) ~ "h1",
    between(month, 7, 12) ~ "h2"
  )) %>% 
  mutate(day_hour = case_when(
    between(hour, 1, 12) ~ "morning",
    between(hour, 13, 24) ~ "not morning"
  )) %>% 
  select(arr_delay, dep_delay, half_year, 
         day_hour, origin, carrier)
```

* Two numeric - `arr_delay`, `dep_delay`
* Two categories 
    - `half_year` (`"h1"`, `"h2"`), 
    - `day_hour` (`"morning"`, `"not morning"`)
* Three categories - `origin` (`"EWR"`, `"JFK"`, `"LGA"`)
* Sixteen categories - `carrier`

***

One numerical variable (mean)

```{r}
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", mu = 50) %>% 
  generate(reps = params$rep_times, type = "bootstrap") %>% 
  calculate(stat = "mean", na.rm = TRUE)
```

One numerical variable (median)

```{r}
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", Med = 55) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "median", na.rm = TRUE)
```

One numerical variable (standard deviation)

*Without removing NA*

```{r}
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", sd = 40) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "sd")
```

*Removing NA*

```{r}
fli_small %>%
  specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
  hypothesize(null = "point", sd = 40) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "sd", na.rm = TRUE)
```

One categorical (2 level) variable

```{r}
fli_small %>%
  specify(response = half_year) %>% # alt: half_year ~ NULL (or half_year ~ 1)
  hypothesize(null = "point", p = c("h1" = .45, "h2" = 0.55)) %>% 
  generate(reps = params$rep_times, type = "simulate") %>% 
  calculate(stat = "prop")
```

Two categorical (2 level) variables

```{r}
fli_small %>%
  specify(half_year ~ day_hour) %>% # alt: response = half_year, explanatory = vs
  hypothesize(null = "independence") %>%
  generate(reps = params$rep_times, type = "permute") %>%
  calculate(stat = "diff in props")
```

One categorical (>2 level) - GoF

```{r}
fli_small %>%
  specify(origin ~ NULL) %>% # alt: response = day_hour
  hypothesize(null = "point", 
              p = c("EWR" = .3, "JFK" = .4, "LGA" = .3)) %>%
  generate(reps = params$rep_times, type = "simulate") %>%
  calculate(stat = "Chisq")
```

Two categorical (>2 level) variables

```{r}
fli_small %>%
  specify(origin ~ carrier) %>% # alt: response = origin, explanatory = carrier
  hypothesize(null = "independence") %>%
  generate(reps = params$rep_times, type = "permute") %>%
  calculate(stat = "Chisq")
```

One numerical variable one categorical (2 levels) (diff in means)

*With NAs*

```{r}
fli_small %>%
  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
  hypothesize(null = "independence") %>%
  generate(reps = params$rep_times, type = "permute") %>%
  calculate(stat = "diff in means")
```

*Without NAs*

```{r}
fli_small %>%
  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
  hypothesize(null = "independence") %>%
  generate(reps = params$rep_times, type = "permute") %>%
  calculate(stat = "diff in means", na.rm = TRUE)
```

One numerical variable one categorical (2 levels) (diff in medians)

```{r}
fli_small %>%
  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
  hypothesize(null = "independence") %>%
  generate(reps = params$rep_times, type = "permute") %>%
  calculate(stat = "diff in medians", na.rm = TRUE)
```

One numerical one categorical (>2 levels) -  ANOVA

```{r}
fli_small %>%
  specify(arr_delay ~ origin) %>% # alt: response = arr_delay, explanatory = day_hour
  hypothesize(null = "independence") %>%
  generate(reps = params$rep_times, type = "permute") %>%
  calculate(stat = "F")
```

Two numerical vars - SLR

```{r}
fli_small %>%
  specify(arr_delay ~ dep_delay) %>% # alt: response = arr_delay, explanatory = dep_delay
  hypothesize(null = "independence") %>%
  generate(reps = params$rep_times, type = "permute") %>%
  calculate(stat = "slope")
```

### Confidence intervals

One numerical (one mean)

```{r}
fli_small %>%
  specify(response = arr_delay) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "mean", na.rm = TRUE)
```

One numerical (one median)

```{r}
fli_small %>%
  specify(response = arr_delay) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "median", na.rm = TRUE)
```

One categorical (one proportion)

```{r}
fli_small %>%
  specify(response = half_year) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "prop", success = "h2")
```

One numerical variable one categorical (2 levels) (diff in means)

```{r}
fli_small %>%
  specify(arr_delay ~ half_year) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "diff in means", na.rm = TRUE)
```

Two categorical variables (diff in proportions)

```{r}
fli_small %>%
  specify(half_year ~ day_hour) %>%
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "diff in props")
```

Two numerical vars - SLR

```{r}
fli_small %>%
  specify(arr_delay ~ dep_delay) %>% 
  generate(reps = params$rep_times, type = "bootstrap") %>%
  calculate(stat = "slope")
```

### 2017-07-20 README.Rmd

@@
   calculate(stat = "median")
+```
+
+One numerical variable (standard deviation)
+
+```
+mtcars %>%
+  specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
+  hypothesize(null = "point", sigma = 5) %>% 
+  generate(reps = 100, type = "bootstrap") %>% 
+  calculate(stat = "sd")
 ```
@@
 
+One numerical (standard deviation)
+
+```
+mtcars %>%
+  specify(response = mpg) %>%
+  generate(reps = 100, type = "bootstrap") %>%
+  calculate(stat = "sd")
+```
+
 One categorical (one proportion)

### 2017-07-20 examples/timing_flights.Rmd

@@
 ---
-output:
-  github_document
+output: github_document
 params:

### 2017-07-20 examples/timing_flights.Rmd
Fix typos

@@
 fli_small %>%
-  specify(origin ~ NULL) %>% # alt: response = day_hour
+  specify(origin ~ NULL) %>% # alt: response = origin
   hypothesize(null = "point", 
@@
   generate(reps = params$rep_times, type = "bootstrap") %>%
-  calculate(stat = "prop", success = "f"),
+  calculate(stat = "prop", success = "h2"),
 replications = 1, columns = "elapsed"

### 2017-07-20 examples/flights_examples.Rmd
Fix typos
Change from Med to med and sd to sigma

@@
 ---
+
+These examples use `r params$num_rows` flights from `nycflights13::flights` and `r params$rep_times` replicates.
 
@@
   specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
-  hypothesize(null = "point", Med = 55) %>%
+  hypothesize(null = "point", med = 55) %>%
   generate(reps = params$rep_times, type = "bootstrap") %>%
@@
   specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
-  hypothesize(null = "point", sd = 40) %>%
+  hypothesize(null = "point", sigma = 40) %>%
   generate(reps = params$rep_times, type = "bootstrap") %>%

### 2017-07-21 README.Rmd

@@
   specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
-  hypothesize(null = "point", Med = 26) %>% 
+  hypothesize(null = "point", med = 26) %>% 
   generate(reps = 100, type = "bootstrap") %>% 

### 2017-07-21 examples/flights_examples.Rmd

@@
   specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
-  hypothesize(null = "point", mu = 50) %>% 
+  hypothesize(null = "point", mu = 0) %>% 
   generate(reps = params$rep_times, type = "bootstrap") %>% 
@@
   specify(response = arr_delay) %>% # alt: arr_delay ~ NULL (or arr_delay ~ 1)
-  hypothesize(null = "point", med = 55) %>%
+  hypothesize(null = "point", med = 0) %>%
   generate(reps = params$rep_times, type = "bootstrap") %>%

### 2017-07-21 examples/profiles_examples.Rmd

@@
   specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
-  hypothesize(null = "point", Med = 55) %>% 
+  hypothesize(null = "point", med = 55) %>% 
   generate(reps = 1000, type = "bootstrap") %>% 

### 2017-08-03 README.Rmd
small commit for testing
update package description

@@
 
-Infer: a grammar for statistical inference
+Infer: An R package for tidyverse-friendly statistical inference
 
@@
 
-The objective of this package is to perform statistical inference using a grammar that illustrates the underlying concepts and a format that coheres with the `tidyverse`.
+The objective of this package is to perform inference using an expressive statistical grammar that coheres with the `tidyverse` design framework.
 
@@
 These examples assume that `mtcars` has been overwritten so that the variables
-`cyl`, `vs`, `am`, `gear`, and `carb` are `factor`s:
+`cyl`, `vs`, `am`, `gear`, and `carb` are `factor`s.
 

### 2017-10-09 vignettes/profiles_examples.R
Add profiles vignette

@@ -1,0 +1,139 @@
+## ----include=FALSE-------------------------------------------------------
+knitr::opts_chunk$set(comment = NA, fig.width = 8, fig.height = 6, out.width="400px") 
+
+## ----message=FALSE, warning=FALSE----------------------------------------
+library(okcupiddata)
+library(stringr)
+library(infer)
+set.seed(2017)
+prof_small <- profiles %>% 
+  dplyr::sample_n(size = 500) %>% 
+  dplyr::mutate(city = dplyr::case_when(
+    str_detect(location, "san fran") ~ "san fran",
+    !str_detect(location, "san fran") ~ "not san fran"
+  )) %>% 
+  dplyr::select(age, sex, city, drugs, height, status)
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
+  hypothesize(null = "point", mu = 50) %>% 
+  generate(reps = 1000, type = "bootstrap") %>% 
+  calculate(stat = "mean") %>% 
+  visualize()
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
+  hypothesize(null = "point", med = 55) %>% 
+  generate(reps = 1000, type = "bootstrap") %>% 
+  calculate(stat = "median") %>% 
+  visualize()
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(response = sex) %>% # alt: sex ~ NULL (or sex ~ 1)
+  hypothesize(null = "point", p = c("m" = .65)) %>% 
+  generate(reps = 1000, type = "simulate") %>% 
+  calculate(stat = "prop") %>% 
+  visualize()
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(sex ~ city) %>% # alt: response = sex, explanatory = vs
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000, type = "permute") %>%
+  calculate(stat = "diff in props") %>% 
+  visualize()
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(drugs ~ NULL) %>% # alt: response = drugs
+  hypothesize(null = "point", 
+              p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
+  generate(reps = 1000, type = "simulate") %>%
+  calculate(stat = "Chisq") %>% 
+  visualize()
+
[…]

### 2017-10-09 vignettes/profiles_examples_both_methods.R
Lay out what needs to be done with t, z, and theory-based methods on second vignette

@@ -1,0 +1,116 @@
+## ----include=FALSE-------------------------------------------------------
+knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
+
+## ----message=FALSE, warning=FALSE----------------------------------------
+library(okcupiddata)
+library(stringr)
+library(infer)
+set.seed(2017)
+prof_small <- profiles %>% 
+  dplyr::sample_n(size = 500) %>% 
+  dplyr::mutate(city = dplyr::case_when(
+    str_detect(location, "san fran") ~ "san fran",
+    !str_detect(location, "san fran") ~ "not san fran"
+  )) %>% 
+  dplyr::select(age, sex, city, drugs, height, status)
+
+## ----eval=FALSE, include=FALSE-------------------------------------------
+#  prof_small %>%
+#    specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
+#    hypothesize(null = "point", mu = 50) %>%
+#    generate(reps = 1000, type = "bootstrap") %>%
+#    calculate(stat = "t") %>%
+#    visualize()
+
+## ----eval=FALSE, include=FALSE-------------------------------------------
+#  prof_small %>%
+#    specify(response = sex) %>% # alt: sex ~ NULL (or sex ~ 1)
+#    hypothesize(null = "point", p = c("m" = .65)) %>%
+#    generate(reps = 1000, type = "simulate") %>%
+#    calculate(stat = "z") %>%
+#    visualize()
+
+## ----eval=FALSE, include=FALSE-------------------------------------------
+#  prof_small %>%
+#    specify(sex ~ city) %>% # alt: response = sex, explanatory = vs
+#    hypothesize(null = "independence") %>%
+#    generate(reps = 1000, type = "permute") %>%
+#    calculate(stat = "diff in props") %>%
+#    visualize()
+
+## ----eval=FALSE, include=FALSE-------------------------------------------
+#  prof_small %>%
+#    specify(drugs ~ NULL) %>% # alt: response = drugs
+#    hypothesize(null = "point",
+#                p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
+#    generate(reps = 1000, type = "simulate") %>%
+#    calculate(stat = "Chisq") %>%
+#    visualize()
+
+## ----eval=FALSE, include=FALSE-------------------------------------------
+#  prof_small %>%
+#    specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
+#    hypothesize(null = "independence") %>%
[…]

### 2017-10-10 docs/articles/profiles_examples.Rmd
Update pkgdown documentation

--- 2017-07-21 examples/profiles_examples.Rmd
@@
 ---
+title: "Randomization Examples using `okcupiddata` `profiles` data"
+author: "Chester Ismay"
+date: "`r Sys.Date()`"
 output: 
-  github_document:
-    toc: true 
-    toc_depth: 3
+  rmarkdown::html_vignette:
+    df_print: kable
+vignette: |
+  %\VignetteIndexEntry{OKCupid profiles example}
+  %\VignetteEngine{knitr::rmarkdown}
+  %\VignetteEncoding{UTF-8}
 ---
 
-### Hypothesis tests
-![h-test diagram](../figs/ht-diagram.png)
+```{r include=FALSE}
+knitr::opts_chunk$set(fig.width = 8, fig.height = 5, cache = TRUE) 
+```
 
-#### Examples
+## Data preparation
 
@@
 ***
+
+## Hypothesis tests
 
@@
 
-### Confidence intervals
+## Confidence intervals
 

### 2017-10-10 docs/articles/profiles_examples_both_methods.R

@@ -1,5 +1,5 @@
 ## ----include=FALSE-------------------------------------------------------
-knitr::opts_chunk$set(fig.width = 8, fig.height = 6) 
+knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
 
 ## ----message=FALSE, warning=FALSE----------------------------------------
 library(okcupiddata)
@@ -14,47 +14,6 @@ prof_small <- profiles %>%
   )) %>% 
   dplyr::select(age, sex, city, drugs, height, status)
 
-## ----eval=FALSE----------------------------------------------------------
-#  prof_small %>%
-#    specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
-#    hypothesize(null = "point", mu = 50) %>%
-#    generate(reps = 1000, type = "bootstrap") %>%
-#    calculate(stat = "t") %>%
-#    visualize()
-
-## ----eval=FALSE----------------------------------------------------------
-#  prof_small %>%
-#    specify(response = sex) %>% # alt: sex ~ NULL (or sex ~ 1)
-#    hypothesize(null = "point", p = c("m" = .65)) %>%
-#    generate(reps = 1000, type = "simulate") %>%
-#    calculate(stat = "z") %>%
-#    visualize()
-
-## ----eval=FALSE----------------------------------------------------------
-#  prof_small %>%
-#    specify(sex ~ city) %>% # alt: response = sex, explanatory = vs
-#    hypothesize(null = "independence") %>%
-#    generate(reps = 1000, type = "permute") %>%
-#    calculate(stat = "diff in props") %>%
-#    visualize()
-
-## ----eval=FALSE----------------------------------------------------------
-#  prof_small %>%
-#    specify(drugs ~ NULL) %>% # alt: response = drugs
-#    hypothesize(null = "point",
-#                p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
-#    generate(reps = 1000, type = "simulate") %>%
-#    calculate(stat = "Chisq") %>%
-#    visualize()
-
-## ----eval=FALSE----------------------------------------------------------
-#  prof_small %>%
-#    specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
-#    hypothesize(null = "independence") %>%
-#    generate(reps = 1000, type = "permute") %>%
-#    calculate(stat = "Chisq") %>%
-#    visualize()
-
 ## ------------------------------------------------------------------------
 prof_small %>%
[…]

### 2017-10-15 README.Rmd
Add profiles vignette
Update pkgdown site

@@
 
-Infer: An R package for tidyverse-friendly statistical inference
+Infer: an R package for tidyverse-friendly statistical inference
 
@@
 
-### Hypothesis tests
-![h-test diagram](figs/ht-diagram.png)
+## Hypothesis tests
+![](figs/ht-diagram.png)
 
@@
 
-One numerical variable (mean)
+### One numerical variable (mean)
 
@@
 
-One numerical variable (median)
+### One numerical variable (median)
 
@@
 
-One numerical variable (standard deviation)
+### One numerical variable (standard deviation)
 
@@
 
-One categorical (2 level) variable
+### One categorical (2 level) variable
 
@@
 
-Two categorical (2 level) variables
+### Two categorical (2 level) variables
 
@@
 
-One categorical (>2 level) - GoF
+### One categorical (>2 level) - GoF
 
@@
 
-Two categorical (>2 level) variables
+### Two categorical (>2 level) variables
 
@@
 
-One numerical variable one categorical (2 levels) (diff in means)
+### One numerical variable, one categorical (2 levels) (diff in means)
 
@@
 
-One numerical variable one categorical (2 levels) (diff in medians)
+### One numerical variable one categorical (2 levels) (diff in medians)
 
@@
 
-One numerical one categorical (>2 levels) -  ANOVA
+### One numerical one categorical (>2 levels) -  ANOVA
 
@@
 
-Two numerical vars - SLR
+### Two numerical vars - SLR
 
@@
 
-### Confidence intervals
+## Confidence intervals
 
-One numerical (one mean)
+### One numerical (one mean)
 
@@
 
-One numerical (one median)
+### One numerical (one median)
 
@@
 
-One numerical (standard deviation)
+### One numerical (standard deviation)
 
@@
 
-One categorical (one proportion)
+### One categorical (one proportion)
 
@@
 
-One numerical variable one categorical (2 levels) (diff in means)
+### One numerical variable one categorical (2 levels) (diff in means)
 
@@
 
-Two categorical variables (diff in proportions)
+### Two categorical variables (diff in proportions)
 

### 2017-10-16 docs/articles/profiles_examples_both_methods.R
Update pkgdown

@@ -15,19 +15,29 @@ prof_small <- profiles %>%
   dplyr::select(age, sex, city, drugs, height, status)
 
 ## ------------------------------------------------------------------------
+obs_t <- prof_small %>% 
+  t_test(formula = age ~ sex) %>% 
+  dplyr::select(statistic) %>% 
+  dplyr::pull()
+
+## ------------------------------------------------------------------------
+obs_t <- prof_small %>% 
+  t_stat(formula = age ~ sex)
+
+## ------------------------------------------------------------------------
 prof_small %>%
   specify(age ~ sex) %>% # alt: response = age, explanatory = sex
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "t") %>% 
-  visualize()
+  visualize(obs_stat = obs_t, direction = "two_sided")
 
 ## ------------------------------------------------------------------------
 prof_small %>%
   specify(age ~ sex) %>% # alt: response = age, explanatory = sex
   hypothesize(null = "independence") %>%
   # calculate(stat = "t") ## Not needed since t is implied based on variable types
-  visualize(method = "theoretical")
+  visualize(method = "theoretical", obs_stat = obs_t, direction = "two_sided")
 
 ## ------------------------------------------------------------------------
 prof_small %>%
@@ -35,7 +45,7 @@ prof_small %>%
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "t") %>% 
-  visualize(method = "both")
+  visualize(method = "both", obs_stat = obs_t, direction = "two_sided")
 
 ## ------------------------------------------------------------------------
 prof_small %>%

### 2017-10-16 docs/articles/two_sample_t.R

@@ -1,0 +1,53 @@
+## ----include=FALSE-------------------------------------------------------
+knitr::opts_chunk$set(fig.width = 7, fig.height = 3) 
+
+## ----message=FALSE, warning=FALSE----------------------------------------
+library(okcupiddata)
+library(stringr)
+library(infer)
+set.seed(2017)
+prof_small <- profiles %>% 
+  dplyr::sample_n(size = 500) %>% 
+  dplyr::mutate(city = dplyr::case_when(
+    str_detect(location, "san fran") ~ "san fran",
+    !str_detect(location, "san fran") ~ "not san fran"
+  )) %>% 
+  dplyr::select(age, sex, city, drugs, height, status)
+
+## ------------------------------------------------------------------------
+obs_t <- prof_small %>% 
+  t_test(formula = age ~ sex) %>% 
+  dplyr::select(statistic) %>% 
+  dplyr::pull()
+
+## ------------------------------------------------------------------------
+obs_t <- prof_small %>% 
+  t_stat(formula = age ~ sex)
+
+## ------------------------------------------------------------------------
+t_null_distn <- prof_small %>%
+  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000, type = "permute") %>%
+  calculate(stat = "t")
+t_null_distn %>% visualize(obs_stat = obs_t, direction = "two_sided")
+
+## ------------------------------------------------------------------------
+t_null_distn %>% 
+  dplyr::summarize(p_value = mean(abs(stat) >= obs_t))
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
+  hypothesize(null = "independence") %>%
+  # calculate(stat = "t") ## Not needed since t is implied based on variable types
+  visualize(method = "theoretical", obs_stat = obs_t, direction = "two_sided")
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000, type = "permute") %>%
+  calculate(stat = "t") %>% 
+  visualize(method = "both")
+

### 2017-10-16 docs/articles/profiles_examples_both_methods.R
Update pkgdown

@@ -15,29 +15,19 @@ prof_small <- profiles %>%
   dplyr::select(age, sex, city, drugs, height, status)
 
 ## ------------------------------------------------------------------------
-obs_t <- prof_small %>% 
-  t_test(formula = age ~ sex) %>% 
-  dplyr::select(statistic) %>% 
-  dplyr::pull()
-
-## ------------------------------------------------------------------------
-obs_t <- prof_small %>% 
-  t_stat(formula = age ~ sex)
-
-## ------------------------------------------------------------------------
 prof_small %>%
   specify(age ~ sex) %>% # alt: response = age, explanatory = sex
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "t") %>% 
-  visualize(obs_stat = obs_t, direction = "two_sided")
+  visualize()
 
 ## ------------------------------------------------------------------------
 prof_small %>%
   specify(age ~ sex) %>% # alt: response = age, explanatory = sex
   hypothesize(null = "independence") %>%
   # calculate(stat = "t") ## Not needed since t is implied based on variable types
-  visualize(method = "theoretical", obs_stat = obs_t, direction = "two_sided")
+  visualize(method = "theoretical")
 
 ## ------------------------------------------------------------------------
 prof_small %>%
@@ -45,7 +35,7 @@ prof_small %>%
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "t") %>% 
-  visualize(method = "both", obs_stat = obs_t, direction = "two_sided")
+  visualize(method = "both")
 
 ## ------------------------------------------------------------------------
 prof_small %>%
@@ -69,20 +59,27 @@ prof_small %>%
   calculate(stat = "F") %>% 
   visualize(method = "both")
 
-## ----eval=FALSE, include=FALSE-------------------------------------------
-#  prof_small %>%
-#    specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
-#    hypothesize(null = "point", mu = 50) %>%
-#    generate(reps = 1000, type = "bootstrap") %>%
-#    calculate(stat = "t")
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(response = sex) %>% # alt: sex ~ NULL (or sex ~ 1)
[…]

### 2017-10-22 R/calculate.R
Add two sample props z example

@@ -2,7 +2,8 @@
 #' @param x the output from \code{\link{hypothesize}} or \code{\link{generate}}
 #' @param stat a string giving the type of the statistic to calculate. Current 
 #' options include "mean", "median", "sd", "prop", "diff in means", 
-#' "diff in medians", "diff in props", "Chisq", "F", and "slope".
+#' "diff in medians", "diff in props", "Chisq", "F", and "slope". (Testing implementations
+#' of "z" and "t".)
 #' @param success a string specifying which level of the response variable should be
 #' used as a success in bootstrapping a one proportion confidence interval
 #' @param ... to pass options like \code{na.rm = TRUE} into functions like mean, sd, etc.
@@ -62,7 +63,7 @@ calculate <- function(x, stat, success = NULL, ...) {
       success <- quo(get_par_levels(x)[1])
     df_out <- x %>%
       # dplyr::summarize(stat = mean(!! col == rlang::eval_tidy(success))) # This doesn't appear to be working
-    # dplyr::group_by(replicate) %>% 
+      # dplyr::group_by(replicate) %>% 
       # The following works but not sure why when looking at the diff in means code?
       dplyr::summarize(stat = mean(rlang::eval_tidy(col) == rlang::eval_tidy(success), ...))
   }
@@ -140,7 +141,20 @@ calculate <- function(x, stat, success = NULL, ...) {
   if (stat == "z"){
     # Two sample proportions
     if (attr(x, "theory_type") == "Two sample props z"){
-      #      df_out <- x %>%
+      
+      df_out <- x %>%
+        dplyr::group_by(replicate, !!attr(x, "explanatory")) %>%
+        dplyr::summarize(prop = mean((!!attr(x, "response")) == levels(!!attr(x, "response"))[1], ...),
+                         num_suc = sum((!!attr(x, "response")) == levels(!!attr(x, "response"))[1], ...),
+                         group_num = n()) %>% 
+        dplyr::summarize(diff_prop = diff(prop),
+                         total_suc = sum(num_suc),
+                         n1 = group_num[1],
+                         n2 = group_num[2],
+                         p_hat = total_suc / (n1 + n2),
+                         denom = sqrt(p_hat * (1 - p_hat) / n1 + p_hat * (1 - p_hat) / n2),
+                         stat = diff_prop / denom) %>% 
+        dplyr::select(-total_suc, -n1, -n2)
       
     } else 
[…]

### 2017-10-22 R/infer.R

@@ -16,4 +16,6 @@ NULL
 if(getRversion() >= "2.15.1")  
   utils::globalVariables(c("prop", "stat", "xbar", "xtilde", "x", "..density..",
                            "statistic", ".", "parameter", "p.value",
-                           "xmin", "xmax", "density"))
+                           "xmin", "xmax", "density", "denom",
+                           "diff_prop", "group_num", "n1", "n2",
+                           "num_suc", "p_hat", "total_suc"))

### 2017-10-22 examples/flights_examples.Rmd
Update pkgdown

@@
 library(nycflights13)
-library(tidyverse)
+library(dplyr)
 library(stringr)

### 2017-11-08 README.Rmd
Update pkgdown
Add installation instructions

@@
 
+# Installation
+
+To install the current stable version of `infer`, make sure to install `devtools` first:
+
+```
+install.packages("devtools")
+devtools::install_github("andrewbpray/infer")
+```
+
+To install the development version of `infer` (with `devtools` installed already):
+
+```
+devtools::install_github("ismayc/infer", ref = "dev")
+```
+
 ## Hypothesis tests
@@
 
-#### Examples
+#### Randomization-based Examples
 
@@
 ```
+
+Check the package vignettes for further examples using theory-based methods
+in combination with randomization-based methods.
 

### 2017-11-08 README.Rmd
Update pkgdown

@@
 install.packages("devtools")
-devtools::install_github("andrewbpray/infer")
+devtools::install_github("andrewpbray/infer")
 ```
@@
 ## Hypothesis tests
-![](figs/ht-diagram.png)
+![](https://github.com/andrewpbray/infer/blob/master/figs/ht-diagram.png)
 
@@
 Check the package vignettes for further examples using theory-based methods
-in combination with randomization-based methods.
+in combination with randomization-based methods. The examples below only show the calculation of randomization-based statistics. Check the vignettes for ways to `visualize()` these statistics.
 

### 2017-11-08 README.Rmd
Improve documentation and fix image link

--- 2017-11-08 README.Rmd
@@
 ## Hypothesis tests
-![](figs/ht-diagram.png)
+
+General framework diagram for hypothesis tests in `infer` is [here](https://github.com/andrewpbray/infer/raw/master/figs/ht-diagram.png).
 
@@
 
-These examples assume that `mtcars` has been overwritten so that the variables
+The examples below only show the calculation of randomization-based statistics and assume that `mtcars` has been overwritten so that the variables
 `cyl`, `vs`, `am`, `gear`, and `carb` are `factor`s.

### 2017-12-27 examples/two_sample_t.Rmd

---
title: "Two sample $t$ test example using `okcupiddata` `profiles` data"
author: "Chester Ismay"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    df_print: kable
vignette: |
  %\VignetteIndexEntry{Two sample t test example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 3) 
```

## Data preparation

```{r message=FALSE, warning=FALSE}
library(okcupiddata)
library(stringr)
library(infer)
set.seed(2017)
prof_small <- profiles %>% 
  dplyr::sample_n(size = 500) %>% 
  dplyr::mutate(city = dplyr::case_when(
    str_detect(location, "san fran") ~ "san fran",
    !str_detect(location, "san fran") ~ "not san fran"
  )) %>% 
  dplyr::select(age, sex, city, drugs, height, status)
```

- `height` and `age` are numerical variables.
- `sex` has two categories (`"m"`, `"f"`)
- `city` has two categories (`"san fran"`, `"not san fran"`)
- `drugs` has three categories (`"never"`, `"sometimes"`, `"often"`) - Also has missing values
- `status` has three categories (`"single"`, `"available"`, `"seeing someone"`)

***

# One numerical variable, one categorical (2 levels)

## Calculate observed statistic

Using `t_test` in `infer`

```{r}
obs_t <- prof_small %>% 
  t_test(formula = age ~ sex) %>% 
  dplyr::select(statistic) %>% 
  dplyr::pull()
```

The observed $t$ statistic is `r obs_t`.

Or using another shortcut function in `infer`:

```{r}
obs_t <- prof_small %>% 
  t_stat(formula = age ~ sex)
```

The observed $t$ statistic is `r obs_t`.

## Randomization approach to t-statistic

```{r}
t_null_distn <- prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t")
t_null_distn %>% visualize(obs_stat = obs_t, direction = "two_sided")
```

## Calculate the randomization-based $p$-value

```{r}
t_null_distn %>% 
  dplyr::summarize(p_value = mean(abs(stat) >= obs_t)) %>% 
  dplyr::pull()
```

## Theoretical distribution

```{r }
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  # calculate(stat = "t") ## Not needed since t is implied based on variable types
  visualize(method = "theoretical", obs_stat = obs_t, direction = "two_sided")
```

## Overlay appropriate $t$ distribution on top of permuted t-statistics

```{r }
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t") %>% 
  visualize(method = "both", obs_stat = obs_t, direction = "two_sided")
```

## Compute theoretical p-value

```{r}
prof_small %>% 
  t_test(formula = age ~ sex) %>% 
  dplyr::select(p_value) %>% 
  dplyr::pull()
```

### 2017-12-27 inst/doc/flights_examples.Rmd
initial commit

--- 2017-07-21 examples/profiles_examples.Rmd
@@
 ---
+title: "Randomization Examples using `nycflights13` `flights` data"
+author: "Chester Ismay and Andrew bray"
+date: "`r Sys.Date()`"
 output: 
-  github_document:
-    toc: true 
-    toc_depth: 3
+  rmarkdown::html_vignette:
+    df_print: kable
+vignette: |
+  %\VignetteIndexEntry{flights example}
+  %\VignetteEngine{knitr::rmarkdown}
+  %\VignetteEncoding{UTF-8}
 ---
 
-### Hypothesis tests
-![h-test diagram](../figs/ht-diagram.png)
+```{r include=FALSE}
+knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
+```
 
-#### Examples
+## Data preparation
 
 ```{r message=FALSE, warning=FALSE}
-library(okcupiddata)
+library(nycflights13)
+library(dplyr)
+library(ggplot2)
 library(stringr)
@@
 set.seed(2017)
-prof_small <- profiles %>% 
-  dplyr::sample_n(size = 500) %>% 
-  dplyr::mutate(city = dplyr::case_when(
-    str_detect(location, "san fran") ~ "san fran",
-    !str_detect(location, "san fran") ~ "not san fran"
+fli_small <- flights %>% 
+  sample_n(size = 500) %>% 
+  mutate(season = case_when(
+    month %in% c(10:12, 1:3) ~ "winter",
+    month %in% c(4:9) ~ "summer"
   )) %>% 
-  dplyr::select(age, sex, city, drugs, height, status)
+  mutate(day_hour = case_when(
+    between(hour, 1, 12) ~ "morning",
+    between(hour, 13, 24) ~ "not morning"
+  )) %>% 
+  select(arr_delay, dep_delay, season, 
+         day_hour, origin, carrier) %>%
+  filter(., complete.cases(.))
 ```
 
-- `height` and `age` are numerical variables.
-- `sex` has two categories (`"m"`, `"f"`)
-- `city` has two categories (`"san fran"`, `"not san fran"`)
-- `drugs` has three categories (`"never"`, `"sometimes"`, `"often"`) - Also has missing values
-- `status` has three categories (`"single"`, `"available"`, `"seeing someone"`)
+* Two numeric - `arr_delay`, `dep_delay`
+* Two categories 
+    - `season` (`"winter"`, `"summer"`), 
+    - `day_hour` (`"morning"`, `"not morning"`)
+* Three categories - `origin` (`"EWR"`, `"JFK"`, `"LGA"`)
+* Sixteen categories - `carrier`
 
@@
 
-One numerical variable (mean)
+## Hypothesis tests
+
+### One numerical variable (mean)
 
 ```{r}
-prof_small %>%
-  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
-  hypothesize(null = "point", mu = 50) %>% 
+x_bar <- fli_small %>%
+  summarize(mean(dep_delay)) %>%
+  pull()
+null <- fli_small %>%
+  specify(response = dep_delay) %>%
+  hypothesize(null = "point", mu = 10) %>% 
   generate(reps = 1000, type = "bootstrap") %>% 
-  calculate(stat = "mean") %>% 
-  visualize()
+  calculate(stat = "mean")
+ggplot(null, aes(x = stat)) +
+  geom_density() +
+  geom_vline(xintercept = x_bar, col = "red")
+null %>%
+  summarize(mean(stat > x_bar)) * 2
 ```
 
-One numerical variable (median)
+### One numerical variable (median): todo
+
+### One categorical (2 level) variable
 
 ```{r}
-prof_small %>%
-  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
-  hypothesize(null = "point", med = 55) %>% 
-  generate(reps = 1000, type = "bootstrap") %>% 
-  calculate(stat = "median") %>% 
-  visualize()
-```
-
-One categorical (2 level) variable
-
-```{r}
-prof_small %>%
-  specify(response = sex) %>% # alt: sex ~ NULL (or sex ~ 1)
-  hypothesize(null = "point", p = c("m" = .65)) %>% 
+p_hat <- fli_small %>%
+  summarize(mean(day_hour == "morning")) %>%
+  pull()
+null <- fli_small %>%
+  specify(response = dep_delay, success = "morning") %>%
+  hypothesize(null = "point", p = .5) %>% 
   generate(reps = 1000, type = "simulate") %>% 
-  calculate(stat = "prop") %>% 
-  visualize()
+  calculate(stat = "prop")
+ggplot(null, aes(x = stat)) +
+  geom_density() +
+  geom_vline(xintercept = p_hat, col = "red")
+null %>%
+  summarize(mean(stat > p_hat)) * 2
 ```
@@
 
-One numerical variable one categorical (2 levels) (diff in means)
+One numerical variable, one categorical (2 levels) (diff in means)
 
@@
 
-One numerical variable one categorical (2 levels) (diff in medians)
+One numerical variable, one categorical (2 levels) (diff in medians)
 

### 2017-12-27 inst/doc/flights_examples.Rmd
implement mean, prop and diff props on flights data.

@@
 null <- fli_small %>%
-  specify(response = dep_delay, success = "morning") %>%
+  specify(response = day_hour, success = "morning") %>%
   hypothesize(null = "point", p = .5) %>% 
@@
 null %>%
-  summarize(mean(stat > p_hat)) * 2
+  summarize(mean(stat < p_hat)) * 2
 ```
@@
 ```{r}
-prof_small %>%
-  specify(sex ~ city) %>% # alt: response = sex, explanatory = vs
+d_hat <- fli_small %>%
+  group_by(season) %>%
+  summarize(prop = mean(day_hour == "morning")) %>%
+  summarize(diff(prop)) %>%
+  pull()
+null <- fli_small %>%
+  specify(day_hour ~ season, success = "morning") %>%
   hypothesize(null = "independence") %>% 
   generate(reps = 1000, type = "permute") %>% 
-  calculate(stat = "diff in props") %>% 
-  visualize()
+  calculate(stat = "diff in props")
+ggplot(null, aes(x = stat)) +
+  geom_density() +
+  geom_vline(xintercept = d_hat, col = "red")
+null %>%
+  summarize(mean(stat < d_hat)) * 2
 ```

### 2017-12-27 inst/doc/flights_examples.Rmd
add GoF

@@
 ```{r}
-prof_small %>%
-  specify(drugs ~ NULL) %>% # alt: response = drugs
-  hypothesize(null = "point", 
-              p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
+null <- fli_small %>%
+  specify(response = origin) %>%
+  hypothesize(null = "point", p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
   generate(reps = 1000, type = "simulate") %>% 
-  calculate(stat = "Chisq") %>% 
-  visualize()
+  calculate(stat = "Chisq")
+expected <- nrow(fli_small)/3
+Chisq_hat <- fli_small %>%
+  count(origin) %>%
+  mutate(z = (n - expected)^2/expected) %>%
+  summarize(sum(z)) %>%
+  pull()
+ggplot(null, aes(x = stat)) +
+  geom_density() +
+  geom_vline(xintercept = Chisq_hat, col = "red")
+null %>%
+  summarize(mean(stat > Chisq_hat)) 
 ```

### 2017-12-29 README.Rmd

--- 2017-11-08 README.Rmd
@@
 ---
-output:
-  github_document:
-    toc: true 
-    toc_depth: 3
+output: github_document
 ---
 
-Infer: an R package for tidyverse-friendly statistical inference
+#Infer
 
----
+------------------------------------------------------------------------
+
 [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer)
@@
 
-# Installation
-
-To install the current stable version of `infer`, make sure to install `devtools` first:
-
-```
-install.packages("devtools")
-devtools::install_github("andrewbpray/infer")
+```{r diagram, echo=FALSE}
+knitr::opts_chunk$set(eval = FALSE)
+knitr::include_graphics("https://raw.githubusercontent.com/andrewpbray/infer/master/figs/ht-diagram.png")
 ```
 
-To install the development version of `infer` (with `devtools` installed already):
+### Installation
 
-```
-devtools::install_github("ismayc/infer", ref = "dev")
+------------------------------------------------------------------------
+
+To install the current stable version of `infer`, make sure to install `remotes` first:
+
+```{r}
+install.packages("remotes")
+remotes::install_github("andrewpbray/infer")
 ```
 
-## Hypothesis tests
-![](figs/ht-diagram.png)
+### Examples
 
-#### Randomization-based Examples
+------------------------------------------------------------------------
 
-These examples assume that `mtcars` has been overwritten so that the variables
-`cyl`, `vs`, `am`, `gear`, and `carb` are `factor`s.
+These examples assume that `mtcars` has been overwritten so that the variables `cyl`, `vs`, `am`, `gear`, and `carb` are `factor`s.
 
-```
+```{r}
 mtcars <- as.data.frame(mtcars) %>%
@@
 
-Check the package vignettes for further examples using theory-based methods
-in combination with randomization-based methods.
+Hypothesis test for a difference in proportions:
 
-***
-
-### One numerical variable (mean)
-
-```
-mtcars %>%
-  specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
-  hypothesize(null = "point", mu = 25) %>% 
-  generate(reps = 100, type = "bootstrap") %>% 
-  calculate(stat = "mean")
-```
-
-### One numerical variable (median)
-
-```
-mtcars %>%
-  specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
-  hypothesize(null = "point", med = 26) %>% 
-  generate(reps = 100, type = "bootstrap") %>% 
-  calculate(stat = "median")
-```
-
-### One numerical variable (standard deviation)
-
-```
-mtcars %>%
-  specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
-  hypothesize(null = "point", sigma = 5) %>% 
-  generate(reps = 100, type = "bootstrap") %>% 
-  calculate(stat = "sd")
-```
-
-### One categorical (2 level) variable
-
-```
-mtcars %>%
-  specify(response = am) %>% # alt: am ~ NULL (or am ~ 1)
-  hypothesize(null = "point", p = c("1" = .25)) %>% 
-  generate(reps = 100, type = "simulate") %>% 
-  calculate(stat = "prop")
-```
-
-### Two categorical (2 level) variables
-
-```
+```{r}
 mtcars %>%
@@
 
-### One categorical (>2 level) - GoF
+Confidence interval for a difference in means:
 
-```
-mtcars %>%
-  specify(cyl ~ NULL) %>% # alt: response = cyl
-  hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25)) %>%
-  generate(reps = 100, type = "simulate") %>%
-  calculate(stat = "Chisq")
-```
-
-### Two categorical (>2 level) variables
-
-```
-mtcars %>%
-  specify(cyl ~ am) %>% # alt: response = cyl, explanatory = am
-  hypothesize(null = "independence") %>%
-  generate(reps = 100, type = "permute") %>%
-  calculate(stat = "Chisq")
-```
-
-### One numerical variable, one categorical (2 levels) (diff in means)
-
-```
-mtcars %>%
-  specify(mpg ~ am) %>% # alt: response = mpg, explanatory = am
-  hypothesize(null = "independence") %>%
-  generate(reps = 100, type = "permute") %>%
-  calculate(stat = "diff in means")
-```
-
-### One numerical variable one categorical (2 levels) (diff in medians)
-
-```
-mtcars %>%
-  specify(mpg ~ am) %>% # alt: response = mpg, explanatory = am
-  hypothesize(null = "independence") %>%
-  generate(reps = 100, type = "permute") %>%
-  calculate(stat = "diff in medians")
-```
-
-### One numerical one categorical (>2 levels) -  ANOVA
-
-```
-mtcars %>%
-  specify(mpg ~ cyl) %>% # alt: response = mpg, explanatory = cyl
-  hypothesize(null = "independence") %>%
-  generate(reps = 100, type = "permute") %>%
-  calculate(stat = "F")
-```
-
-### Two numerical vars - SLR
-
-```
-mtcars %>%
-  specify(mpg ~ hp) %>% # alt: response = mpg, explanatory = cyl
-  hypothesize(null = "independence") %>%
-  generate(reps = 100, type = "permute") %>%
-  calculate(stat = "slope")
-```
-
-## Confidence intervals
-
-### One numerical (one mean)
-
-```
-mtcars %>%
-  specify(response = mpg) %>%
-  generate(reps = 100, type = "bootstrap") %>%
-  calculate(stat = "mean")
-```
-
-### One numerical (one median)
-
-```
-mtcars %>%
-  specify(response = mpg) %>%
-  generate(reps = 100, type = "bootstrap") %>%
-  calculate(stat = "median")
-```
-
-### One numerical (standard deviation)
-
-```
-mtcars %>%
-  specify(response = mpg) %>%
-  generate(reps = 100, type = "bootstrap") %>%
-  calculate(stat = "sd")
-```
-
-### One categorical (one proportion)
-
-```
-mtcars %>%
-  specify(response = am) %>%
-  generate(reps = 100, type = "bootstrap") %>%
-  calculate(stat = "prop", success = "1")
-```
-
-### One numerical variable one categorical (2 levels) (diff in means)
-
-```
+```{r}
 mtcars %>%
@@
 ```
-
-### Two categorical variables (diff in proportions)
-
-```
-mtcars %>%
-  specify(am ~ vs) %>%
-  generate(reps = 100, type = "bootstrap") %>%
-  calculate(stat = "diff in props")
-```
-
-### Two numerical vars - SLR
-
-```
-mtcars %>%
-  specify(mpg ~ hp) %>% 
-  generate(reps = 100, type = "bootstrap") %>%
-  calculate(stat = "slope")
-```

### 2017-12-30 README.Rmd
Add covr

@@
 
-[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer)
+[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![Coverage status](https://codecov.io/gh/andrewpbray/infer//branch/master/graph/badge.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
 

### 2017-12-31 README.Rmd
Add codecov

--- 2017-12-29 README.Rmd
@@
 
-[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer)
+[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer//master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
 
-The objective of this package is to perform inference using an expressive statistical grammar that coheres with the `tidyverse` design framework.
+The objective of this package is to perform statistical inference using an expressive statistical grammar that coheres with the `tidyverse` design framework.
 

### 2018-01-04 R/calculate.R
Add order parameter for stat = "diff in ..." and associated test to go with it

@@ -4,6 +4,10 @@
 #' @param stat a string giving the type of the statistic to calculate. Current
 #' options include "mean", "median", "sd", "prop", "diff in means",
 #' "diff in medians", "diff in props", "Chisq", "F", and "slope".
+#' @param order a string vector of specifying the order in which the levels of 
+#' the explanatory variable should be ordered for subtraction, where 
+#' \code{order = c("first", "second")} means \code{("first" - "second")}
+#' Needed for inference on difference in means, medians, or proportions.
 #' @param ... to pass options like \code{na.rm = TRUE} into functions like mean, sd, etc.
 #' @return A tibble containing a \code{stat} column of calculated statistics
 #' @importFrom dplyr group_by summarize
@@ -19,7 +23,7 @@
 #'     generate(reps = 100, type = "permute") %>%
 #'     calculate(stat = "diff in props")
 
-calculate <- function(x, stat, ...) {
+calculate <- function(x, stat, order = NULL, ...) {
   
   # TODO: Check to see if dplyr::group_by(replicate) is needed since
   # generate() does a grouping of replicate
@@ -107,12 +111,27 @@ calculate <- function(x, stat, ...) {
     }
   }
   
+  if(stat %in% c("diff in means", "diff in medians", "diff in props")){
+    if(length(unique(x[[as.character(attr(x, "explanatory"))]])) != 2){
+      stop("Statistic is a difference, the explanatory variable should have two levels.")
+    }
+    if(is.null(order)){
+      stop("Statistic is a difference, specify the order in which to subtract.")
+    }
+    if(!is.null(order) & (order[1] %in% unique(x[[as.character(attr(x, "explanatory"))]]) == FALSE)){
+      stop(paste(order[1], "is not a level of the explanatory variable."))
+    }
+    if(!is.null(order) & (order[2] %in% unique(x[[as.character(attr(x, "explanatory"))]]) == FALSE)){
+      stop(paste(order[2], "is not a level of the explanatory variable."))
+    }
+  }
+  
   if (stat == "diff in means") {
     df_out <- x %>%
       dplyr::group_by(replicate, UQ(attr(x, "explanatory"))) %>%
       dplyr::summarize(xbar = mean(UQ(attr(x, "response"), ...))) %>%
[…]

### 2018-01-04 README.Rmd
implement order and success

@@
 mtcars %>%
-  specify(am ~ vs) %>% # alt: response = am, explanatory = vs
+  specify(am ~ vs, success = "1") %>%
   hypothesize(null = "independence") %>%
   generate(reps = 100, type = "permute") %>%
-  calculate(stat = "diff in props")
+  calculate(stat = "diff in props", order = c("1", "0"))
 ```
@@
   generate(reps = 100, type = "bootstrap") %>%
-  calculate(stat = "diff in means")
+  calculate(stat = "diff in means", order = c("1", "0"))
 ```

### 2018-01-04 inst/doc/mtcars_examples.Rmd
fix typo in p-value and warnings.

---
title: "Examples using `mtcars` data"
author: "Chester Ismay and Andrew bray"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette
vignette: |
  %\VignetteIndexEntry{flights example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
```

## Data preparation

```{r message=FALSE, warning=FALSE}
library(nycflights13)
library(dplyr)
library(ggplot2)
library(stringr)
library(infer)
mtcars <- as.data.frame(mtcars) %>%
  mutate(cyl = factor(cyl),
         vs = factor(vs),
         am = factor(am),
         gear = factor(gear),
         carb = factor(carb))
```

***

One numerical variable (mean)

```{r}
mtcars %>%
  specify(response = mpg) %>% # formula alt: mpg ~ NULL
  hypothesize(null = "point", mu = 25) %>% 
  generate(reps = 100, type = "bootstrap") %>% 
  calculate(stat = "mean")
```

One numerical variable (median)

```{r}
mtcars %>%
  specify(response = mpg) %>% # formula alt: mpg ~ NULL
  hypothesize(null = "point", med = 26) %>% 
  generate(reps = 100, type = "bootstrap") %>% 
  calculate(stat = "median")
```

One numerical variable (standard deviation)

```{r}
mtcars %>%
  specify(response = mpg) %>% # formula alt: mpg ~ NULL
  hypothesize(null = "point", sigma = 5) %>% 
  generate(reps = 100, type = "bootstrap") %>% 
  calculate(stat = "sd")
```

One categorical (2 level) variable

```{r}
mtcars %>%
  specify(response = am, success = "1") %>% # formula alt: am ~ NULL
  hypothesize(null = "point", p = .25) %>% 
  generate(reps = 100, type = "simulate") %>% 
  calculate(stat = "prop")
```

Two categorical (2 level) variables

```{r}
mtcars %>%
  specify(am ~ vs, success = "1") %>% # alt: response = am, explanatory = vs
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in props", order = c("0", "1"))
```

One categorical (>2 level) - GoF

```{r}
mtcars %>%
  specify(cyl ~ NULL) %>% # alt: response = cyl
  hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25)) %>%
  generate(reps = 100, type = "simulate") %>%
  calculate(stat = "Chisq")
```

Two categorical (>2 level) variables

```{r warning = FALSE}
mtcars %>%
  specify(cyl ~ am) %>% # alt: response = cyl, explanatory = am
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "Chisq")
```

One numerical variable one categorical (2 levels) (diff in means)

```{r}
mtcars %>%
  specify(mpg ~ am) %>% # alt: response = mpg, explanatory = am
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in means", order = c("0", "1"))
```

One numerical variable one categorical (2 levels) (diff in medians)

```{r}
mtcars %>%
  specify(mpg ~ am) %>% # alt: response = mpg, explanatory = am
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in medians", order = c("0", "1"))
```

One numerical one categorical (>2 levels) -  ANOVA

```{r}
mtcars %>%
  specify(mpg ~ cyl) %>% # alt: response = mpg, explanatory = cyl
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "F")
```

Two numerical vars - SLR

```{r}
mtcars %>%
  specify(mpg ~ hp) %>% # alt: response = mpg, explanatory = cyl
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "slope")
```

### Confidence intervals

One numerical (one mean)

```{r}
mtcars %>%
  specify(response = mpg) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "mean")
```

One numerical (one median)

```{r}
mtcars %>%
  specify(response = mpg) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "median")
```

One numerical (standard deviation)

```{r}
mtcars %>%
  specify(response = mpg) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "sd")
```

One categorical (one proportion)

```{r}
mtcars %>%
  specify(response = am, success = "1") %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "prop")
```

One numerical variable one categorical (2 levels) (diff in means)

```{r}
mtcars %>%
  specify(mpg ~ am) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("0", "1"))
```

Two categorical variables (diff in proportions)

```{r}
mtcars %>%
  specify(am ~ vs, success = "1") %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "diff in props", order = c("0", "1"))
```

Two numerical vars - SLR

```{r}
mtcars %>%
  specify(mpg ~ hp) %>% 
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "slope")
```

### 2018-01-04 inst/doc/flights_examples.R

@@ -1,23 +1,7 @@
----
-title: "Randomization Examples using `nycflights13` `flights` data"
-author: "Chester Ismay and Andrew bray"
-date: "`r Sys.Date()`"
-output: 
-  rmarkdown::html_vignette:
-    df_print: kable
-vignette: |
-  %\VignetteIndexEntry{flights example}
-  %\VignetteEngine{knitr::rmarkdown}
-  %\VignetteEncoding{UTF-8}
----
-
-```{r include=FALSE}
+## ----include=FALSE-------------------------------------------------------
 knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
-```
 
-## Data preparation
-
-```{r message=FALSE, warning=FALSE}
+## ----message=FALSE, warning=FALSE----------------------------------------
 library(nycflights13)
 library(dplyr)
 library(ggplot2)
@@ -37,22 +21,8 @@ fli_small <- flights %>%
   select(arr_delay, dep_delay, season, 
          day_hour, origin, carrier) %>%
   filter(., complete.cases(.))
-```
 
-* Two numeric - `arr_delay`, `dep_delay`
-* Two categories 
-    - `season` (`"winter"`, `"summer"`), 
-    - `day_hour` (`"morning"`, `"not morning"`)
-* Three categories - `origin` (`"EWR"`, `"JFK"`, `"LGA"`)
-* Sixteen categories - `carrier`
-
-***
-
-# Hypothesis tests
-
-### One numerical variable (mean)
-
-```{r}
+## ------------------------------------------------------------------------
 x_bar <- fli_small %>%
   summarize(mean(dep_delay)) %>%
   pull()
@@ -66,11 +36,8 @@ ggplot(null, aes(x = stat)) +
   geom_vline(xintercept = x_bar, color = "red")
 null %>%
   summarize(p_value = mean(stat > x_bar) * 2)
-```
 
-### One numerical variable (median)
-
-```{r}
+## ------------------------------------------------------------------------
 x_tilde <- fli_small %>%
   summarize(median(dep_delay)) %>%
   pull()
@@ -84,11 +51,8 @@ ggplot(null, aes(x = stat)) +
   geom_vline(xintercept = x_tilde, color = "red")
 null %>%
   summarize(p_value = mean(stat < x_tilde) * 2)
-```
 
-### One categorical (2 level) variable
-
-```{r}
+## ------------------------------------------------------------------------
 p_hat <- fli_small %>%
[…]

### 2018-01-04 inst/doc/mtcars_examples.R

@@ -1,22 +1,7 @@
----
-title: "Examples using `mtcars` data"
-author: "Chester Ismay and Andrew bray"
-date: "`r Sys.Date()`"
-output: 
-  rmarkdown::html_vignette
-vignette: |
-  %\VignetteIndexEntry{flights example}
-  %\VignetteEngine{knitr::rmarkdown}
-  %\VignetteEncoding{UTF-8}
----
-
-```{r include=FALSE}
+## ----include=FALSE-------------------------------------------------------
 knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
-```
 
-## Data preparation
-
-```{r message=FALSE, warning=FALSE}
+## ----message=FALSE, warning=FALSE----------------------------------------
 library(nycflights13)
 library(dplyr)
 library(ggplot2)
@@ -28,183 +13,123 @@ mtcars <- as.data.frame(mtcars) %>%
          am = factor(am),
          gear = factor(gear),
          carb = factor(carb))
-```
 
-
-***
-
-One numerical variable (mean)
-
-```{r}
+## ------------------------------------------------------------------------
 mtcars %>%
   specify(response = mpg) %>% # formula alt: mpg ~ NULL
   hypothesize(null = "point", mu = 25) %>% 
   generate(reps = 100, type = "bootstrap") %>% 
   calculate(stat = "mean")
-```
 
-One numerical variable (median)
-
-```{r}
+## ------------------------------------------------------------------------
 mtcars %>%
   specify(response = mpg) %>% # formula alt: mpg ~ NULL
   hypothesize(null = "point", med = 26) %>% 
   generate(reps = 100, type = "bootstrap") %>% 
   calculate(stat = "median")
-```
 
-One numerical variable (standard deviation)
-
-```{r}
+## ------------------------------------------------------------------------
 mtcars %>%
   specify(response = mpg) %>% # formula alt: mpg ~ NULL
   hypothesize(null = "point", sigma = 5) %>% 
   generate(reps = 100, type = "bootstrap") %>% 
   calculate(stat = "sd")
-```
 
-One categorical (2 level) variable
-
-```{r}
+## ------------------------------------------------------------------------
 mtcars %>%
   specify(response = am, success = "1") %>% # formula alt: am ~ NULL
   hypothesize(null = "point", p = .25) %>% 
   generate(reps = 100, type = "simulate") %>% 
   calculate(stat = "prop")
-```
 
-Two categorical (2 level) variables
-
-```{r}
[…]

### 2018-01-08 README.Rmd
Update README with CRAN reference

@@
 ------------------------------------------------------------------------
-
-[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer//master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
+[![](http://cranlogs.r-pkg.org/badges/infer)](http://cran.rstudio.com/web/packages/infer/index.html) [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer//master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
 
@@
 
-To install the current stable version of `infer`, make sure to install `remotes` first:
+To install the current stable version of `infer` from CRAN:
+
+```{r}
+install.packages("infer")
+```
+
+To install the developmental version of `infer`, make sure to install `remotes` first:
 

### 2018-01-08 README.Rmd

@@
 ------------------------------------------------------------------------
-[![](http://cranlogs.r-pkg.org/badges/infer)](http://cran.rstudio.com/web/packages/infer/index.html) [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer//master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
+
+[![CRAN badge](http://cranlogs.r-pkg.org/badges/infer)](http://cran.rstudio.com/web/packages/infer/index.html) [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
 

### 2018-01-11 docs/articles/flights_examples.Rmd
Updated pkgdown site

---
title: "Randomization Examples using `nycflights13` `flights` data"
author: "Chester Ismay and Andrew bray"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    df_print: kable
vignette: |
  %\VignetteIndexEntry{flights example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
```

## Data preparation

```{r message=FALSE, warning=FALSE}
library(nycflights13)
library(dplyr)
library(ggplot2)
library(stringr)
library(infer)
set.seed(2017)
fli_small <- flights %>% 
  sample_n(size = 500) %>% 
  mutate(season = case_when(
    month %in% c(10:12, 1:3) ~ "winter",
    month %in% c(4:9) ~ "summer"
  )) %>% 
  mutate(day_hour = case_when(
    between(hour, 1, 12) ~ "morning",
    between(hour, 13, 24) ~ "not morning"
  )) %>% 
  select(arr_delay, dep_delay, season, 
         day_hour, origin, carrier) %>%
  filter(., complete.cases(.))
```

* Two numeric - `arr_delay`, `dep_delay`
* Two categories 
    - `season` (`"winter"`, `"summer"`), 
    - `day_hour` (`"morning"`, `"not morning"`)
* Three categories - `origin` (`"EWR"`, `"JFK"`, `"LGA"`)
* Sixteen categories - `carrier`

***

# Hypothesis tests

### One numerical variable (mean)

```{r}
x_bar <- fli_small %>%
  summarize(mean(dep_delay)) %>%
  pull()
null <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", mu = 10) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean")
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = x_bar, color = "red")
null %>%
  summarize(p_value = mean(stat > x_bar) * 2)
```

### One numerical variable (median)

```{r}
x_tilde <- fli_small %>%
  summarize(median(dep_delay)) %>%
  pull()
null <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", med = 0) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "median")
ggplot(null, aes(x = stat)) +
  geom_bar() +
  geom_vline(xintercept = x_tilde, color = "red")
null %>%
  summarize(p_value = mean(stat < x_tilde) * 2)
```

### One categorical (2 level) variable

```{r}
p_hat <- fli_small %>%
  summarize(mean(day_hour == "morning")) %>%
  pull()
null <- fli_small %>%
  specify(response = day_hour, success = "morning") %>%
  hypothesize(null = "point", p = .5) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "prop")
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = p_hat, color = "red")
null %>%
  summarize(p_value = mean(stat < p_hat) * 2)
```

### Two categorical (2 level) variables

```{r}
d_hat <- fli_small %>%
  group_by(season) %>%
  summarize(prop = mean(day_hour == "morning")) %>%
  summarize(diff(prop)) %>%
  pull()
null <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "diff in props", order = c("summer", "winter"))
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = d_hat, color = "red")
null %>%
  summarize(p_value = mean(stat < d_hat) * 2)
```

### One categorical (>2 level) - GoF

```{r}
Chisq_hat <- chisq.test(table(fli_small$origin))$stat
null <- fli_small %>%
  specify(response = origin) %>%
  hypothesize(null = "point", p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "Chisq")
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = Chisq_hat, color = "red")
null %>%
  summarize(p_value = mean(stat > Chisq_hat)) 
```

### Two categorical (>2 level) variables

```{r}
Chisq_hat <- chisq.test(table(fli_small$day_hour, fli_small$origin))$stat
null <- fli_small %>%
  specify(day_hour ~ origin) %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "Chisq")
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = Chisq_hat, color = "red")
null %>%
  summarize(p_value = mean(stat > Chisq_hat)) 
```

### One numerical variable, one categorical (2 levels) (diff in means)

```{r}
d_hat <- fli_small %>% 
  group_by(season) %>% 
  summarize(mean_stat = mean(dep_delay)) %>% 
  summarize(diff(mean_stat)) %>% 
  pull()
null <- fli_small %>%
  specify(dep_delay ~ season) %>% # alt: response = dep_delay, explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("summer", "winter"))
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = d_hat, color = "red")
null %>%
  summarize(p_value = mean(stat > d_hat) * 2)   
```

### One numerical variable, one categorical (2 levels) (diff in medians)

```{r}
d_hat <- fli_small %>% 
  group_by(season) %>% 
  summarize(median_stat = median(dep_delay)) %>% 
  summarize(diff(median_stat)) %>% 
  pull()
null <- fli_small %>%
  specify(dep_delay ~ season) %>% # alt: response = dep_delay, explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", order = c("summer", "winter"))
ggplot(null, aes(x = stat)) +
  geom_bar() +
  geom_vline(xintercept = d_hat, color = "red")
null %>%
  summarize(p_value = mean(stat > d_hat) * 2)    
```

### One numerical, one categorical (>2 levels) -  ANOVA

```{r}
F_hat <- anova(aov(formula = arr_delay ~ origin, data = fli_small))$`F value`[1]
null <- fli_small %>%
   specify(arr_delay ~ origin) %>% # alt: response = arr_delay, explanatory = origin
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "F")
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = F_hat, color = "red")  
null %>% 
  summarize(p_value = mean(stat > F_hat))
```

### Two numerical vars - SLR

```{r}
slope_hat <- lm(arr_delay ~ dep_delay, data = fli_small) %>% 
  broom::tidy() %>% 
  filter(term == "dep_delay") %>% 
  select(estimate) %>% 
  pull()
null <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% # alt: response = arr_delay, explanatory = dep_delay
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "slope")
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = slope_hat, color = "red")  
null %>% 
  summarize(p_value = mean(stat > slope_hat) * 2)   
```

## Confidence intervals

### One numerical (one mean)

```{r}
x_bar <- fli_small %>% 
   summarize(mean(arr_delay)) %>% 
   pull()
boot <- fli_small %>%
   specify(response = arr_delay) %>%
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "mean") %>% 
   pull()
c(lower = x_bar - 2 * sd(boot), 
  upper = x_bar + 2 * sd(boot))
```

### One numerical (one median)

```{r}
x_tilde <- fli_small %>% 
   summarize(median(arr_delay)) %>% 
   pull()
boot <- fli_small %>%
   specify(response = arr_delay) %>%
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "median") %>% 
   pull()
c(lower = x_tilde - 2 * sd(boot), 
  upper = x_tilde + 2 * sd(boot))
```

### One categorical (one proportion)

```{r}
p_hat <- fli_small %>%
  summarize(mean(day_hour == "morning")) %>%
  pull()
boot <- fli_small %>%
  specify(response = day_hour, success = "morning") %>%
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "prop") %>%
  pull()
c(lower = p_hat - 2 * sd(boot), 
  upper = p_hat + 2 * sd(boot))
```

### One numerical variable, one categorical (2 levels) (diff in means)

```{r}
d_hat <- fli_small %>% 
  group_by(season) %>% 
  summarize(mean_stat = mean(arr_delay)) %>% 
  summarize(diff(mean_stat)) %>% 
  pull()
boot <- fli_small %>%
   specify(arr_delay ~ season) %>%
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "diff in means", order = c("summer", "winter")) %>% 
   pull()
c(lower = p_hat - 2 * sd(boot), 
  upper = p_hat + 2 * sd(boot))
```

### Two categorical variables (diff in proportions)

```{r}
d_hat <- fli_small %>%
  group_by(season) %>%
  summarize(prop = mean(day_hour == "morning")) %>%
  summarize(diff(prop)) %>%
  pull()
boot <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "diff in props", order = c("summer", "winter")) %>%
  pull()
c(lower = d_hat - 2 * sd(boot), 
  upper = d_hat + 2 * sd(boot))
```

### Two numerical vars - SLR

```{r}
slope_hat <- lm(arr_delay ~ dep_delay, data = fli_small) %>% 
  broom::tidy() %>% 
  filter(term == "dep_delay") %>% 
  select(estimate) %>% 
  pull()
boot <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% 
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "slope") %>% 
   pull()
c(lower = slope_hat - 2 * sd(boot), 
  upper = slope_hat + 2 * sd(boot))   
```

### 2018-01-12 README.Rmd

@@
 
-[![CRAN badge](http://cranlogs.r-pkg.org/badges/infer)](http://cran.rstudio.com/web/packages/infer/index.html) [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
+[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)
+[![CRAN badge](http://cranlogs.r-pkg.org/badges/infer)](http://cran.rstudio.com/web/packages/infer/index.html) 
+[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) 
+[![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
 

### 2018-01-13 README.Rmd
we dont need no stinking badges

--- 2018-01-08 README.Rmd
@@
 
-[![CRAN badge](http://cranlogs.r-pkg.org/badges/infer)](http://cran.rstudio.com/web/packages/infer/index.html) [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
+[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)
+[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) 
+[![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
 

### 2018-01-15 inst/doc/flights_examples.R
Fix p_hat typo

@@ -88,7 +88,8 @@ null %>%
 Chisq_hat <- chisq.test(table(fli_small$origin))$stat
 null <- fli_small %>%
   specify(response = origin) %>%
-  hypothesize(null = "point", p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
+  hypothesize(null = "point", 
+              p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
   generate(reps = 1000, type = "simulate") %>% 
   calculate(stat = "Chisq")
 ggplot(null, aes(x = stat)) +
@@ -117,7 +118,8 @@ d_hat <- fli_small %>%
   summarize(diff(mean_stat)) %>% 
   pull()
 null <- fli_small %>%
-  specify(dep_delay ~ season) %>% # alt: response = dep_delay, explanatory = season
+  specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
+  # explanatory = season
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "diff in means", order = c("summer", "winter"))
@@ -134,7 +136,8 @@ d_hat <- fli_small %>%
   summarize(diff(median_stat)) %>% 
   pull()
 null <- fli_small %>%
-  specify(dep_delay ~ season) %>% # alt: response = dep_delay, explanatory = season
+  specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
+  # explanatory = season
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "diff in medians", order = c("summer", "winter"))
@@ -145,9 +148,12 @@ null %>%
   summarize(p_value = mean(stat > d_hat) * 2)    
 
 ## ------------------------------------------------------------------------
-F_hat <- anova(aov(formula = arr_delay ~ origin, data = fli_small))$`F value`[1]
+F_hat <- anova(
+               aov(formula = arr_delay ~ origin, data = fli_small)
+               )$`F value`[1]
 null <- fli_small %>%
-   specify(arr_delay ~ origin) %>% # alt: response = arr_delay, explanatory = origin
+   specify(arr_delay ~ origin) %>% # alt: response = arr_delay, 
+   # explanatory = origin
    hypothesize(null = "independence") %>%
    generate(reps = 1000, type = "permute") %>%
[…]

### 2018-01-15 inst/doc/mtcars_examples.Rmd

@@
 author: "Chester Ismay and Andrew bray"
-date: "`r Sys.Date()`"
+date: "2018-01-05"
 output: 
@@
 vignette: |
-  %\VignetteIndexEntry{flights example}
+  %\VignetteIndexEntry{mtcars example}
   %\VignetteEngine{knitr::rmarkdown}
@@
          carb = factor(carb))
+# For reproducibility         
+set.seed(2018)         
 ```
@@
 
-```{r}
+```{r eval=FALSE}
 mtcars %>%

### 2018-01-18 inst/doc/flights_examples.Rmd
Add back in one prop examples and test

--- 2017-12-27 inst/doc/flights_examples.Rmd
@@
 
-## Hypothesis tests
+# Hypothesis tests
 
@@
   geom_density() +
-  geom_vline(xintercept = x_bar, col = "red")
+  geom_vline(xintercept = x_bar, color = "red")
 null %>%
-  summarize(mean(stat > x_bar)) * 2
+  summarize(p_value = mean(stat > x_bar) * 2)
 ```
 
-### One numerical variable (median): todo
-
-### One categorical (2 level) variable
+### One numerical variable (median)
 
 ```{r}
-p_hat <- fli_small %>%
-  summarize(mean(day_hour == "morning")) %>%
+x_tilde <- fli_small %>%
+  summarize(median(dep_delay)) %>%
   pull()
 null <- fli_small %>%
-  specify(response = dep_delay, success = "morning") %>%
-  hypothesize(null = "point", p = .5) %>% 
-  generate(reps = 1000, type = "simulate") %>% 
-  calculate(stat = "prop")
+  specify(response = dep_delay) %>%
+  hypothesize(null = "point", med = 0) %>% 
+  generate(reps = 1000, type = "bootstrap") %>% 
+  calculate(stat = "median")
+ggplot(null, aes(x = stat)) +
+  geom_bar() +
+  geom_vline(xintercept = x_tilde, color = "red")
+null %>%
+  summarize(p_value = mean(stat < x_tilde) * 2)
+```
+
+### Two categorical (2 level) variables
+
+```{r}
+d_hat <- fli_small %>%
+  group_by(season) %>%
+  summarize(prop = mean(day_hour == "morning")) %>%
+  summarize(diff(prop)) %>%
+  pull()
+null <- fli_small %>%
+  specify(day_hour ~ season, success = "morning") %>%
+  hypothesize(null = "independence") %>% 
+  generate(reps = 1000, type = "permute") %>% 
+  calculate(stat = "diff in props", order = c("summer", "winter"))
 ggplot(null, aes(x = stat)) +
   geom_density() +
-  geom_vline(xintercept = p_hat, col = "red")
+  geom_vline(xintercept = d_hat, color = "red")
 null %>%
-  summarize(mean(stat > p_hat)) * 2
+  summarize(p_value = mean(stat < d_hat) * 2)
 ```
 
-Two categorical (2 level) variables
+### One categorical (>2 level) - GoF
 
 ```{r}
-prof_small %>%
-  specify(sex ~ city) %>% # alt: response = sex, explanatory = vs
+Chisq_hat <- chisq.test(table(fli_small$origin))$stat
+null <- fli_small %>%
+  specify(response = origin) %>%
+  hypothesize(null = "point", 
+              p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
+  generate(reps = 1000, type = "simulate") %>% 
+  calculate(stat = "Chisq")
+ggplot(null, aes(x = stat)) +
+  geom_density() +
+  geom_vline(xintercept = Chisq_hat, color = "red")
+null %>%
+  summarize(p_value = mean(stat > Chisq_hat)) 
+```
+
+### Two categorical (>2 level) variables
+
+```{r}
+Chisq_hat <- chisq.test(table(fli_small$day_hour, fli_small$origin))$stat
+null <- fli_small %>%
+  specify(day_hour ~ origin) %>%
   hypothesize(null = "independence") %>% 
   generate(reps = 1000, type = "permute") %>% 
-  calculate(stat = "diff in props") %>% 
-  visualize()
+  calculate(stat = "Chisq")
+ggplot(null, aes(x = stat)) +
+  geom_density() +
+  geom_vline(xintercept = Chisq_hat, color = "red")
+null %>%
+  summarize(p_value = mean(stat > Chisq_hat)) 
 ```
 
-One categorical (>2 level) - GoF
+### One numerical variable, one categorical (2 levels) (diff in means)
 
 ```{r}
-prof_small %>%
-  specify(drugs ~ NULL) %>% # alt: response = drugs
-  hypothesize(null = "point", 
-              p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
-  generate(reps = 1000, type = "simulate") %>%
-  calculate(stat = "Chisq") %>% 
-  visualize()
+d_hat <- fli_small %>% 
+  group_by(season) %>% 
+  summarize(mean_stat = mean(dep_delay)) %>% 
+  summarize(diff(mean_stat)) %>% 
+  pull()
+null <- fli_small %>%
+  specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
+  # explanatory = season
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000, type = "permute") %>%
+  calculate(stat = "diff in means", order = c("summer", "winter"))
+ggplot(null, aes(x = stat)) +
+  geom_density() +
+  geom_vline(xintercept = d_hat, color = "red")
+null %>%
+  summarize(p_value = mean(stat > d_hat) * 2)   
 ```
 
-Two categorical (>2 level) variables
+### One numerical variable, one categorical (2 levels) (diff in medians)
 
 ```{r}
-prof_small %>%
-  specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
+d_hat <- fli_small %>% 
+  group_by(season) %>% 
+  summarize(median_stat = median(dep_delay)) %>% 
+  summarize(diff(median_stat)) %>% 
+  pull()
+null <- fli_small %>%
+  specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
+  # explanatory = season
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "Chisq") %>% 
-  visualize()
+  calculate(stat = "diff in medians", order = c("summer", "winter"))
+ggplot(null, aes(x = stat)) +
+  geom_bar() +
+  geom_vline(xintercept = d_hat, color = "red")
+null %>%
+  summarize(p_value = mean(stat > d_hat) * 2)    
 ```
 
-One numerical variable, one categorical (2 levels) (diff in means)
+### One numerical, one categorical (>2 levels) -  ANOVA
 
 ```{r}
-prof_small %>%
-  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
+F_hat <- anova(
+               aov(formula = arr_delay ~ origin, data = fli_small)
+               )$`F value`[1]
+null <- fli_small %>%
+   specify(arr_delay ~ origin) %>% # alt: response = arr_delay, 
+   # explanatory = origin
    hypothesize(null = "independence") %>%
    generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "diff in means") %>% 
-  visualize()
+   calculate(stat = "F")
+ggplot(null, aes(x = stat)) +
+  geom_density() +
+  geom_vline(xintercept = F_hat, color = "red")  
+null %>% 
+  summarize(p_value = mean(stat > F_hat))
 ```
 
-One numerical variable, one categorical (2 levels) (diff in medians)
+### Two numerical vars - SLR
 
 ```{r}
-prof_small %>%
-  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
+slope_hat <- lm(arr_delay ~ dep_delay, data = fli_small) %>% 
+  broom::tidy() %>% 
+  filter(term == "dep_delay") %>% 
+  select(estimate) %>% 
+  pull()
+null <- fli_small %>%
+   specify(arr_delay ~ dep_delay) %>% # alt: response = arr_delay, 
+   # explanatory = dep_delay
    hypothesize(null = "independence") %>%
    generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "diff in medians") %>% 
-  visualize()
-```
-
-One numerical one categorical (>2 levels) -  ANOVA
-
-```{r}
-prof_small %>%
-  specify(age ~ status) %>% # alt: response = age, explanatory = status
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "F") %>% 
-  visualize()
-```
-
-Two numerical vars - SLR
-
-```{r}
-prof_small %>%
-  specify(age ~ height) %>% # alt: response = age, explanatory = height
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "slope") %>% 
-  visualize()
+   calculate(stat = "slope")
+ggplot(null, aes(x = stat)) +
+  geom_density() +
+  geom_vline(xintercept = slope_hat, color = "red")  
+null %>% 
+  summarize(p_value = mean(stat > slope_hat) * 2)   
 ```
@@
 
-One numerical (one mean)
+### One numerical (one mean)
+
+```{r eval=FALSE}
+x_bar <- fli_small %>%
+   summarize(mean(arr_delay)) %>%
+   pull()
+boot <- fli_small %>%
+   specify(response = arr_delay) %>%
+   generate(reps = 1000, type = "bootstrap") %>%
+   calculate(stat = "mean") %>%
+   pull()
+c(lower = x_bar - 2 * sd(boot),
+  upper = x_bar + 2 * sd(boot))
+```
+
+### One categorical (one proportion)
+
+```{r eval=FALSE}
+p_hat <- fli_small %>%
+ summarize(mean(day_hour == "morning")) %>%
+ pull()
+boot <- fli_small %>%
+ specify(response = day_hour, success = "morning") %>%
+ generate(reps = 1000, type = "bootstrap") %>%
+ calculate(stat = "prop") %>%
+ pull()
+c(lower = p_hat - 2 * sd(boot),
+ upper = p_hat + 2 * sd(boot))
+```
+
+### One numerical variable, one categorical (2 levels) (diff in means)
 
 ```{r}
-prof_small %>%
-  specify(response = age) %>%
+d_hat <- fli_small %>% 
+  group_by(season) %>% 
+  summarize(mean_stat = mean(arr_delay)) %>% 
+  summarize(diff(mean_stat)) %>% 
+  pull()
+boot <- fli_small %>%
+   specify(arr_delay ~ season) %>%
    generate(reps = 1000, type = "bootstrap") %>%
-  calculate(stat = "mean") %>% 
-  visualize()
+   calculate(stat = "diff in means", order = c("summer", "winter")) %>% 
+   pull()
+c(lower = d_hat - 2 * sd(boot), 
+  upper = d_hat + 2 * sd(boot))
 ```
 
-One numerical (one median)
+### Two categorical variables (diff in proportions)
 
 ```{r}
-prof_small %>%
-  specify(response = age) %>%
+d_hat <- fli_small %>%
+  group_by(season) %>%
+  summarize(prop = mean(day_hour == "morning")) %>%
+  summarize(diff(prop)) %>%
+  pull()
+boot <- fli_small %>%
+  specify(day_hour ~ season, success = "morning") %>%
   generate(reps = 1000, type = "bootstrap") %>% 
-  calculate(stat = "median") %>% 
-  visualize()
+  calculate(stat = "diff in props", order = c("summer", "winter")) %>%
+  pull()
+c(lower = d_hat - 2 * sd(boot), 
+  upper = d_hat + 2 * sd(boot))
 ```
 
-One categorical (one proportion)
+### Two numerical vars - SLR
 
 ```{r}
-prof_small %>%
-  specify(response = sex) %>%
-  generate(reps = 1000, type = "bootstrap") %>%
-  calculate(stat = "prop", success = "f") %>% 
-  visualize()
-```
-
-One numerical variable one categorical (2 levels) (diff in means)
-
-```{r}
-prof_small %>%
-  specify(age ~ sex) %>%
-  generate(reps = 1000, type = "bootstrap") %>%
-  calculate(stat = "diff in means") %>% 
-  visualize()
-```
-
-Two categorical variables (diff in proportions)
-
-```{r}
-prof_small %>%
-  specify(sex ~ city) %>%
-  generate(reps = 1000, type = "bootstrap") %>%
-  calculate(stat = "diff in props") %>% 
-  visualize()
-```
-
-Two numerical vars - SLR
-
-```{r}
-prof_small %>%
-  specify(age ~ height) %>% 
+slope_hat <- lm(arr_delay ~ dep_delay, data = fli_small) %>% 
+  broom::tidy() %>% 
+  filter(term == "dep_delay") %>% 
+  select(estimate) %>% 
+  pull()
+boot <- fli_small %>%
+   specify(arr_delay ~ dep_delay) %>% 
    generate(reps = 1000, type = "bootstrap") %>%
    calculate(stat = "slope") %>% 
-  visualize()
+   pull()
+c(lower = slope_hat - 2 * sd(boot), 
+  upper = slope_hat + 2 * sd(boot))   
 ```

### 2018-01-20 inst/doc/flights_examples.Rmd

@@
   %\VignetteIndexEntry{flights example}
+  %\VignetteEncoding{UTF-8}
   %\VignetteEngine{knitr::rmarkdown}
-  %\VignetteEncoding{UTF-8}
+editor_options: 
+  chunk_output_type: console
 ---
@@
   summarize(p_value = mean(stat < x_tilde) * 2)
+```
+
+### One categorical (one proportion)
+
+```{r}
+p_hat <- fli_small %>%
+  summarize(mean(day_hour == "morning")) %>%
+  pull()
+null <- fli_small %>%
+  specify(response = day_hour, success = "morning") %>%
+  hypothesize(null = "point", p = .5) %>%
+  generate(reps = 1000, type = "simulate") %>%
+  calculate(stat = "prop")
+ggplot(null, aes(x = stat)) +
+  geom_bar() +
+  geom_vline(xintercept = p_hat, color = "red")
+null %>%
+  summarize(p_value = mean(stat < p_hat) * 2)
+```
+
+Logical variables will be coerced to factors:
+
+```{r}
+null <- fli_small %>%
+  mutate(day_hour_logical = (day_hour == "morning")) %>%
+  specify(response = day_hour_logical, success = "TRUE") %>%
+  hypothesize(null = "point", p = .5) %>%
+  generate(reps = 1000, type = "simulate") %>%
+  calculate(stat = "prop")
 ```
@@
 
-```{r eval=FALSE}
+```{r}
 x_bar <- fli_small %>%
@@
 
-```{r eval=FALSE}
+```{r}
 p_hat <- fli_small %>%

### 2018-01-20 README.Rmd
Update README.Rmd
Update README on GitHub

@@
 
-[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)
-[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) 
-[![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
+[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/andrewpbray/infer?branch=master&svg=true)](https://ci.appveyor.com/project/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
 
@@
 ```
+
+Other examples are available in the package vignettes.
+
+***
+
+Please note that this project is released with a [Contributor Code of Conduct](https://github.com/andrewpbray/infer/blob/master/CONDUCT.md).
+By participating in this project you agree to abide by its terms.

### 2018-03-08 README.Rmd

@@
 
-[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/andrewpbray/infer?branch=master&svg=true)](https://ci.appveyor.com/project/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
+<!--figs/infer.svg-->
+<!--http://www.r-pkg.org/badges/version/infer-->
+<!--figs/master.svg-->
+<!--https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg-->
+
+[![CRAN_Status_Badge](figs/infer.svg)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/andrewpbray/infer?branch=master&svg=true)](https://ci.appveyor.com/project/andrewpbray/infer) [![Coverage Status](figs/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
 
@@
 ```
+
+To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first:
+
+```{r}
+install.packages("remotes")
+remotes::install_github("andrewpbray/infer", ref = "develop")
+```
+
+To see the things we are working on with the package as vignettes/Articles, check out 
+the developmental `pkgdown` site at <https://infer-dev.netlify.com>.
+
+### Contributing
+
+We welcome others helping us make this package as user friendly and efficient as possible. Please review
+our [contributing](CONTRIBUTING.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
+helping us to write `testthat` tests and help us in building vignettes that show how to (and how NOT to)
+use the package.
 

### 2018-03-08 vignettes/profiles_examples.R
Update vignettes

@@ -7,6 +7,7 @@ library(stringr)
 library(infer)
 set.seed(2017)
 prof_small <- profiles %>% 
+  na.omit() %>% 
   dplyr::sample_n(size = 500) %>% 
   dplyr::mutate(city = dplyr::case_when(
     str_detect(location, "san fran") ~ "san fran",
@@ -24,7 +25,7 @@ prof_small %>%
 
 ## ------------------------------------------------------------------------
 prof_small %>%
-  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
+  specify(response = age) %>% # alt: age ~ NULL
   hypothesize(null = "point", med = 55) %>% 
   generate(reps = 1000, type = "bootstrap") %>% 
   calculate(stat = "median") %>% 
@@ -32,7 +33,7 @@ prof_small %>%
 
 ## ------------------------------------------------------------------------
 prof_small %>%
-  specify(response = sex) %>% # alt: sex ~ NULL (or sex ~ 1)
+  specify(response = sex, success = "m") %>% # alt: sex ~ NULL
   hypothesize(null = "point", p = c("m" = .65)) %>% 
   generate(reps = 1000, type = "simulate") %>% 
   calculate(stat = "prop") %>% 
@@ -40,10 +41,10 @@ prof_small %>%
 
 ## ------------------------------------------------------------------------
 prof_small %>%
-  specify(sex ~ city) %>% # alt: response = sex, explanatory = vs
+  specify(sex ~ city) %>% # alt: response = sex, explanatory = city
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "diff in props") %>% 
+  calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
   visualize()
 
 ## ------------------------------------------------------------------------
@@ -68,7 +69,7 @@ prof_small %>%
   specify(age ~ sex) %>% # alt: response = age, explanatory = sex
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "diff in means") %>% 
+  calculate(stat = "diff in means", order = c("m", "f")) %>% 
   visualize()
 
 ## ------------------------------------------------------------------------
@@ -76,7 +77,7 @@ prof_small %>%
   specify(age ~ sex) %>% # alt: response = age, explanatory = sex
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
[…]

### 2018-03-08 inst/doc/mtcars_examples.Rmd
Build vignettes

--- 2018-01-04 inst/doc/mtcars_examples.Rmd
@@
 ```{r message=FALSE, warning=FALSE}
-library(nycflights13)
+library(infer)
 library(dplyr)
-library(ggplot2)
-library(stringr)
-library(infer)
 mtcars <- as.data.frame(mtcars) %>%

### 2018-03-08 inst/doc/flights_examples.R

@@ -1,0 +1,257 @@
+## ----include=FALSE-------------------------------------------------------
+knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
+
+## ----message=FALSE, warning=FALSE----------------------------------------
+library(nycflights13)
+library(dplyr)
+library(ggplot2)
+library(stringr)
+library(infer)
+set.seed(2017)
+fli_small <- flights %>% 
+  sample_n(size = 500) %>% 
+  mutate(season = case_when(
+    month %in% c(10:12, 1:3) ~ "winter",
+    month %in% c(4:9) ~ "summer"
+  )) %>% 
+  mutate(day_hour = case_when(
+    between(hour, 1, 12) ~ "morning",
+    between(hour, 13, 24) ~ "not morning"
+  )) %>% 
+  select(arr_delay, dep_delay, season, 
+         day_hour, origin, carrier) %>%
+  filter(., complete.cases(.))
+
+## ------------------------------------------------------------------------
+x_bar <- fli_small %>%
+  summarize(mean(dep_delay)) %>%
+  pull()
+null <- fli_small %>%
+  specify(response = dep_delay) %>%
+  hypothesize(null = "point", mu = 10) %>% 
+  generate(reps = 1000, type = "bootstrap") %>% 
+  calculate(stat = "mean")
+ggplot(null, aes(x = stat)) +
+  geom_density() +
+  geom_vline(xintercept = x_bar, color = "red")
+null %>%
+  summarize(p_value = mean(stat > x_bar) * 2)
+
+## ------------------------------------------------------------------------
+x_tilde <- fli_small %>%
+  summarize(median(dep_delay)) %>%
+  pull()
+null <- fli_small %>%
+  specify(response = dep_delay) %>%
+  hypothesize(null = "point", med = 0) %>% 
+  generate(reps = 1000, type = "bootstrap") %>% 
+  calculate(stat = "median")
+ggplot(null, aes(x = stat)) +
+  geom_bar() +
+  geom_vline(xintercept = x_tilde, color = "red")
+null %>%
+  summarize(p_value = mean(stat < x_tilde) * 2)
+
+## ------------------------------------------------------------------------
+p_hat <- fli_small %>%
+  summarize(mean(day_hour == "morning")) %>%
+  pull()
+null <- fli_small %>%
+  specify(response = day_hour, success = "morning") %>%
+  hypothesize(null = "point", p = .5) %>%
[…]

### 2018-03-08 inst/doc/two_sample_t.Rmd

---
title: "Two sample $t$ test example using `nycflights13` `flights` data"
author: "Chester Ismay"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    df_print: kable
vignette: |
  %\VignetteIndexEntry{Two sample t test flights example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 3) 
```

## Data preparation

```{r message=FALSE, warning=FALSE}
library(nycflights13)
library(dplyr)
library(stringr)
library(infer)
set.seed(2017)
fli_small <- flights %>% 
  sample_n(size = 500) %>% 
  mutate(half_year = case_when(
    between(month, 1, 6) ~ "h1",
    between(month, 7, 12) ~ "h2"
  )) %>% 
  mutate(day_hour = case_when(
    between(hour, 1, 12) ~ "morning",
    between(hour, 13, 24) ~ "not morning"
  )) %>% 
  select(arr_delay, dep_delay, half_year, 
         day_hour, origin, carrier)
```

* Two numeric - `arr_delay`, `dep_delay`
* Two categories 
    - `half_year` (`"h1"`, `"h2"`), 
    - `day_hour` (`"morning"`, `"not morning"`)
* Three categories - `origin` (`"EWR"`, `"JFK"`, `"LGA"`)
* Sixteen categories - `carrier`

***

# One numerical variable, one categorical (2 levels)

## Calculate observed statistic

Using `t_test` in `infer`

```{r}
obs_t <- fli_small %>% 
  t_test(formula = arr_delay ~ half_year) %>% 
  dplyr::select(statistic) %>% 
  dplyr::pull()
```

The observed $t$ statistic is `r obs_t`.

Or using another shortcut function in `infer`:

```{r}
obs_t <- fli_small %>% 
  t_stat(formula = arr_delay ~ half_year)
```

The observed $t$ statistic is `r obs_t`.

## Randomization approach to t-statistic

```{r}
t_null_distn <- fli_small %>%
  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t")
t_null_distn %>% visualize(obs_stat = obs_t, direction = "two_sided")
```

## Calculate the randomization-based $p$-value

```{r}
t_null_distn %>% 
  dplyr::summarize(p_value = mean(abs(stat) >= obs_t)) %>% 
  dplyr::pull()
```

## Theoretical distribution

```{r }
fli_small %>%
  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
  hypothesize(null = "independence") %>%
  # calculate(stat = "t") ## Not needed since t is implied based on variable types
  visualize(method = "theoretical", obs_stat = obs_t, direction = "two_sided")
```

## Overlay appropriate $t$ distribution on top of permuted t-statistics

```{r eval=FALSE}
fli_small %>%
  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t") %>% 
  visualize(method = "both", obs_stat = obs_t, direction = "two_sided")
```

```{r echo=FALSE}
# To use same distribution calculated above
t_null_distn %>% 
  visualize(method = "both", obs_stat = obs_t, direction = "two_sided")
```

## Compute theoretical p-value

```{r}
fli_small %>% 
  t_test(formula = arr_delay ~ half_year) %>% 
  dplyr::select(p_value) %>% 
  dplyr::pull()
```

### 2018-03-08 README.Rmd
Update md links in README

@@
 To see the things we are working on with the package as vignettes/Articles, check out 
-the developmental `pkgdown` site at <https://infer-dev.netlify.com>.
+the developmental `pkgdown` site at <http://bit.ly/infer-dev>.
 
@@
 We welcome others helping us make this package as user friendly and efficient as possible. Please review
-our [contributing](CONTRIBUTING.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
+our [contributing](https://github.com/andrewpbray/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
 helping us to write `testthat` tests and help us in building vignettes that show how to (and how NOT to)

### 2018-03-08 inst/doc/profiles_examples.Rmd
Update pkgdown and vignettes

--- 2017-10-10 docs/articles/profiles_examples.Rmd
@@
 ```{r include=FALSE}
-knitr::opts_chunk$set(fig.width = 8, fig.height = 5, cache = TRUE) 
+knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
 ```
+
+# Note
+
+The `okcupiddata` is thought by some to be controversial. Its use here is only
+to check for a variety of different variable types and levels. It will remain only in this
+"cutting edge" version of the package as we continue to add and test examples.
 
@@
 prof_small <- profiles %>% 
+  na.omit() %>% 
   dplyr::sample_n(size = 500) %>% 
@@
 prof_small %>%
-  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
+  specify(response = age) %>% # alt: age ~ NULL
   hypothesize(null = "point", med = 55) %>% 
@@
 prof_small %>%
-  specify(response = sex) %>% # alt: sex ~ NULL (or sex ~ 1)
+  specify(response = sex, success = "m") %>%
   hypothesize(null = "point", p = c("m" = .65)) %>% 
@@
 prof_small %>%
-  specify(sex ~ city) %>% # alt: response = sex, explanatory = vs
+  specify(sex ~ city, success = "m") %>%
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "diff in props") %>% 
+  calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
   visualize()
@@
   generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "diff in means") %>% 
+  calculate(stat = "diff in means", order = c("m", "f")) %>% 
   visualize()
@@
   generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "diff in medians") %>% 
+  calculate(stat = "diff in medians", order = c("m", "f")) %>% 
   visualize()
@@
 prof_small %>%
-  specify(response = sex) %>%
+  specify(response = sex, success = "f") %>%
   generate(reps = 1000, type = "bootstrap") %>%
-  calculate(stat = "prop", success = "f") %>% 
+  calculate(stat = "prop") %>% 
   visualize()
@@
   generate(reps = 1000, type = "bootstrap") %>%
-  calculate(stat = "diff in means") %>% 
+  calculate(stat = "diff in means", order = c("m", "f")) %>% 
   visualize()
@@
 prof_small %>%
-  specify(sex ~ city) %>%
+  specify(sex ~ city, success = "m") %>%
   generate(reps = 1000, type = "bootstrap") %>%
-  calculate(stat = "diff in props") %>% 
+  calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
   visualize()

### 2018-03-08 docs/articles/chisq_test.R

@@ -1,0 +1,62 @@
+## ----include=FALSE-------------------------------------------------------
+knitr::opts_chunk$set(fig.width = 8, fig.height = 3) 
+
+## ----message=FALSE, warning=FALSE----------------------------------------
+library(nycflights13)
+library(dplyr)
+library(ggplot2)
+library(stringr)
+library(infer)
+set.seed(2017)
+fli_small <- flights %>% 
+  na.omit() %>% 
+  sample_n(size = 500) %>% 
+  mutate(season = case_when(
+    month %in% c(10:12, 1:3) ~ "winter",
+    month %in% c(4:9) ~ "summer"
+  )) %>% 
+  mutate(day_hour = case_when(
+    between(hour, 1, 12) ~ "morning",
+    between(hour, 13, 24) ~ "not morning"
+  )) %>% 
+  select(arr_delay, dep_delay, season, 
+         day_hour, origin, carrier)
+
+## ------------------------------------------------------------------------
+obs_chisq <- fli_small %>% 
+  chisq_test(formula = origin ~ season) %>% 
+  dplyr::select(statistic) %>% 
+  dplyr::pull()
+
+## ------------------------------------------------------------------------
+obs_chisq <- fli_small %>% 
+  chisq_stat(formula = origin ~ season)
+
+## ------------------------------------------------------------------------
+chisq_null_distn <- fli_small %>%
+  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000, type = "permute") %>%
+  calculate(stat = "Chisq")
+chisq_null_distn %>% visualize(obs_stat = obs_chisq, direction = "greater")
+
+## ------------------------------------------------------------------------
+chisq_null_distn %>% 
+  dplyr::summarize(p_value = mean(stat >= obs_chisq)) %>% 
+  dplyr::pull()
+
+## ------------------------------------------------------------------------
+fli_small %>%
+  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
+  hypothesize(null = "independence") %>%
+  # calculate(stat = "Chisq") ## Not needed since t is implied based on variable types
+  visualize(method = "theoretical", obs_stat = obs_chisq)
+
+## ----eval=FALSE----------------------------------------------------------
+#  fli_small %>%
+#    specify(origin ~ season) %>% # alt: response = origin, explanatory = season
[…]

### 2018-03-08 inst/doc/chisq_test.R

@@ -4,68 +4,70 @@ knitr::opts_chunk$set(fig.width = 8, fig.height = 3)
 ## ----message=FALSE, warning=FALSE----------------------------------------
 library(nycflights13)
 library(dplyr)
+library(ggplot2)
 library(stringr)
 library(infer)
 set.seed(2017)
 fli_small <- flights %>% 
+  na.omit() %>% 
   sample_n(size = 500) %>% 
-  mutate(half_year = case_when(
-    between(month, 1, 6) ~ "h1",
-    between(month, 7, 12) ~ "h2"
+  mutate(season = case_when(
+    month %in% c(10:12, 1:3) ~ "winter",
+    month %in% c(4:9) ~ "summer"
   )) %>% 
   mutate(day_hour = case_when(
     between(hour, 1, 12) ~ "morning",
     between(hour, 13, 24) ~ "not morning"
   )) %>% 
-  select(arr_delay, dep_delay, half_year, 
+  select(arr_delay, dep_delay, season, 
          day_hour, origin, carrier)
 
 ## ------------------------------------------------------------------------
-obs_t <- fli_small %>% 
-  t_test(formula = arr_delay ~ half_year) %>% 
+obs_chisq <- fli_small %>% 
+  chisq_test(formula = origin ~ season) %>% 
   dplyr::select(statistic) %>% 
   dplyr::pull()
 
 ## ------------------------------------------------------------------------
-obs_t <- fli_small %>% 
-  t_stat(formula = arr_delay ~ half_year)
+obs_chisq <- fli_small %>% 
+  chisq_stat(formula = origin ~ season)
 
 ## ------------------------------------------------------------------------
-t_null_distn <- fli_small %>%
-  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
+chisq_null_distn <- fli_small %>%
+  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "t")
-t_null_distn %>% visualize(obs_stat = obs_t, direction = "two_sided")
+  calculate(stat = "Chisq")
+chisq_null_distn %>% visualize(obs_stat = obs_chisq, direction = "greater")
 
 ## ------------------------------------------------------------------------
-t_null_distn %>% 
[…]

### 2018-03-08 inst/doc/profiles_examples.R

@@ -7,6 +7,7 @@ library(stringr)
 library(infer)
 set.seed(2017)
 prof_small <- profiles %>% 
+  na.omit() %>% 
   dplyr::sample_n(size = 500) %>% 
   dplyr::mutate(city = dplyr::case_when(
     str_detect(location, "san fran") ~ "san fran",
@@ -24,7 +25,7 @@ prof_small %>%
 
 ## ------------------------------------------------------------------------
 prof_small %>%
-  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
+  specify(response = age) %>% # alt: age ~ NULL
   hypothesize(null = "point", med = 55) %>% 
   generate(reps = 1000, type = "bootstrap") %>% 
   calculate(stat = "median") %>% 
@@ -32,7 +33,7 @@ prof_small %>%
 
 ## ------------------------------------------------------------------------
 prof_small %>%
-  specify(response = sex) %>% # alt: sex ~ NULL (or sex ~ 1)
+  specify(response = sex, success = "m") %>%
   hypothesize(null = "point", p = c("m" = .65)) %>% 
   generate(reps = 1000, type = "simulate") %>% 
   calculate(stat = "prop") %>% 
@@ -40,10 +41,10 @@ prof_small %>%
 
 ## ------------------------------------------------------------------------
 prof_small %>%
-  specify(sex ~ city) %>% # alt: response = sex, explanatory = vs
+  specify(sex ~ city, success = "m") %>%
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "diff in props") %>% 
+  calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
   visualize()
 
 ## ------------------------------------------------------------------------
@@ -68,7 +69,7 @@ prof_small %>%
   specify(age ~ sex) %>% # alt: response = age, explanatory = sex
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "diff in means") %>% 
+  calculate(stat = "diff in means", order = c("m", "f")) %>% 
   visualize()
 
 ## ------------------------------------------------------------------------
@@ -76,7 +77,7 @@ prof_small %>%
   specify(age ~ sex) %>% # alt: response = age, explanatory = sex
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "diff in medians") %>% 
[…]

### 2018-03-08 inst/doc/two_sample_t.R

@@ -35,7 +35,7 @@ t_null_distn <- fli_small %>%
   specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "t")
+  calculate(stat = "t", order = c("h1", "h2"))
 t_null_distn %>% visualize(obs_stat = obs_t, direction = "two_sided")
 
 ## ------------------------------------------------------------------------
@@ -55,7 +55,7 @@ fli_small %>%
 #    specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
 #    hypothesize(null = "independence") %>%
 #    generate(reps = 1000, type = "permute") %>%
-#    calculate(stat = "t") %>%
+#    calculate(stat = "t", order = c("h1", "h2")) %>%
 #    visualize(method = "both", obs_stat = obs_t, direction = "two_sided")
 
 ## ----echo=FALSE----------------------------------------------------------

### 2018-03-08 vignettes/profiles_examples.R

@@ -1,140 +1,0 @@
-## ----include=FALSE-------------------------------------------------------
-knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
-
-## ----message=FALSE, warning=FALSE----------------------------------------
-library(okcupiddata)
-library(stringr)
-library(infer)
-set.seed(2017)
-prof_small <- profiles %>% 
-  na.omit() %>% 
-  dplyr::sample_n(size = 500) %>% 
-  dplyr::mutate(city = dplyr::case_when(
-    str_detect(location, "san fran") ~ "san fran",
-    !str_detect(location, "san fran") ~ "not san fran"
-  )) %>% 
-  dplyr::select(age, sex, city, drugs, height, status)
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
-  hypothesize(null = "point", mu = 50) %>% 
-  generate(reps = 1000, type = "bootstrap") %>% 
-  calculate(stat = "mean") %>% 
-  visualize()
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(response = age) %>% # alt: age ~ NULL
-  hypothesize(null = "point", med = 55) %>% 
-  generate(reps = 1000, type = "bootstrap") %>% 
-  calculate(stat = "median") %>% 
-  visualize()
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(response = sex, success = "m") %>% # alt: sex ~ NULL
-  hypothesize(null = "point", p = c("m" = .65)) %>% 
-  generate(reps = 1000, type = "simulate") %>% 
-  calculate(stat = "prop") %>% 
-  visualize()
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(sex ~ city) %>% # alt: response = sex, explanatory = city
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
-  visualize()
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(drugs ~ NULL) %>% # alt: response = drugs
-  hypothesize(null = "point", 
-              p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
-  generate(reps = 1000, type = "simulate") %>%
-  calculate(stat = "Chisq") %>% 
-  visualize()
-
-## ------------------------------------------------------------------------
[…]

### 2018-03-08 vignettes/profiles_examples_both_methods.R

@@ -1,180 +1,0 @@
-## ----include=FALSE-------------------------------------------------------
-knitr::opts_chunk$set(fig.width = 7, fig.height = 3) 
-
-## ----message=FALSE, warning=FALSE----------------------------------------
-library(okcupiddata)
-library(stringr)
-library(infer)
-set.seed(2017)
-prof_small <- profiles %>% 
-  dplyr::sample_n(size = 500) %>% 
-  dplyr::mutate(city = dplyr::case_when(
-    str_detect(location, "san fran") ~ "san fran",
-    !str_detect(location, "san fran") ~ "not san fran"
-  )) %>% 
-  dplyr::select(age, sex, city, drugs, height, status)
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "t") %>% 
-  visualize()
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
-  hypothesize(null = "independence") %>%
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "t") ## Not needed since t is implied based on variable types
-  visualize(method = "theoretical")
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "t") %>% 
-  visualize(method = "both")
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(age ~ status) %>% # alt: response = age, explanatory = status
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "F") %>% 
-  visualize()
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(age ~ status) %>% # alt: response = age, explanatory = status
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "F") ## Not needed since t is implied based on variable types
-  hypothesize(null = "independence") %>%
-  visualize(method = "theoretical")
-
[…]

### 2018-03-09 README.Rmd
Add more details to README

--- 2018-01-20 README.Rmd
@@
 
-#Infer
+# Infer
 
 ------------------------------------------------------------------------
+
+<!--figs/infer.svg-->
+<!--http://www.r-pkg.org/badges/version/infer-->
+<!--figs/master.svg-->
+<!--https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg-->
 
@@
 
+To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first:
+
+```{r}
+install.packages("remotes")
+remotes::install_github("andrewpbray/infer", ref = "develop")
+```
+
+To see the things we are working on with the package as vignettes/Articles, check out 
+the developmental `pkgdown` site at <https://infer-dev.netlify.com>.
+
+### Contributing
+
+We welcome others helping us make this package as user friendly and efficient as possible. Please review
+our [contributing](https://github.com/andrewpbray/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
+helping us to write `testthat` tests and help us in building vignettes that show how to (and how NOT to)
+use the package.
+
 ### Examples
@@
 
-Hypothesis test for a difference in proportions:
+Hypothesis test for a difference in proportions (using the formula interface 
+`y ~ x` in `specify()`):
 
@@
 
-Confidence interval for a difference in means:
+Confidence interval for a difference in means (using the non-formula interface
+giving both the `response` and `explanatory` variables in `specify()`):
 
@@
 mtcars %>%
-  specify(mpg ~ am) %>%
+  specify(response = mpg, explanatory = am) %>%
   generate(reps = 100, type = "bootstrap") %>%
@@
 ```
+
+Note that the formula and non-formula interfaces work for all implemented inference
+procedures in `infer`. Use whatever is more natural for you. If you will be doing
+modeling using functions like `lm()` and `glm()`, we recommend you begin to use the
+formula `y ~ x` notation as soon as possible though.
 

### 2018-03-23 inst/doc/flights_examples.Rmd
Update pkgdown and vignettes

@@
   pull()
-null <- fli_small %>%
+null_distn <- fli_small %>%
   specify(response = dep_delay) %>%
@@
   calculate(stat = "mean")
-ggplot(null, aes(x = stat)) +
+ggplot(data = null_distn, mapping = aes(x = stat)) +
   geom_density() +
   geom_vline(xintercept = x_bar, color = "red")
-null %>%
+null_distn %>%
   summarize(p_value = mean(stat > x_bar) * 2)
@@
   calculate(stat = "median")
-ggplot(null, aes(x = stat)) +
+ggplot(null_distn, aes(x = stat)) +
   geom_bar() +
   geom_vline(xintercept = x_tilde, color = "red")
-null %>%
+null_distn %>%
   summarize(p_value = mean(stat < x_tilde) * 2)
@@
   pull()
-null <- fli_small %>%
+null_distn <- fli_small %>%
   specify(response = day_hour, success = "morning") %>%
@@
   calculate(stat = "prop")
-ggplot(null, aes(x = stat)) +
+ggplot(null_distn, aes(x = stat)) +
   geom_bar() +
   geom_vline(xintercept = p_hat, color = "red")
-null %>%
+null_distn %>%
   summarize(p_value = mean(stat < p_hat) * 2)
@@
 ```{r}
-null <- fli_small %>%
+null_distn <- fli_small %>%
   mutate(day_hour_logical = (day_hour == "morning")) %>%
@@
   pull()
-null <- fli_small %>%
+null_distn <- fli_small %>%
   specify(day_hour ~ season, success = "morning") %>%
@@
   calculate(stat = "diff in props", order = c("summer", "winter"))
-ggplot(null, aes(x = stat)) +
+ggplot(null_distn, aes(x = stat)) +
   geom_density() +
   geom_vline(xintercept = d_hat, color = "red")
-null %>%
+null_distn %>%
   summarize(p_value = mean(stat < d_hat) * 2)
@@
 Chisq_hat <- chisq.test(table(fli_small$origin))$stat
-null <- fli_small %>%
+null_distn <- fli_small %>%
   specify(response = origin) %>%
@@
   calculate(stat = "Chisq")
-ggplot(null, aes(x = stat)) +
+ggplot(null_distn, aes(x = stat)) +
   geom_density() +
   geom_vline(xintercept = Chisq_hat, color = "red")
-null %>%
+null_distn %>%
   summarize(p_value = mean(stat > Chisq_hat)) 
@@
 Chisq_hat <- chisq.test(table(fli_small$day_hour, fli_small$origin))$stat
-null <- fli_small %>%
-  specify(day_hour ~ origin) %>%
+null_distn <- fli_small %>%
+  specify(day_hour ~ origin, success = "morning") %>%
   hypothesize(null = "independence") %>% 
@@
   pull()
-null <- fli_small %>%
+null_distn <- fli_small %>%
   specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
@@
   calculate(stat = "diff in means", order = c("summer", "winter"))
-ggplot(null, aes(x = stat)) +
+ggplot(null_distn, aes(x = stat)) +
   geom_density() +
   geom_vline(xintercept = d_hat, color = "red")
-null %>%
+null_distn %>%
   summarize(p_value = mean(stat > d_hat) * 2)   
@@
   calculate(stat = "diff in medians", order = c("summer", "winter"))
-ggplot(null, aes(x = stat)) +
+ggplot(null_distn, aes(x = stat)) +
   geom_bar() +
   geom_vline(xintercept = d_hat, color = "red")
-null %>%
+null_distn %>%
   summarize(p_value = mean(stat > d_hat) * 2)    
@@
                )$`F value`[1]
-null <- fli_small %>%
+null_distn <- fli_small %>%
    specify(arr_delay ~ origin) %>% # alt: response = arr_delay, 
@@
    calculate(stat = "F")
-ggplot(null, aes(x = stat)) +
+ggplot(null_distn, aes(x = stat)) +
   geom_density() +
   geom_vline(xintercept = F_hat, color = "red")  
-null %>% 
+null_distn %>% 
   summarize(p_value = mean(stat > F_hat))
@@
   pull()
-null <- fli_small %>%
-   specify(arr_delay ~ dep_delay) %>% # alt: response = arr_delay, 
-   # explanatory = dep_delay
+null_distn <- fli_small %>%
+   specify(arr_delay ~ dep_delay) %>% 
    hypothesize(null = "independence") %>%
@@
    calculate(stat = "slope")
-ggplot(null, aes(x = stat)) +
+ggplot(null_distn, aes(x = stat)) +
   geom_density() +
   geom_vline(xintercept = slope_hat, color = "red")  
-null %>% 
+null_distn %>% 
   summarize(p_value = mean(stat > slope_hat) * 2)   

### 2018-03-23 inst/doc/profiles_examples_both_methods.Rmd
Update pkgdown and vignettes

---
title: "Randomization and Traditional Examples using `okcupiddata` `profiles` data"
author: "Chester Ismay"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    df_print: kable
vignette: |
  %\VignetteIndexEntry{OKCupid profiles example with resampling & theory-based methods}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 3) 
```

# Note

The `okcupiddata` is thought by some to be controversial. Its use here is only
to check for a variety of different variable types and levels. It will remain only in this
"cutting edge" version of the package as we continue to add and test examples.

## Data preparation

```{r message=FALSE, warning=FALSE}
library(okcupiddata)
library(stringr)
library(infer)
set.seed(2017)
prof_small <- profiles %>% 
  dplyr::sample_n(size = 500) %>% 
  dplyr::mutate(city = dplyr::case_when(
    str_detect(location, "san fran") ~ "san fran",
    !str_detect(location, "san fran") ~ "not san fran"
  )) %>% 
  dplyr::select(age, sex, city, drugs, height, status)
```

- `height` and `age` are numerical variables.
- `sex` has two categories (`"m"`, `"f"`)
- `city` has two categories (`"san fran"`, `"not san fran"`)
- `drugs` has three categories (`"never"`, `"sometimes"`, `"often"`) - Also has missing values
- `status` has three categories (`"single"`, `"available"`, `"seeing someone"`)

***

## Hypothesis tests

## Implemented

### One numerical variable, one categorical (2 levels)

Randomization approach to t-statistic

```{r}
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t", order = c("m", "f")) %>% 
  visualize()
```

Theoretical distribution

```{r }
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "t") ## Not needed since t implied based on variable types
  visualize(method = "theoretical")
```

Overlay appropriate $t$ distribution on top of permuted t-statistics

```{r }
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t", order = c("m", "f")) %>% 
  visualize(method = "both")
```

### One numerical, one categorical (>2 levels) -  ANOVA

Randomization approach to F-statistic

```{r}
prof_small %>%
  specify(age ~ status) %>% # alt: response = age, explanatory = status
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "F") %>% 
  visualize()
```

Theoretical distribution

```{r}
prof_small %>%
  specify(age ~ status) %>% # alt: response = age, explanatory = status
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "F") ## Not needed since F implied based on variable types
  hypothesize(null = "independence") %>%
  visualize(method = "theoretical")
```

Overlay appropriate $F$ distribution on top of permuted F-statistics

```{r}
prof_small %>%
  specify(age ~ status) %>% # alt: response = age, explanatory = status
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "F") %>% 
  visualize(method = "both")
```

## One categorical (2 level) variable

Randomization approach to z-statistic

```{r}
prof_small %>%
  specify(response = sex, success = "m") %>% 
  hypothesize(null = "point", p = c("m" = .65, "f" = .35)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "z") %>% 
  visualize()
```

Theoretical distribution

```{r}
prof_small %>%
  specify(response = sex, success = "m") %>%
  hypothesize(null = "point", p = c("m" = .65, "f" = .35)) %>% 
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "z") ## Not needed since z implied based on variable types
  visualize(method = "theoretical")
```

Overlay standard normal distribution on top of permuted z-statistics

```{r}
prof_small %>%
  specify(response = sex, success = "m") %>%
  hypothesize(null = "point", p = c("m" = .65, "f" = .35)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "z") %>% 
  visualize(method = "both")
```

## Two categorical (2 level) variables

Randomization approach to z-statistic

```{r}
prof_small %>%
  specify(sex ~ city, success = "m") %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "z", order = c("san fran", "not san fran")) %>% 
  visualize()
```

Theoretical distribution

```{r}
prof_small %>%
  specify(sex ~ city, success = "m") %>%
  hypothesize(null = "independence") %>% 
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "z") ## Not needed since z implied based on variable types
  visualize(method = "theoretical")
```

Overlay standard normal distribution on top of permuted z-statistics

```{r}
prof_small %>%
  specify(sex ~ city, success = "m") %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "z", order = c("san fran", "not san fran")) %>% 
  visualize(method = "both")
```

## Testing

## Two categorical (>2 level) variables

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "Chisq") %>% 
  visualize()
```

Theoretical distribution

```{r}
prof_small %>%
  specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
  hypothesize(null = "independence") %>%
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "Chisq") ## Not needed since Chisq implied based on variable types
  visualize(method = "theoretical")
```

Overlay standard chi-square distribution on top of permuted statistics

```{r}
prof_small %>%
  specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "Chisq") %>% 
  visualize(method = "both")
```

### To Do (Also overlay appropriate chi-sq distn)

One categorical (>2 level) - GoF

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "Chisq") %>% 
  visualize()
```

***

## TO DO

### To Do (slope $t$ stat)
### To Do (Also overlay appropriate t distn)

Two numerical vars - SLR

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "slope") %>% 
  visualize()
```

### To Do (one mean $t$ stat)
### To Do (Also overlay appropriate t distn)

One numerical variable (mean)

**Testing but not working yet**

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
  hypothesize(null = "point", mu = 50) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "t") %>% 
  visualize()
```

## Confidence intervals

### To Do (one mean $t$ stat)
### To Do (Also overlay appropriate t distn)

One numerical (one mean)

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(response = age) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "mean") %>% 
  visualize()
```

### To Do (one prop $z$ stat)
### To Do (Also overlay std normal distn)

One categorical (one proportion)

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(response = sex) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "prop", success = "f") %>% 
  visualize()
```

### Currently testing t-stat
### To Do (Also overlay appropriate t distn)
### To Do (Shift t stats to be centered at 0 for bootstrapping)

One numerical variable one categorical (2 levels) (diff in means)

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(age ~ sex) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "t") %>% 
  visualize()
```

### To Do (two prop $z$ stat)
### To Do (Also overlay appropriate std normal distn)
### To Do (Shift z stats to be centered at 0 for bootstrapping)

Two categorical variables (diff in proportions)

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(sex ~ city) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in props") %>% 
  visualize()
```

### To Do (slope $t$ stat)
### To Do (Also overlay appropriate t distn)
### To Do (Shift t stats to be centered at 0 for bootstrapping)

Two numerical vars - SLR

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(age ~ height) %>% 
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "slope") %>% 
  visualize()
```

### 2018-03-23 inst/doc/flights_examples.R

@@ -26,49 +26,49 @@ fli_small <- flights %>%
 x_bar <- fli_small %>%
   summarize(mean(dep_delay)) %>%
   pull()
-null <- fli_small %>%
+null_distn <- fli_small %>%
   specify(response = dep_delay) %>%
-  hypothesize(null = "point", mu = 10) %>% 
-  generate(reps = 1000, type = "bootstrap") %>% 
+  hypothesize(null = "point", mu = 10) %>%
+  generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "mean")
-ggplot(null, aes(x = stat)) +
+ggplot(data = null_distn, mapping = aes(x = stat)) +
   geom_density() +
   geom_vline(xintercept = x_bar, color = "red")
-null %>%
+null_distn %>%
   summarize(p_value = mean(stat > x_bar) * 2)
 
 ## ------------------------------------------------------------------------
 x_tilde <- fli_small %>%
   summarize(median(dep_delay)) %>%
   pull()
-null <- fli_small %>%
+null_distn <- fli_small %>%
   specify(response = dep_delay) %>%
   hypothesize(null = "point", med = 0) %>% 
   generate(reps = 1000, type = "bootstrap") %>% 
   calculate(stat = "median")
-ggplot(null, aes(x = stat)) +
+ggplot(null_distn, aes(x = stat)) +
   geom_bar() +
   geom_vline(xintercept = x_tilde, color = "red")
-null %>%
+null_distn %>%
   summarize(p_value = mean(stat < x_tilde) * 2)
 
 ## ------------------------------------------------------------------------
 p_hat <- fli_small %>%
   summarize(mean(day_hour == "morning")) %>%
   pull()
-null <- fli_small %>%
+null_distn <- fli_small %>%
   specify(response = day_hour, success = "morning") %>%
   hypothesize(null = "point", p = .5) %>%
   generate(reps = 1000, type = "simulate") %>%
   calculate(stat = "prop")
-ggplot(null, aes(x = stat)) +
+ggplot(null_distn, aes(x = stat)) +
   geom_bar() +
   geom_vline(xintercept = p_hat, color = "red")
-null %>%
+null_distn %>%
   summarize(p_value = mean(stat < p_hat) * 2)
 
 ## ------------------------------------------------------------------------
-null <- fli_small %>%
+null_distn <- fli_small %>%
   mutate(day_hour_logical = (day_hour == "morning")) %>%
[…]

### 2018-03-23 vignettes/profiles_examples_both_methods.R

@@ -1,0 +1,196 @@
+## ----include=FALSE-------------------------------------------------------
+knitr::opts_chunk$set(fig.width = 7, fig.height = 3) 
+
+## ----message=FALSE, warning=FALSE----------------------------------------
+library(okcupiddata)
+library(stringr)
+library(infer)
+set.seed(2017)
+prof_small <- profiles %>% 
+  dplyr::sample_n(size = 500) %>% 
+  dplyr::mutate(city = dplyr::case_when(
+    str_detect(location, "san fran") ~ "san fran",
+    !str_detect(location, "san fran") ~ "not san fran"
+  )) %>% 
+  dplyr::select(age, sex, city, drugs, height, status)
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000, type = "permute") %>%
+  calculate(stat = "t", order = c("m", "f")) %>% 
+  visualize()
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
+  hypothesize(null = "independence") %>%
+  # generate() is not needed since we are not doing randomization
+  # calculate(stat = "t") ## Not needed since t implied based on variable types
+  visualize(method = "theoretical")
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000, type = "permute") %>%
+  calculate(stat = "t", order = c("m", "f")) %>% 
+  visualize(method = "both")
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(age ~ status) %>% # alt: response = age, explanatory = status
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000, type = "permute") %>%
+  calculate(stat = "F") %>% 
+  visualize()
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(age ~ status) %>% # alt: response = age, explanatory = status
+  # generate() is not needed since we are not doing randomization
+  # calculate(stat = "F") ## Not needed since F implied based on variable types
+  hypothesize(null = "independence") %>%
+  visualize(method = "theoretical")
+
[…]

### 2018-03-23 inst/doc/profiles_examples_both_methods.Rmd
Update pkgdown and vignettes

@@
 
-## Testing
+## Two categorical (>2 level) variables
 
-## Two categorical (>2 level) variables
+Randomization approach to $\chi^2$-statistic
 
@@
 
-### To Do (Also overlay appropriate chi-sq distn)
+## One categorical (>2 level) - GoF
 
-One categorical (>2 level) - GoF
+Randomization approach to $\chi^2$-statistic
 
-```{r eval=FALSE, include=FALSE}
+```{r}
 prof_small %>%
@@
   hypothesize(null = "point", 
-              p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
+              p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
   generate(reps = 1000, type = "simulate") %>%
@@
   visualize()
+```
+
+Theoretical distribution
+
+```{r}
+prof_small %>%
+  specify(drugs ~ NULL) %>% # alt: response = drugs
+  hypothesize(null = "point", 
+              p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
+#  generate(reps = 1000, type = "simulate") %>%
+#  calculate(stat = "Chisq") %>% 
+  visualize(method = "theoretical")
+```
+
+Overlay standard chi-square distribution on top of permuted statistics
+
+```{r}
+prof_small %>%
+  specify(drugs ~ NULL) %>% # alt: response = drugs
+  hypothesize(null = "point", 
+              p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
+  generate(reps = 1000, type = "simulate") %>%
+  calculate(stat = "Chisq") %>% 
+  visualize(method = "both")
 ```
@@
 ### To Do (Also overlay appropriate t distn)
+
+<!-- ## Testing -->
 

### 2018-03-23 vignettes/chisq_test.R

@@ -1,73 +1,0 @@
-## ----include=FALSE-------------------------------------------------------
-knitr::opts_chunk$set(fig.width = 8, fig.height = 3) 
-
-## ----message=FALSE, warning=FALSE----------------------------------------
-library(nycflights13)
-library(dplyr)
-library(ggplot2)
-library(stringr)
-library(infer)
-set.seed(2017)
-fli_small <- flights %>% 
-  na.omit() %>% 
-  sample_n(size = 500) %>% 
-  mutate(season = case_when(
-    month %in% c(10:12, 1:3) ~ "winter",
-    month %in% c(4:9) ~ "summer"
-  )) %>% 
-  mutate(day_hour = case_when(
-    between(hour, 1, 12) ~ "morning",
-    between(hour, 13, 24) ~ "not morning"
-  )) %>% 
-  select(arr_delay, dep_delay, season, 
-         day_hour, origin, carrier)
-
-## ------------------------------------------------------------------------
-obs_chisq <- fli_small %>% 
-  chisq_test(formula = origin ~ season) %>% 
-  dplyr::select(statistic) %>% 
-  dplyr::pull()
-
-## ------------------------------------------------------------------------
-obs_chisq <- fli_small %>% 
-  chisq_stat(formula = origin ~ season)
-
-## ------------------------------------------------------------------------
-chisq_null_distn <- fli_small %>%
-  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "Chisq")
-chisq_null_distn %>% visualize(obs_stat = obs_chisq, direction = "greater")
-
-## ------------------------------------------------------------------------
-chisq_null_distn %>% 
-  dplyr::summarize(p_value = mean(stat >= obs_chisq)) %>% 
-  dplyr::pull()
-
-## ------------------------------------------------------------------------
-fli_small %>%
-  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
-  hypothesize(null = "independence") %>%
-  # calculate(stat = "Chisq") ## Not needed since t is implied based on variable types
-  visualize(method = "theoretical", obs_stat = obs_chisq, direction = "right")
-
-## ----eval=FALSE----------------------------------------------------------
-#  fli_small %>%
-#    specify(origin ~ season) %>% # alt: response = origin, explanatory = season
[…]

### 2018-03-24 README.Rmd
Add standardized slope (t)

@@
 
-To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first:
+To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first. This version was last updated on `r Sys.Date()`.
 
@@
 
+------------------------------------------------------------------------
+
 We welcome others helping us make this package as user friendly and efficient as possible. Please review
@@
 helping us to write `testthat` tests and help us in building vignettes that show how to (and how NOT to)
-use the package.
+use the package. By participating in this project you agree to abide by its terms.
 
@@
 Other examples are available in the package vignettes.
-
-***
-
-Please note that this project is released with a [Contributor Code of Conduct](https://github.com/andrewpbray/infer/blob/master/CONDUCT.md).
-By participating in this project you agree to abide by its terms.

### 2018-03-24 R/calculate.R

@@ -302,6 +302,17 @@ calc_impl.t <- function(stat, x, order, ...) {
     df_out <- x %>%
       dplyr::summarize(stat = stats::t.test(
         !! attr(x, "response") ~ !! attr(x, "explanatory"))[["statistic"]])
+  }
+    
+  # Standardized slope
+  else if (attr(x, "theory_type") == "Slope with t"){
+    explan_string <- as.character(attr(x, "explanatory"))
+  
+    x %>%
+      dplyr::summarize(stat = summary(
+          stats::lm(!!(attr(x, "response")) ~ !!(attr(x, "explanatory")))
+        )[["coefficients"]][explan_string, "t value"])
+    
     
     # One sample mean (TESTING - not currently working)
   } else if (attr(x, "theory_type") == "One sample t"){

### 2018-03-26 README.Rmd
Show time of most recent push to develop/docs
Update pkgdown

@@
 
-To install the developmental version of `infer`, make sure to install `remotes` first:
+To install the developmental version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this developmental version is at https://infer.netlify.com.
 
@@
 
-To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first. This version was last updated on `r Sys.Date()`.
+To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first. This version was last updated on `r Sys.time()`.
 

### 2018-03-26 docs/articles/flights_examples.R

@@ -9,6 +9,7 @@ library(stringr)
 library(infer)
 set.seed(2017)
 fli_small <- flights %>% 
+  na.omit() %>%
   sample_n(size = 500) %>% 
   mutate(season = case_when(
     month %in% c(10:12, 1:3) ~ "winter",
@@ -19,8 +20,7 @@ fli_small <- flights %>%
     between(hour, 13, 24) ~ "not morning"
   )) %>% 
   select(arr_delay, dep_delay, season, 
-         day_hour, origin, carrier) %>%
-  filter(., complete.cases(.))
+         day_hour, origin, carrier)
 
 ## ------------------------------------------------------------------------
 x_bar <- fli_small %>%

### 2018-03-26 docs/articles/mtcars_examples.R

@@ -4,7 +4,7 @@ knitr::opts_chunk$set(fig.width = 8, fig.height = 5)
 ## ----message=FALSE, warning=FALSE----------------------------------------
 library(infer)
 library(dplyr)
-mtcars <- as.data.frame(mtcars) %>%
+mtcars <- mtcars %>%
   mutate(cyl = factor(cyl),
          vs = factor(vs),
          am = factor(am),

### 2018-03-26 docs/articles/profiles_examples.R

@@ -33,7 +33,7 @@ prof_small %>%
 
 ## ------------------------------------------------------------------------
 prof_small %>%
-  specify(response = sex, success = "m") %>% # alt: sex ~ NULL
+  specify(response = sex, success = "m") %>%
   hypothesize(null = "point", p = c("m" = .65)) %>% 
   generate(reps = 1000, type = "simulate") %>% 
   calculate(stat = "prop") %>% 
@@ -41,7 +41,7 @@ prof_small %>%
 
 ## ------------------------------------------------------------------------
 prof_small %>%
-  specify(sex ~ city) %>% # alt: response = sex, explanatory = city
+  specify(sex ~ city, success = "m") %>%
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
@@ -112,9 +112,9 @@ prof_small %>%
 
 ## ------------------------------------------------------------------------
 prof_small %>%
-  specify(response = sex) %>%
+  specify(response = sex, success = "f") %>%
   generate(reps = 1000, type = "bootstrap") %>%
-  calculate(stat = "prop", success = "f") %>% 
+  calculate(stat = "prop") %>% 
   visualize()
 
 ## ------------------------------------------------------------------------
@@ -126,7 +126,7 @@ prof_small %>%
 
 ## ------------------------------------------------------------------------
 prof_small %>%
-  specify(sex ~ city) %>%
+  specify(sex ~ city, success = "m") %>%
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
   visualize()

### 2018-03-30 inst/doc/chisq_test.Rmd
Add shade_color and fix two-tailed highlighting

---
title: "Chi-squared test example using `nycflights13` `flights` data"
author: "Chester Ismay"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    df_print: kable
vignette: |
  %\VignetteIndexEntry{Chi-squared test flights example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 3) 
```

## Data preparation

```{r message=FALSE, warning=FALSE}
library(nycflights13)
library(dplyr)
library(ggplot2)
library(stringr)
library(infer)
set.seed(2017)
fli_small <- flights %>% 
  na.omit() %>% 
  sample_n(size = 500) %>% 
  mutate(season = case_when(
    month %in% c(10:12, 1:3) ~ "winter",
    month %in% c(4:9) ~ "summer"
  )) %>% 
  mutate(day_hour = case_when(
    between(hour, 1, 12) ~ "morning",
    between(hour, 13, 24) ~ "not morning"
  )) %>% 
  select(arr_delay, dep_delay, season, 
         day_hour, origin, carrier)
```

* Two numeric - `arr_delay`, `dep_delay`
* Two categories 
    - `season` (`"winter"`, `"summer"`), 
    - `day_hour` (`"morning"`, `"not morning"`)
* Three categories - `origin` (`"EWR"`, `"JFK"`, `"LGA"`)
* Sixteen categories - `carrier`

***

# One numerical variable, one categorical (2 levels)

## Calculate observed statistic

Using `chisq_test` in `infer`

```{r}
obs_chisq <- fli_small %>% 
  chisq_test(formula = origin ~ season) %>% 
  dplyr::select(statistic) %>% 
  dplyr::pull()
```

The observed $t$ statistic is `r obs_chisq`.

Or using another shortcut function in `infer`:

```{r}
obs_chisq <- fli_small %>% 
  chisq_stat(formula = origin ~ season)
```

The observed $\chi^2$ statistic is `r obs_chisq`.

## Randomization approach to $\chi^2$-statistic

```{r}
chisq_null_distn <- fli_small %>%
  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "Chisq")
chisq_null_distn %>% visualize(obs_stat = obs_chisq, direction = "greater")
```

## Calculate the randomization-based $p$-value

```{r}
chisq_null_distn %>% 
  dplyr::summarize(p_value = mean(stat >= obs_chisq)) %>% 
  dplyr::pull()
```

## Theoretical distribution

```{r }
fli_small %>%
  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
  hypothesize(null = "independence") %>%
  # calculate(stat = "Chisq") ## Not needed since Chisq is implied based on variable types
  visualize(method = "theoretical", obs_stat = obs_chisq, direction = "right")
```

## Overlay appropriate $\chi^2$ distribution on top of permuted statistics

```{r eval=FALSE}
fli_small %>%
  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "Chisq") %>% 
  visualize(method = "both", obs_stat = obs_chisq, direction = "right")
```

```{r echo=FALSE}
# To use same distribution calculated above
chisq_null_distn %>% 
  visualize(method = "both", obs_stat = obs_chisq, direction = "right")
```

## Compute theoretical p-value

```{r}
fli_small %>% 
  chisq_test(formula = origin ~ season) %>% 
  dplyr::select(p_value) %>% 
  dplyr::pull()
```

### 2018-03-30 inst/doc/profiles_examples.Rmd
Add shade_color and fix two-tailed highlighting

@@
 library(okcupiddata)
-library(stringr)
 library(infer)
+
 set.seed(2017)
@@
   dplyr::mutate(city = dplyr::case_when(
-    str_detect(location, "san fran") ~ "san fran",
-    !str_detect(location, "san fran") ~ "not san fran"
+    stringr::str_detect(location, "san fran") ~ "san fran",
+    !stringr::str_detect(location, "san fran") ~ "not san fran"
   )) %>% 
@@
 ```{r}
+x_bar <- prof_small %>% 
+  dplyr::summarize(mean(age)) %>% 
+  dplyr::pull()
 prof_small %>%
   specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
-  hypothesize(null = "point", mu = 50) %>% 
+  hypothesize(null = "point", mu = 34) %>% 
   generate(reps = 1000, type = "bootstrap") %>% 
   calculate(stat = "mean") %>% 
-  visualize()
+  visualize(obs_stat = x_bar, direction = "both")
 ```
@@
 ```{r}
+x_tilde <- prof_small %>% 
+  dplyr::summarize(median(age)) %>% 
+  dplyr::pull()
 prof_small %>%
   specify(response = age) %>% # alt: age ~ NULL
-  hypothesize(null = "point", med = 55) %>% 
+  hypothesize(null = "point", med = 29) %>% 
   generate(reps = 1000, type = "bootstrap") %>% 
   calculate(stat = "median") %>% 
-  visualize()
+  visualize(obs_stat = x_tilde, direction = "both")
 ```
@@
 ```{r}
+p_hat <- prof_small %>% 
+  dplyr::summarize(mean(sex == "f")) %>% 
+  dplyr::pull()
 prof_small %>%
-  specify(response = sex, success = "m") %>%
-  hypothesize(null = "point", p = c("m" = .65)) %>% 
+  specify(response = sex, success = "f") %>%
+  hypothesize(null = "point", p = c("f" = .35)) %>% 
   generate(reps = 1000, type = "simulate") %>% 
   calculate(stat = "prop") %>% 
-  visualize()
+  visualize(obs_stat = p_hat, direction = "right")
 ```
@@
 ```{r}
+obs_diff <- prof_small %>% 
+  dplyr::group_by(city) %>% 
+  dplyr::summarize(prop = mean(sex == "m")) %>%
+  dplyr::summarize(diff(prop)) %>%
+  dplyr::pull()
 prof_small %>%
@@
   calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
-  visualize()
+  visualize(obs_stat = obs_diff, direction = "both")
 ```
@@
 ```{r}
+Chisq_hat <- chisq.test(table(prof_small$drugs))$stat
 prof_small %>%
@@
   calculate(stat = "Chisq") %>% 
-  visualize()
+  # Only "right" or "greater" as options here
+  visualize(obs_stat = Chisq_hat, direction = "right")
 ```
@@
 ```{r}
+Chisq_hat <- prof_small %>% chisq_stat(formula = drugs ~ status)
 prof_small %>%
@@
 ```{r}
+obs_diff <- prof_small %>% 
+  dplyr::group_by(sex) %>% 
+  dplyr::summarize(mean_age = mean(age)) %>% 
+  dplyr::summarize(diff(mean_age)) %>% 
+  dplyr::pull()
 prof_small %>%
@@
   calculate(stat = "diff in means", order = c("m", "f")) %>% 
-  visualize()
+  visualize(obs_stat = obs_diff, direction = "both")
 ```
@@
 ```{r}
+obs_diff <- prof_small %>% 
+  dplyr::group_by(sex) %>% 
+  dplyr::summarize(median_age = median(age)) %>% 
+  dplyr::summarize(diff(median_age)) %>% 
+  dplyr::pull()
 prof_small %>%
@@
   calculate(stat = "diff in medians", order = c("m", "f")) %>% 
-  visualize()
+  visualize(obs_stat = obs_diff, direction = "two_sided")
 ```
@@
   calculate(stat = "F") %>% 
-  visualize()
+  # Only "right" or "greater" as options here
+  visualize(obs_stat = obs_diff, direction = "greater")
 ```
@@
   calculate(stat = "slope") %>% 
-  visualize()
+  visualize(obs_stat = obs_diff, direction = "right")
 ```

### 2018-03-30 R/visualize.R

@@ -11,6 +11,7 @@
 #' statistic is
 #' @param obs_stat_color a character or hex string specifying the color of
 #'  the observed statistic
+#' @param shade_color a character or hex string specifying the color to shade
 #' @param direction a string specifying in which direction the shading 
 #' should occur. Options are "less", "greater", or "two_sided".
 #' Can also specify "left", "right", or "both".
@@ -56,7 +57,8 @@
 visualize <- function(data, bins = 15, method = "randomization", 
                       dens_color = "black",
                       obs_stat = NULL, 
-                      obs_stat_color = "#00BFC4",
+                      obs_stat_color = "#e51010",#"#00BFC4",
+                      shade_color = "#efb8b8",
                       direction = NULL, ...) {
   
   assertive::assert_is_data.frame(data)
@@ -70,14 +72,16 @@ visualize <- function(data, bins = 15, method = "randomization",
                                           dens_color = dens_color,
                                           obs_stat = obs_stat, 
                                           obs_stat_color = obs_stat_color,
-                                          direction = direction, ...)
+                                          direction = direction, 
+                                          shade_color = shade_color, ...)
     
   } else if(method == "theoretical"){
     infer_plot <- visualize_theoretical(data = data,
                                         dens_color = dens_color,
                                         obs_stat = obs_stat, 
                                         obs_stat_color = obs_stat_color,
-                                        direction = direction, ...)
+                                        direction = direction, 
+                                        shade_color = shade_color, ...)
     
     
   } else { #method == "both"
@@ -85,7 +89,8 @@ visualize <- function(data, bins = 15, method = "randomization",
                                  dens_color = dens_color,
                                  obs_stat = obs_stat, 
                                  obs_stat_color = obs_stat_color,
-                                 direction = direction, ...)
+                                 direction = direction,
+                                 shade_color = shade_color, ...)
     
   }
   
@@ -224,7 +229,7 @@ shade_density_check <- function(data = data,
                                 direction, 
[…]

### 2018-03-30 inst/doc/flights_examples.R

@@ -1,0 +1,256 @@
+## ----include=FALSE-------------------------------------------------------
+knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
+
+## ----message=FALSE, warning=FALSE----------------------------------------
+library(nycflights13)
+library(dplyr)
+library(ggplot2)
+library(stringr)
+library(infer)
+set.seed(2017)
+fli_small <- flights %>% 
+  na.omit() %>%
+  sample_n(size = 500) %>% 
+  mutate(season = case_when(
+    month %in% c(10:12, 1:3) ~ "winter",
+    month %in% c(4:9) ~ "summer"
+  )) %>% 
+  mutate(day_hour = case_when(
+    between(hour, 1, 12) ~ "morning",
+    between(hour, 13, 24) ~ "not morning"
+  )) %>% 
+  select(arr_delay, dep_delay, season, 
+         day_hour, origin, carrier)
+
+## ------------------------------------------------------------------------
+x_bar <- fli_small %>%
+  summarize(mean(dep_delay)) %>%
+  pull()
+null_distn <- fli_small %>%
+  specify(response = dep_delay) %>%
+  hypothesize(null = "point", mu = 10) %>%
+  generate(reps = 1000, type = "bootstrap") %>%
+  calculate(stat = "mean")
+ggplot(data = null_distn, mapping = aes(x = stat)) +
+  geom_density() +
+  geom_vline(xintercept = x_bar, color = "red")
+null_distn %>%
+  summarize(p_value = mean(stat > x_bar) * 2)
+
+## ------------------------------------------------------------------------
+x_tilde <- fli_small %>%
+  summarize(median(dep_delay)) %>%
+  pull()
+null_distn <- fli_small %>%
+  specify(response = dep_delay) %>%
+  hypothesize(null = "point", med = 0) %>% 
+  generate(reps = 1000, type = "bootstrap") %>% 
+  calculate(stat = "median")
+ggplot(null_distn, aes(x = stat)) +
+  geom_bar() +
+  geom_vline(xintercept = x_tilde, color = "red")
+null_distn %>%
+  summarize(p_value = mean(stat < x_tilde) * 2)
+
+## ------------------------------------------------------------------------
+p_hat <- fli_small %>%
+  summarize(mean(day_hour == "morning")) %>%
+  pull()
+null_distn <- fli_small %>%
+  specify(response = day_hour, success = "morning") %>%
[…]

### 2018-03-30 inst/doc/profiles_examples.R

@@ -1,0 +1,169 @@
+## ----include=FALSE-------------------------------------------------------
+knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
+
+## ----message=FALSE, warning=FALSE----------------------------------------
+library(okcupiddata)
+library(infer)
+
+set.seed(2017)
+prof_small <- profiles %>% 
+  na.omit() %>% 
+  dplyr::sample_n(size = 500) %>% 
+  dplyr::mutate(city = dplyr::case_when(
+    stringr::str_detect(location, "san fran") ~ "san fran",
+    !stringr::str_detect(location, "san fran") ~ "not san fran"
+  )) %>% 
+  dplyr::select(age, sex, city, drugs, height, status)
+
+## ------------------------------------------------------------------------
+x_bar <- prof_small %>% 
+  dplyr::summarize(mean(age)) %>% 
+  dplyr::pull()
+prof_small %>%
+  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
+  hypothesize(null = "point", mu = 34) %>% 
+  generate(reps = 1000, type = "bootstrap") %>% 
+  calculate(stat = "mean") %>% 
+  visualize(obs_stat = x_bar, direction = "both")
+
+## ------------------------------------------------------------------------
+x_tilde <- prof_small %>% 
+  dplyr::summarize(median(age)) %>% 
+  dplyr::pull()
+prof_small %>%
+  specify(response = age) %>% # alt: age ~ NULL
+  hypothesize(null = "point", med = 29) %>% 
+  generate(reps = 1000, type = "bootstrap") %>% 
+  calculate(stat = "median") %>% 
+  visualize(obs_stat = x_tilde, direction = "both")
+
+## ------------------------------------------------------------------------
+p_hat <- prof_small %>% 
+  dplyr::summarize(mean(sex == "f")) %>% 
+  dplyr::pull()
+prof_small %>%
+  specify(response = sex, success = "f") %>%
+  hypothesize(null = "point", p = c("f" = .35)) %>% 
+  generate(reps = 1000, type = "simulate") %>% 
+  calculate(stat = "prop") %>% 
+  visualize(obs_stat = p_hat, direction = "right")
+
+## ------------------------------------------------------------------------
+obs_diff <- prof_small %>% 
+  dplyr::group_by(city) %>% 
+  dplyr::summarize(prop = mean(sex == "m")) %>%
[…]

### 2018-03-30 inst/doc/profiles_examples_both_methods.Rmd
Tweak vignettes

@@
 
-The `okcupiddata` is thought by some to be controversial. Its use here is only
+There has been some recent [controversy](https://www.wired.com/2016/05/okcupid-study-reveals-perils-big-data-science/) surrounding data of this sort similar to what is given in the {okcupiddata} package.
+Explicit permission was obtained from OkCupid and usernames were not included in the data set for that package.
+Its use here is only
 to check for a variety of different variable types and levels. It will remain only in this
 "cutting edge" version of the package as we continue to add and test examples.
+
+The `method = "both"` examples here do another randomization instead of using the one
+with `visualize()` set to the default of `method = "randomization"`. This is to show the full
+pipeline for a variety of examples, but more than likely you'll want to do something like the
+following instead in practice.
+
+```{r eval=FALSE}
+null_distn <- prof_small %>%
+  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000, type = "permute") %>%
+  calculate(stat = "t", order = c("m", "f"))
+
+null_distn %>% visualize()
+null_distn %>% visualize(method = "both")
+```
 
@@
 
-```{r eval=FALSE, include=FALSE}
+```{r}
 prof_small %>%
@@
               p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
-#  generate(reps = 1000, type = "simulate") %>%
-#  calculate(stat = "Chisq") %>% 
+  # generate() is not needed since we are not doing randomization
+  # calculate(stat = "Chisq") ## Not needed since z implied based on variable types
   visualize(method = "theoretical")
@@
 
-***
+## Two numerical vars - SLR
 
-## TO DO
+Randomization approach to $t$-statistic
 
-### To Do (slope $t$ stat)
-### To Do (Also overlay appropriate t distn)
-
-<!-- ## Testing -->
-
-Two numerical vars - SLR
-
-```{r eval=FALSE, include=FALSE}
+```{r}
 prof_small %>%
@@
   generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "slope") %>% 
+  calculate(stat = "t") %>% 
   visualize()
@@
 
-### To Do (one mean $t$ stat)
-### To Do (Also overlay appropriate t distn)
+Theoretical distribution
 
-One numerical variable (mean)
+```{r}
+prof_small %>%
+  specify(age ~ height) %>% # alt: response = age, explanatory = height
+  hypothesize(null = "independence") %>%
+  # generate() is not needed since we are not doing randomization
+  # calculate(stat = "t") ## Not needed since z implied based on variable types
+  visualize(method = "theoretical")
+```
 
-**Testing but not working yet**
+Overlay appropriate $t$ distribution on top of permuted t-statistics
 
-```{r eval=FALSE, include=FALSE}
+```{r}
+prof_small %>%
+  specify(age ~ height) %>% # alt: response = age, explanatory = height
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000, type = "permute") %>%
+  calculate(stat = "t") %>% 
+  visualize(method = "both")
+```
+
+# Determining whether or not to implement
+
+Note that all code from here throughout the rest of this vignette is to think about but is not currently implemented
+
+## One numerical variable (mean)
+
+Randomization approach to $t$-statistic (Not implemented)
+
+```{r eval=FALSE}
 prof_small %>%
@@
   visualize()
+```
+
+Theoretical distribution (Implemented)
+
+```{r}
+prof_small %>%
+  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
+  hypothesize(null = "point", mu = 50) %>% 
+#  generate(reps = 1000, type = "bootstrap") %>% 
+#  calculate(stat = "t") %>% 
+  visualize(method = "theoretical")
+```
+
+Overlay appropriate $t$ distribution on top of permuted t-statistics (Not implemented)
+
+```{r eval=FALSE}
+prof_small %>%
+  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
+  hypothesize(null = "point", mu = 50) %>% 
+  generate(reps = 1000, type = "bootstrap") %>% 
+  calculate(stat = "t") %>% 
+  visualize(method = "both")
 ```
@@
 
-```{r eval=FALSE, include=FALSE}
+```{r eval=FALSE}
 prof_small %>%
@@
 
-### Currently testing t-stat
 ### To Do (Also overlay appropriate t distn)

### 2018-03-30 inst/doc/profiles_examples.Rmd
Tweak pkgdown

@@
 
-The `okcupiddata` is thought by some to be controversial. Its use here is only
-to check for a variety of different variable types and levels. It will remain only in this
-"cutting edge" version of the package as we continue to add and test examples.
+There has been some recent [controversy](https://www.wired.com/2016/05/okcupid-study-reveals-perils-big-data-science/) 
+surrounding data of this sort similar to what is given in the {okcupiddata}
+package. Explicit permission was obtained from OkCupid and usernames were not
+included in the data set for that package. Its use here is only
+to check for a variety of different variable types and levels. It will remain 
+only in this "cutting edge" version of the package as we continue to add 
+and test examples.
 
@@
 ```{r}
+F_hat <- anova(
+               aov(formula = age ~ status, data = prof_small)
+               )$`F value`[1]
 prof_small %>%
@@
   # Only "right" or "greater" as options here
-  visualize(obs_stat = obs_diff, direction = "greater")
+  visualize(obs_stat = F_hat, direction = "greater")
 ```
@@
 ```{r}
+slope_hat <- lm(age ~ height, data = prof_small) %>% 
+  broom::tidy() %>% 
+  filter(term == "height") %>% 
+  select(estimate) %>% 
+  pull()
 prof_small %>%
@@
   calculate(stat = "slope") %>% 
-  visualize(obs_stat = obs_diff, direction = "right")
+  visualize(obs_stat = slope_hat, direction = "both")
 ```

### 2018-03-30 inst/doc/chisq_test.Rmd
Tweak pkgdown

@@
   hypothesize(null = "independence") %>%
-  # calculate(stat = "Chisq") ## Not needed since Chisq is implied based on variable types
+  # calculate(stat = "Chisq") ## Not needed since Chisq is implied
   visualize(method = "theoretical", obs_stat = obs_chisq, direction = "right")

### 2018-03-30 inst/doc/profiles_examples_both_methods.Rmd
Tweak pkgdown

@@
   # generate() is not needed since we are not doing randomization
-  # calculate(stat = "Chisq") ## Not needed since Chisq implied based on variable types
+  # calculate(stat = "Chisq") ## Not needed since Chisq implied
   visualize(method = "theoretical")
@@
   # generate() is not needed since we are not doing randomization
-  # calculate(stat = "Chisq") ## Not needed since z implied based on variable types
+  # calculate(stat = "Chisq") ## Not needed since Chisq implied
   visualize(method = "theoretical")
@@
   # generate() is not needed since we are not doing randomization
-  # calculate(stat = "t") ## Not needed since z implied based on variable types
+  # calculate(stat = "t") ## Not needed since t implied based on variable types
   visualize(method = "theoretical")

### 2018-03-30 inst/doc/two_sample_t.Rmd
Tweak pkgdown

@@
 t_null_distn <- fli_small %>%
-  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
+  # alt: response = arr_delay, explanatory = half_year
+  specify(arr_delay ~ half_year) %>%
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "t")
+  calculate(stat = "t", order = c("h1", "h2"))
 t_null_distn %>% visualize(obs_stat = obs_t, direction = "two_sided")
@@
 fli_small %>%
-  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
+  # alt: response = arr_delay, explanatory = half_year
+  specify(arr_delay ~ half_year) %>%
   hypothesize(null = "independence") %>%
-  # calculate(stat = "t") ## Not needed since t is implied based on variable types
+  # calculate(stat = "t") ## Not needed since t is implied
   visualize(method = "theoretical", obs_stat = obs_t, direction = "two_sided")
@@
 fli_small %>%
-  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
+  # alt: response = arr_delay, explanatory = half_year
+  specify(arr_delay ~ half_year) %>%
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "t") %>% 
+  calculate(stat = "t", order = c("h1", "h2")) %>% 
   visualize(method = "both", obs_stat = obs_t, direction = "two_sided")

### 2018-03-30 inst/doc/profiles_examples.R

@@ -123,9 +123,9 @@ prof_small %>%
 ## ------------------------------------------------------------------------
 slope_hat <- lm(age ~ height, data = prof_small) %>% 
   broom::tidy() %>% 
-  filter(term == "height") %>% 
-  select(estimate) %>% 
-  pull()
+  dplyr::filter(term == "height") %>% 
+  dplyr::select(estimate) %>% 
+  dplyr::pull()
 prof_small %>%
   specify(age ~ height) %>% # alt: response = age, explanatory = height
   hypothesize(null = "independence") %>%

### 2018-03-30 inst/doc/profiles_examples_both_methods.R

@@ -134,7 +134,7 @@ prof_small %>%
   specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
   hypothesize(null = "independence") %>%
   # generate() is not needed since we are not doing randomization
-  # calculate(stat = "Chisq") ## Not needed since Chisq implied based on variable types
+  # calculate(stat = "Chisq") ## Not needed since Chisq implied
   visualize(method = "theoretical")
 
 ## ------------------------------------------------------------------------
@@ -160,7 +160,7 @@ prof_small %>%
   hypothesize(null = "point", 
               p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
   # generate() is not needed since we are not doing randomization
-  # calculate(stat = "Chisq") ## Not needed since z implied based on variable types
+  # calculate(stat = "Chisq") ## Not needed since Chisq implied
   visualize(method = "theoretical")
 
 ## ------------------------------------------------------------------------
@@ -185,7 +185,7 @@ prof_small %>%
   specify(age ~ height) %>% # alt: response = age, explanatory = height
   hypothesize(null = "independence") %>%
   # generate() is not needed since we are not doing randomization
-  # calculate(stat = "t") ## Not needed since z implied based on variable types
+  # calculate(stat = "t") ## Not needed since t implied based on variable types
   visualize(method = "theoretical")
 
 ## ------------------------------------------------------------------------

### 2018-03-30 inst/doc/two_sample_t.R

@@ -32,7 +32,8 @@ obs_t <- fli_small %>%
 
 ## ------------------------------------------------------------------------
 t_null_distn <- fli_small %>%
-  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
+  # alt: response = arr_delay, explanatory = half_year
+  specify(arr_delay ~ half_year) %>%
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "t", order = c("h1", "h2"))
@@ -45,14 +46,16 @@ t_null_distn %>%
 
 ## ------------------------------------------------------------------------
 fli_small %>%
-  specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
+  # alt: response = arr_delay, explanatory = half_year
+  specify(arr_delay ~ half_year) %>%
   hypothesize(null = "independence") %>%
-  # calculate(stat = "t") ## Not needed since t is implied based on variable types
+  # calculate(stat = "t") ## Not needed since t is implied
   visualize(method = "theoretical", obs_stat = obs_t, direction = "two_sided")
 
 ## ----eval=FALSE----------------------------------------------------------
 #  fli_small %>%
-#    specify(arr_delay ~ half_year) %>% # alt: response = arr_delay, explanatory = half_year
+#    # alt: response = arr_delay, explanatory = half_year
+#    specify(arr_delay ~ half_year) %>%
 #    hypothesize(null = "independence") %>%
 #    generate(reps = 1000, type = "permute") %>%
 #    calculate(stat = "t", order = c("h1", "h2")) %>%

### 2018-03-30 vignettes/profiles_examples.R

@@ -1,177 +1,0 @@
-## ----include=FALSE-------------------------------------------------------
-knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
-
-## ----message=FALSE, warning=FALSE----------------------------------------
-library(okcupiddata)
-library(infer)
-
-set.seed(2017)
-prof_small <- profiles %>% 
-  na.omit() %>% 
-  dplyr::sample_n(size = 500) %>% 
-  dplyr::mutate(city = dplyr::case_when(
-    stringr::str_detect(location, "san fran") ~ "san fran",
-    !stringr::str_detect(location, "san fran") ~ "not san fran"
-  )) %>% 
-  dplyr::select(age, sex, city, drugs, height, status)
-
-## ------------------------------------------------------------------------
-x_bar <- prof_small %>% 
-  dplyr::summarize(mean(age)) %>% 
-  dplyr::pull()
-prof_small %>%
-  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
-  hypothesize(null = "point", mu = 34) %>% 
-  generate(reps = 1000, type = "bootstrap") %>% 
-  calculate(stat = "mean") %>% 
-  visualize(obs_stat = x_bar, direction = "both")
-
-## ------------------------------------------------------------------------
-x_tilde <- prof_small %>% 
-  dplyr::summarize(median(age)) %>% 
-  dplyr::pull()
-prof_small %>%
-  specify(response = age) %>% # alt: age ~ NULL
-  hypothesize(null = "point", med = 29) %>% 
-  generate(reps = 1000, type = "bootstrap") %>% 
-  calculate(stat = "median") %>% 
-  visualize(obs_stat = x_tilde, direction = "both")
-
-## ------------------------------------------------------------------------
-p_hat <- prof_small %>% 
-  dplyr::summarize(mean(sex == "f")) %>% 
-  dplyr::pull()
-prof_small %>%
-  specify(response = sex, success = "f") %>%
-  hypothesize(null = "point", p = c("f" = .35)) %>% 
-  generate(reps = 1000, type = "simulate") %>% 
-  calculate(stat = "prop") %>% 
-  visualize(obs_stat = p_hat, direction = "right")
-
-## ------------------------------------------------------------------------
-obs_diff <- prof_small %>% 
-  dplyr::group_by(city) %>% 
-  dplyr::summarize(prop = mean(sex == "m")) %>%
[…]

### 2018-03-30 vignettes/profiles_examples_both_methods.R

@@ -1,257 +1,0 @@
-## ----include=FALSE-------------------------------------------------------
-knitr::opts_chunk$set(fig.width = 7, fig.height = 3) 
-
-## ----eval=FALSE----------------------------------------------------------
-#  null_distn <- prof_small %>%
-#    specify(age ~ sex) %>% # alt: response = age, explanatory = sex
-#    hypothesize(null = "independence") %>%
-#    generate(reps = 1000, type = "permute") %>%
-#    calculate(stat = "t", order = c("m", "f"))
-#  
-#  null_distn %>% visualize()
-#  null_distn %>% visualize(method = "both")
-
-## ----message=FALSE, warning=FALSE----------------------------------------
-library(okcupiddata)
-library(stringr)
-library(infer)
-set.seed(2017)
-prof_small <- profiles %>% 
-  na.omit() %>% 
-  dplyr::sample_n(size = 500) %>% 
-  dplyr::mutate(city = dplyr::case_when(
-    str_detect(location, "san fran") ~ "san fran",
-    !str_detect(location, "san fran") ~ "not san fran"
-  )) %>% 
-  dplyr::select(age, sex, city, drugs, height, status)
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "t", order = c("m", "f")) %>% 
-  visualize()
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
-  hypothesize(null = "independence") %>%
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "t") ## Not needed since t implied based on variable types
-  visualize(method = "theoretical")
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "t", order = c("m", "f")) %>% 
-  visualize(method = "both")
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(age ~ status) %>% # alt: response = age, explanatory = status
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "F") %>% 
-  visualize()
-
[…]

### 2018-04-11 inst/doc/profiles_examples_both_methods.Rmd
Update pkgdown and inst

@@
 ---
-title: "Randomization and Traditional Examples using `okcupiddata` `profiles` data"
+title: "Simulation-based and Traditional Examples using `okcupiddata` `profiles` data"
 author: "Chester Ismay"
@@
 
-The `method = "both"` examples here do another randomization instead of using the one
-with `visualize()` set to the default of `method = "randomization"`. This is to show the full
+The `method = "both"` examples here do another simulation-based instead of using the one
+with `visualize()` set to the default of `method = "simulation"`. This is to show the full
 pipeline for a variety of examples, but more than likely you'll want to do something like the
@@
 
-Randomization approach to t-statistic
+Simulation-based approach to t-statistic
 
@@
   hypothesize(null = "independence") %>%
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "t") ## Not needed since t implied based on variable types
+  # generate() is not needed since we are not doing simulation-based
+  calculate(stat = "t") %>% 
   visualize(method = "theoretical")
@@
 
-Randomization approach to F-statistic
+Simulation-based approach to F-statistic
 
@@
   specify(age ~ status) %>% # alt: response = age, explanatory = status
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "F") ## Not needed since F implied based on variable types
   hypothesize(null = "independence") %>%
+  # generate() is not needed since we are not doing simulation-based
+  calculate(stat = "F") %>%
   visualize(method = "theoretical")
@@
 
-Randomization approach to z-statistic
+Simulation-based approach to z-statistic
 
@@
   hypothesize(null = "point", p = c("m" = .65, "f" = .35)) %>% 
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "z") ## Not needed since z implied based on variable types
+  # generate() is not needed since we are not doing simulation-based
+  calculate(stat = "z") %>%
   visualize(method = "theoretical")
@@
   hypothesize(null = "independence") %>% 
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "z") ## Not needed since z implied based on variable types
+  # generate() is not needed since we are not doing simulation-based
+  calculate(stat = "z", order = c("san fran", "not san fran")) %>%
   visualize(method = "theoretical")
@@
 
-Randomization approach to $\chi^2$-statistic
+Simulation-based approach to $\chi^2$-statistic
 
@@
   hypothesize(null = "independence") %>%
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "Chisq") ## Not needed since Chisq implied
+  # generate() is not needed since we are not doing simulation-based
+  calculate(stat = "Chisq") %>%
   visualize(method = "theoretical")
@@
               p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "Chisq") ## Not needed since Chisq implied
+  # generate() is not needed since we are not doing simulation-based
+  calculate(stat = "Chisq") %>%
   visualize(method = "theoretical")
@@
 
-Randomization approach to $t$-statistic
+Simulation-based approach to $t$-statistic
 
@@
   hypothesize(null = "independence") %>%
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "t") ## Not needed since t implied based on variable types
+  # generate() is not needed since we are not doing simulation-based
+  calculate(stat = "t") %>%
   visualize(method = "theoretical")
@@
 
-Randomization approach to $t$-statistic (Not implemented)
+Simulation-based approach to $t$-statistic (Not implemented)
 

### 2018-04-11 inst/doc/flights_examples.R

@@ -90,10 +90,12 @@ ggplot(null_distn, aes(x = stat)) +
   geom_density() +
   geom_vline(xintercept = d_hat, color = "red")
 null_distn %>%
-  summarize(p_value = mean(stat < d_hat) * 2)
+  summarize(p_value = mean(stat < d_hat) * 2) %>%
+  pull()
 
 ## ------------------------------------------------------------------------
-Chisq_hat <- chisq.test(table(fli_small$origin))$stat
+Chisq_hat <- fli_small %>%
+  chisq_stat(formula = origin ~ NULL)
 null_distn <- fli_small %>%
   specify(response = origin) %>%
   hypothesize(null = "point", 
@@ -104,10 +106,12 @@ ggplot(null_distn, aes(x = stat)) +
   geom_density() +
   geom_vline(xintercept = Chisq_hat, color = "red")
 null_distn %>%
-  summarize(p_value = mean(stat > Chisq_hat)) 
+  summarize(p_value = mean(stat > Chisq_hat)) %>%
+  pull()
 
 ## ------------------------------------------------------------------------
-Chisq_hat <- chisq.test(table(fli_small$day_hour, fli_small$origin))$stat
+Chisq_hat <- fli_small %>%
+  chisq_stat(formula = day_hour ~ origin)
 null_distn <- fli_small %>%
   specify(day_hour ~ origin, success = "morning") %>%
   hypothesize(null = "independence") %>% 
@@ -117,7 +121,8 @@ ggplot(null_distn, aes(x = stat)) +
   geom_density() +
   geom_vline(xintercept = Chisq_hat, color = "red")
 null_distn %>%
-  summarize(p_value = mean(stat > Chisq_hat)) 
+  summarize(p_value = mean(stat > Chisq_hat)) %>%
+  pull()
 
 ## ------------------------------------------------------------------------
 d_hat <- fli_small %>% 
@@ -135,7 +140,8 @@ ggplot(null_distn, aes(x = stat)) +
   geom_density() +
   geom_vline(xintercept = d_hat, color = "red")
 null_distn %>%
-  summarize(p_value = mean(stat > d_hat) * 2)   
+  summarize(p_value = mean(stat < d_hat) * 2) %>%
+  pull()
 
 ## ------------------------------------------------------------------------
 d_hat <- fli_small %>% 
@@ -153,7 +159,8 @@ ggplot(null_distn, aes(x = stat)) +
[…]

### 2018-04-11 inst/doc/profiles_examples_both_methods.R

@@ -37,8 +37,8 @@ prof_small %>%
 prof_small %>%
   specify(age ~ sex) %>% # alt: response = age, explanatory = sex
   hypothesize(null = "independence") %>%
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "t") ## Not needed since t implied based on variable types
+  # generate() is not needed since we are not doing simulation-based
+  calculate(stat = "t") %>% 
   visualize(method = "theoretical")
 
 ## ------------------------------------------------------------------------
@@ -60,9 +60,9 @@ prof_small %>%
 ## ------------------------------------------------------------------------
 prof_small %>%
   specify(age ~ status) %>% # alt: response = age, explanatory = status
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "F") ## Not needed since F implied based on variable types
   hypothesize(null = "independence") %>%
+  # generate() is not needed since we are not doing simulation-based
+  calculate(stat = "F") %>%
   visualize(method = "theoretical")
 
 ## ------------------------------------------------------------------------
@@ -85,8 +85,8 @@ prof_small %>%
 prof_small %>%
   specify(response = sex, success = "m") %>%
   hypothesize(null = "point", p = c("m" = .65, "f" = .35)) %>% 
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "z") ## Not needed since z implied based on variable types
+  # generate() is not needed since we are not doing simulation-based
+  calculate(stat = "z") %>%
   visualize(method = "theoretical")
 
 ## ------------------------------------------------------------------------
@@ -109,8 +109,8 @@ prof_small %>%
 prof_small %>%
   specify(sex ~ city, success = "m") %>%
   hypothesize(null = "independence") %>% 
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "z") ## Not needed since z implied based on variable types
+  # generate() is not needed since we are not doing simulation-based
+  calculate(stat = "z", order = c("san fran", "not san fran")) %>%
   visualize(method = "theoretical")
 
 ## ------------------------------------------------------------------------
@@ -133,8 +133,8 @@ prof_small %>%
 prof_small %>%
   specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
   hypothesize(null = "independence") %>%
-  # generate() is not needed since we are not doing randomization
-  # calculate(stat = "Chisq") ## Not needed since Chisq implied
[…]

### 2018-04-11 inst/doc/two_sample_t.Rmd
Update build vignettes

@@
   hypothesize(null = "independence") %>%
-  # calculate(stat = "t") ## Not needed since t is implied
+  # generate() ## Not used for theoretical
+  calculate(stat = "t", order = c("h1", "h2")) %>%
   visualize(method = "theoretical", obs_stat = obs_t, direction = "two_sided")

### 2018-04-11 inst/doc/chisq_test.Rmd

@@
 
-The observed $t$ statistic is `r obs_chisq`.
+The observed $\chi^2$ statistic is `r obs_chisq`.
 
@@
   hypothesize(null = "independence") %>%
-  # calculate(stat = "Chisq") ## Not needed since Chisq is implied
+  # generate() ## Not used for theoretical
+  calculate(stat = "Chisq") %>%
   visualize(method = "theoretical", obs_stat = obs_chisq, direction = "right")

### 2018-04-16 R/visualize.R
Testing specify %>% calculate

@@ -7,7 +7,7 @@
 #' with "both" corresponding to "simulation" and "theoretical"
 #' @param dens_color a character or hex string specifying the color of the
 #'  theoretical density curve
-#' @param obs_stat a numeric value corresponding to what the observed 
+#' @param obs_stat a numeric value or 1x1 data frame corresponding to what the observed 
 #' statistic is
 #' @param obs_stat_color a character or hex string specifying the color of
 #'  the observed statistic
@@ -64,14 +64,22 @@ visualize <- function(data, bins = 15, method = "simulation",
   assertive::assert_is_data.frame(data)
   assertive::assert_is_numeric(bins)
   assertive::assert_is_character(method)
-  if(!is.null(obs_stat))
-    assertive::assert_is_numeric(obs_stat)
+  
+  if(!is.null(obs_stat)){
+    if("data.frame" %in% class(obs_stat)){
+      assertive::assert_is_data.frame(obs_stat)
+      # [[1]] is used in case `stat` is not specified as name of 1x1
+      obs_stat <- obs_stat[[1]]
+    }
+    else{
+      assertive::assert_is_numeric(obs_stat)
+    }
+  }
   assertive::assert_is_character(dens_color)
   assertive::assert_is_character(obs_stat_color)
   assertive::assert_is_character(shade_color)
   if(!is.null(direction))
     assertive::assert_is_character(direction)
-  
   
   if(!is.null(direction) && is.null(obs_stat))
     stop("Shading requires observed statistic `obs_stat` value to be given.")
@@ -86,6 +94,7 @@ visualize <- function(data, bins = 15, method = "simulation",
                                           shade_color = shade_color, ...)
     
   } else if(method == "theoretical"){
+    
     infer_plot <- visualize_theoretical(data = data,
                                         dens_color = dens_color,
                                         obs_stat = obs_stat, 
@@ -118,9 +127,9 @@ visualize <- function(data, bins = 15, method = "simulation",
     )
   }
   
-  if(!is.null(obs_stat) && !is.null(direction)){
+  if(!is.null(obs_stat)){#&& !is.null(direction)
     infer_plot <- infer_plot +
-      geom_vline(xintercept = obs_stat, size = 2, color = obs_stat_color)
+      geom_vline(xintercept = obs_stat, size = 2, color = obs_stat_color, ...)
   }
   
   infer_plot
@@ -268,12 +277,12 @@ shade_density_check <- function(data = data,
[…]

### 2018-04-17 inst/doc/two_sample_t.R
Add back in okcupiddata examples

@@ -1,75 +1,0 @@
-## ----include=FALSE-------------------------------------------------------
-knitr::opts_chunk$set(fig.width = 8, fig.height = 3) 
-
-## ----message=FALSE, warning=FALSE----------------------------------------
-library(nycflights13)
-library(dplyr)
-library(stringr)
-library(infer)
-set.seed(2017)
-fli_small <- flights %>% 
-  sample_n(size = 500) %>% 
-  mutate(half_year = case_when(
-    between(month, 1, 6) ~ "h1",
-    between(month, 7, 12) ~ "h2"
-  )) %>% 
-  mutate(day_hour = case_when(
-    between(hour, 1, 12) ~ "morning",
-    between(hour, 13, 24) ~ "not morning"
-  )) %>% 
-  select(arr_delay, dep_delay, half_year, 
-         day_hour, origin, carrier)
-
-## ------------------------------------------------------------------------
-obs_t <- fli_small %>% 
-  t_test(formula = arr_delay ~ half_year) %>% 
-  dplyr::select(statistic) %>% 
-  dplyr::pull()
-
-## ------------------------------------------------------------------------
-obs_t <- fli_small %>% 
-  t_stat(formula = arr_delay ~ half_year)
-
-## ------------------------------------------------------------------------
-t_null_distn <- fli_small %>%
-  # alt: response = arr_delay, explanatory = half_year
-  specify(arr_delay ~ half_year) %>%
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "t", order = c("h1", "h2"))
-t_null_distn %>% visualize(obs_stat = obs_t, direction = "two_sided")
-
-## ------------------------------------------------------------------------
-t_null_distn %>% 
-  dplyr::summarize(p_value = mean(abs(stat) >= obs_t)) %>% 
-  dplyr::pull()
-
-## ------------------------------------------------------------------------
-fli_small %>%
-  # alt: response = arr_delay, explanatory = half_year
-  specify(arr_delay ~ half_year) %>%
-  hypothesize(null = "independence") %>%
-  # generate() ## Not used for theoretical
-  calculate(stat = "t", order = c("h1", "h2")) %>%
-  visualize(method = "theoretical", obs_stat = obs_t, direction = "two_sided")
-
-## ----eval=FALSE----------------------------------------------------------
-#  fli_small %>%
-#    # alt: response = arr_delay, explanatory = half_year
[…]

### 2018-05-05 tests/testthat/test-wrappers.R
Update pkgdown and vignettes

@@ -31,6 +31,17 @@ test_that("chisq_test works", {
 })
 
 test_that("_stat functions work", {
+  # Missing `success`
+  # Test of independence
   expect_silent(iris3 %>% chisq_stat(Sepal.Length.Group ~ Species))
+  another_way <- iris3 %>%
+    chisq_test(Sepal.Length.Group ~ Species) %>%
+    dplyr::select(statistic)
+  obs_stat_way <- iris3 %>% 
+    chisq_stat(Sepal.Length.Group ~ Species, success = ">5")
+  expect_equivalent(another_way, obs_stat_way)
   expect_silent(iris2 %>% t_stat(Sepal.Width ~ Species))
+  
+  # Goodness of Fit
+
 })

### 2018-05-11 README.Rmd
Add netlify link
Tweak header on pkgdown site

@@
 
-To install the developmental version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this developmental version is at https://infer.netlify.com.
+To install the developmental version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this developmental version is at <https://infer.netlify.com>.
 
@@
 our [contributing](https://github.com/andrewpbray/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
-helping us to write `testthat` tests and help us in building vignettes that show how to (and how NOT to)
+helping us to write `testthat` tests and in building vignettes that show how to (and how NOT to)
 use the package. By participating in this project you agree to abide by its terms.

### 2018-05-11 R/calculate.R

@@ -331,9 +331,7 @@ calc_impl.z <- function(stat, x, order, ...) {
   } else
     # One sample proportion
     if (attr(x, "theory_type") == "One sample prop z"){
- #     if(!is.null(attr(x, "params"))){
         # When `hypothesize()` has been called
-        
         success <- attr(x, "success")
         
         p0 <- attr(x, "params")[1]
@@ -350,9 +348,9 @@ calc_impl.z <- function(stat, x, order, ...) {
           ) / sqrt( (p0 * (1 - p0)) / num_rows))
         
         df_out
-#      } else
-#        # Straight from `specify()`
-        
+
+        # Straight from `specify()` doesn't make sense
+        # since standardizing requires a hypothesized value
     }
 }
 

### 2018-05-13 docs/articles/profiles_examples.R
Update pkgdown and vignettes

@@ -1,140 +1,0 @@
-## ----include=FALSE-------------------------------------------------------
-knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
-
-## ----message=FALSE, warning=FALSE----------------------------------------
-library(okcupiddata)
-library(stringr)
-library(infer)
-set.seed(2017)
-prof_small <- profiles %>% 
-  na.omit() %>% 
-  dplyr::sample_n(size = 500) %>% 
-  dplyr::mutate(city = dplyr::case_when(
-    str_detect(location, "san fran") ~ "san fran",
-    !str_detect(location, "san fran") ~ "not san fran"
-  )) %>% 
-  dplyr::select(age, sex, city, drugs, height, status)
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
-  hypothesize(null = "point", mu = 50) %>% 
-  generate(reps = 1000, type = "bootstrap") %>% 
-  calculate(stat = "mean") %>% 
-  visualize()
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(response = age) %>% # alt: age ~ NULL
-  hypothesize(null = "point", med = 55) %>% 
-  generate(reps = 1000, type = "bootstrap") %>% 
-  calculate(stat = "median") %>% 
-  visualize()
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(response = sex, success = "m") %>%
-  hypothesize(null = "point", p = c("m" = .65)) %>% 
-  generate(reps = 1000, type = "simulate") %>% 
-  calculate(stat = "prop") %>% 
-  visualize()
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(sex ~ city, success = "m") %>%
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
-  calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
-  visualize()
-
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(drugs ~ NULL) %>% # alt: response = drugs
-  hypothesize(null = "point", 
-              p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
-  generate(reps = 1000, type = "simulate") %>%
-  calculate(stat = "Chisq") %>% 
-  visualize()
-
-## ------------------------------------------------------------------------
-prof_small %>%
[…]

### 2018-05-13 inst/doc/chisq_test.Rmd
Update vignettes

@@
 ```
+
+**Note**: The `type` argument in `generate()` is automatically filled based on the entries for `specify()` and
+`hypothesize()`. It can be removed throughout the examples that follow. It is left in to reiterate the type of generation process being performed.
 
@@
 chisq_null_distn %>% 
-  dplyr::summarize(p_value = mean(stat >= obs_chisq)) %>% 
+  dplyr::summarize(p_value = mean(stat >= pull(obs_chisq))) %>% 
   dplyr::pull()
@@
 fli_small %>%
-  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
+  specify(origin ~ season) %>% 
   hypothesize(null = "independence") %>%
@@
 fli_small %>%
-  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
+  specify(origin ~ season) %>%  %>% # alt: response = origin, explanatory = season
   hypothesize(null = "independence") %>%

### 2018-05-13 inst/doc/flights_examples.Rmd
Update vignettes

@@
 title: "Randomization Examples using `nycflights13` `flights` data"
-author: "Chester Ismay and Andrew bray"
+author: "Chester Ismay and Andrew Bray"
 date: "2018-01-05"
@@
 ---
+
+**Note**: The `type` argument in `generate()` is automatically filled based on the entries for `specify()` and
+`hypothesize()`. It can be removed throughout the examples that follow. It is left in to reiterate the type of generation process being performed.
 
@@
 fli_small <- flights %>% 
+  na.omit() %>%
   sample_n(size = 500) %>% 
@@
   select(arr_delay, dep_delay, season, 
-         day_hour, origin, carrier) %>%
-  filter(., complete.cases(.))
+         day_hour, origin, carrier)
 ```
@@
   pull()
+```
+
+```{r}
 null_distn <- fli_small %>%
@@
 null_distn %>%
-  summarize(p_value = mean(stat > x_bar) * 2)
+  summarize(p_value = mean(stat >= x_bar) * 2)
 ```
@@
   specify(response = dep_delay) %>%
-  hypothesize(null = "point", med = 0) %>% 
+  hypothesize(null = "point", med = -1) %>% 
   generate(reps = 1000, type = "bootstrap") %>% 
@@
 null_distn %>%
-  summarize(p_value = mean(stat < x_tilde) * 2)
+  summarize(p_value = mean(stat <= x_tilde) * 2)
 ```
@@
 null_distn %>%
-  summarize(p_value = mean(stat < p_hat) * 2)
+  summarize(p_value = mean(stat <= p_hat) * 2)
 ```
@@
   generate(reps = 1000, type = "permute") %>% 
-  calculate(stat = "diff in props", order = c("summer", "winter"))
+  calculate(stat = "diff in props", order = c("winter", "summer"))
 ggplot(null_distn, aes(x = stat)) +
@@
 null_distn %>%
-  summarize(p_value = mean(stat < d_hat) * 2)
+  summarize(p_value = mean(stat <= d_hat) * 2) %>%
+  pull()
 ```
@@
 ```{r}
-Chisq_hat <- chisq.test(table(fli_small$origin))$stat
+Chisq_hat <- fli_small %>%
+  chisq_stat(formula = origin ~ NULL)
 null_distn <- fli_small %>%
@@
   geom_density() +
-  geom_vline(xintercept = Chisq_hat, color = "red")
+  geom_vline(xintercept = pull(Chisq_hat), color = "red")
 null_distn %>%
-  summarize(p_value = mean(stat > Chisq_hat)) 
+  summarize(p_value = mean(stat >= pull(Chisq_hat))) %>%
+  pull()
 ```
@@
 ```{r}
-Chisq_hat <- chisq.test(table(fli_small$day_hour, fli_small$origin))$stat
+Chisq_hat <- fli_small %>%
+  chisq_stat(formula = day_hour ~ origin)
 null_distn <- fli_small %>%
@@
   summarize(mean_stat = mean(dep_delay)) %>% 
-  summarize(diff(mean_stat)) %>% 
+  # Since summer - winter
+  summarize(-diff(mean_stat)) %>% 
   pull()
@@
 null_distn %>%
-  summarize(p_value = mean(stat > d_hat) * 2)   
+  summarize(p_value = mean(stat <= d_hat) * 2) %>%
+  pull()
 ```
@@
   summarize(median_stat = median(dep_delay)) %>% 
-  summarize(diff(median_stat)) %>% 
+  # Since summer - winter
+  summarize(-diff(median_stat)) %>% 
   pull()
@@
 null_distn %>%
-  summarize(p_value = mean(stat > d_hat) * 2)    
+  summarize(p_value = mean(stat >= d_hat) * 2) %>%
+  pull()
 ```
@@
 null_distn %>% 
-  summarize(p_value = mean(stat > F_hat))
+  summarize(p_value = mean(stat >= F_hat)) %>%
+  pull()
 ```
@@
 null_distn %>% 
-  summarize(p_value = mean(stat > slope_hat) * 2)   
+  summarize(p_value = mean(stat >= slope_hat) * 2) %>%
+  pull()
 ```
@@
   summarize(mean_stat = mean(arr_delay)) %>% 
-  summarize(diff(mean_stat)) %>% 
+  # Since summer - winter
+  summarize(-diff(mean_stat)) %>% 
   pull()
@@
   summarize(prop = mean(day_hour == "morning")) %>%
-  summarize(diff(prop)) %>%
+  # Since summer - winter
+  summarize(-diff(prop)) %>%
   pull()

### 2018-05-13 inst/doc/mtcars_examples.Rmd
Update vignettes

@@
 title: "Examples using `mtcars` data"
-author: "Chester Ismay and Andrew bray"
+author: "Chester Ismay and Andrew Bray"
 date: "2018-01-05"
@@
 
+**Note**: The `type` argument in `generate()` is automatically filled based on the entries for `specify()` and
+`hypothesize()`. It can be removed throughout the examples that follow. It is left in to reiterate the type of generation process being performed.
+
 ## Data preparation
@@
 library(dplyr)
-mtcars <- as.data.frame(mtcars) %>%
+mtcars <- mtcars %>%
   mutate(cyl = factor(cyl),
@@
   calculate(stat = "median")
-```
-
-One numerical variable (standard deviation)
-
-```{r}
-mtcars %>%
-  specify(response = mpg) %>% # formula alt: mpg ~ NULL
-  hypothesize(null = "point", sigma = 5) %>% 
-  generate(reps = 100, type = "bootstrap") %>% 
-  calculate(stat = "sd")
 ```
@@
 
+One numerical variable (standard deviation)
+
+**Not currently implemented**
+
+```{r eval=FALSE}
+mtcars %>%
+  specify(response = mpg) %>% # formula alt: mpg ~ NULL
+  hypothesize(null = "point", sigma = 5) %>% 
+  generate(reps = 100, type = "bootstrap") %>% 
+  calculate(stat = "sd")
+```
+
 ### Confidence intervals

### 2018-05-13 inst/doc/profiles_examples.Rmd
Update vignettes

--- 2018-03-08 inst/doc/profiles_examples.Rmd
@@
 library(okcupiddata)
-library(stringr)
+#remotes::install_github("andrewpbray/infer", ref = "develop")
 library(infer)
+
 set.seed(2017)
@@
 ```{r}
+x_bar <- prof_small %>% 
+  dplyr::summarize(mean(age)) %>% 
+  dplyr::pull()
 prof_small %>%
   specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
-  hypothesize(null = "point", mu = 50) %>% 
-  generate(reps = 1000, type = "bootstrap") %>% 
+  hypothesize(null = "point", mu = 34) %>% 
+  generate(reps = 1000) %>% 
   calculate(stat = "mean") %>% 
-  visualize()
+  visualize(obs_stat = x_bar, direction = "both")
 ```
@@
 ```{r}
+x_tilde <- prof_small %>% 
+  dplyr::summarize(median(age)) %>% 
+  dplyr::pull()
 prof_small %>%
   specify(response = age) %>% # alt: age ~ NULL
-  hypothesize(null = "point", med = 55) %>% 
-  generate(reps = 1000, type = "bootstrap") %>% 
+  hypothesize(null = "point", med = 29) %>% 
+  generate(reps = 1000) %>% 
   calculate(stat = "median") %>% 
-  visualize()
+  visualize(obs_stat = x_tilde, direction = "both")
 ```
@@
 ```{r}
+p_hat <- prof_small %>% 
+  dplyr::summarize(mean(sex == "f")) %>% 
+  dplyr::pull()
 prof_small %>%
-  specify(response = sex, success = "m") %>%
-  hypothesize(null = "point", p = c("m" = .65)) %>% 
-  generate(reps = 1000, type = "simulate") %>% 
+  specify(response = sex, success = "f") %>%
+  hypothesize(null = "point", p = c("f" = .35)) %>% 
+  generate(reps = 1000) %>% 
   calculate(stat = "prop") %>% 
-  visualize()
+  visualize(obs_stat = p_hat, direction = "right")
 ```
@@
   hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
+  generate(reps = 1000) %>%
   calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
-  visualize()
+  visualize(obs_stat = obs_diff, direction = "both")
 ```
@@
               p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
-  generate(reps = 1000, type = "simulate") %>%
+  generate(reps = 1000) %>%
   calculate(stat = "Chisq") %>% 
-  visualize()
+  # Only "right" or "greater" as options here
+  visualize(obs_stat = Chisq_hat, direction = "right")
 ```
@@
   hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
+  generate(reps = 1000) %>%
   calculate(stat = "Chisq") %>% 
-  visualize()
+  # Only "right" or "greater" as options here
+  visualize(obs_stat = Chisq_hat, direction = "right")
 ```
@@
   hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
+  generate(reps = 1000) %>%
   calculate(stat = "diff in means", order = c("m", "f")) %>% 
-  visualize()
+  visualize(obs_stat = obs_diff, direction = "both")
 ```
@@
   hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
+  generate(reps = 1000) %>%
   calculate(stat = "diff in medians", order = c("m", "f")) %>% 
-  visualize()
+  visualize(obs_stat = obs_diff, direction = "two_sided")
 ```
@@
   hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
+  generate(reps = 1000) %>%
   calculate(stat = "F") %>% 
-  visualize()
+  # Only "right" or "greater" as options here
+  visualize(obs_stat = F_hat, direction = "greater")
 ```
@@
 ```{r}
+slope_hat <- lm(age ~ height, data = prof_small) %>% 
+  broom::tidy() %>% 
+  dplyr::filter(term == "height") %>% 
+  dplyr::select(estimate) %>% 
+  dplyr::pull()
 prof_small %>%
@@
   hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
+  generate(reps = 1000) %>%
   calculate(stat = "slope") %>% 
-  visualize()
+  visualize(obs_stat = slope_hat, direction = "both")
 ```
@@
 ## Confidence intervals
+
+### Confidence interval shading is not implemented yet
 
@@
   specify(response = age) %>%
-  generate(reps = 1000, type = "bootstrap") %>%
+  generate(reps = 1000) %>%
   calculate(stat = "mean") %>% 
@@
   specify(response = age) %>%
-  generate(reps = 1000, type = "bootstrap") %>%
+  generate(reps = 1000) %>%
   calculate(stat = "median") %>% 
@@
   specify(response = sex, success = "f") %>%
-  generate(reps = 1000, type = "bootstrap") %>%
+  generate(reps = 1000) %>%
   calculate(stat = "prop") %>% 
@@
   specify(age ~ sex) %>%
-  generate(reps = 1000, type = "bootstrap") %>%
+  generate(reps = 1000) %>%
   calculate(stat = "diff in means", order = c("m", "f")) %>% 
@@
   specify(sex ~ city, success = "m") %>%
-  generate(reps = 1000, type = "bootstrap") %>%
+  generate(reps = 1000) %>%
   calculate(stat = "diff in props", order = c("san fran", "not san fran")) %>% 
@@
   specify(age ~ height) %>% 
-  generate(reps = 1000, type = "bootstrap") %>%
+  generate(reps = 1000) %>%
   calculate(stat = "slope") %>% 

### 2018-05-13 inst/doc/two_sample_t.Rmd
Update vignettes

@@
 obs_t <- fli_small %>% 
-  t_test(formula = arr_delay ~ half_year) %>% 
+  t_test(formula = arr_delay ~ half_year, alternative = "two_sided",
+         order = c("h1", "h2")) %>% 
   dplyr::select(statistic) %>% 
@@
 obs_t <- fli_small %>% 
-  t_stat(formula = arr_delay ~ half_year)
+  t_stat(formula = arr_delay ~ half_year, order = c("h1", "h2"))
 ```
@@
 t_null_distn %>% 
-  dplyr::summarize(p_value = mean(abs(stat) >= obs_t)) %>% 
+  dplyr::summarize(p_value = mean(abs(stat) >= pull(obs_t))) %>% 
   dplyr::pull()
@@
 fli_small %>% 
-  t_test(formula = arr_delay ~ half_year) %>% 
+  t_test(formula = arr_delay ~ half_year,
+         alternative = "two_sided",
+         order = c("h1", "h2")) %>% 
   dplyr::select(p_value) %>% 

### 2018-05-13 inst/doc/chisq_test.R

@@ -1,0 +1,74 @@
+## ----include=FALSE-------------------------------------------------------
+knitr::opts_chunk$set(fig.width = 8, fig.height = 3) 
+
+## ----message=FALSE, warning=FALSE----------------------------------------
+library(nycflights13)
+library(dplyr)
+library(ggplot2)
+library(stringr)
+library(infer)
+set.seed(2017)
+fli_small <- flights %>% 
+  na.omit() %>% 
+  sample_n(size = 500) %>% 
+  mutate(season = case_when(
+    month %in% c(10:12, 1:3) ~ "winter",
+    month %in% c(4:9) ~ "summer"
+  )) %>% 
+  mutate(day_hour = case_when(
+    between(hour, 1, 12) ~ "morning",
+    between(hour, 13, 24) ~ "not morning"
+  )) %>% 
+  select(arr_delay, dep_delay, season, 
+         day_hour, origin, carrier)
+
+## ------------------------------------------------------------------------
+obs_chisq <- fli_small %>% 
+  chisq_test(formula = origin ~ season) %>% 
+  dplyr::select(statistic) %>% 
+  dplyr::pull()
+
+## ------------------------------------------------------------------------
+obs_chisq <- fli_small %>% 
+  chisq_stat(formula = origin ~ season)
+
+## ------------------------------------------------------------------------
+chisq_null_distn <- fli_small %>%
+  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000, type = "permute") %>%
+  calculate(stat = "Chisq")
+chisq_null_distn %>% visualize(obs_stat = obs_chisq, direction = "greater")
+
+## ------------------------------------------------------------------------
+chisq_null_distn %>% 
+  dplyr::summarize(p_value = mean(stat >= pull(obs_chisq))) %>% 
+  dplyr::pull()
+
+## ------------------------------------------------------------------------
+fli_small %>%
+  specify(origin ~ season) %>% 
+  hypothesize(null = "independence") %>%
+  # generate() ## Not used for theoretical
+  calculate(stat = "Chisq") %>%
+  visualize(method = "theoretical", obs_stat = obs_chisq, direction = "right")
+
+## ----eval=FALSE----------------------------------------------------------
+#  fli_small %>%
+#    specify(origin ~ season) %>%  %>% # alt: response = origin, explanatory = season
+#    hypothesize(null = "independence") %>%
[…]

### 2018-05-13 inst/doc/mtcars_examples.R

@@ -1,0 +1,134 @@
+## ----include=FALSE-------------------------------------------------------
+knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
+
+## ----message=FALSE, warning=FALSE----------------------------------------
+library(infer)
+library(dplyr)
+mtcars <- mtcars %>%
+  mutate(cyl = factor(cyl),
+         vs = factor(vs),
+         am = factor(am),
+         gear = factor(gear),
+         carb = factor(carb))
+# For reproducibility         
+set.seed(2018)         
+
+## ------------------------------------------------------------------------
+mtcars %>%
+  specify(response = mpg) %>% # formula alt: mpg ~ NULL
+  hypothesize(null = "point", mu = 25) %>% 
+  generate(reps = 100, type = "bootstrap") %>% 
+  calculate(stat = "mean")
+
+## ------------------------------------------------------------------------
+mtcars %>%
+  specify(response = mpg) %>% # formula alt: mpg ~ NULL
+  hypothesize(null = "point", med = 26) %>% 
+  generate(reps = 100, type = "bootstrap") %>% 
+  calculate(stat = "median")
+
+## ------------------------------------------------------------------------
+mtcars %>%
+  specify(response = am, success = "1") %>% # formula alt: am ~ NULL
+  hypothesize(null = "point", p = .25) %>% 
+  generate(reps = 100, type = "simulate") %>% 
+  calculate(stat = "prop")
+
+## ------------------------------------------------------------------------
+mtcars %>%
+  specify(am ~ vs, success = "1") %>% # alt: response = am, explanatory = vs
+  hypothesize(null = "independence") %>%
+  generate(reps = 100, type = "permute") %>%
+  calculate(stat = "diff in props", order = c("0", "1"))
+
+## ------------------------------------------------------------------------
+mtcars %>%
+  specify(cyl ~ NULL) %>% # alt: response = cyl
+  hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25)) %>%
+  generate(reps = 100, type = "simulate") %>%
+  calculate(stat = "Chisq")
+
+## ----warning = FALSE-----------------------------------------------------
+mtcars %>%
+  specify(cyl ~ am) %>% # alt: response = cyl, explanatory = am
+  hypothesize(null = "independence") %>%
+  generate(reps = 100, type = "permute") %>%
+  calculate(stat = "Chisq")
+
+## ------------------------------------------------------------------------
[…]

### 2018-05-13 inst/doc/profiles_examples.R

@@ -1,0 +1,178 @@
+## ----include=FALSE-------------------------------------------------------
+knitr::opts_chunk$set(fig.width = 8, fig.height = 5) 
+
+## ----message=FALSE, warning=FALSE----------------------------------------
+library(okcupiddata)
+#remotes::install_github("andrewpbray/infer", ref = "develop")
+library(infer)
+
+set.seed(2017)
+prof_small <- profiles %>% 
+  na.omit() %>% 
+  dplyr::sample_n(size = 500) %>% 
+  dplyr::mutate(city = dplyr::case_when(
+    stringr::str_detect(location, "san fran") ~ "san fran",
+    !stringr::str_detect(location, "san fran") ~ "not san fran"
+  )) %>% 
+  dplyr::select(age, sex, city, drugs, height, status)
+
+## ------------------------------------------------------------------------
+x_bar <- prof_small %>% 
+  dplyr::summarize(mean(age)) %>% 
+  dplyr::pull()
+prof_small %>%
+  specify(response = age) %>% # alt: age ~ NULL (or age ~ 1)
+  hypothesize(null = "point", mu = 34) %>% 
+  generate(reps = 1000) %>% 
+  calculate(stat = "mean") %>% 
+  visualize(obs_stat = x_bar, direction = "both")
+
+## ------------------------------------------------------------------------
+x_tilde <- prof_small %>% 
+  dplyr::summarize(median(age)) %>% 
+  dplyr::pull()
+prof_small %>%
+  specify(response = age) %>% # alt: age ~ NULL
+  hypothesize(null = "point", med = 29) %>% 
+  generate(reps = 1000) %>% 
+  calculate(stat = "median") %>% 
+  visualize(obs_stat = x_tilde, direction = "both")
+
+## ------------------------------------------------------------------------
+p_hat <- prof_small %>% 
+  dplyr::summarize(mean(sex == "f")) %>% 
+  dplyr::pull()
+prof_small %>%
+  specify(response = sex, success = "f") %>%
+  hypothesize(null = "point", p = c("f" = .35)) %>% 
+  generate(reps = 1000) %>% 
+  calculate(stat = "prop") %>% 
+  visualize(obs_stat = p_hat, direction = "right")
+
+## ------------------------------------------------------------------------
+obs_diff <- prof_small %>% 
+  dplyr::group_by(city) %>% 
+  dplyr::summarize(prop = mean(sex == "m")) %>%
[…]

### 2018-05-13 inst/doc/profiles_examples_both_methods.R

@@ -1,0 +1,258 @@
+## ----include=FALSE-------------------------------------------------------
+knitr::opts_chunk$set(fig.width = 7, fig.height = 3) 
+
+## ----eval=FALSE----------------------------------------------------------
+#  null_distn <- prof_small %>%
+#    specify(age ~ sex) %>% # alt: response = age, explanatory = sex
+#    hypothesize(null = "independence") %>%
+#    generate(reps = 1000) %>%
+#    calculate(stat = "t", order = c("m", "f"))
+#  
+#  null_distn %>% visualize()
+#  null_distn %>% visualize(method = "both")
+
+## ----message=FALSE, warning=FALSE----------------------------------------
+library(okcupiddata)
+library(stringr)
+#remotes::install_github("andrewpbray/infer", ref = "develop")
+library(infer)
+set.seed(2017)
+prof_small <- profiles %>% 
+  na.omit() %>% 
+  dplyr::sample_n(size = 500) %>% 
+  dplyr::mutate(city = dplyr::case_when(
+    str_detect(location, "san fran") ~ "san fran",
+    !str_detect(location, "san fran") ~ "not san fran"
+  )) %>% 
+  dplyr::select(age, sex, city, drugs, height, status)
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000) %>%
+  calculate(stat = "t", order = c("m", "f")) %>% 
+  visualize()
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
+  hypothesize(null = "independence") %>%
+  # generate() is not needed since we are not doing simulation-based
+  calculate(stat = "t") %>% 
+  visualize(method = "theoretical")
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000) %>%
+  calculate(stat = "t", order = c("m", "f")) %>% 
+  visualize(method = "both")
+
+## ------------------------------------------------------------------------
+prof_small %>%
+  specify(age ~ status) %>% # alt: response = age, explanatory = status
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000) %>%
+  calculate(stat = "F") %>% 
+  visualize()
+
[…]

### 2018-06-13 inst/doc/chisq_test.Rmd
Update pkgdown and vignettes

@@
 
-Using `chisq_test` in `infer`
+The recommended approach is to use `specify() %>% calculate()`:
+
+```{r}
+obs_chisq <- fli_small %>%
+  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
+  calculate(stat = "Chisq")
+```
+
+The observed $\chi^2$ statistic is `r obs_chisq`.
+
+Or using `chisq_test` in `infer`
 
@@
   chisq_test(formula = origin ~ season) %>% 
-  dplyr::select(statistic) %>% 
-  dplyr::pull()
+  dplyr::select(statistic)
 ```
 
-The observed $\chi^2$ statistic is `r obs_chisq`.
+Again, the observed $\chi^2$ statistic is `r obs_chisq`.
 
@@
 
-The observed $\chi^2$ statistic is `r obs_chisq`.
+Lastly, the observed $\chi^2$ statistic is `r obs_chisq`.
 
@@
 chisq_null_distn %>% 
-  dplyr::summarize(p_value = mean(stat >= pull(obs_chisq))) %>% 
-  dplyr::pull()
+  p_value(obs_stat = obs_chisq, direction = "greater")
 ```

### 2018-06-13 inst/doc/two_sample_t.Rmd
Update pkgdown and vignettes

@@
 
-Using `t_test` in `infer`
+The recommended approach is to use `specify() %>% calculate()`:
+
+```{r}
+obs_t <- fli_small %>%
+  specify(arr_delay ~ half_year) %>%
+  calculate(stat = "t", order = c("h1", "h2"))
+```
+
+The observed $\chi^2$ statistic is `r obs_chisq`.
+
+Or using `t_test` in `infer`
 
@@
 t_null_distn %>% 
-  dplyr::summarize(p_value = mean(abs(stat) >= pull(obs_t))) %>% 
-  dplyr::pull()
+  p_value(obs_stat = obs_t, direction = "greater")
 ```

### 2018-06-13 inst/doc/profiles_examples_both_methods.R

@@ -39,7 +39,7 @@ prof_small %>%
   specify(age ~ sex) %>% # alt: response = age, explanatory = sex
   hypothesize(null = "independence") %>%
   # generate() is not needed since we are not doing simulation-based
-  calculate(stat = "t") %>% 
+  calculate(stat = "t", order = c("f", "m")) %>% 
   visualize(method = "theoretical")
 
 ## ------------------------------------------------------------------------
@@ -173,29 +173,32 @@ prof_small %>%
   calculate(stat = "Chisq") %>% 
   visualize(method = "both")
 
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(age ~ height) %>% # alt: response = age, explanatory = height
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000) %>%
-  calculate(stat = "t") %>% 
-  visualize()
+## ----echo=FALSE, eval=FALSE----------------------------------------------
+#  # Simulation-based approach to $t$-statistic
+#  prof_small %>%
+#    specify(age ~ height) %>% # alt: response = age, explanatory = height
+#    hypothesize(null = "independence") %>%
+#    generate(reps = 1000) %>%
+#    calculate(stat = "t") %>%
+#    visualize()
 
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(age ~ height) %>% # alt: response = age, explanatory = height
-  hypothesize(null = "independence") %>%
-  # generate() is not needed since we are not doing simulation-based
-  calculate(stat = "t") %>%
-  visualize(method = "theoretical")
+## ----echo=FALSE, eval=FALSE----------------------------------------------
+#  #Theoretical distribution
+#  prof_small %>%
+#    specify(age ~ height) %>% # alt: response = age, explanatory = height
+#    hypothesize(null = "independence") %>%
+#    # generate() is not needed since we are not doing simulation-based
+#    calculate(stat = "t") %>%
+#    visualize(method = "theoretical")
 
-## ------------------------------------------------------------------------
-prof_small %>%
-  specify(age ~ height) %>% # alt: response = age, explanatory = height
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000) %>%
-  calculate(stat = "t") %>% 
-  visualize(method = "both")
+## ----echo=FALSE, eval=FALSE----------------------------------------------
+#  # Overlay appropriate $t$ distribution on top of permuted t-statistics
+#  prof_small %>%
[…]

### 2018-06-13 inst/doc/two_sample_t.R

@@ -21,6 +21,11 @@ fli_small <- flights %>%
          day_hour, origin, carrier)
 
 ## ------------------------------------------------------------------------
+obs_t <- fli_small %>%
+  specify(arr_delay ~ half_year) %>%
+  calculate(stat = "t", order = c("h1", "h2"))
+
+## ------------------------------------------------------------------------
 obs_t <- fli_small %>% 
   t_test(formula = arr_delay ~ half_year, alternative = "two_sided",
          order = c("h1", "h2")) %>% 
@@ -42,8 +47,7 @@ t_null_distn %>% visualize(obs_stat = obs_t, direction = "two_sided")
 
 ## ------------------------------------------------------------------------
 t_null_distn %>% 
-  dplyr::summarize(p_value = mean(abs(stat) >= pull(obs_t))) %>% 
-  dplyr::pull()
+  p_value(obs_stat = obs_t, direction = "greater")
 
 ## ------------------------------------------------------------------------
 fli_small %>%

### 2018-07-11 inst/doc/flights_examples.Rmd

@@
 ```
+
+This vignette is designed to show how to use the {infer} package with {dplyr} syntax.
+It does not show how to calculate observed statistics or p-values using the {infer} package.
+To see examples of these, check out the "Computation of observed statistics..." vignette instead.
 
@@
 Chisq_hat <- fli_small %>%
-  chisq_stat(formula = origin ~ NULL)
+  specify(response = origin) %>%
+  hypothesize(null = "point", 
+              p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
+  calculate(stat = "Chisq")
 null_distn <- fli_small %>%

### 2018-07-24 README.Rmd
Add infer hex

@@
 
-# Infer
+# infer R Package <img src="https://github.com/tidymodels/infer/blob/develop/figs/infer_gnome.png?raw=true" align="right" width=125 />
 
@@
 <!--figs/master.svg-->
-<!--https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg-->
+<!--https://img.shields.io/codecov/c/github/tidymodels/infer/master.svg-->
 
-[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/andrewpbray/infer?branch=master&svg=true)](https://ci.appveyor.com/project/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)
+[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/tidymodels/infer.svg?branch=master)](https://travis-ci.org/tidymodels/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/tidymodels/infer?branch=master&svg=true)](https://ci.appveyor.com/project/tidymodels/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/master.svg)](https://codecov.io/github/tidymodels/infer/?branch=master)
 
@@
 knitr::opts_chunk$set(eval = FALSE)
-knitr::include_graphics("https://raw.githubusercontent.com/andrewpbray/infer/master/figs/ht-diagram.png")
+knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/figs/ht-diagram.png")
 ```
@@
 install.packages("remotes")
-remotes::install_github("andrewpbray/infer")
+remotes::install_github("tidymodels/infer")
 ```
@@
 install.packages("remotes")
-remotes::install_github("andrewpbray/infer", ref = "develop")
+remotes::install_github("tidymodels/infer", ref = "develop")
 ```
@@
 We welcome others helping us make this package as user friendly and efficient as possible. Please review
-our [contributing](https://github.com/andrewpbray/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
+our [contributing](https://github.com/tidymodels/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
 helping us to write `testthat` tests and in building vignettes that show how to (and how NOT to)

### 2018-09-03 R/conf_int.R
use get_p_value() & get_confidence_interval() consistently

@@ -1,7 +1,6 @@
 #' Compute confidence interval
 #'
 #' Only simulation-based methods are (currently only) supported.
-#' `get_confidence_interval()` and `get_ci()` are both aliases of `conf_int()`.
 #'
 #' @param x Data frame of calculated statistics or containing attributes of
 #'   theoretical distribution values. Currently, dependent on statistics being
@@ -16,34 +15,42 @@
 #'
 #' @return A 1 x 2 tibble with values corresponding to lower and upper values in
 #'   the confidence interval.
+#' @section Aliases:
+#' `conf_int()` and `get_ci()` are deprecated aliases of `get_confidence_interval()`.
 #'
 #' @examples
+#' # Prepare the dataset
 #' mtcars_df <- mtcars %>%
 #'   dplyr::mutate(am = factor(am))
+#'
+#' # Calculate the difference in means in the dataset
 #' d_hat <- mtcars_df %>%
 #'   specify(mpg ~ am) %>%
 #'   calculate(stat = "diff in means", order = c("1", "0"))
+#'
+#' # Same calculation on 100 bootstrap replicates
 #' bootstrap_distn <- mtcars_df %>%
 #'   specify(mpg ~ am) %>%
-#'   generate(reps = 100) %>%
+#'   generate(reps = 100, type = "bootstrap") %>%
 #'   calculate(stat = "diff in means", order = c("1", "0"))
-#' bootstrap_distn %>% conf_int(level = 0.9)
-#' bootstrap_distn %>% conf_int(type = "se", point_estimate = d_hat)
 #'
-#' @name get_ci
-NULL
-
-#' @rdname get_ci
+#' # Use level to set the confidence level
+#' bootstrap_distn %>%
+#'   get_confidence_interval(level = 0.9)
+#'
+#' # To calculate std error, set the type and point estimate
+#' bootstrap_distn %>%
+#'   get_confidence_interval(type = "se", point_estimate = d_hat)
+#' @name get_confidence_interval
 #' @export
-conf_int <- function(x, level = 0.95, type = "percentile",
-                     point_estimate = NULL) {
+get_confidence_interval <- function(x, level = 0.95, type = "percentile",
+  point_estimate = NULL){
+
   check_ci_args(x, level, type, point_estimate)
 
-  if (type == "percentile") {
-    ci_vec <- stats::quantile(
-      x[["stat"]],
[…]

### 2018-09-03 inst/doc/chisq_test.Rmd

@@
 chisq_null_distn %>% 
-  p_value(obs_stat = obs_chisq, direction = "greater")
+  get_p_value(obs_stat = obs_chisq, direction = "greater")
 ```
@@
 fli_small %>%
-  specify(origin ~ season) %>%  %>% # alt: response = origin, explanatory = season
+  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
   hypothesize(null = "independence") %>%

### 2018-09-03 inst/doc/observed_stat_examples.Rmd

---
title: "Full infer pipeline examples using `nycflights13` `flights` data"
author: "Chester Ismay"
date: "Updated on 2018-06-14"
output: 
  rmarkdown::html_vignette:
    df_print: kable
vignette: |
  %\VignetteIndexEntry{Full infer pipeline examples}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.width = 6, fig.height = 3.5) 
options(digits = 4)
```

## Data preparation

```{r message=FALSE, warning=FALSE}
library(nycflights13)
library(dplyr)
library(ggplot2)
library(stringr)
library(infer)
set.seed(2017)
fli_small <- flights %>% 
  na.omit() %>%
  sample_n(size = 500) %>% 
  mutate(season = case_when(
    month %in% c(10:12, 1:3) ~ "winter",
    month %in% c(4:9) ~ "summer"
  )) %>% 
  mutate(day_hour = case_when(
    between(hour, 1, 12) ~ "morning",
    between(hour, 13, 24) ~ "not morning"
  )) %>% 
  select(arr_delay, dep_delay, season, 
         day_hour, origin, carrier)
```

* Two numeric - `arr_delay`, `dep_delay`
* Two categories 
    - `season` (`"winter"`, `"summer"`), 
    - `day_hour` (`"morning"`, `"not morning"`)
* Three categories - `origin` (`"EWR"`, `"JFK"`, `"LGA"`)
* Sixteen categories - `carrier`

***

# Hypothesis tests

### One numerical variable (mean)

**Observed stat**
```{r}
( x_bar <- fli_small %>%
  specify(response = dep_delay) %>%
  calculate(stat = "mean") )
```

```{r}
null_distn <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", mu = 10) %>%
  generate(reps = 1000) %>%
  calculate(stat = "mean")
null_distn %>% 
  visualize(obs_stat = x_bar, direction = "two_sided")
null_distn %>%
  get_p_value(obs_stat = x_bar, direction = "two_sided")
```

### One numerical variable (standardized mean $t$)

**Observed stat**
```{r}
( t_bar <- fli_small %>%
  specify(response = dep_delay) %>%
  calculate(stat = "t") )
```

```{r}
null_distn <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", mu = 8) %>%
  generate(reps = 1000) %>%
  calculate(stat = "t")
null_distn %>% 
  visualize(obs_stat = t_bar, direction = "two_sided")
null_distn %>%
  get_p_value(obs_stat = t_bar, direction = "two_sided")
```

### One numerical variable (median)

**Observed stat**

```{r}
( x_tilde <- fli_small %>%
  specify(response = dep_delay) %>%
  calculate(stat = "median") )
```

```{r}
null_distn <- fli_small %>%
  specify(response = dep_delay) %>%
  hypothesize(null = "point", med = -1) %>% 
  generate(reps = 1000) %>% 
  calculate(stat = "median")
null_distn %>% 
  visualize(obs_stat = x_tilde, direction = "two_sided")
null_distn %>%
  get_p_value(obs_stat = x_tilde, direction = "two_sided")
```

### One categorical (one proportion)

**Observed stat**

```{r}
( p_hat <- fli_small %>%
  specify(response = day_hour, success = "morning") %>%
  calculate(stat = "prop") )
```

```{r}
null_distn <- fli_small %>%
  specify(response = day_hour, success = "morning") %>%
  hypothesize(null = "point", p = .5) %>%
  generate(reps = 1000) %>%
  calculate(stat = "prop")
null_distn %>% 
  visualize(obs_stat = p_hat, direction = "two_sided")
null_distn %>%
  get_p_value(obs_stat = p_hat, direction = "two_sided")
```

Logical variables will be coerced to factors:

```{r}
null_distn <- fli_small %>%
  mutate(day_hour_logical = (day_hour == "morning")) %>%
  specify(response = day_hour_logical, success = "TRUE") %>%
  hypothesize(null = "point", p = .5) %>%
  generate(reps = 1000) %>%
  calculate(stat = "prop")
```

### One categorical variable (standardized proportion $z$)

Not yet implemented.

### Two categorical (2 level) variables

**Observed stat**

```{r}
( d_hat <- fli_small %>% 
  specify(day_hour ~ season, success = "morning") %>%
  calculate(stat = "diff in props", order = c("winter", "summer")) )
```

```{r}
null_distn <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000) %>% 
  calculate(stat = "diff in props", order = c("winter", "summer"))
null_distn %>% 
  visualize(obs_stat = d_hat, direction = "two_sided")
null_distn %>%
  get_p_value(obs_stat = d_hat, direction = "two_sided")
```

### Two categorical (2 level) variables (z)

**Standardized observed stat**

```{r}
( z_hat <- fli_small %>% 
  specify(day_hour ~ season, success = "morning") %>%
  calculate(stat = "z", order = c("winter", "summer")) )
```

```{r}
null_distn <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000) %>% 
  calculate(stat = "z", order = c("winter", "summer"))
null_distn %>% 
  visualize(obs_stat = z_hat, direction = "two_sided")
null_distn %>%
  get_p_value(obs_stat = z_hat, direction = "two_sided")
```

Note the similarities in this plot and the previous one.

### One categorical (>2 level) - GoF

**Observed stat**

Note the need to add in the hypothesized values here to compute the observed statistic.

```{r}
( Chisq_hat <- fli_small %>%
  specify(response = origin) %>%
  hypothesize(null = "point", 
              p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
  calculate(stat = "Chisq") )
```

```{r}
null_distn <- fli_small %>%
  specify(response = origin) %>%
  hypothesize(null = "point", 
              p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "Chisq")
null_distn %>% 
  visualize(obs_stat = Chisq_hat, direction = "greater")
null_distn %>%
  get_p_value(obs_stat = Chisq_hat, direction = "greater")
```

### Two categorical (>2 level) variables

**Observed stat**

```{r}
( Chisq_hat <- fli_small %>%
  specify(formula = day_hour ~ origin) %>% 
  calculate(stat = "Chisq") )
```

```{r}
null_distn <- fli_small %>%
  specify(day_hour ~ origin) %>%
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "Chisq")
null_distn %>% 
  visualize(obs_stat = Chisq_hat, direction = "greater")
null_distn %>%
  get_p_value(obs_stat = Chisq_hat, direction = "greater")
```

### One numerical variable, one categorical (2 levels) (diff in means)

**Observed stat**

```{r}
( d_hat <- fli_small %>% 
  specify(dep_delay ~ season) %>% 
  calculate(stat = "diff in means", order = c("summer", "winter")) )
```

```{r}
null_distn <- fli_small %>%
  specify(dep_delay ~ season) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("summer", "winter"))
null_distn %>% 
  visualize(obs_stat = d_hat, direction = "two_sided")
null_distn %>%
  get_p_value(obs_stat = d_hat, direction = "two_sided")
```

### One numerical variable, one categorical (2 levels) (t)

**Standardized observed stat**

```{r}
( t_hat <- fli_small %>% 
  specify(dep_delay ~ season) %>% 
  calculate(stat = "t", order = c("summer", "winter")) )
```

```{r}
null_distn <- fli_small %>%
  specify(dep_delay ~ season) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "t", order = c("summer", "winter"))
null_distn %>% 
  visualize(obs_stat = t_hat, direction = "two_sided")
null_distn %>%
  get_p_value(obs_stat = t_hat, direction = "two_sided")
```

Note the similarities in this plot and the previous one.

### One numerical variable, one categorical (2 levels) (diff in medians)

**Observed stat**

```{r}
( d_hat <- fli_small %>% 
  specify(dep_delay ~ season) %>% 
  calculate(stat = "diff in medians", order = c("summer", "winter")) )
```

```{r}
null_distn <- fli_small %>%
  specify(dep_delay ~ season) %>% # alt: response = dep_delay, 
  # explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in medians", order = c("summer", "winter"))
null_distn %>% 
  visualize(obs_stat = d_hat, direction = "two_sided")
null_distn %>%
  get_p_value(obs_stat = d_hat, direction = "two_sided")
```

### One numerical, one categorical (>2 levels) -  ANOVA

**Observed stat**

```{r}
( F_hat <- fli_small %>% 
  specify(arr_delay ~ origin) %>%
  calculate(stat = "F") )
```

```{r}
null_distn <- fli_small %>%
   specify(arr_delay ~ origin) %>%
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "F")
null_distn %>% 
  visualize(obs_stat = F_hat, direction = "greater")
null_distn %>%
  get_p_value(obs_stat = F_hat, direction = "greater")
```

### Two numerical vars - SLR

**Observed stat**

```{r}
( slope_hat <- fli_small %>% 
  specify(arr_delay ~ dep_delay) %>% 
  calculate(stat = "slope") )
```

```{r}
null_distn <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% 
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "slope")
null_distn %>% 
  visualize(obs_stat = slope_hat, direction = "two_sided")
null_distn %>%
  get_p_value(obs_stat = slope_hat, direction = "two_sided")
```

### Two numerical vars - correlation

**Observed stat**

```{r}
( correlation_hat <- fli_small %>% 
  specify(arr_delay ~ dep_delay) %>% 
  calculate(stat = "correlation") )
```

```{r}
null_distn <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% 
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "correlation")
null_distn %>% 
  visualize(obs_stat = correlation_hat, direction = "two_sided")
null_distn %>%
  get_p_value(obs_stat = correlation_hat, direction = "two_sided")
```

### Two numerical vars - SLR (t)

Not currently implemented since $t$ could refer to standardized slope or standardized correlation.

```{r echo=FALSE, eval=FALSE}
# **Standardized observed stat**
( t_hat <- fli_small %>% 
  specify(arr_delay ~ dep_delay) %>% 
  calculate(stat = "t") )
```

```{r echo=FALSE, eval=FALSE}
null_distn <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% 
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "t")
null_distn %>% 
  visualize(obs_stat = t_hat, direction = "two_sided")
null_distn %>%
  get_p_value(obs_stat = t_hat, direction = "two_sided")
```

## Confidence intervals

### One numerical (one mean)

**Point estimate**

```{r}
( x_bar <- fli_small %>% 
  specify(response = arr_delay) %>%
  calculate(stat = "mean") )
```

```{r}
boot <- fli_small %>%
   specify(response = arr_delay) %>%
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "mean")
( percentile_ci <- get_ci(boot) )
boot %>% visualize(endpoints = percentile_ci, direction = "between")
( standard_error_ci <- get_ci(boot, type = "se", point_estimate = x_bar) )
boot %>% visualize(endpoints = standard_error_ci, direction = "between")
```

### One numerical (one mean - standardized)

**Point estimate**

```{r}
( t_hat <- fli_small %>% 
  specify(response = arr_delay) %>%
  calculate(stat = "t") )
```

```{r}
boot <- fli_small %>%
   specify(response = arr_delay) %>%
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "t")
( percentile_ci <- get_ci(boot) )
boot %>% visualize(endpoints = percentile_ci, direction = "between")
( standard_error_ci <- get_ci(boot, type = "se", point_estimate = t_hat) )
boot %>% visualize(endpoints = standard_error_ci, direction = "between")
```

### One categorical (one proportion)

**Point estimate**

```{r}
( p_hat <- fli_small %>% 
   specify(response = day_hour, success = "morning") %>%
   calculate(stat = "prop") )
```

```{r}
boot <- fli_small %>%
 specify(response = day_hour, success = "morning") %>%
 generate(reps = 1000, type = "bootstrap") %>%
 calculate(stat = "prop")
( percentile_ci <- get_ci(boot) )
boot %>% visualize(endpoints = percentile_ci, direction = "between")
( standard_error_ci <- get_ci(boot, type = "se", point_estimate = p_hat) )
boot %>% visualize(endpoints = standard_error_ci, direction = "between")
```

### One categorical variable (standardized proportion $z$)

Not yet implemented.

### One numerical variable, one categorical (2 levels) (diff in means)

**Point estimate**

```{r}
( d_hat <- fli_small %>%
  specify(arr_delay ~ season) %>%
  calculate(stat = "diff in means", order = c("summer", "winter")) )
```

```{r}
boot <- fli_small %>%
   specify(arr_delay ~ season) %>%
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "diff in means", order = c("summer", "winter"))
( percentile_ci <- get_ci(boot) )
boot %>% visualize(endpoints = percentile_ci, direction = "between")
( standard_error_ci <- get_ci(boot, type = "se", point_estimate = d_hat) )
boot %>% visualize(endpoints = standard_error_ci, direction = "between")
```

### One numerical variable, one categorical (2 levels) (t)

**Standardized point estimate**

```{r}
( t_hat <- fli_small %>%
  specify(arr_delay ~ season) %>%
  calculate(stat = "t", order = c("summer", "winter")) )
```

```{r}
boot <- fli_small %>%
   specify(arr_delay ~ season) %>%
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "t", order = c("summer", "winter"))
( percentile_ci <- get_ci(boot) )
boot %>% visualize(endpoints = percentile_ci, direction = "between")
( standard_error_ci <- get_ci(boot, type = "se", point_estimate = t_hat) )
boot %>% visualize(endpoints = standard_error_ci, direction = "between")
```

### Two categorical variables (diff in proportions)

**Point estimate**

```{r}
( d_hat <- fli_small %>% 
  specify(day_hour ~ season, success = "morning") %>%
  calculate(stat = "diff in props", order = c("summer", "winter")) )
```

```{r}
boot <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "diff in props", order = c("summer", "winter"))
( percentile_ci <- get_ci(boot) )
boot %>% visualize(endpoints = percentile_ci, direction = "between")
( standard_error_ci <- get_ci(boot, type = "se", point_estimate = d_hat) )
boot %>% visualize(endpoints = standard_error_ci, direction = "between")
```

### Two categorical variables (z)

**Standardized point estimate**

```{r}
( z_hat <- fli_small %>% 
  specify(day_hour ~ season, success = "morning") %>%
  calculate(stat = "z", order = c("summer", "winter")) )
```

```{r}
boot <- fli_small %>%
  specify(day_hour ~ season, success = "morning") %>%
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "z", order = c("summer", "winter"))
( percentile_ci <- get_ci(boot) )
boot %>% visualize(endpoints = percentile_ci, direction = "between")
( standard_error_ci <- get_ci(boot, type = "se", point_estimate = z_hat) )
boot %>% visualize(endpoints = standard_error_ci, direction = "between")
```

### Two numerical vars - SLR

**Point estimate**

```{r}
( slope_hat <- fli_small %>% 
  specify(arr_delay ~ dep_delay) %>%
  calculate(stat = "slope") )
```

```{r}
boot <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% 
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "slope")
( percentile_ci <- get_ci(boot) )
boot %>% visualize(endpoints = percentile_ci, direction = "between")
( standard_error_ci <- get_ci(boot, type = "se", point_estimate = slope_hat) )
boot %>% visualize(endpoints = standard_error_ci, direction = "between") 
```

### Two numerical vars - correlation

**Point estimate**

```{r}
( correlation_hat <- fli_small %>% 
  specify(arr_delay ~ dep_delay) %>%
  calculate(stat = "correlation") )
```

```{r}
boot <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% 
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "correlation")
( percentile_ci <- get_ci(boot) )
boot %>% visualize(endpoints = percentile_ci, direction = "between")
( standard_error_ci <- get_ci(boot, type = "se", 
                            point_estimate = correlation_hat) )
boot %>% visualize(endpoints = standard_error_ci, direction = "between")  
```

### Two numerical vars - t

Not currently implemented since $t$ could refer to standardized slope or standardized correlation.

```{r eval=FALSE, echo=FALSE}
# **Point estimate**
( t_hat <- fli_small %>% 
  specify(arr_delay ~ dep_delay) %>%
  calculate(stat = "t") )
```

```{r eval=FALSE, echo=FALSE}
boot <- fli_small %>%
   specify(arr_delay ~ dep_delay) %>% 
   generate(reps = 1000, type = "bootstrap") %>%
   calculate(stat = "t")
( percentile_ci <- get_ci(boot) )
boot %>% visualize(endpoints = percentile_ci, direction = "between")
( standard_error_ci <- get_ci(boot, type = "se", point_estimate = t_hat) )
boot %>% visualize(endpoints = standard_error_ci, direction = "between")  
```

### 2018-09-14 inst/doc/observed_stat_examples.Rmd
Update vignettes to use `shade_*()` visualization functions.

@@
 null_distn %>% 
-  visualize(obs_stat = x_bar, direction = "two_sided")
+  visualize() +
+    shade_p_value(obs_stat = x_bar, direction = "two_sided")
 null_distn %>%
@@
 null_distn %>% 
-  visualize(obs_stat = t_bar, direction = "two_sided")
+  visualize() +
+    shade_p_value(obs_stat = t_bar, direction = "two_sided")
 null_distn %>%
@@
 null_distn %>% 
-  visualize(obs_stat = x_tilde, direction = "two_sided")
+  visualize() +
+    shade_p_value(obs_stat = x_tilde, direction = "two_sided")
 null_distn %>%
@@
 null_distn %>% 
-  visualize(obs_stat = p_hat, direction = "two_sided")
+  visualize() +
+    shade_p_value(obs_stat = p_hat, direction = "two_sided")
 null_distn %>%
@@
 null_distn %>% 
-  visualize(obs_stat = d_hat, direction = "two_sided")
+  visualize() +
+    shade_p_value(obs_stat = d_hat, direction = "two_sided")
 null_distn %>%
@@
 null_distn %>% 
-  visualize(obs_stat = z_hat, direction = "two_sided")
+  visualize() +
+    shade_p_value(obs_stat = z_hat, direction = "two_sided")
 null_distn %>%
@@
 null_distn %>% 
-  visualize(obs_stat = Chisq_hat, direction = "greater")
+  visualize() +
+    shade_p_value(obs_stat = Chisq_hat, direction = "greater")
 null_distn %>%
@@
 null_distn %>% 
-  visualize(obs_stat = t_hat, direction = "two_sided")
+  visualize() +
+    shade_p_value(obs_stat = t_hat, direction = "two_sided")
 null_distn %>%
@@
 null_distn %>% 
-  visualize(obs_stat = F_hat, direction = "greater")
+  visualize() +
+    shade_p_value(obs_stat = F_hat, direction = "greater")
 null_distn %>%
@@
 null_distn %>% 
-  visualize(obs_stat = slope_hat, direction = "two_sided")
+  visualize() +
+    shade_p_value(obs_stat = slope_hat, direction = "two_sided")
 null_distn %>%
@@
 null_distn %>% 
-  visualize(obs_stat = correlation_hat, direction = "two_sided")
+  visualize() +
+    shade_p_value(obs_stat = correlation_hat, direction = "two_sided")
 null_distn %>%
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", point_estimate = x_bar) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between")
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = standard_error_ci)
 ```
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", point_estimate = t_hat) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between")
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = standard_error_ci)
 ```
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", point_estimate = p_hat) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between")
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = standard_error_ci)
 ```
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", point_estimate = d_hat) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between")
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = standard_error_ci)
 ```
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", point_estimate = z_hat) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between")
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = standard_error_ci)
 ```
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", point_estimate = slope_hat) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between") 
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = standard_error_ci)
 ```
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", 
                             point_estimate = correlation_hat) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between")  
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = standard_error_ci)
 ```
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", point_estimate = t_hat) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between")  
+boot %>%
+  visualize() +
+    shade_confidence_interval(endpoints = standard_error_ci)
 ```

### 2018-09-14 inst/doc/observed_stat_examples.R

@@ -35,7 +35,8 @@ null_distn <- fli_small %>%
   generate(reps = 1000) %>%
   calculate(stat = "mean")
 null_distn %>% 
-  visualize(obs_stat = x_bar, direction = "two_sided")
+  visualize() +
+    shade_p_value(obs_stat = x_bar, direction = "two_sided")
 null_distn %>%
   get_p_value(obs_stat = x_bar, direction = "two_sided")
 
@@ -51,7 +52,8 @@ null_distn <- fli_small %>%
   generate(reps = 1000) %>%
   calculate(stat = "t")
 null_distn %>% 
-  visualize(obs_stat = t_bar, direction = "two_sided")
+  visualize() +
+    shade_p_value(obs_stat = t_bar, direction = "two_sided")
 null_distn %>%
   get_p_value(obs_stat = t_bar, direction = "two_sided")
 
@@ -67,7 +69,8 @@ null_distn <- fli_small %>%
   generate(reps = 1000) %>% 
   calculate(stat = "median")
 null_distn %>% 
-  visualize(obs_stat = x_tilde, direction = "two_sided")
+  visualize() +
+    shade_p_value(obs_stat = x_tilde, direction = "two_sided")
 null_distn %>%
   get_p_value(obs_stat = x_tilde, direction = "two_sided")
 
@@ -83,7 +86,8 @@ null_distn <- fli_small %>%
   generate(reps = 1000) %>%
   calculate(stat = "prop")
 null_distn %>% 
-  visualize(obs_stat = p_hat, direction = "two_sided")
+  visualize() +
+    shade_p_value(obs_stat = p_hat, direction = "two_sided")
 null_distn %>%
   get_p_value(obs_stat = p_hat, direction = "two_sided")
 
@@ -107,7 +111,8 @@ null_distn <- fli_small %>%
   generate(reps = 1000) %>% 
   calculate(stat = "diff in props", order = c("winter", "summer"))
 null_distn %>% 
-  visualize(obs_stat = d_hat, direction = "two_sided")
+  visualize() +
+    shade_p_value(obs_stat = d_hat, direction = "two_sided")
 null_distn %>%
   get_p_value(obs_stat = d_hat, direction = "two_sided")
 
@@ -123,7 +128,8 @@ null_distn <- fli_small %>%
   generate(reps = 1000) %>% 
   calculate(stat = "z", order = c("winter", "summer"))
 null_distn %>% 
[…]

### 2018-09-24 inst/doc/observed_stat_examples.Rmd

--- 2018-09-03 inst/doc/observed_stat_examples.Rmd
@@
   calculate(stat = "mean")
-null_distn %>% 
-  visualize(obs_stat = x_bar, direction = "two_sided")
+
+visualize(null_distn) +
+  shade_p_value(obs_stat = x_bar, direction = "two_sided")
 null_distn %>%
@@
   calculate(stat = "t")
-null_distn %>% 
-  visualize(obs_stat = t_bar, direction = "two_sided")
+
+visualize(null_distn) +
+  shade_p_value(obs_stat = t_bar, direction = "two_sided")
 null_distn %>%
@@
   calculate(stat = "median")
-null_distn %>% 
-  visualize(obs_stat = x_tilde, direction = "two_sided")
+
+visualize(null_distn) +
+  shade_p_value(obs_stat = x_tilde, direction = "two_sided")
 null_distn %>%
@@
   calculate(stat = "prop")
-null_distn %>% 
-  visualize(obs_stat = p_hat, direction = "two_sided")
+
+visualize(null_distn) +
+  shade_p_value(obs_stat = p_hat, direction = "two_sided")
 null_distn %>%
@@
   calculate(stat = "diff in props", order = c("winter", "summer"))
-null_distn %>% 
-  visualize(obs_stat = d_hat, direction = "two_sided")
+
+visualize(null_distn) +
+  shade_p_value(obs_stat = d_hat, direction = "two_sided")
 null_distn %>%
@@
   calculate(stat = "z", order = c("winter", "summer"))
-null_distn %>% 
-  visualize(obs_stat = z_hat, direction = "two_sided")
+
+visualize(null_distn) +
+  shade_p_value(obs_stat = z_hat, direction = "two_sided")
 null_distn %>%
@@
   calculate(stat = "Chisq")
-null_distn %>% 
-  visualize(obs_stat = Chisq_hat, direction = "greater")
+
+visualize(null_distn) +
+  shade_p_value(obs_stat = Chisq_hat, direction = "greater")
 null_distn %>%
@@
   calculate(stat = "diff in means", order = c("summer", "winter"))
-null_distn %>% 
-  visualize(obs_stat = d_hat, direction = "two_sided")
+
+visualize(null_distn) +
+  shade_p_value(obs_stat = d_hat, direction = "two_sided")
 null_distn %>%
@@
   calculate(stat = "t", order = c("summer", "winter"))
-null_distn %>% 
-  visualize(obs_stat = t_hat, direction = "two_sided")
+
+visualize(null_distn) +
+  shade_p_value(obs_stat = t_hat, direction = "two_sided")
 null_distn %>%
@@
   calculate(stat = "diff in medians", order = c("summer", "winter"))
-null_distn %>% 
-  visualize(obs_stat = d_hat, direction = "two_sided")
+
+visualize(null_distn) +
+  shade_p_value(obs_stat = d_hat, direction = "two_sided")
 null_distn %>%
@@
    calculate(stat = "F")
-null_distn %>% 
-  visualize(obs_stat = F_hat, direction = "greater")
+
+visualize(null_distn) +
+  shade_p_value(obs_stat = F_hat, direction = "greater")
 null_distn %>%
@@
    calculate(stat = "slope")
-null_distn %>% 
-  visualize(obs_stat = slope_hat, direction = "two_sided")
+
+visualize(null_distn) +
+  shade_p_value(obs_stat = slope_hat, direction = "two_sided")
 null_distn %>%
@@
    calculate(stat = "correlation")
-null_distn %>% 
-  visualize(obs_stat = correlation_hat, direction = "two_sided")
+
+visualize(null_distn) +
+  shade_p_value(obs_stat = correlation_hat, direction = "two_sided")
 null_distn %>%
@@
    calculate(stat = "t")
-null_distn %>% 
-  visualize(obs_stat = t_hat, direction = "two_sided")
+
+visualize(null_distn) +
+  shade_p_value(obs_stat = t_hat, direction = "two_sided")
 null_distn %>%
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", point_estimate = x_bar) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between")
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = standard_error_ci)
 ```
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", point_estimate = t_hat) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between")
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = standard_error_ci)
 ```
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", point_estimate = p_hat) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between")
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = standard_error_ci)
 ```
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", point_estimate = d_hat) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between")
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = standard_error_ci)
 ```
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", point_estimate = z_hat) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between")
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = standard_error_ci)
 ```
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", point_estimate = slope_hat) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between") 
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = standard_error_ci)
 ```
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", 
                             point_estimate = correlation_hat) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between")  
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = standard_error_ci)
 ```
@@
 ( percentile_ci <- get_ci(boot) )
-boot %>% visualize(endpoints = percentile_ci, direction = "between")
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = percentile_ci)
 ( standard_error_ci <- get_ci(boot, type = "se", point_estimate = t_hat) )
-boot %>% visualize(endpoints = standard_error_ci, direction = "between")  
+
+visualize(boot) +
+  shade_confidence_interval(endpoints = standard_error_ci)
 ```

### 2019-08-17 README.Rmd
remove second install method (master is kept synced with CRAN).

@@
 
-To install the developmental version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this developmental version is at <https://infer.netlify.com>.
-
-```{r}
-install.packages("remotes")
-remotes::install_github("tidymodels/infer")
-```
-
-To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first. This version was last updated on `r Sys.time()`.
+To install the developmental version of `infer` (do so at your own risk), make sure to install `remotes` first.
 

### 2019-11-18 README.Rmd
Update README.Rmd

--- 2018-07-24 README.Rmd
@@
 
-[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/tidymodels/infer.svg?branch=master)](https://travis-ci.org/tidymodels/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/tidymodels/infer?branch=master&svg=true)](https://ci.appveyor.com/project/tidymodels/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/master.svg)](https://codecov.io/github/tidymodels/infer/?branch=master)
+[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/tidymodels/infer.svg?branch=master)](https://travis-ci.org/tidymodels/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/tidymodels/infer?branch=master&svg=true)](https://ci.appveyor.com/project/tidymodels/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/master.svg)](https://codecov.io/github/tidymodels/infer/?branch=master)
 
@@
 
-To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first. This version was last updated on `r Sys.time()`.
+To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first.
 

### 2019-12-23 R/wrappers.R
address some r cmd check business :-)

@@ -27,6 +27,8 @@
 #' @param ... For passing in other arguments to [t.test()][stats::t.test()].
 #'
 #' @examples
+#' library(tidyr)
+#' 
 #' # t test for number of hours worked per week
 #' # by college degree status
 #' gss %>%
@@ -136,6 +138,8 @@ t_test <- function(x, formula,
 #' @param ... Pass in arguments to \\{infer\\} functions.
 #'
 #' @examples
+#' library(tidyr)
+#' 
 #' # t test statistic for true mean number of hours worked
 #' # per week of 40
 #' gss %>%

### 2019-12-26 README.Rmd
make readme a lil cozier, update examples!

@@
 
-# infer R Package <img src="https://github.com/tidymodels/infer/blob/develop/figs/infer_gnome.png?raw=true" align="right" width=125 />
+# infer R Package <img src="https://github.com/tidymodels/infer/blob/master/figs/infer_gnome.png?raw=true" align="right" width=125 />
 
@@
 The objective of this package is to perform statistical inference using an expressive statistical grammar that coheres with the `tidyverse` design framework.
+The package is centered around 4 main verbs, supplemented with many utilities to visualize and extract value from their outputs.
+
++ `specify()` allows you to specify the variable, or relationship between variables, that you're interested in.
++ `hypothesize()` allows you to declare the null hypothesis.
++ `generate()` allows you to generate data reflecting the null hypothesis.
++ `calculate()` allows you to calculate a distribution of statistics from the generated data to form the null distribution.
+
+To learn more about the principles underlying the package design, see `vignette("infer")`.
+
+```{r load-package, echo = FALSE, message = FALSE, warning = FALSE}
+library(devtools)
+devtools::load_all()
+```
 
 ```{r diagram, echo=FALSE}
-knitr::opts_chunk$set(eval = FALSE)
 knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/figs/ht-diagram.png")
@@
 
-```{r}
+```{r, eval = FALSE}
 install.packages("infer")
@@
 
-To install the developmental version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this developmental version is at <https://infer.netlify.com>.
+To install the developmental version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at <https://infer.netlify.com>.
 
-```{r}
+```{r, eval = FALSE}
 install.packages("remotes")
@@
 
-```{r}
+```{r, eval = FALSE}
 install.packages("remotes")
@@
 
-To see the things we are working on with the package as vignettes/Articles, check out 
-the developmental `pkgdown` site at <https://infer-dev.netlify.com>.
+To see documentation for the developmental version of `infer`, the developmental `pkgdown` site is available at <https://infer-dev.netlify.com>.
 
@@
 
-We welcome others helping us make this package as user friendly and efficient as possible. Please review
-our [contributing](https://github.com/tidymodels/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
-helping us to write `testthat` tests and in building vignettes that show how to (and how NOT to)
-use the package. By participating in this project you agree to abide by its terms.
+We welcome others helping us make this package as user-friendly and efficient as possible. Please review
+our [contributing](https://github.com/tidymodels/infer/blob/master/CONTRIBUTING.md) and [conduct](https://github.com/tidymodels/infer/blob/master/CONDUCT.md) guidelines.
+Please see the open [issues](https://github.com/tidymodels/infer/issues) for more specific fixes/additions needing attention.
+By participating in this project you agree to abide by its terms.
 
@@
 
-These examples assume that `mtcars` has been overwritten so that the variables `cyl`, `vs`, `am`, `gear`, and `carb` are `factor`s.
+These examples are pulled from the "Full infer Pipeline Examples" vignette, accessible by calling `vignette("observed_stat_examples")`.
+They make use of the `gss` dataset supplied by the package, providing a sample of data from the [General Social Survey](https://gss.norc.org).
+The data looks like this:
 
-```{r}
-mtcars <- as.data.frame(mtcars) %>%
-  mutate(cyl = factor(cyl),
-          vs = factor(vs),
-          am = factor(am),
-          gear = factor(gear),
-          carb = factor(carb))
+```{r load-gss, warning = FALSE, message = FALSE}
+# load in the dataset
+data(gss)
+
+# take a glimpse at it
+str(gss)
 ```
 
-Hypothesis test for a difference in proportions (using the formula interface 
-`y ~ x` in `specify()`):
+As an example, we'll run an analysis of variance on `age` and `partyid`, testing whether the age of a respondent is independent of their political party affiliation.
 
-```{r}
-mtcars %>%
-  specify(am ~ vs, success = "1") %>%
-  hypothesize(null = "independence") %>%
-  generate(reps = 100, type = "permute") %>%
-  calculate(stat = "diff in props", order = c("1", "0"))
+Calculating the observed statistic,
+
+```{r, message = FALSE, warning = FALSE}
+F_hat <- gss %>% 
+  specify(age ~ partyid) %>%
+  calculate(stat = "F")
 ```
 
-Confidence interval for a difference in means (using the non-formula interface
-giving both the `response` and `explanatory` variables in `specify()`):
+Then, generating the null distribution,
 
-```{r}
-mtcars %>%
-  specify(response = mpg, explanatory = am) %>%
-  generate(reps = 100, type = "bootstrap") %>%
-  calculate(stat = "diff in means", order = c("1", "0"))
+```{r, message = FALSE, warning = FALSE}
+null_distn <- gss %>%
+   specify(age ~ partyid) %>%
+   hypothesize(null = "independence") %>%
+   generate(reps = 1000, type = "permute") %>%
+   calculate(stat = "F")
 ```
 
-Note that the formula and non-formula interfaces work for all implemented inference
-procedures in `infer`. Use whatever is more natural for you. If you will be doing
-modeling using functions like `lm()` and `glm()`, we recommend you begin to use the
-formula `y ~ x` notation as soon as possible though.
+Visualizing the observed statistic alongside the null distribution,
 
-Other examples are available in the package vignettes.
+```{r, message = FALSE, warning = FALSE}
+visualize(null_distn) +
+  shade_p_value(obs_stat = F_hat, direction = "greater")
+```
+
+Calculating the p-value from the null distribution and observed statistic,
+
+```{r, message = FALSE, warning = FALSE}
+null_distn %>%
+  get_p_value(obs_stat = F_hat, direction = "greater")
+```
+
+Note that the formula and non-formula interfaces  (i.e.
+`age ~ partyid` vs.
+`response = age, explanatory =  partyid`) work for all implemented inference procedures in `infer`.
+Use whatever is more natural for you.
+If you will be doing modeling using functions like `lm()` and `glm()`, though, we recommend you begin to use the formula `y ~ x` notation as soon as possible.
+
+Other resources are available in the package vignettes!
+See `vignette("observed_stat_examples")` for more examples like the one above, and `vignette("infer")` for discussion of the underlying principles of the package design.

### 2019-12-27 README.Rmd
clarify "developmental" language

@@
 
-To install the developmental version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at <https://infer.netlify.com>.
+To install the developmental stable version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at <https://infer.netlify.com>.
 
@@
 
-To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first.
+To install the experimental version of `infer` (do so at your own risk), make sure to install `remotes` first.
 
@@
 
-To see documentation for the developmental version of `infer`, the developmental `pkgdown` site is available at <https://infer-dev.netlify.com>.
+To see documentation for the experimental version of `infer`, the `pkgdown` site is available at <https://infer-dev.netlify.com>.
 

### 2020-03-22 README.Rmd

@@
 
-[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/tidymodels/infer.svg?branch=master)](https://travis-ci.org/tidymodels/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/tidymodels/infer?branch=master&svg=true)](https://ci.appveyor.com/project/tidymodels/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/master.svg)](https://codecov.io/github/tidymodels/infer/?branch=master)
+[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/tidymodels/infer.svg?branch=master)](https://travis-ci.org/tidymodels/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/master.svg)](https://codecov.io/github/tidymodels/infer/?branch=master)
 

### 2020-04-30 R/get_p_value.R
switch preferred spelling to two-sided

@@ -12,8 +12,8 @@
 #' @param obs_stat A numeric value or a 1x1 data frame (as extreme or more
 #'   extreme than this).
 #' @param direction A character string. Options are `"less"`, `"greater"`, or
-#'   `"two_sided"`. Can also use `"left"`, `"right"`, `"both"`, 
-#'   `"two-sided"`, or `"two sided"`.
+#'   `"two-sided"`. Can also use `"left"`, `"right"`, `"both"`, 
+#'   `"two_sided"`, or `"two sided"`.
 #'
 #' @return A 1x1 [tibble][tibble::tibble] with value between 0 and 1.
 #'

### 2020-04-30 R/shade_p_value.R

@@ -12,8 +12,8 @@
 #' @param obs_stat A numeric value or 1x1 data frame corresponding to what the
 #'   observed statistic is.
 #' @param direction A string specifying in which direction the shading should
-#'   occur. Options are `"less"`, `"greater"`, or `"two_sided"`. Can
-#'   also give `"left"`, `"right"`, `"both"`, `"two-sided"`, or `"two sided"`. 
+#'   occur. Options are `"less"`, `"greater"`, or `"two-sided"`. Can
+#'   also give `"left"`, `"right"`, `"both"`, `"two_sided"`, or `"two sided"`. 
 #'   If `NULL` then no shading is actually done.
 #' @param color A character or hex string specifying the color of the observed
 #'   statistic as a vertical line on the plot.

### 2020-05-27 R/get_p_value.R
fix spelling errors

@@ -3,7 +3,7 @@
 #' @description
 #' \lifecycle{stable}
 #'
-#' Compute a p-value from a null distribution and observed statistc. 
+#' Compute a p-value from a null distribution and observed statistic. 
 #' Simulation-based methods are (currently only) supported.
 #' 
 #' Learn more in `vignette("infer")`.

### 2020-06-29 README.Rmd
update conduct, tidymodels resources

@@
 
-We welcome others helping us make this package as user-friendly and efficient as possible. Please review
-our [contributing](https://github.com/tidymodels/infer/blob/master/CONTRIBUTING.md) and [conduct](https://github.com/tidymodels/infer/blob/master/CONDUCT.md) guidelines.
-Please see the open [issues](https://github.com/tidymodels/infer/issues) for more specific fixes/additions needing attention.
+We welcome others helping us make this package as user-friendly and efficient as possible.
+Please review our [contributing](https://github.com/tidymodels/infer/blob/master/CONTRIBUTING.md) and [conduct](https://github.com/tidymodels/infer/blob/master/CONDUCT.md) guidelines.
 By participating in this project you agree to abide by its terms.
+
+For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on RStudio Community](https://rstd.io/tidymodels-community).
+If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/tune/issues).
+Either way, learn how to create and share a [reprex](https://rstd.io/reprex) (a minimal, reproducible example), to clearly communicate about your code.
+Check out further details on [contributing guidelines for tidymodels packages](https://www.tidymodels.org/contribute/) and [how to get help](https://www.tidymodels.org/help/).
 

### 2020-10-12 README.Rmd
update pkgdown link

@@
 
-# infer R Package <img src="https://github.com/tidymodels/infer/blob/master/figs/infer_gnome.png?raw=true" align="right" width=125 />
+# infer R Package <img src="https://github.com/tidymodels/infer/blob/master/figs/infer_gnome.png?raw=true" align="right" width=250 />
 
@@
 
-To install the developmental stable version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at <https://infer.netlify.com>.
+To install the developmental stable version of `infer`, make sure to install `remotes` first. The `pkgdown` website for the package is at <https://infer.tidymodels.org>.
 
@@
 ```
-
-To install the experimental version of `infer` (do so at your own risk), make sure to install `remotes` first.
-
-```{r, eval = FALSE}
-install.packages("remotes")
-remotes::install_github("tidymodels/infer", ref = "develop")
-```
-
-To see documentation for the experimental version of `infer`, the `pkgdown` site is available at <https://infer-dev.netlify.com>.
 
@@
 For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on RStudio Community](https://rstd.io/tidymodels-community).
-If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/tune/issues).
+If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/infer/issues).
 Either way, learn how to create and share a [reprex](https://rstd.io/reprex) (a minimal, reproducible example), to clearly communicate about your code.

### 2020-10-12 README.Rmd
adjust figure path
The visualize output in the README has a bad path on the websites.
link to image file in readme

@@
 
-```{r, message = FALSE, warning = FALSE}
+```{r viz, message = FALSE, warning = FALSE, eval = FALSE}
 visualize(null_distn) +
   shade_p_value(obs_stat = F_hat, direction = "greater")
+```
+
+```{r viz-graphic, message = FALSE, warning = FALSE, echo = FALSE}
+knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/README_files/figure-gfm/viz-1.png")
 ```

### 2020-11-06 README.Rmd
bump travis and appveyor
increases the number of GitHub Actions checks and brings them into alignment with most tidymodels non-core (notably, drops macOS devel, as those dailies frequent headaches)

--- 2020-06-29 README.Rmd
@@
 
-[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/tidymodels/infer.svg?branch=master)](https://travis-ci.org/tidymodels/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/master.svg)](https://codecov.io/github/tidymodels/infer/?branch=master)
+[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)[![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/master.svg)](https://codecov.io/github/tidymodels/infer/?branch=master)
 

### 2020-12-22 tests/testthat/test-visualize.R
merge develop into prop_test
need the new z functionality from #351

@@ -1,7 +1,6 @@
 context("visualize")
 
 library(dplyr)
-library(vdiffr)
 
 set.seed(42)
 

### 2021-01-13 README.Rmd
adjust redirecting URLs

--- 2020-10-12 README.Rmd
@@
 
-To install the developmental stable version of `infer`, make sure to install `remotes` first. The `pkgdown` website for the package is at <https://infer.tidymodels.org>.
+To install the developmental stable version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at <https://https://infer.tidymodels.org/>.
 

### 2021-05-20 README.Rmd
correct https URLs
adjust site url syntax
remove redundant horizontal line
github md style automatically draws a horizontal line after level 1 headers

@@
 
-# infer R Package <img src="https://github.com/tidymodels/infer/blob/master/figs/infer_gnome.png?raw=true" align="right" width=250 />
-
-------------------------------------------------------------------------
+# infer R Package <img src="https://github.com/tidymodels/infer/blob/master/figs/infer_gnome.png?raw=true" align="right" width=280 />
 
@@
 
-To install the developmental stable version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at <https://https://infer.tidymodels.org/>.
+To install the developmental stable version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at [infer.tidymodels.org](https://infer.tidymodels.org/).
 

### 2021-06-14 README.Rmd
add alt text to README figures

@@
 
-```{r diagram, echo=FALSE}
+```{r diagram, echo = FALSE, fig.cap = " ", fig.alt = "A diagram showing four steps to carry out randomization-based inference: specify hypothesis, generate data, calculate statistic, and visualize.
+From left to right, each step is connected by an arrow, while the diagram indicates that generating data and calculating statistics can happen iteratively."}
 knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/figs/ht-diagram.png")
@@
 
-```{r viz-graphic, message = FALSE, warning = FALSE, echo = FALSE}
+```{r viz-graphic, message = FALSE, warning = FALSE, echo = FALSE, fig.cap = " ", fig.alt = "A histogram showing a distribution of F statistics, right-tailed and centered around one half.
+The x axis ranges from zero to five.
+The region of the histogram to the right of the observed statistic, just above two, is shaded red to represent the p-value."}
 knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/README_files/figure-gfm/viz-1.png")

### 2021-06-16 README.Rmd

@@
 
-```{r viz-graphic, message = FALSE, warning = FALSE, echo = FALSE, fig.cap = " ", fig.alt = "A histogram showing a distribution of F statistics, right-tailed and centered around one half.
+```{r viz-graphic, message = FALSE, warning = FALSE, echo = FALSE, fig.cap = " ", fig.alt = "A histogram showing a distribution of F statistics, right-tailed and centered around one.
 The x axis ranges from zero to five.

### 2021-06-16 README.Rmd

@@
 ```
+
+If you're interested in learning more about randomization-based statistical inference generally, including applied examples of this package, we recommend checking out [Statistical Inference Via Data Science: A ModernDive Into R and the Tidyverse](https://moderndive.com/) and [Introduction to Modern Statistics](https://openintro-ims.netlify.app/).
 

### 2021-06-21 R/visualize.R
transition vignettes / docs to preferred syntax
`method = "theoretical"` is now superseded--whereever it was used in vignettes, replace it with a workflow using an explicit null distribution.

@@ -11,13 +11,17 @@ ggplot2::ggplot_add
 #' 
 #' Learn more in `vignette("infer")`.
 #'
-#' @param data A distribution of statistics (for [calculate()]-based workflows)
-#'   or coefficient estimates (for [`fit()`][fit.infer()]-based workflows)
-#'   outputted by infer.
+#' @param data A null distribution. For simulation-based inference, a data frame 
+#'   containing a distribution of [calculate()]d statistics 
+#'   or [`fit()`][fit.infer()]ted coefficient estimates. This object should 
+#'   have been passed to [generate()] before being supplied or 
+#'   [calculate()] to [`fit()`][fit.infer()]. For theory-based inference,
+#'   the output of [assume()].
 #' @param bins The number of bins in the histogram.
 #' @param method A string giving the method to display. Options are
 #'   `"simulation"`, `"theoretical"`, or `"both"` with `"both"` corresponding to
-#'   `"simulation"` and `"theoretical"`.
+#'   `"simulation"` and `"theoretical"`. If `data` is the output of [assume()],
+#'   this argument will be ignored and default to `"theoretical"`.
 #' @param dens_color A character or hex string specifying the color of the
 #'   theoretical density curve.
 #' @param ... Other arguments passed along to \\{ggplot2\\} functions.
@@ -32,9 +36,11 @@ ggplot2::ggplot_add
 #'
 #' @return 
 #' 
-#' For [calculate()]-based workflows, a ggplot object showing the 
-#' simulation-based distribution as a histogram or bar graph. Also used to 
-#' show the theoretical curves.
+#' For [calculate()]-based workflows, a ggplot showing the simulation-based
+#' distribution as a histogram or bar graph. Can also be used to display
+#' theoretical distributions.
+#'  
+#' For [assume()]-based workflows, a ggplot showing the theoretical distribution.
 #' 
 #' For [`fit()`][fit.infer()]-based workflows, a `patchwork` object
 #' showing the simulation-based distributions as a histogram or bar graph.

### 2021-06-22 R/assume.R
use `hypothesize()` for HT

@@ -13,6 +13,14 @@
 #' and [get_confidence_interval()] in the same way that simulation-based
 #' null distributions can.
 #' 
+#' To define a theoretical null distribution (for use in hypothesis testing),
+#' be sure to provide a null hypothesis via [hypothesize()]. To define a
+#' theoretical sampling distribution (for use in confidence intervals), 
+#' provide the output of [specify()]. Sampling distributions (only
+#' implemented for `t` and `z`) lie on the scale of the data, and will be
+#' recentered and rescaled to match the corresponding `stat` given in
+#' [calculate()] to calculate the observed statistic.
+#' 
 #' @param x The output of [specify()] or [hypothesize()], giving the
 #'   observed data, variable(s) of interest, and (optionally) null hypothesis.
 #' @param distribution The distribution in question, as a string. One of
@@ -44,6 +52,7 @@
 #' # with the `partyid` explanatory variable
 #' gss %>% 
 #'   specify(age ~ partyid) %>% 
+#'   hypothesize(null = "independence") %>%
 #'   assume(
 #'     distribution = "F", 
 #'     c(length(unique(gss$partyid)) - 1, nrow(gss) - 1)
@@ -53,12 +62,20 @@
 #' # on the `finrela` variable
 #' gss %>%
 #'   specify(response = finrela) %>%
+#'     hypothesize(null = "point",
+#'                 p = c("far below average" = 1/6,
+#'                       "below average" = 1/6,
+#'                       "average" = 1/6,
+#'                       "above average" = 1/6,
+#'                       "far above average" = 1/6,
+#'                       "DK" = 1/6)) %>%
 #'   assume("Chisq", length(unique(gss$finrela)) - 1)
 #' 
 #' # Chi-squared test of independence
 #' # on the `finrela` and `sex` variables
 #' gss %>%
 #'   specify(formula = finrela ~ sex) %>%
+#'   hypothesize(null = "independence") %>%
 #'   assume(
 #'     distribution = "Chisq", 
 #'     df = (length(unique(gss$finrela)) - 1) * 
@@ -68,11 +85,13 @@
 #' # T distribution
 #' gss %>% 
 #'   specify(age ~ college) %>%
+#'   hypothesize(null = "independence") %>%
 #'   assume("t", nrow(gss) - 1)
 #' 
 #' # Z distribution
[…]

### 2021-06-24 figs/paper/paper.tex
initial JOSS paper commit

\documentclass[10pt,a4paper,onecolumn]{article}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{tikz}
\usepackage{hyperref}
\hypersetup{colorlinks,breaklinks,
            urlcolor=[rgb]{0.0, 0.5, 1.0},
            linkcolor=[rgb]{0.0, 0.5, 1.0}}
\usepackage{caption}
\usepackage{tcolorbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{seqsplit}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage[
  backend=biber,
%  style=alphabetic,
%  citestyle=numeric
]{biblatex}
\bibliography{paper.bib}

% --- Page layout -------------------------------------------------------------
\usepackage[top=3.5cm, bottom=3cm, right=1.5cm, left=1.0cm,
            headheight=2.2cm, reversemp, includemp, marginparwidth=4.5cm]{geometry}

% --- Default font ------------------------------------------------------------
% \renewcommand\familydefault{\sfdefault}

% --- Style -------------------------------------------------------------------
\renewcommand{\bibfont}{\small \sffamily}
\renewcommand{\captionfont}{\small\sffamily}
\renewcommand{\captionlabelfont}{\bfseries}

% --- Section/SubSection/SubSubSection ----------------------------------------
\titleformat{\section}
  {\normalfont\sffamily\Large\bfseries}
  {}{0pt}{}
\titleformat{\subsection}
  {\normalfont\sffamily\large\bfseries}
  {}{0pt}{}
\titleformat{\subsubsection}
  {\normalfont\sffamily\bfseries}
  {}{0pt}{}
\titleformat*{\paragraph}
  {\sffamily\normalsize}

% --- Header / Footer ---------------------------------------------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
%\renewcommand{\headrulewidth}{0.50pt}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[L]{\hspace{-0.75cm}\includegraphics[width=5.5cm]{/Library/Frameworks/R.framework/Versions/4.1/Resources/library/rticles/rmarkdown/templates/joss/resources/JOSS-logo.png}}
\fancyhead[C]{}
\fancyhead[R]{}
\renewcommand{\footrulewidth}{0.25pt}

\fancyfoot[L]{\footnotesize{\sffamily Couch et. al., (2021). infer: An R
package for tidyverse-friendly statistical
inference. \textit{Journal of Open Source Software}, (), . \href{https://doi.org/}{https://doi.org/}}}

\fancyfoot[R]{\sffamily \thepage}
\makeatletter
\let\ps@plain\ps@fancy
\fancyheadoffset[L]{4.5cm}
\fancyfootoffset[L]{4.5cm}

% --- Macros ---------

\definecolor{linky}{rgb}{0.0, 0.5, 1.0}

\newtcolorbox{repobox}
   {colback=red, colframe=red!75!black,
     boxrule=0.5pt, arc=2pt, left=6pt, right=6pt, top=3pt, bottom=3pt}

\newcommand{\ExternalLink}{%
   \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{%
       \begin{scope}[x=1ex, y=1ex]
           \clip (-0.1,-0.1)
               --++ (-0, 1.2)
               --++ (0.6, 0)
               --++ (0, -0.6)
               --++ (0.6, 0)
               --++ (0, -1);
           \path[draw,
               line width = 0.5,
               rounded corners=0.5]
               (0,0) rectangle (1,1);
       \end{scope}
       \path[draw, line width = 0.5] (0.5, 0.5)
           -- (1, 1);
       \path[draw, line width = 0.5] (0.6, 1)
           -- (1, 1) -- (1, 0.6);
       }
   }

% --- Title / Authors ---------------------------------------------------------
% patch \maketitle so that it doesn't center
\patchcmd{\@maketitle}{center}{flushleft}{}{}
\patchcmd{\@maketitle}{center}{flushleft}{}{}
% patch \maketitle so that the font size for the title is normal
\patchcmd{\@maketitle}{\LARGE}{\LARGE\sffamily}{}{}
% patch the patch by authblk so that the author block is flush left
\def\maketitle{{%
  \renewenvironment{tabular}[2][]
    {\begin{flushleft}}
    {\end{flushleft}}
  \AB@maketitle}}
\makeatletter
\renewcommand\AB@affilsepx{ \protect\Affilfont}
%\renewcommand\AB@affilnote[1]{{\bfseries #1}\hspace{2pt}}
\renewcommand\AB@affilnote[1]{{\bfseries #1}\hspace{3pt}}
\makeatother
\renewcommand\Authfont{\sffamily\bfseries}
\renewcommand\Affilfont{\sffamily\small\mdseries}
\setlength{\affilsep}{1em}

\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}

\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}

\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}

\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={infer: An R package for tidyverse-friendly statistical inference},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Pandoc citation processing
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\newenvironment{cols}[1][]{}{}

\newenvironment{col}[1]{\begin{minipage}{#1}\ignorespaces}{%
\end{minipage}
\ifhmode\unskip\fi
\aftergroup\useignorespacesandallpars}

\def\useignorespacesandallpars#1\ignorespaces\fi{%
#1\fi\ignorespacesandallpars}

\makeatletter
\def\ignorespacesandallpars{%
  \@ifnextchar\par
    {\expandafter\ignorespacesandallpars\@gobble}%
    {}%
}
\makeatother

\title{infer: An R package for tidyverse-friendly statistical inference}

        \author[1, 2]{Simon Couch}
          \author[3]{Andrew Bray}
          \author[4]{Chester Ismay}
          \author[5]{Evgeni Chasnovski}
          \author[6]{Ben Baumer}
          \author[2, 7]{Mine Çetinkaya-Rundel}

      \affil[1]{Johns Hopkins, Department of Biostatistics}
      \affil[2]{RStudio}
      \affil[3]{UC Berkeley, Department of Statistics and Reed College
Mathematics Department (on leave)}
      \affil[4]{Flatiron School}
      \affil[5]{No Affiliation}
      \affil[6]{Smith College, Program in Statistical \& Data Sciences}
      \affil[7]{Duke University, Department of Statistical Science}
  \date{\vspace{-5ex}}

\begin{document}
\maketitle

\marginpar{
  %\hrule
  \sffamily\small

  {\bfseries DOI:} \href{https://doi.org/}{\color{linky}{}}

  \vspace{2mm}

  {\bfseries Software}
  \begin{itemize}
    \setlength\itemsep{0em}
    \item \href{}{\color{linky}{Review}} \ExternalLink
    \item \href{}{\color{linky}{Repository}} \ExternalLink
    \item \href{}{\color{linky}{Archive}} \ExternalLink
  \end{itemize}

  \vspace{2mm}

  {\bfseries Submitted:} \\
  {\bfseries Published:}

  \vspace{2mm}
  {\bfseries License}\\
  Authors of papers retain copyright and release the work under a Creative Commons Attribution 4.0 International License (\href{http://creativecommons.org/licenses/by/4.0/}{\color{linky}{CC-BY}}).
}

\hypertarget{summary}{%
\section{Summary}\label{summary}}

\texttt{infer} implements an expressive grammar to perform statistical
inference that coheres with the \texttt{tidyverse} design framework
(Wickham et al., 2019). Rather than providing methods for specific
statistical tests, this package consolidates the principles that are
shared among common hypothesis tests into a set of four main verbs
(functions), supplemented with many utilities to visualize and extract
value from their outputs.

\hypertarget{statement-of-need}{%
\section{Statement of Need}\label{statement-of-need}}

Packages implementing methods for basic statistical inference in R are
highly variable in their interfaces. The structure of inputted data,
argument names, expected argument types, argument orders, output types,
and spelling cases varies widely both within and among packages. This
diversity in approaches obscures the intuition shared among common
inferential procedures, makes details of usage difficult to remember,
and prevents an expressive and idiomatic coding style.

infer is an R package for randomization-based hypothesis testing,
naturalizing an intuitive understanding of statistical inference via a
unified and expressive grammar. Four functions provide functionality
encompassing a large swath of basic frequentist statistical inference,
abstracting away details of specific tests and shifting the focus of the
analyst to the observed data and the processes that generated it. Such a
grammar lends itself to applications in teaching, data pedagogy
research, applied scientific research, and advanced predictive modeling.
For one, the principled approach of the package has made it especially
well-fit for use in teaching introductory statistics (Baumer, Bray,
Çetinkaya-Rundel, \& Hardin, 2020; Ismay \& Kim, 2019) and research in
data pedagogy (Çetinkaya-Rundel \& Ellison, 2021; Fergusson \&
Pfannkuch, 2021; Loy, 2021). Further, the package has already seen usage
in a number of published scientific applications (Ask et al., 2021;
Fallon \& Hinds, 2021; McLean et al., 2021). Finally, the package
integrates with the greater tidymodels collection of packages, a
burgeoning software ecosystem for tidyverse-aligned predictive modeling
used across many modern research and industrial applications (Kuhn \&
Wickham, 2020). To date, the package has been downloaded more than
400,000 times.

\hypertarget{underlying-principles}{%
\section{Underlying Principles}\label{underlying-principles}}

Regardless of the hypothesis test in question, an analyst asks the same
kind of question when conducting statistical inference: is the
effect/difference in the observed data real, or due to random chance? To
answer this question, the analyst begins by assuming that the effect in
the observed data was simply due to random chance, and calls this
assumption the \emph{null hypothesis}. (In reality, they might not
believe in the null hypothesis at all---the null hypothesis is in
opposition to the \emph{alternate hypothesis}, which supposes that the
effect present in the observed data is actually due to the fact that
``something is going on.'') The analyst then calculates a \emph{test
statistic} from the data that describes the observed effect. They can
use this test statistic to calculate a \emph{p-value} via juxtaposition
with a \emph{null distribution}, giving the probability that the
observed data could come about if the null hypothesis were true. If this
probability is below some pre-defined \emph{significance level}
\(\alpha\), then the analyst can reject the null hypothesis.

The workflow of this package is designed around this idea. Starting out
with some dataset,

\begin{itemize}
\tightlist
\item
  \texttt{specify()} allows the analyst to specify the variable, or
  relationship between variables, that they're interested in.
\item
  \texttt{hypothesize()} allows the analyst to declare the null
  hypothesis.
\item
  \texttt{generate()} allows the analyst to generate data reflecting the
  null hypothesis.
\item
  \texttt{calculate()} allows the analyst to calculate summary
  statistics, either from

  \begin{itemize}
  \tightlist
  \item
    the observed data, to form the observed test statistic.
  \item
    data \texttt{generate()}d to reflect the null hypothesis, to form
    the randomization-based null distribution of test statistics.
  \end{itemize}
\end{itemize}

As such, the ultimate output of an infer pipeline using these four
functions is generally an \emph{observed statistic} or \emph{null
distribution} of test statistics. These four functions are thus
supplemented with many utilities to visualize and extract value from
their outputs.

\begin{itemize}
\tightlist
\item
  \texttt{visualize()} plots the null distribution of test statistics

  \begin{itemize}
  \tightlist
  \item
    \texttt{shade\_p\_value()} situates the observed statistic in the
    null distribution, shading the region as or more extreme
  \item
    \texttt{shade\_confidence\_interval()} situates the confidence
    interval region in the null distribution, shading the region with
    the bounds
  \end{itemize}
\item
  \texttt{get\_p\_value()} calculates a p-value via the juxtaposition of
  the test statistic and null distribution
\item
  \texttt{get\_confidence\_interval()} calculates a confidence interval
  via the juxtaposition of the test statistic and null distribution
\end{itemize}

Beyond this, the package offers

\begin{itemize}
\tightlist
\item
  methods for inference using theory-based distributions
\item
  shorthand wrappers for common statistical tests using tidy data
\item
  model-fitting workflows to accommodate multiple explanatory variables
\end{itemize}

\hypertarget{comparison-to-other-packages}{%
\section{Comparison to Other
Packages}\label{comparison-to-other-packages}}

\texttt{broom} and \texttt{parameters} convert model objects to unified
output formats, though do not provide methods for fitting models,
describing null distributions, or calculating summary statistics from
tabular data. \texttt{statsexpressions}, and adjacent packages in the
\texttt{easystats} ecosystem, implement wrappers with consistent
interfaces for theory-based hypothesis tests. The structure of each of
these packages is defined by model types, where each model type has its
own associated function and/or model object. In contrast, \texttt{infer}
is structured around four functions, situating statistics and model
types within a more abstracted grammar. \texttt{infer}'s initial release
on the Comprehensive R Archive Network predated that of each of the
packages mentioned above, with the exception of \texttt{broom} (R Core
Team, 2021).

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

We acknowledge contributions from Albert Kim, Jo Hardin, Jay Lee, Amelia
McNamara, Nick Solomon, and Richie Cotton.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-ask2021per}{}%
Ask, A. V., Jenssen, B. M., Tartu, S., Angelier, F., Chastel, O., \&
Gabrielsen, G. W. (2021). Per-and polyfluoroalkyl substances are
positively associated with thyroid hormones in an arctic seabird.
\emph{Environmental Toxicology and Chemistry}, \emph{40}(3), 820--831.

\leavevmode\hypertarget{ref-baumer2020teaching}{}%
Baumer, B. S., Bray, A. P., Çetinkaya-Rundel, M., \& Hardin, J. S.
(2020). Teaching introductory statistics with DataCamp. \emph{Journal of
Statistics Education}, \emph{28}(1), 89--97.

\leavevmode\hypertarget{ref-cetinkaya2021fresh}{}%
Çetinkaya-Rundel, M., \& Ellison, V. (2021). A fresh look at
introductory data science. \emph{Journal of Statistics and Data Science
Education}, \emph{29}(sup1), S16--S26.

\leavevmode\hypertarget{ref-fallon2021single}{}%
Fallon, M. E., \& Hinds, M. T. (2021). Single cell morphological metrics
and cytoskeletal alignment regulate VCAM-1 protein expression.
\emph{Biochemical and Biophysical Research Communications}, \emph{555},
160--167.

\leavevmode\hypertarget{ref-fergusson2021introducing}{}%
Fergusson, A., \& Pfannkuch, M. (2021). Introducing teachers who use
GUI-driven tools for the randomization test to code-driven tools.
\emph{Mathematical Thinking and Learning}, 1--21.

\leavevmode\hypertarget{ref-ismay2019statistical}{}%
Ismay, C., \& Kim, A. Y. (2019). \emph{Statistical inference via data
science: A ModernDive into {R} and the tidyverse}. CRC Press.

\leavevmode\hypertarget{ref-kuhn2020tidymodels}{}%
Kuhn, M., \& Wickham, H. (2020). Tidymodels: A collection of packages
for modeling and machine learning using tidyverse principles.
\emph{Boston, MA, USA.}

\leavevmode\hypertarget{ref-loy2021bringing}{}%
Loy, A. (2021). Bringing visual inference to the classroom.
\emph{Journal of Statistics and Data Science Education}, 1--12.

\leavevmode\hypertarget{ref-mclean2021controlled}{}%
McLean, Z. L., Appleby, S. J., Fermin, L. M., Henderson, H. V., Wei, J.,
Wells, D. N., \& Oback, B. (2021). Controlled cytoplast arrest and
morula aggregation enhance development, cryoresilience, and in vivo
survival of cloned sheep embryos. \emph{Cellular Reprogramming},
\emph{23}(1), 14--25.

\leavevmode\hypertarget{ref-CRAN}{}%
R Core Team. (2021). \emph{R: A language and environment for statistical
computing}. Vienna, Austria: R Foundation for Statistical Computing.

\leavevmode\hypertarget{ref-wickham2019welcome}{}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D.,
François, R., Grolemund, G., et al. (2019). Welcome to the tidyverse.
\emph{Journal of Open Source Software}, \emph{4}(43), 1686.

\end{CSLReferences}

\end{document}

### 2021-06-24 figs/paper/paper.Rmd
spellcheck

---
title: 'infer: An R package for tidyverse-friendly statistical inference'
tags:
  - data science
  - tidyverse
  - inference
  - R
authors:
- name: Simon Couch
  orcid: 0000-0001-5676-5107
  affiliation: "1, 2"
- name: Andrew Bray
  orcid: 0000-0002-4037-7414
  affiliation: 3
- name: Chester Ismay
  orcid: 0000-0003-2820-2547
  affiliation: 4
- name: Evgeni Chasnovski
  orcid: 0000-0002-1617-4019
  affiliation: 5
- name: Ben Baumer
  orcid: 0000-0002-3279-0516
  affiliation: 6
- name: Mine Çetinkaya-Rundel
  orcid: 0000-0001-6452-2420
  affiliation: "2, 7"
affiliations:
 - name: Johns Hopkins, Department of Biostatistics
   index: 1
 - name: RStudio
   index: 2
 - name: UC Berkeley, Department of Statistics and Reed College Mathematics Department (on leave)
   index: 3
 - name: Flatiron School
   index: 4
 - name: No Affiliation
   index: 5
 - name: Smith College, Program in Statistical & Data Sciences
   index: 6
 - name: Duke University, Department of Statistical Science
   index: 7

citation_author: Couch et. al.
date: 12 June 2021
year: 2021
bibliography: paper.bib
output: 
  rticles::joss_article:
    keep_tex: true
    includes:
      in_header: columns.tex
csl: apa.csl
journal: JOSS
---

# Summary

`infer` implements an expressive grammar to perform statistical inference that coheres with the `tidyverse` design framework [@wickham2019welcome]. Rather than providing methods for specific statistical tests, this package consolidates the principles that are shared among common hypothesis tests into a set of four main verbs (functions), supplemented with many utilities to visualize and extract value from their outputs.

# Statement of Need

Packages implementing methods for basic statistical inference in R are highly variable in their interfaces. The structure of inputted data, argument names, expected argument types, argument orders, output types, and spelling cases varies widely both within and among packages. This diversity in approaches obscures the intuition shared among common inferential procedures, makes details of usage difficult to remember, and prevents an expressive and idiomatic coding style.

infer is an R package for randomization-based hypothesis testing, naturalizing an intuitive understanding of statistical inference via a unified and expressive grammar. Four functions provide functionality encompassing a large swath of basic frequentist statistical inference, abstracting away details of specific tests and shifting the focus of the analyst to the observed data and the processes that generated it. Such a grammar lends itself to applications in teaching, data pedagogy research, applied scientific research, and advanced predictive modeling. For one, the principled approach of the package has made it especially well-fit for use in teaching introductory statistics [@ismay2019statistical; @baumer2020teaching] and research in data pedagogy [@cetinkaya2021fresh; @fergusson2021introducing; @loy2021bringing]. Further, the package has already seen usage in a number of published scientific applications [@mclean2021controlled; @ask2021per; @fallon2021single]. Finally, the package integrates with the greater tidymodels collection of packages, a burgeoning software ecosystem for tidyverse-aligned predictive modeling used across many modern research and industrial applications [@kuhn2020tidymodels]. To date, the package has been downloaded more than 400,000 times.

# Underlying Principles

Regardless of the hypothesis test in question, an analyst asks the same kind of question when conducting statistical inference: is the effect/difference in the observed data real, or due to random chance? To answer this question, the analyst begins by assuming that the effect in the observed data was simply due to random chance, and calls this assumption the *null hypothesis*. (In reality, they might not believe in the null hypothesis at all---the null hypothesis is in opposition to the *alternate hypothesis*, which supposes that the effect present in the observed data is actually due to the fact that "something is going on.") The analyst then calculates a *test statistic* from the data that describes the observed effect. They can use this test statistic to calculate a *p-value* via juxtaposition with a *null distribution*, giving the probability that the observed data could come about if the null hypothesis were true. If this probability is below some pre-defined *significance level* $\alpha$, then the analyst can reject the null hypothesis.

The workflow of this package is designed around this idea. Starting out with some dataset,

+ `specify()` allows the analyst to specify the variable, or relationship between variables, that they're interested in.
+ `hypothesize()` allows the analyst to declare the null hypothesis.
+ `generate()` allows the analyst to generate data reflecting the null hypothesis.
+ `calculate()` allows the analyst to calculate summary statistics, either from
     * the observed data, to form the observed test statistic.
     * data `generate()`d to reflect the null hypothesis, to form the randomization-based null distribution of test statistics.

As such, the ultimate output of an infer pipeline using these four functions is generally an _observed statistic_ or _null distribution_ of test statistics. These four functions are thus supplemented with many utilities to visualize and extract value from their outputs.

+ `visualize()` plots the null distribution of test statistics.
     * `shade_p_value()` situates the observed statistic in the null distribution, shading the region as or more extreme.
     * `shade_confidence_interval()` situates the confidence interval region in the null distribution, shading the region within the bounds.
+ `get_p_value()` calculates a p-value via the juxtaposition of the test statistic and null distribution.
+ `get_confidence_interval()` calculates a confidence interval via the juxtaposition of the test statistic and null distribution.

Beyond this, the package offers

* methods for inference using theory-based distributions
* shorthand wrappers for common statistical tests using tidy data
* model-fitting workflows to accommodate multiple explanatory variables

# Comparison to Other Packages

`broom` and `parameters` convert model objects to unified output formats, though do not provide methods for fitting models, describing null distributions, or calculating summary statistics from tabular data. `statsexpressions`, and adjacent packages in the `easystats` ecosystem, implement wrappers with consistent interfaces for theory-based hypothesis tests. At a higher level, the structure of each of these packages is defined by model types, where each model type has its own associated function and/or model object. In contrast, `infer` is structured around four functions, situating statistics and model types within a more abstracted grammar. `infer`'s initial release on the Comprehensive R Archive Network predated that of each of the packages mentioned above, with the exception of `broom` [@CRAN].

# Acknowledgements

We acknowledge contributions from Albert Kim, Jo Hardin, Jay Lee, Amelia McNamara, Nick Solomon, and Richie Cotton.

# References

### 2021-06-24 figs/paper/paper.tex
spellcheck

@@
 \item
-  \texttt{visualize()} plots the null distribution of test statistics
+  \texttt{visualize()} plots the null distribution of test statistics.
 
@@
     \texttt{shade\_p\_value()} situates the observed statistic in the
-    null distribution, shading the region as or more extreme
+    null distribution, shading the region as or more extreme.
   \item
     \texttt{shade\_confidence\_interval()} situates the confidence
-    interval region in the null distribution, shading the region with
-    the bounds
+    interval region in the null distribution, shading the region within
+    the bounds.
   \end{itemize}
@@
   \texttt{get\_p\_value()} calculates a p-value via the juxtaposition of
-  the test statistic and null distribution
+  the test statistic and null distribution.
 \item
   \texttt{get\_confidence\_interval()} calculates a confidence interval
-  via the juxtaposition of the test statistic and null distribution
+  via the juxtaposition of the test statistic and null distribution.
 \end{itemize}
@@
 \texttt{easystats} ecosystem, implement wrappers with consistent
-interfaces for theory-based hypothesis tests. The structure of each of
-these packages is defined by model types, where each model type has its
-own associated function and/or model object. In contrast, \texttt{infer}
-is structured around four functions, situating statistics and model
-types within a more abstracted grammar. \texttt{infer}'s initial release
-on the Comprehensive R Archive Network predated that of each of the
-packages mentioned above, with the exception of \texttt{broom} (R Core
-Team, 2021).
+interfaces for theory-based hypothesis tests. At a higher level, the
+structure of each of these packages is defined by model types, where
+each model type has its own associated function and/or model object. In
+contrast, \texttt{infer} is structured around four functions, situating
+statistics and model types within a more abstracted grammar.
+\texttt{infer}'s initial release on the Comprehensive R Archive Network
+predated that of each of the packages mentioned above, with the
+exception of \texttt{broom} (R Core Team, 2021).
 

### 2021-06-24 figs/paper/paper.tex
ben's edits

@@
 
-        \author[1, 2]{Simon Couch}
-          \author[3]{Andrew Bray}
+        \author[1, 2]{Simon P. Couch}
+          \author[3]{Andrew P. Bray}
           \author[4]{Chester Ismay}
           \author[5]{Evgeni Chasnovski}
-          \author[6]{Ben Baumer}
+          \author[6]{Benjamin S. Baumer}
           \author[2, 7]{Mine Çetinkaya-Rundel}
@@
 \texttt{infer} implements an expressive grammar to perform statistical
-inference that coheres with the \texttt{tidyverse} design framework
+inference that adheres to the \texttt{tidyverse} design framework
 (Wickham et al., 2019). Rather than providing methods for specific
@@
 
-infer is an R package for randomization-based hypothesis testing,
-naturalizing an intuitive understanding of statistical inference via a
-unified and expressive grammar. Four functions provide functionality
-encompassing a large swath of basic frequentist statistical inference,
-abstracting away details of specific tests and shifting the focus of the
-analyst to the observed data and the processes that generated it. Such a
-grammar lends itself to applications in teaching, data pedagogy
-research, applied scientific research, and advanced predictive modeling.
-For one, the principled approach of the package has made it especially
-well-fit for use in teaching introductory statistics (Baumer, Bray,
-Çetinkaya-Rundel, \& Hardin, 2020; Ismay \& Kim, 2019) and research in
-data pedagogy (Çetinkaya-Rundel \& Ellison, 2021; Fergusson \&
-Pfannkuch, 2021; Loy, 2021). Further, the package has already seen usage
-in a number of published scientific applications (Ask et al., 2021;
-Fallon \& Hinds, 2021; McLean et al., 2021). Finally, the package
-integrates with the greater tidymodels collection of packages, a
+\texttt{infer} is an R package for randomization-based hypothesis
+testing, naturalizing an intuitive understanding of statistical
+inference via a unified and expressive grammar. Four functions provide
+functionality encompassing a large swath of basic frequentist
+statistical inference, abstracting away details of specific tests and
+shifting the focus of the analyst to the observed data and the processes
+that generated it. Such a grammar lends itself to applications in
+teaching, data pedagogy research, applied scientific research, and
+advanced predictive modeling. For one, the principled approach of the
+package has made it an especially good fit for teaching introductory
+statistics (Baumer, Bray, Çetinkaya-Rundel, \& Hardin, 2020; Ismay \&
+Kim, 2019) and research in data pedagogy (Çetinkaya-Rundel \& Ellison,
+2021; Fergusson \& Pfannkuch, 2021; Loy, 2021). Further, the package has
+already seen usage in a number of published scientific applications (Ask
+et al., 2021; Fallon \& Hinds, 2021; McLean et al., 2021). Finally, the
+package integrates with the greater tidymodels collection of packages, a
 burgeoning software ecosystem for tidyverse-aligned predictive modeling
@@
   \texttt{specify()} allows the analyst to specify the variable, or
-  relationship between variables, that they're interested in.
+  relationship between variables, that they are interested in.
 \item
@@
 
-Beyond this, the package offers
+Beyond this, the package offers:
 
@@
 predated that of each of the packages mentioned above, with the
-exception of \texttt{broom} (R Core Team, 2021).
+exception of \texttt{broom}, a package situated in the same
+\texttt{tidymodels} ecosystem (R Core Team, 2021).
 
@@
 
-We acknowledge contributions from Albert Kim, Jo Hardin, Jay Lee, Amelia
-McNamara, Nick Solomon, and Richie Cotton.
+We acknowledge contributions from Albert Y. Kim, Jo Hardin, Jay Lee,
+Amelia McNamara, Nick Solomon, and Richie Cotton.
 
@@
 \emph{Environmental Toxicology and Chemistry}, \emph{40}(3), 820--831.
+doi:\href{https://doi.org/10.1002/etc.4978}{10.1002/etc.4978}
 
@@
 Statistics Education}, \emph{28}(1), 89--97.
+doi:\href{https://doi.org/10.1080/10691898.2020.1730734}{10.1080/10691898.2020.1730734}
 
@@
 Education}, \emph{29}(sup1), S16--S26.
+doi:\href{https://doi.org/10.1080/10691898.2020.1804497}{10.1080/10691898.2020.1804497}
 
@@
 160--167.
+doi:\href{https://doi.org/10.1016/j.bbrc.2021.03.129}{10.1016/j.bbrc.2021.03.129}
 
@@
 \emph{Mathematical Thinking and Learning}, 1--21.
+doi:\href{https://doi.org/10.1080/10986065.2021.1922856}{10.1080/10986065.2021.1922856}
 
@@
 science: A ModernDive into {R} and the tidyverse}. CRC Press.
+doi:\href{https://doi.org/10.1080/00224065.2020.1848366}{10.1080/00224065.2020.1848366}
 
@@
 for modeling and machine learning using tidyverse principles.
-\emph{Boston, MA, USA.}
+\emph{Boston, MA, USA.} Retrieved from \url{https://tidymodels.org}
 
@@
 \emph{Journal of Statistics and Data Science Education}, 1--12.
+doi:\href{https://doi.org/10.1080/26939169.2021.1920866}{10.1080/26939169.2021.1920866}
 
@@
 \emph{23}(1), 14--25.
+doi:\href{https://doi.org/10.1089/cell.2020.0078}{10.1089/cell.2020.0078}
 
@@
 computing}. Vienna, Austria: R Foundation for Statistical Computing.
+Retrieved from \url{https://www.R-project.org/}
 
@@
 \emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+doi:\href{https://doi.org/10.21105/joss.01686}{10.21105/joss.01686}
 

### 2021-06-25 figs/paper/paper.tex
mine's edits

@@
 statistical tests, this package consolidates the principles that are
-shared among common hypothesis tests into a set of four main verbs
-(functions), supplemented with many utilities to visualize and extract
-value from their outputs.
+shared among common hypothesis tests and confidence intervals into a set
+of four main verbs (functions), supplemented with many utilities to
+visualize and extract value from their outputs.
 
@@
 package has made it an especially good fit for teaching introductory
-statistics (Baumer, Bray, Çetinkaya-Rundel, \& Hardin, 2020; Ismay \&
-Kim, 2019) and research in data pedagogy (Çetinkaya-Rundel \& Ellison,
-2021; Fergusson \& Pfannkuch, 2021; Loy, 2021). Further, the package has
-already seen usage in a number of published scientific applications (Ask
-et al., 2021; Fallon \& Hinds, 2021; McLean et al., 2021). Finally, the
-package integrates with the greater tidymodels collection of packages, a
-burgeoning software ecosystem for tidyverse-aligned predictive modeling
-used across many modern research and industrial applications (Kuhn \&
-Wickham, 2020). To date, the package has been downloaded more than
-400,000 times.
+statistics and data science (Baumer, Bray, Çetinkaya-Rundel, \& Hardin,
+2020; Çetinkaya-Rundel \& Ellison, 2021; Ismay \& Kim, 2019) and
+research in data pedagogy (Fergusson \& Pfannkuch, 2021; Loy, 2021).
+Further, the package has already seen usage in a number of published
+scientific applications (Ask et al., 2021; Fallon \& Hinds, 2021; McLean
+et al., 2021). Finally, the package integrates with the greater
+tidymodels collection of packages, a burgeoning software ecosystem for
+tidyverse-aligned predictive modeling used across many modern research
+and industrial applications (Kuhn \& Wickham, 2020). To date, the
+package has been downloaded more than 400,000 times.
 
@@
   \texttt{generate()} allows the analyst to generate data reflecting the
-  null hypothesis.
+  null hypothesis or using the bootstrap.
 \item
@@
   \item
-    data \texttt{generate()}d to reflect the null hypothesis, to form
-    the randomization-based null distribution of test statistics.
+    data \texttt{generate()}d to reflect the null hypothesis, to form a
+    randomization-based null distribution of test statistics.
   \end{itemize}
@@
 distribution} of test statistics. These four functions are thus
-supplemented with many utilities to visualize and extract value from
+supplemented with several utilities to visualize and extract value from
 their outputs.
@@
     null distribution, shading the region as or more extreme.
-  \item
-    \texttt{shade\_confidence\_interval()} situates the confidence
-    interval region in the null distribution, shading the region within
-    the bounds.
   \end{itemize}
@@
   the test statistic and null distribution.
-\item
-  \texttt{get\_confidence\_interval()} calculates a confidence interval
-  via the juxtaposition of the test statistic and null distribution.
 \end{itemize}
+
+The workflow outlined above can also be used for constructing confidence
+intervals via bootstrapping with the omission of the
+\texttt{hypothesize()} step in the pipeline. The resulting bootstrap
+distribution can then be visualized with \texttt{visualize()}, the
+confidence interval region can be situated in the bootstrap distribution
+with \texttt{shade\_confidence\_interval()}, and the bounds of the
+confidence interval can be calculated with
+\texttt{get\_confidence\_interval()}.
 
@@
 output formats, though do not provide methods for fitting models,
-describing null distributions, or calculating summary statistics from
-tabular data. \texttt{statsexpressions}, and adjacent packages in the
-\texttt{easystats} ecosystem, implement wrappers with consistent
-interfaces for theory-based hypothesis tests. At a higher level, the
-structure of each of these packages is defined by model types, where
-each model type has its own associated function and/or model object. In
-contrast, \texttt{infer} is structured around four functions, situating
-statistics and model types within a more abstracted grammar.
-\texttt{infer}'s initial release on the Comprehensive R Archive Network
-predated that of each of the packages mentioned above, with the
-exception of \texttt{broom}, a package situated in the same
-\texttt{tidymodels} ecosystem (R Core Team, 2021).
+describing null distributions, performing bootstrapping, or calculating
+summary statistics from tabular data. \texttt{statsexpressions}, and
+adjacent packages in the \texttt{easystats} ecosystem, implement
+wrappers with consistent interfaces for theory-based hypothesis tests.
+At a higher level, the structure of each of these packages is defined by
+model types, where each model type has its own associated function
+and/or model object. In contrast, \texttt{infer} is structured around
+four functions, situating statistics and model types within a more
+abstracted grammar. \texttt{infer}'s initial release on the
+Comprehensive R Archive Network predated that of each of the packages
+mentioned above, with the exception of \texttt{broom}, a package
+situated in the same \texttt{tidymodels} ecosystem (R Core Team, 2021).
 

### 2021-07-09 figs/paper/paper.Rmd
Update figs/paper/paper.Rmd

@@
 authors:
-- name: Simon Couch
+- name: Simon P. Couch
   orcid: 0000-0001-5676-5107
   affiliation: "1, 2"
-- name: Andrew Bray
+- name: Andrew P. Bray
   orcid: 0000-0002-4037-7414
@@
   affiliation: 5
-- name: Ben Baumer
+- name: Benjamin S. Baumer
   orcid: 0000-0002-3279-0516
@@
 
-`infer` implements an expressive grammar to perform statistical inference that coheres with the `tidyverse` design framework [@wickham2019welcome].
-Rather than providing methods for specific statistical tests, this package consolidates the principles that are shared among common hypothesis tests into a set of four main verbs (functions), supplemented with many utilities to visualize and extract value from their outputs.
+`infer` implements an expressive grammar to perform statistical inference that adheres to the `tidyverse` design framework [@wickham2019welcome].
+Rather than providing methods for specific statistical tests, this package consolidates the principles that are shared among common hypothesis tests and confidence intervals into a set of four main verbs (functions), supplemented with many utilities to visualize and extract value from their outputs.
 
@@
 
-infer is an R package for randomization-based hypothesis testing, naturalizing an intuitive understanding of statistical inference via a unified and expressive grammar.
+`infer` is an R package for randomization-based hypothesis testing, naturalizing an intuitive understanding of statistical inference via a unified and expressive grammar.
 Four functions provide functionality encompassing a large swath of basic frequentist statistical inference, abstracting away details of specific tests and shifting the focus of the analyst to the observed data and the processes that generated it.
 Such a grammar lends itself to applications in teaching, data pedagogy research, applied scientific research, and advanced predictive modeling.
-For one, the principled approach of the package has made it especially well-fit for use in teaching introductory statistics [@ismay2019statistical; @baumer2020teaching] and research in data pedagogy [@cetinkaya2021fresh; @fergusson2021introducing; @loy2021bringing].
+For one, the principled approach of the package has made it an especially good fit for teaching introductory statistics and data science [@ismay2019statistical; @baumer2020teaching; @cetinkaya2021fresh] and research in data pedagogy [@fergusson2021introducing; @loy2021bringing].
 Further, the package has already seen usage in a number of published scientific applications [@mclean2021controlled; @ask2021per; @fallon2021single].
@@
 
-+ `specify()` allows the analyst to specify the variable, or relationship between variables, that they're interested in.
++ `specify()` allows the analyst to specify the variable, or relationship between variables, that they are interested in.
 + `hypothesize()` allows the analyst to declare the null hypothesis.
-+ `generate()` allows the analyst to generate data reflecting the null hypothesis.
++ `generate()` allows the analyst to generate data reflecting the null hypothesis or using the bootstrap.
 + `calculate()` allows the analyst to calculate summary statistics, either from
      * the observed data, to form the observed test statistic.
-     * data `generate()`d to reflect the null hypothesis, to form the randomization-based null distribution of test statistics.
+     * data `generate()`d to reflect the null hypothesis, to form a randomization-based null distribution of test statistics.
 
 As such, the ultimate output of an infer pipeline using these four functions is generally an _observed statistic_ or _null distribution_ of test statistics.
-These four functions are thus supplemented with many utilities to visualize and extract value from their outputs.
+These four functions are thus supplemented with several utilities to visualize and extract value from their outputs.
 
@@
      * `shade_p_value()` situates the observed statistic in the null distribution, shading the region as or more extreme.
-     * `shade_confidence_interval()` situates the confidence interval region in the null distribution, shading the region within the bounds.
 + `get_p_value()` calculates a p-value via the juxtaposition of the test statistic and null distribution.
-+ `get_confidence_interval()` calculates a confidence interval via the juxtaposition of the test statistic and null distribution.
 
-Beyond this, the package offers
+The workflow outlined above can also be used for constructing confidence intervals via bootstrapping with the omission of the `hypothesize()` step in the pipeline.
+The resulting bootstrap distribution can then be visualized with `visualize()`, the confidence interval region can be situated in the bootstrap distribution with `shade_confidence_interval()`, and the bounds of the confidence interval can be calculated with `get_confidence_interval()`.
+
+Beyond this, the package offers:
 
@@
 
-`broom` and `parameters` convert model objects to unified output formats, though do not provide methods for fitting models, describing null distributions, or calculating summary statistics from tabular data.
+`broom` and `parameters` convert model objects to unified output formats, though they do not provide methods for fitting models, describing null distributions, performing bootstrapping, or calculating summary statistics from tabular data.
 `statsexpressions`, and adjacent packages in the `easystats` ecosystem, implement wrappers with consistent interfaces for theory-based hypothesis tests.
@@
 In contrast, `infer` is structured around four functions, situating statistics and model types within a more abstracted grammar.
-`infer`'s initial release on the Comprehensive R Archive Network predated that of each of the packages mentioned above, with the exception of `broom` [@CRAN].
+`infer`'s initial release on the Comprehensive R Archive Network predated that of each of the packages mentioned above, with the exception of `broom`, a package situated in the same `tidymodels` ecosystem [@CRAN].
 
@@
 
-We acknowledge contributions from Albert Kim, Jo Hardin, Jay Lee, Amelia McNamara, Nick Solomon, and Richie Cotton.
+We acknowledge contributions from Albert Y. Kim, Jo Hardin, Jay Lee, Amelia McNamara, Nick Solomon, and Richie Cotton.
 

### 2021-07-10 figs/paper/paper.Rmd
Update figs/paper/paper.Rmd
"the package" -> "the `infer` package"

@@
 Such a grammar lends itself to applications in teaching, data pedagogy research, applied scientific research, and advanced predictive modeling.
-For one, the principled approach of the package has made it an especially good fit for teaching introductory statistics and data science [@ismay2019statistical; @baumer2020teaching; @cetinkaya2021fresh] and research in data pedagogy [@fergusson2021introducing; @loy2021bringing].
+For one, the principled approach of the `infer` package has made it an especially good fit for teaching introductory statistics and data science [@ismay2019statistical; @baumer2020teaching; @cetinkaya2021fresh] and research in data pedagogy [@fergusson2021introducing; @loy2021bringing].
 Further, the package has already seen usage in a number of published scientific applications [@mclean2021controlled; @ask2021per; @fallon2021single].
@@
      * `shade_p_value()` situates the observed statistic in the null distribution, shading the region as or more extreme.
-+ `get_p_value()` calculates a p-value via the juxtaposition of the test statistic and null distribution.
++ `get_p_value()` calculates a p-value via the juxtaposition of the test statistic and the null distribution.
 
@@
 
-Beyond this, the package offers:
+Beyond this, the `infer` package offers:
 

### 2021-07-11 figs/paper/paper.tex
note Downey's "there is only one test"

@@
 advanced predictive modeling. For one, the principled approach of the
-package has made it an especially good fit for teaching introductory
-statistics and data science (Baumer, Bray, Çetinkaya-Rundel, \& Hardin,
-2020; Çetinkaya-Rundel \& Ellison, 2021; Ismay \& Kim, 2019) and
-research in data pedagogy (Fergusson \& Pfannkuch, 2021; Loy, 2021).
-Further, the package has already seen usage in a number of published
-scientific applications (Ask et al., 2021; Fallon \& Hinds, 2021; McLean
-et al., 2021). Finally, the package integrates with the greater
-tidymodels collection of packages, a burgeoning software ecosystem for
-tidyverse-aligned predictive modeling used across many modern research
-and industrial applications (Kuhn \& Wickham, 2020). To date, the
-package has been downloaded more than 400,000 times.
+\texttt{infer} package has made it an especially good fit for teaching
+introductory statistics and data science (Baumer, Bray,
+Çetinkaya-Rundel, \& Hardin, 2020; Çetinkaya-Rundel \& Ellison, 2021;
+Ismay \& Kim, 2019) and research in data pedagogy (Fergusson \&
+Pfannkuch, 2021; Loy, 2021). Further, the package has already seen usage
+in a number of published scientific applications (Ask et al., 2021;
+Fallon \& Hinds, 2021; McLean et al., 2021). Finally, the package
+integrates with the greater tidymodels collection of packages, a
+burgeoning software ecosystem for tidyverse-aligned predictive modeling
+used across many modern research and industrial applications (Kuhn \&
+Wickham, 2020). To date, the package has been downloaded more than
+400,000 times.
 
@@
   \texttt{get\_p\_value()} calculates a p-value via the juxtaposition of
-  the test statistic and null distribution.
+  the test statistic and the null distribution.
 \end{itemize}
@@
 
-Beyond this, the package offers:
+Beyond this, the \texttt{infer} package offers:
 
@@
 \texttt{broom} and \texttt{parameters} convert model objects to unified
-output formats, though do not provide methods for fitting models,
+output formats, though they do not provide methods for fitting models,
 describing null distributions, performing bootstrapping, or calculating
@@
 four functions, situating statistics and model types within a more
-abstracted grammar. \texttt{infer}'s initial release on the
-Comprehensive R Archive Network predated that of each of the packages
-mentioned above, with the exception of \texttt{broom}, a package
-situated in the same \texttt{tidymodels} ecosystem (R Core Team, 2021).
+abstracted grammar.\footnote{This grammar follows from Allen Downey's
+  ``there is only one test'' framework (Downey, 2011).} \texttt{infer}'s
+initial release on the Comprehensive R Archive Network predated that of
+each of the packages mentioned above, with the exception of
+\texttt{broom}, a package situated in the same \texttt{tidymodels}
+ecosystem (R Core Team, 2021).
 
@@
 doi:\href{https://doi.org/10.1080/10691898.2020.1804497}{10.1080/10691898.2020.1804497}
+
+\leavevmode\hypertarget{ref-downey2011think}{}%
+Downey, A. B. (2011). \emph{Think stats}. " O'Reilly Media, Inc.".
 

### 2021-07-13 R/assume.R
clarify boot vs null distribution (closes #403)
Decided to tack edits re: #403 on to this PR as there are a few edits to related docs here. Null distributions are no longer be passed to CI functions in documentation!

@@ -11,7 +11,7 @@
 #' the distributional details supplied in the `distribution` and `df` arguments.
 #' However, `assume()` output can be passed to [visualize()], [get_p_value()],
 #' and [get_confidence_interval()] in the same way that simulation-based
-#' null distributions can.
+#' distributions can.
 #' 
 #' To define a theoretical null distribution (for use in hypothesis testing),
 #' be sure to provide a null hypothesis via [hypothesize()]. To define a

### 2021-07-13 R/visualize.R

@@ -53,7 +53,7 @@ ggplot2::ggplot_add
 #'
 #' @examples
 #'   
-#' # find a null distribution
+#' # generate a null distribution
 #' null_dist <- gss %>%
 #'   # we're interested in the number of hours worked per week
 #'   specify(response = hours) %>%
@@ -62,6 +62,13 @@ ggplot2::ggplot_add
 #'   # generating data points for a null distribution
 #'   generate(reps = 1000, type = "bootstrap") %>%
 #'   # calculating a distribution of means
+#'   calculate(stat = "mean")
+#'   
+#' # or a bootstrap distribution, omitting the hypothesize() step,
+#' # for use in confidence intervals
+#' boot_dist <- gss %>%
+#'   specify(response = hours) %>%
+#'   generate(reps = 1000, type = "bootstrap") %>%
 #'   calculate(stat = "mean")
 #'   
 #' # we can easily plot the null distribution by piping into visualize
@@ -75,7 +82,7 @@ ggplot2::ggplot_add
 #'   calculate(stat = "mean")
 #'   
 #' # find a confidence interval around the point estimate
-#' ci <- null_dist %>%
+#' ci <- boot_dist %>%
 #'   get_confidence_interval(point_estimate = point_estimate,
 #'                           # at the 95% confidence level
 #'                           level = .95,

### 2021-07-13 R/get_p_value.R
make `assume`s `df` argument optional

@@ -85,7 +85,7 @@
 #' # define a null distribution
 #' null_dist <- gss %>%
 #'   specify(response = hours) %>%
-#'   assume("t", nrow(gss) - 1)
+#'   assume("t")
 #' 
 #' # calculate a p-value
 #' get_p_value(null_dist, obs_stat, direction = "both")

### 2021-07-13 R/shade_p_value.R

@@ -58,7 +58,7 @@
 #' null_dist_theoretical <- gss %>%
 #'   specify(response = hours) %>%
 #'   hypothesize(null = "point", mu = 40) %>%
-#'   assume(distribution = "t", df = nrow(gss) - 1) 
+#'   assume(distribution = "t") 
 #'   
 #' null_dist_theoretical %>%
 #'   visualize() +

### 2021-07-13 R/visualize.R

@@ -104,7 +104,7 @@ ggplot2::ggplot_add
 #' sampling_dist <- gss %>%
 #'   specify(response = hours) %>%
 #'   hypothesize(null = "point", mu = 40) %>%
-#'   assume(distribution = "t", df = nrow(gss) - 1) 
+#'   assume(distribution = "t") 
 #'   
 #' visualize(sampling_dist)
 #' 

### 2021-07-13 tests/testthat/test-get_confidence_interval.R

@@ -258,7 +258,7 @@ test_that("theoretical CIs align with simulation-based (mean)", {
   null_dist_theor <- gss %>%
     specify(response = hours) %>%
     hypothesize(null = "point", mu = 40) %>%
-    assume(distribution = "t", nrow(gss) - 1)
+    assume(distribution = "t")
   
   expect_equal(
     get_confidence_interval(
@@ -326,7 +326,7 @@ test_that("theoretical CIs align with simulation-based (diff in means)", {
   
   null_dist_theor <- gss %>%
     specify(age ~ college) %>% 
-    assume(distribution = "t", nrow(gss) - 1)
+    assume(distribution = "t")
   
   expect_equal(
     get_confidence_interval(
@@ -386,7 +386,7 @@ test_that("theoretical CIs check arguments properly", {
   
   null_dist_theor <- gss %>%
     specify(age ~ college) %>% 
-    assume(distribution = "t", nrow(gss) - 1)
+    assume(distribution = "t")
   
   # check that type is handled correctly
   expect_equal(

### 2021-07-14 R/calculate.R
note lack of support for testing means via `"z"` (#368)

@@ -16,7 +16,9 @@
 #'   options include `"mean"`, `"median"`, `"sum"`, `"sd"`, `"prop"`, `"count"`,
 #'   `"diff in means"`, `"diff in medians"`, `"diff in props"`, `"Chisq"` (or
 #'   `"chisq"`), `"F"` (or `"f"`), `"t"`, `"z"`, `"ratio of props"`, `"slope"`,
-#'   `"odds ratio"`, and `"correlation"`.
+#'   `"odds ratio"`, and `"correlation"`. `infer` only supports theoretical 
+#'   tests on one or two means via the `"t"` distribution and one or two 
+#'   proportions via the `"z"`.
 #' @param order A string vector of specifying the order in which the levels of
 #'   the explanatory variable should be ordered for subtraction (or division
 #'   for ratio-based statistics), where `order = c("first", "second")` means 
@@ -35,6 +37,7 @@
 #' cases will be NaN. The package will omit non-finite values from
 #' visualizations (with a warning) and raise an error in p-value calculations.
 #'
+#' 
 #' @examples
 #'
 #' # calculate a null distribution of hours worked per week under

### 2021-07-14 R/assume.R
recommend `hypothesize()`ing for obs stat, not before `assume()`

@@ -57,39 +57,35 @@
 #' # with the `partyid` explanatory variable
 #' gss %>% 
 #'   specify(age ~ partyid) %>% 
-#'   hypothesize(null = "independence") %>%
 #'   assume(distribution = "F")
 #' 
 #' # Chi-squared goodness of fit distribution
 #' # on the `finrela` variable
 #' gss %>%
 #'   specify(response = finrela) %>%
-#'     hypothesize(null = "point",
-#'                 p = c("far below average" = 1/6,
-#'                       "below average" = 1/6,
-#'                       "average" = 1/6,
-#'                       "above average" = 1/6,
-#'                       "far above average" = 1/6,
-#'                       "DK" = 1/6)) %>%
+#'   hypothesize(null = "point",
+#'               p = c("far below average" = 1/6,
+#'                     "below average" = 1/6,
+#'                     "average" = 1/6,
+#'                     "above average" = 1/6,
+#'                     "far above average" = 1/6,
+#'                     "DK" = 1/6)) %>%
 #'   assume("Chisq")
 #' 
 #' # Chi-squared test of independence
 #' # on the `finrela` and `sex` variables
 #' gss %>%
 #'   specify(formula = finrela ~ sex) %>%
-#'   hypothesize(null = "independence") %>%
 #'   assume(distribution = "Chisq")
 #' 
 #' # T distribution
 #' gss %>% 
 #'   specify(age ~ college) %>%
-#'   hypothesize(null = "independence") %>%
 #'   assume("t")
 #' 
 #' # Z distribution
 #' gss %>%
 #'   specify(response = sex, success = "female") %>%
-#'   hypothesize(null = "point", p = .5) %>%
 #'   assume("z")
 #' 
 #' \dontrun{
@@ -107,7 +103,6 @@
 #' # construct a null distribution
 #' null_dist <- gss %>%
 #'   specify(response = hours) %>%
-#'   hypothesize(null = "point", mu = 40) %>%
 #'   assume("t")
 #' 
 #' # juxtapose them visually
@@ -128,7 +123,6 @@
 #' # construct a null distribution
 #' null_dist <- gss %>% 
 #'   specify(age ~ partyid) %>%
-#'   hypothesize(null = "independence") %>%
 #'   assume(distribution = "F")
 #' 
 #' # juxtapose them visually

### 2021-07-14 R/shade_confidence_interval.R

@@ -66,7 +66,6 @@
 #' # align with the confidence interval
 #' sampling_dist <- gss %>%
 #'   specify(response = hours) %>%
-#'   hypothesize(null = "point", mu = 40) %>%
 #'   assume(distribution = "t") 
 #'   
 #' visualize(sampling_dist) +

### 2021-07-14 R/shade_p_value.R

@@ -57,7 +57,6 @@
 #' # theoretical distributions, too!
 #' null_dist_theoretical <- gss %>%
 #'   specify(response = hours) %>%
-#'   hypothesize(null = "point", mu = 40) %>%
 #'   assume(distribution = "t") 
 #'   
 #' null_dist_theoretical %>%

### 2021-07-14 R/visualize.R

@@ -103,7 +103,6 @@ ggplot2::ggplot_add
 #' # a theory-based distribution with `assume()`
 #' sampling_dist <- gss %>%
 #'   specify(response = hours) %>%
-#'   hypothesize(null = "point", mu = 40) %>%
 #'   assume(distribution = "t") 
 #'   
 #' visualize(sampling_dist)

### 2021-07-30 figs/paper/paper.Rmd
note `mosaic`, adjust citation

@@
 
+Several software packages on the Comprehensive R Archive Network share functionality with `infer` [@CRAN].
 `broom` and `parameters` convert model objects to unified output formats, though they do not provide methods for fitting models, describing null distributions, performing bootstrapping, or calculating summary statistics from tabular data.
 `statsexpressions`, and adjacent packages in the `easystats` ecosystem, implement wrappers with consistent interfaces for theory-based hypothesis tests.
-At a higher level, the structure of each of these packages is defined by model types, where each model type has its own associated function and/or model object.
-In contrast, `infer` is structured around four functions, situating statistics and model types within a more abstracted grammar.
-`infer`'s initial release on the Comprehensive R Archive Network predated that of each of the packages mentioned above, with the exception of `broom`, a package situated in the same `tidymodels` ecosystem [@CRAN].
+Similarly, `mosaic` is a package used to teach statistics by unifying summary statistics, visualization, and modeling with a consistent API built around R's formula interface.
+The `mosaic` package also includes functionality to conduct randomization-based inference.
+At a higher level, though, the structure of each of these packages is defined by model types and statistics, where each model type or statistic has its own associated function and/or object class.
+In contrast, `infer` is structured around four functions, situating statistics and model types within a more abstracted grammar.^[This grammar follows from Allen Downey's "there is only one test" framework [@downey2016].]
 

### 2021-07-30 figs/paper/paper.tex
note `mosaic`, adjust citation

@@
 
-\texttt{broom} and \texttt{parameters} convert model objects to unified
-output formats, though they do not provide methods for fitting models,
-describing null distributions, performing bootstrapping, or calculating
-summary statistics from tabular data. \texttt{statsexpressions}, and
-adjacent packages in the \texttt{easystats} ecosystem, implement
-wrappers with consistent interfaces for theory-based hypothesis tests.
-At a higher level, the structure of each of these packages is defined by
-model types, where each model type has its own associated function
-and/or model object. In contrast, \texttt{infer} is structured around
-four functions, situating statistics and model types within a more
-abstracted grammar.\footnote{This grammar follows from Allen Downey's
-  ``there is only one test'' framework (Downey, 2011).} \texttt{infer}'s
-initial release on the Comprehensive R Archive Network predated that of
-each of the packages mentioned above, with the exception of
-\texttt{broom}, a package situated in the same \texttt{tidymodels}
-ecosystem (R Core Team, 2021).
+Several software packages on the Comprehensive R Archive Network share
+functionality with \texttt{infer} (R Core Team, 2021). \texttt{broom}
+and \texttt{parameters} convert model objects to unified output formats,
+though they do not provide methods for fitting models, describing null
+distributions, performing bootstrapping, or calculating summary
+statistics from tabular data. \texttt{statsexpressions}, and adjacent
+packages in the \texttt{easystats} ecosystem, implement wrappers with
+consistent interfaces for theory-based hypothesis tests. Similarly,
+\texttt{mosaic} is a package used to teach statistics by unifying
+summary statistics, visualization, and modeling with a consistent API
+built around R's formula interface. The \texttt{mosaic} package also
+includes functionality to conduct randomization-based inference. At a
+higher level, though, the structure of each of these packages is defined
+by model types and statistics, where each model type or statistic has
+its own associated function and/or object class. In contrast,
+\texttt{infer} is structured around four functions, situating statistics
+and model types within a more abstracted grammar.\footnote{This grammar
+  follows from Allen Downey's ``there is only one test'' framework
+  (Downey, 2016).}
 
@@
 
-\leavevmode\hypertarget{ref-downey2011think}{}%
-Downey, A. B. (2011). \emph{Think stats}. " O'Reilly Media, Inc.".
+\leavevmode\hypertarget{ref-downey2016}{}%
+Downey, A. B. (2016). There is still only one test.
 

### 2021-08-10 README.Rmd
standardize distribution naming

@@
 ```{r, message = FALSE, warning = FALSE}
-null_distn <- gss %>%
+null_dist <- gss %>%
    specify(age ~ partyid) %>%
@@
 ```{r viz, message = FALSE, warning = FALSE, eval = FALSE}
-visualize(null_distn) +
+visualize(null_dist) +
   shade_p_value(obs_stat = F_hat, direction = "greater")
@@
 ```{r, message = FALSE, warning = FALSE}
-null_distn %>%
+null_dist %>%
   get_p_value(obs_stat = F_hat, direction = "greater")

### 2021-08-10 R/shade_p_value.R

@@ -55,11 +55,11 @@
 #'   
 #' # you can shade confidence intervals on top of
 #' # theoretical distributions, too!
-#' null_dist_theoretical <- gss %>%
+#' null_dist_theor <- gss %>%
 #'   specify(response = hours) %>%
 #'   assume(distribution = "t") 
 #'   
-#' null_dist_theoretical %>%
+#' null_dist_theor %>%
 #'   visualize() +
 #'   shade_p_value(obs_stat = point_estimate, direction = "two-sided")
 #' 

### 2021-09-07 man-roxygen/seeds.Rmd
add `man-roxygen` section on `set.seed`

# Reproducibility

When using the infer package for research, or in other cases when exact reproducibility is a priority, be sure the set the seed for R's random number generator. infer will respect the random seed specified in the `set.seed()` function, returning the same results when `generate()`ing new data given an identical seed. For instance, we can calculate the difference in mean `age` by `college` degree status using the `gss` dataset from 10 versions of the `gss` resampled with permutation using the following code.

```{r, include = FALSE}
library(infer)
```

```{r}
set.seed(1)

gss %>%
  specify(age ~ college) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 5, type = "permute") %>%
  calculate("diff in means", order = c("degree", "no degree"))
```

Setting the seed again and rerunning the same code will result in the same answer.

```{r}
# set the seed
set.seed(1)

gss %>%
  specify(age ~ college) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 5, type = "permute") %>%
  calculate("diff in means", order = c("degree", "no degree"))
```

Please keep this in mind when writing infer code that utilizes resampling with `generate()`.

### 2021-09-07 R/fit.R

@@ -72,6 +72,8 @@ generics::fit
 #' multivariate analysis of variance and regression" (Marti J. Anderson,
 #' 2001), \doi{10.1139/cjfas-58-3-626}.
 #' 
+#' @includeRmd man-roxygen/seeds.Rmd
+#' 
 #' @examples
 #' # fit a linear model predicting number of hours worked per
 #' # week using respondent age and degree status.

### 2021-09-07 man-roxygen/seeds.Rmd
update wording with Mine's suggestion

@@
 When using the infer package for research, or in other cases when exact reproducibility is a priority, be sure the set the seed for R's random number generator.
-infer will respect the random seed specified in the `set.seed()` function, returning the same results when `generate()`ing new data given an identical seed.
+infer will respect the random seed specified in the `set.seed()` function, returning the same result when `generate()`ing data given an identical seed.
 For instance, we can calculate the difference in mean `age` by `college` degree status using the `gss` dataset from 10 versions of the `gss` resampled with permutation using the following code.
@@
 
-Setting the seed again and rerunning the same code will result in the same answer.
+Setting the seed to the same value again and rerunning the same code will produce the same result.
 

### 2021-09-12 figs/paper/paper.tex
refine JOSS paper citations

@@
 distributions, performing bootstrapping, or calculating summary
-statistics from tabular data. \texttt{statsexpressions}, and adjacent
-packages in the \texttt{easystats} ecosystem, implement wrappers with
-consistent interfaces for theory-based hypothesis tests. Similarly,
-\texttt{mosaic} is a package used to teach statistics by unifying
-summary statistics, visualization, and modeling with a consistent API
-built around R's formula interface. The \texttt{mosaic} package also
-includes functionality to conduct randomization-based inference. At a
+statistics from tabular data (Lüdecke, Ben-Shachar, Patil, \& Makowski,
+2020; Robinson, Hayes, \& Couch, 2021). \texttt{statsExpressions}, and
+adjacent packages in the \texttt{easystats} ecosystem, implement
+wrappers with consistent interfaces for theory-based hypothesis tests
+(Patil, 2021). Similarly, \texttt{mosaic} is a package used to teach
+statistics by unifying summary statistics, visualization, and modeling
+with a consistent API built around R's formula interface. The
+\texttt{mosaic} package also includes functionality to conduct
+randomization-based inference (Pruim, Kaplan, \& Horton, 2017). At a
 higher level, though, the structure of each of these packages is defined
@@
 \leavevmode\hypertarget{ref-downey2016}{}%
-Downey, A. B. (2016). There is still only one test.
+Downey, A. B. (2016). There is still only one test. Retrieved from
+\url{http://allendowney.blogspot.com/2016/06/there-is-still-only-one-test.html}
 
@@
 
+\leavevmode\hypertarget{ref-r-parameters}{}%
+Lüdecke, D., Ben-Shachar, M. S., Patil, I., \& Makowski, D. (2020).
+Extracting, computing and exploring the parameters of statistical models
+using {R}. \emph{Journal of Open Source Software}, \emph{5}(53), 2445.
+doi:\href{https://doi.org/10.21105/joss.02445}{10.21105/joss.02445}
+
 \leavevmode\hypertarget{ref-mclean2021controlled}{}%
@@
 
+\leavevmode\hypertarget{ref-r-statsExpressions}{}%
+Patil, I. (2021). {statsExpressions: {R} Package for Tidy Dataframes and
+Expressions with Statistical Details}. \emph{{Journal of Open Source
+Software}}, \emph{6}(61), 3236.
+doi:\href{https://doi.org/10.21105/joss.03236}{10.21105/joss.03236}
+
+\leavevmode\hypertarget{ref-r-mosaic}{}%
+Pruim, R., Kaplan, D. T., \& Horton, N. J. (2017). The mosaic package:
+Helping students to 'think with data' using r. \emph{The R Journal},
+\emph{9}(1), 77--102. Retrieved from
+\url{https://journal.r-project.org/archive/2017/RJ-2017-024/index.html}
+
 \leavevmode\hypertarget{ref-CRAN}{}%
@@
 Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-r-broom}{}%
+Robinson, D., Hayes, A., \& Couch, S. (2021). \emph{Broom: Convert
+statistical objects into tidy tibbles}. Retrieved from
+\url{https://CRAN.R-project.org/package=broom}
 

### 2021-10-28 README.Rmd
Move to "main"

@@
 
-# infer R Package <img src="https://github.com/tidymodels/infer/blob/master/figs/infer_gnome.png?raw=true" align="right" width=280 />
+# infer R Package <img src="figs/infer_gnome.png" align="right" width=280 />
 
@@
 <!--http://www.r-pkg.org/badges/version/infer-->
-<!--figs/master.svg-->
-<!--https://img.shields.io/codecov/c/github/tidymodels/infer/master.svg-->
+<!--figs/main.svg-->
+<!--https://img.shields.io/codecov/c/github/tidymodels/infer/main.svg-->
 
-[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)[![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/master.svg)](https://codecov.io/github/tidymodels/infer/?branch=master)
+[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)[![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/main.svg)](https://codecov.io/github/tidymodels/infer/?branch=main)
 
@@
 From left to right, each step is connected by an arrow, while the diagram indicates that generating data and calculating statistics can happen iteratively."}
-knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/figs/ht-diagram.png")
+knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/main/figs/ht-diagram.png")
 ```
@@
 We welcome others helping us make this package as user-friendly and efficient as possible.
-Please review our [contributing](https://github.com/tidymodels/infer/blob/master/CONTRIBUTING.md) and [conduct](https://github.com/tidymodels/infer/blob/master/CONDUCT.md) guidelines.
+Please review our [contributing](https://github.com/tidymodels/infer/blob/main/CONTRIBUTING.md) and [conduct](https://github.com/tidymodels/infer/blob/main/CONDUCT.md) guidelines.
 By participating in this project you agree to abide by its terms.
@@
 The region of the histogram to the right of the observed statistic, just above two, is shaded red to represent the p-value."}
-knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/README_files/figure-gfm/viz-1.png")
+knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/main/README_files/figure-gfm/viz-1.png")
 ```

### 2022-04-12 README.Rmd
update badges

@@
 
-[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)[![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/main.svg)](https://codecov.io/github/tidymodels/infer/?branch=main)
+[![R-CMD-check](https://github.com/tidymodels/infer/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/tidymodels/infer/actions/workflows/check-standard.yaml)
+[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)
+[![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/main.svg)](https://codecov.io/github/tidymodels/infer/?branch=main)
 

### 2022-04-12 README.Rmd
address pkgdown warnings
* vignette metadata
* use hex included in built package for pkgdown site

@@
 
-# infer R Package <img src="figs/infer_gnome.png" align="right" width=280 />
+# infer R Package <img src="man/figures/infer.png" align="right" width=280 />
 
@@
 ```{r load-package, echo = FALSE, message = FALSE, warning = FALSE}
-library(devtools)
-devtools::load_all()
+library(infer)
 ```

### 2022-12-01 README.Rmd
bump redirecting URLs

@@
 
-For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on RStudio Community](https://rstd.io/tidymodels-community).
+For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on RStudio Community](https://community.rstudio.com/new-topic?category_id=15&tags=tidymodels,question).
 If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/infer/issues).
-Either way, learn how to create and share a [reprex](https://rstd.io/reprex) (a minimal, reproducible example), to clearly communicate about your code.
+Either way, learn how to create and share a [reprex](https://reprex.tidyverse.org/articles/learn-reprex.html) (a minimal, reproducible example), to clearly communicate about your code.
 Check out further details on [contributing guidelines for tidymodels packages](https://www.tidymodels.org/contribute/) and [how to get help](https://www.tidymodels.org/help/).

### 2023-03-06 README.Rmd
RStudio -> Posit

@@
 
-For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on RStudio Community](https://community.rstudio.com/new-topic?category_id=15&tags=tidymodels,question).
+For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on Posit Community](https://community.rstudio.com/new-topic?category_id=15&tags=tidymodels,question).
 If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/infer/issues).

### 2023-03-07 README.Rmd
`usethis::use_tidy_logo()`

@@
 
-# infer R Package <img src="man/figures/infer.png" align="right" width=280 />
+# infer R Package <img src="man/figures/logo.png" align="right" width=280 />
 
@@
 ```{r, eval = FALSE}
-install.packages("remotes")
-remotes::install_github("tidymodels/infer")
+# install.packages("pak")
+pak::pak("tidymodels/infer")
 ```

### 2023-09-06 README.Rmd
release v1.0.5 (#506)

@@
 We welcome others helping us make this package as user-friendly and efficient as possible.
-Please review our [contributing](https://github.com/tidymodels/infer/blob/main/CONTRIBUTING.md) and [conduct](https://github.com/tidymodels/infer/blob/main/CONDUCT.md) guidelines.
+Please review our [contributing](https://github.com/tidymodels/infer/blob/main/CONTRIBUTING.md) and [conduct](https://github.com/tidymodels/infer/blob/main/.github/CODE_OF_CONDUCT.md) guidelines.
 By participating in this project you agree to abide by its terms.

### 2024-01-31 README.Rmd
describe package logo (closes #512)
in general, the package is in a good spot with alt text.
transition redirecting URL

@@
 
-# infer R Package <img src="man/figures/logo.png" align="right" width=280 />
+# infer R Package <img src="man/figures/logo.png" alt="A hexagonal logo.
+A silhouette of a fir tree sits atop green text, reading 'infer'.
+The logo has a white background and green border." align="right" width=280 />
 
@@
 [![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)
-[![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/main.svg)](https://codecov.io/github/tidymodels/infer/?branch=main)
+[![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/main.svg)](https://app.codecov.io/github/tidymodels/infer/?branch=main)
 

### 2024-03-26 README.Rmd
infer 1.0.7 release candidate (#536)
* update redirecting URL

* update CRAN comments

* Increment version number to 1.0.7

@@
 
-For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on Posit Community](https://community.rstudio.com/new-topic?category_id=15&tags=tidymodels,question).
+For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on Posit Community](https://forum.posit.co/new-topic?category_id=15&tags=tidymodels,question).
 If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/infer/issues).

### 2024-08-15 README.Rmd
update README to fit the tidy formatting
Deleted backticks from the packages' names and added commas after i.e.

@@
 
-The objective of this package is to perform statistical inference using an expressive statistical grammar that coheres with the `tidyverse` design framework.
+The objective of this package is to perform statistical inference using an expressive statistical grammar that coheres with the tidyverse design framework.
 The package is centered around 4 main verbs, supplemented with many utilities to visualize and extract value from their outputs.
@@
 
-To install the current stable version of `infer` from CRAN:
+To install the current stable version of infer from CRAN:
 
@@
 
-To install the developmental stable version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at [infer.tidymodels.org](https://infer.tidymodels.org/).
+To install the developmental stable version of infer, make sure to install remotes first. The `pkgdown` website for this version is at [infer.tidymodels.org](https://infer.tidymodels.org/).
 
@@
 
-Note that the formula and non-formula interfaces  (i.e.
-`age ~ partyid` vs.
+Note that the formula and non-formula interfaces  (i.e., `age ~ partyid` vs.
 `response = age, explanatory =  partyid`) work for all implemented inference procedures in `infer`.

### 2025-04-25 README.Rmd
apply suggestion from review
transition to the base pipe

@@
 
-To install the developmental stable version of infer, make sure to install remotes first. The `pkgdown` website for this version is at [infer.tidymodels.org](https://infer.tidymodels.org/).
+To install the developmental stable version of infer, make sure to install remotes first. The pkgdown website for this version is at [infer.tidymodels.org](https://infer.tidymodels.org/).
 
@@
 ```{r, message = FALSE, warning = FALSE}
-F_hat <- gss %>% 
-  specify(age ~ partyid) %>%
+F_hat <- gss |> 
+  specify(age ~ partyid) |>
   calculate(stat = "F")
@@
 ```{r, message = FALSE, warning = FALSE}
-null_dist <- gss %>%
-   specify(age ~ partyid) %>%
-   hypothesize(null = "independence") %>%
-   generate(reps = 1000, type = "permute") %>%
+null_dist <- gss |>
+   specify(age ~ partyid) |>
+   hypothesize(null = "independence") |>
+   generate(reps = 1000, type = "permute") |>
    calculate(stat = "F")
@@
 ```{r, message = FALSE, warning = FALSE}
-null_dist %>%
+null_dist |>
   get_p_value(obs_stat = F_hat, direction = "greater")

### 2025-04-25 R/generate.R

@@ -46,24 +46,24 @@
 #'
 #' @examples
 #' # generate a null distribution by taking 200 bootstrap samples
-#' gss %>%
-#'  specify(response = hours) %>%
-#'  hypothesize(null = "point", mu = 40) %>%
+#' gss |>
+#'  specify(response = hours) |>
+#'  hypothesize(null = "point", mu = 40) |>
 #'  generate(reps = 200, type = "bootstrap")
 #'
 #' # generate a null distribution for the independence of
 #' # two variables by permuting their values 200 times
-#' gss %>%
-#'  specify(partyid ~ age) %>%
-#'  hypothesize(null = "independence") %>%
+#' gss |>
+#'  specify(partyid ~ age) |>
+#'  hypothesize(null = "independence") |>
 #'  generate(reps = 200, type = "permute")
 #'
 #' # generate a null distribution via sampling from a
 #' # binomial distribution 200 times
-#' gss %>%
-#' specify(response = sex, success = "female") %>%
-#'   hypothesize(null = "point", p = .5) %>%
-#'   generate(reps = 200, type = "draw") %>%
+#' gss |>
+#' specify(response = sex, success = "female") |>
+#'   hypothesize(null = "point", p = .5) |>
+#'   generate(reps = 200, type = "draw") |>
 #'   calculate(stat = "z")
 #'
 #' # more in-depth explanation of how to use the infer package
@@ -257,9 +257,9 @@ permute <- function(x, reps = 1, variables, ..., call = caller_env()) {
     reps,
     permute_once(x, variables, call = call),
     simplify = FALSE
-  ) %>%
-    dplyr::bind_rows() %>%
-    dplyr::mutate(replicate = rep(1:reps, each = !!nrow_x)) %>%
+  ) |>
+    dplyr::bind_rows() |>
+    dplyr::mutate(replicate = rep(1:reps, each = !!nrow_x)) |>
     group_by_replicate(reps, nrow_x)
 
   df_out <- copy_attrs(to = df_out, from = x)

### 2025-04-25 R/get_confidence_interval.R

@@ -64,15 +64,15 @@
 #'
 #' @examples
 #'
-#' boot_dist <- gss %>%
+#' boot_dist <- gss |>
 #'   # We're interested in the number of hours worked per week
-#'   specify(response = hours) %>%
+#'   specify(response = hours) |>
 #'   # Generate bootstrap samples
-#'   generate(reps = 1000, type = "bootstrap") %>%
+#'   generate(reps = 1000, type = "bootstrap") |>
 #'   # Calculate mean of each bootstrap sample
 #'   calculate(stat = "mean")
 #'
-#' boot_dist %>%
+#' boot_dist |>
 #'   # Calculate the confidence interval around the point estimate
 #'   get_confidence_interval(
 #'     # At the 95% confidence level; percentile method
@@ -80,11 +80,11 @@
 #'   )
 #'
 #' # for type = "se" or type = "bias-corrected" we need a point estimate
-#' sample_mean <- gss %>%
-#'   specify(response = hours) %>%
+#' sample_mean <- gss |>
+#'   specify(response = hours) |>
 #'   calculate(stat = "mean")
 #'
-#' boot_dist %>%
+#' boot_dist |>
 #'   get_confidence_interval(
 #'     point_estimate = sample_mean,
 #'     # At the 95% confidence level
@@ -96,8 +96,8 @@
 #' # using a theoretical distribution -----------------------------------
 #'
 #' # define a sampling distribution
-#' sampling_dist <- gss %>%
-#'   specify(response = hours) %>%
+#' sampling_dist <- gss |>
+#'   specify(response = hours) |>
 #'   assume("t")
 #'
 #' # get the confidence interval---note that the
@@ -112,8 +112,8 @@
 #'
 #' # fit a linear model predicting number of hours worked per
 #' # week using respondent age and degree status.
-#' observed_fit <- gss %>%
-#'   specify(hours ~ age + college) %>%
+#' observed_fit <- gss |>
+#'   specify(hours ~ age + college) |>
 #'   fit()
 #'
 #' observed_fit
@@ -121,10 +121,10 @@
 #' # fit 100 models to resamples of the gss dataset, where the response
 #' # `hours` is permuted in each. note that this code is the same as
 #' # the above except for the addition of the `generate` step.
-#' null_fits <- gss %>%
-#'   specify(hours ~ age + college) %>%
-#'   hypothesize(null = "independence") %>%
-#'   generate(reps = 100, type = "permute") %>%
[…]

### 2025-04-25 R/get_p_value.R

@@ -57,34 +57,34 @@
 #' # using a simulation-based null distribution ------------------------------
 #'
 #' # find the point estimate---mean number of hours worked per week
-#' point_estimate <- gss %>%
-#'   specify(response = hours) %>%
+#' point_estimate <- gss |>
+#'   specify(response = hours) |>
 #'   calculate(stat = "mean")
 #'
 #' # starting with the gss dataset
-#' gss %>%
+#' gss |>
 #'   # ...we're interested in the number of hours worked per week
-#'   specify(response = hours) %>%
+#'   specify(response = hours) |>
 #'   # hypothesizing that the mean is 40
-#'   hypothesize(null = "point", mu = 40) %>%
+#'   hypothesize(null = "point", mu = 40) |>
 #'   # generating data points for a null distribution
-#'   generate(reps = 1000, type = "bootstrap") %>%
+#'   generate(reps = 1000, type = "bootstrap") |>
 #'   # finding the null distribution
-#'   calculate(stat = "mean") %>%
+#'   calculate(stat = "mean") |>
 #    # calculate the p-value for the point estimate
 #'   get_p_value(obs_stat = point_estimate, direction = "two-sided")
 #'
 #' # using a theoretical null distribution -----------------------------------
 #'
 #' # calculate the observed statistic
-#' obs_stat <- gss %>%
-#'   specify(response = hours) %>%
-#'   hypothesize(null = "point", mu = 40) %>%
+#' obs_stat <- gss |>
+#'   specify(response = hours) |>
+#'   hypothesize(null = "point", mu = 40) |>
 #'   calculate(stat = "t")
 #'
 #' # define a null distribution
-#' null_dist <- gss %>%
-#'   specify(response = hours) %>%
+#' null_dist <- gss |>
+#'   specify(response = hours) |>
 #'   assume("t")
 #'
 #' # calculate a p-value
@@ -94,8 +94,8 @@
 #'
 #' # fit a linear model predicting number of hours worked per
 #' # week using respondent age and degree status.
-#' observed_fit <- gss %>%
-#'   specify(hours ~ age + college) %>%
+#' observed_fit <- gss |>
+#'   specify(hours ~ age + college) |>
 #'   fit()
 #'
 #' observed_fit
@@ -103,10 +103,10 @@
 #' # fit 100 models to resamples of the gss dataset, where the response
 #' # `hours` is permuted in each. note that this code is the same as
[…]

### 2025-04-25 R/hypothesize.R

@@ -36,13 +36,13 @@
 #'
 #' @examples
 #' # hypothesize independence of two variables
-#' gss %>%
-#'  specify(college ~ partyid, success = "degree") %>%
+#' gss |>
+#'  specify(college ~ partyid, success = "degree") |>
 #'  hypothesize(null = "independence")
 #'
 #' # hypothesize a mean number of hours worked per week of 40
-#' gss %>%
-#'   specify(response = hours) %>%
+#' gss |>
+#'   specify(response = hours) |>
 #'   hypothesize(null = "point", mu = 40)
 #'
 #' # more in-depth explanation of how to use the infer package

### 2025-04-25 R/observe.R

@@ -17,22 +17,22 @@
 #'
 #' @examples
 #' # calculating the observed mean number of hours worked per week
-#' gss %>%
+#' gss |>
 #'   observe(hours ~ NULL, stat = "mean")
 #'
 #' # equivalently, calculating the same statistic with the core verbs
-#' gss %>%
-#'   specify(response = hours) %>%
+#' gss |>
+#'   specify(response = hours) |>
 #'   calculate(stat = "mean")
 #'
 #' # calculating a t statistic for hypothesized mu = 40 hours worked/week
-#' gss %>%
+#' gss |>
 #'   observe(hours ~ NULL, stat = "t", null = "point", mu = 40)
 #'
 #' # equivalently, calculating the same statistic with the core verbs
-#' gss %>%
-#'   specify(response = hours) %>%
-#'   hypothesize(null = "point", mu = 40) %>%
+#' gss |>
+#'   specify(response = hours) |>
+#'   hypothesize(null = "point", mu = 40) |>
 #'   calculate(stat = "t")
 #'
 #' # similarly for a difference in means in age based on whether
@@ -45,8 +45,8 @@
 #' )
 #'
 #' # equivalently, calculating the same statistic with the core verbs
-#' gss %>%
-#'   specify(age ~ college) %>%
+#' gss |>
+#'   specify(age ~ college) |>
 #'   calculate("diff in means", order = c("degree", "no degree"))
 #'
 #' # for a more in-depth explanation of how to use the infer package
@@ -104,27 +104,30 @@ observe <- function(
   }
 
   # pass arguments on to core verbs
-  specify(
+  res <- 
+    specify(
     x = x,
     formula = formula,
     response = {{ response }},
     explanatory = {{ explanatory }},
     success = success
-  ) %>%
-    hypothesize_fn(
-      null = if (has_explanatory(.)) {
-        "independence"
-      } else {
-        "point"
-      },
-      p = p,
-      mu = mu,
-      med = med,
-      sigma = sigma
-    ) %>%
-    calculate(
-      stat = stat,
-      order = order,
-      ...
     )
+  
+  hypothesize_fn(
+    res,
+    null = if (has_explanatory(res)) {
+      "independence"
+    } else {
+      "point"
+    },
+    p = p,
+    mu = mu,
+    med = med,
+    sigma = sigma
+  ) |>
+  calculate(
+    stat = stat,
+    order = order,
+    ...
+  )
 }

### 2025-04-25 R/shade_confidence_interval.R

@@ -28,21 +28,21 @@
 #'
 #' @examples
 #' # find the point estimate---mean number of hours worked per week
-#' point_estimate <- gss %>%
-#'   specify(response = hours) %>%
+#' point_estimate <- gss |>
+#'   specify(response = hours) |>
 #'   calculate(stat = "mean")
 #'
 #' # ...and a bootstrap distribution
-#' boot_dist <- gss %>%
+#' boot_dist <- gss |>
 #'   # ...we're interested in the number of hours worked per week
-#'   specify(response = hours) %>%
+#'   specify(response = hours) |>
 #'   # generating data points
-#'   generate(reps = 1000, type = "bootstrap") %>%
+#'   generate(reps = 1000, type = "bootstrap") |>
 #'   # finding the distribution from the generated data
 #'   calculate(stat = "mean")
 #'
 #' # find a confidence interval around the point estimate
-#' ci <- boot_dist %>%
+#' ci <- boot_dist |>
 #'   get_confidence_interval(point_estimate = point_estimate,
 #'                           # at the 95% confidence level
 #'                           level = .95,
@@ -51,12 +51,12 @@
 #'
 #'
 #' # and plot it!
-#' boot_dist %>%
+#' boot_dist |>
 #'   visualize() +
 #'   shade_confidence_interval(ci)
 #'
 #' # or just plot the bounds
-#' boot_dist %>%
+#' boot_dist |>
 #'   visualize() +
 #'   shade_confidence_interval(ci, fill = NULL)
 #'
@@ -64,8 +64,8 @@
 #' # theoretical distributions, too---the theoretical
 #' # distribution will be recentered and rescaled to
 #' # align with the confidence interval
-#' sampling_dist <- gss %>%
-#'   specify(response = hours) %>%
+#' sampling_dist <- gss |>
+#'   specify(response = hours) |>
 #'   assume(distribution = "t")
 #'
 #' visualize(sampling_dist) +
@@ -76,17 +76,17 @@
 #' # explanatory variables, use a `fit()`-based workflow
 #'
 #' # fit 1000 linear models with the `hours` variable permuted
-#' null_fits <- gss %>%
-#'  specify(hours ~ age + college) %>%
-#'  hypothesize(null = "independence") %>%
-#'  generate(reps = 1000, type = "permute") %>%
+#' null_fits <- gss |>
+#'  specify(hours ~ age + college) |>
[…]

### 2025-04-25 R/shade_p_value.R

@@ -32,34 +32,34 @@
 #'
 #' @examples
 #' # find the point estimate---mean number of hours worked per week
-#' point_estimate <- gss %>%
-#'   specify(response = hours) %>%
-#'   hypothesize(null = "point", mu = 40) %>%
+#' point_estimate <- gss |>
+#'   specify(response = hours) |>
+#'   hypothesize(null = "point", mu = 40) |>
 #'   calculate(stat = "t")
 #'
 #' # ...and a null distribution
-#' null_dist <- gss %>%
+#' null_dist <- gss |>
 #'   # ...we're interested in the number of hours worked per week
-#'   specify(response = hours) %>%
+#'   specify(response = hours) |>
 #'   # hypothesizing that the mean is 40
-#'   hypothesize(null = "point", mu = 40) %>%
+#'   hypothesize(null = "point", mu = 40) |>
 #'   # generating data points for a null distribution
-#'   generate(reps = 1000, type = "bootstrap") %>%
+#'   generate(reps = 1000, type = "bootstrap") |>
 #'   # estimating the null distribution
 #'   calculate(stat = "t")
 #'
 #' # shade the p-value of the point estimate
-#' null_dist %>%
+#' null_dist |>
 #'   visualize() +
 #'   shade_p_value(obs_stat = point_estimate, direction = "two-sided")
 #'
 #' # you can shade confidence intervals on top of
 #' # theoretical distributions, too!
-#' null_dist_theory <- gss %>%
-#'   specify(response = hours) %>%
+#' null_dist_theory <- gss |>
+#'   specify(response = hours) |>
 #'   assume(distribution = "t")
 #'
-#' null_dist_theory %>%
+#' null_dist_theory |>
 #'   visualize() +
 #'   shade_p_value(obs_stat = point_estimate, direction = "two-sided")
 #'
@@ -68,17 +68,17 @@
 #' # explanatory variables, use a `fit()`-based workflow
 #'
 #' # fit 1000 linear models with the `hours` variable permuted
-#' null_fits <- gss %>%
-#'  specify(hours ~ age + college) %>%
-#'  hypothesize(null = "independence") %>%
-#'  generate(reps = 1000, type = "permute") %>%
+#' null_fits <- gss |>
+#'  specify(hours ~ age + college) |>
+#'  hypothesize(null = "independence") |>
+#'  generate(reps = 1000, type = "permute") |>
 #'  fit()
 #'
[…]

### 2025-04-25 R/wrappers.R

@@ -28,8 +28,8 @@
 #'
 #' # t test for number of hours worked per week
 #' # by college degree status
-#' gss %>%
-#'    tidyr::drop_na(college) %>%
+#' gss |>
+#'    tidyr::drop_na(college) |>
 #'    t_test(formula = hours ~ college,
 #'       order = c("degree", "no degree"),
 #'       alternative = "two-sided")
@@ -87,7 +87,7 @@ t_test <- function(
       mu = mu,
       conf.level = conf_level,
       ...
-    ) %>%
+    ) |>
       broom::glance()
   } else {
     # one sample
@@ -96,12 +96,12 @@ t_test <- function(
       alternative = alternative,
       mu = mu,
       conf.level = conf_level
-    ) %>%
+    ) |>
       broom::glance()
   }
 
   if (conf_int) {
-    results <- prelim %>%
+    results <- prelim |>
       dplyr::select(
         statistic,
         t_df = parameter,
@@ -112,7 +112,7 @@ t_test <- function(
         upper_ci = conf.high
       )
   } else {
-    results <- prelim %>%
+    results <- prelim |>
       dplyr::select(
         statistic,
         t_df = parameter,
@@ -147,13 +147,13 @@ t_test <- function(
 #'
 #' # t test statistic for true mean number of hours worked
 #' # per week of 40
-#' gss %>%
+#' gss |>
 #'    t_stat(response = hours, mu = 40)
 #'
 #' # t test statistic for number of hours worked per week
 #' # by college degree status
-#' gss %>%
-#'    tidyr::drop_na(college) %>%
+#' gss |>
+#'    tidyr::drop_na(college) |>
 #'    t_stat(formula = hours ~ college,
 #'       order = c("degree", "no degree"),
 #'       alternative = "two-sided")
@@ -210,7 +210,7 @@ t_stat <- function(
       mu = mu,
       conf.level = conf_level,
       ...
-    ) %>%
+    ) |>
       broom::glance()
   } else {
     # one sample
@@ -219,14 +219,14 @@ t_stat <- function(
       alternative = alternative,
       mu = mu,
       conf.level = conf_level
-    ) %>%
+    ) |>
       broom::glance()
   }
 
   # removed unnecessary if(conf_int) clause; only the statistic itself
   # was returned regardless
-  results <- prelim %>%
-    dplyr::select(statistic) %>%
+  results <- prelim |>
+    dplyr::select(statistic) |>
     pull()
 
   results
[…]

### 2025-04-25 data-raw/save_gss.R

@@ -9,13 +9,13 @@ download.file("https://gss.norc.org/documents/stata/GSS_stata.zip", temp)
 
 # if this next line errors with "No such file or directory", try
 # incrementing the number after "_R"
-gss_orig <- haven::read_dta(unz(temp, filename = "GSS7218_R2.DTA")) %>%
+gss_orig <- haven::read_dta(unz(temp, filename = "GSS7218_R2.DTA")) |>
   haven::as_factor()
 unlink(temp)
 
 # select relevant columns
-gss_small <- gss_orig %>%
-  filter(!stringr::str_detect(sample, "blk oversamp")) %>% # this is for weighting
+gss_small <- gss_orig |>
+  filter(!stringr::str_detect(sample, "blk oversamp")) |> # this is for weighting
   select(
     year,
     age,
@@ -28,26 +28,26 @@ gss_small <- gss_orig %>%
     class,
     finrela,
     weight = wtssall
-  ) %>%
+  ) |>
   mutate_if(
     is.factor,
     ~ fct_collapse(., NULL = c("IAP", "NA", "iap", "na"))
-  ) %>%
+  ) |>
   mutate(
-    age = age %>%
-      fct_recode("89" = "89 or older", NULL = "DK") %>% # truncated at 89
-      as.character() %>%
+    age = age |>
+      fct_recode("89" = "89 or older", NULL = "DK") |> # truncated at 89
+      as.character() |>
       as.numeric(),
-    hompop = hompop %>%
-      fct_collapse(NULL = c("DK")) %>%
-      as.character() %>%
+    hompop = hompop |>
+      fct_collapse(NULL = c("DK")) |>
+      as.character() |>
       as.numeric(),
-    hours = hours %>%
-      fct_recode("89" = "89+ hrs", NULL = "DK") %>% # truncated at 89
-      as.character() %>%
+    hours = hours |>
+      fct_recode("89" = "89+ hrs", NULL = "DK") |> # truncated at 89
+      as.character() |>
       as.numeric(),
-    weight = weight %>%
-      as.character() %>%
+    weight = weight |>
+      as.character() |>
       as.numeric(),
     partyid = fct_collapse(
       partyid,
@@ -67,22 +67,22 @@ gss_small <- gss_orig %>%
 
 # sample 3k rows, first dropping NAs
 set.seed(20200201)
-gss <- gss_small %>%
-  drop_na() %>%
[…]

### 2025-04-25 tests/testthat/helper-data.R

@@ -11,18 +11,18 @@ eps <- if (capabilities("long.double")) {
   0.01
 }
 
-gss_tbl <- tibble::as_tibble(gss) %>%
-  dplyr::filter(!(is.na(sex) | is.na(college))) %>%
-  dplyr::mutate(partyid = as.character(partyid)) %>%
+gss_tbl <- tibble::as_tibble(gss) |>
+  dplyr::filter(!(is.na(sex) | is.na(college))) |>
+  dplyr::mutate(partyid = as.character(partyid)) |>
   dplyr::filter(partyid %in% c("ind", "rep", "dem"))
 
-gss_calc <- gss_tbl %>%
-  specify(college ~ sex, success = "no degree") %>%
-  hypothesize(null = "independence") %>%
-  generate(reps = 1000, type = "permute") %>%
+gss_calc <- gss_tbl |>
+  specify(college ~ sex, success = "no degree") |>
+  hypothesize(null = "independence") |>
+  generate(reps = 1000, type = "permute") |>
   calculate(stat = "diff in props", order = c("female", "male"))
 
-mtcars_df <- mtcars %>%
+mtcars_df <- mtcars |>
   dplyr::mutate(
     cyl = factor(cyl),
     vs = factor(vs),
@@ -31,8 +31,8 @@ mtcars_df <- mtcars %>%
     carb = factor(carb)
   )
 
-obs_diff <- gss_tbl %>%
-  specify(college ~ sex, success = "no degree") %>%
+obs_diff <- gss_tbl |>
+  specify(college ~ sex, success = "no degree") |>
   calculate(stat = "diff in props", order = c("female", "male"))
 
 set.seed(2018)
@@ -40,18 +40,18 @@ test_df <- tibble::tibble(stat = rnorm(100))
 
 # Data for visualization tests
 
-gss_permute <- gss_tbl %>%
-  specify(college ~ sex, success = "no degree") %>%
-  hypothesize(null = "independence") %>%
-  generate(reps = 100, type = "permute") %>%
+gss_permute <- gss_tbl |>
+  specify(college ~ sex, success = "no degree") |>
+  hypothesize(null = "independence") |>
+  generate(reps = 100, type = "permute") |>
   calculate(stat = "z", order = c("female", "male"))
 
-gss_viz_sim <- gss_permute %>% visualize(method = "simulation")
+gss_viz_sim <- gss_permute |> visualize(method = "simulation")
 
[…]

### 2025-04-25 tests/testthat/test-aliases.R

@@ -1,24 +1,24 @@
 test_that("aliases work", {
   expect_equal(
-    gss_calc %>%
-      get_pvalue(obs_stat = -0.2, direction = "right") %>%
+    gss_calc |>
+      get_pvalue(obs_stat = -0.2, direction = "right") |>
       dplyr::pull(),
     expected = 1,
     tolerance = eps
   )
 
-  expect_silent(gss_permute %>% get_ci())
+  expect_silent(gss_permute |> get_ci())
 })
 
 test_that("old aliases produce informative error", {
   expect_snapshot(
     error = TRUE,
-    res <- gss_calc %>%
+    res <- gss_calc |>
       p_value(obs_stat = -0.2, direction = "right")
   )
 
   expect_snapshot(
     error = TRUE,
-    res_ <- gss_permute %>% conf_int()
+    res_ <- gss_permute |> conf_int()
   )
 })

### 2025-04-25 tests/testthat/test-fit.R

@@ -1,7 +1,7 @@
-x1 <- gss[1:100, ] %>% specify(response = hours)
-x2 <- gss[1:100, ] %>% specify(hours ~ NULL)
-x3 <- gss[1:100, ] %>% specify(response = hours, explanatory = c(age, college))
-x4 <- gss[1:100, ] %>% specify(hours ~ age + college)
+x1 <- gss[1:100, ] |> specify(response = hours)
+x2 <- gss[1:100, ] |> specify(hours ~ NULL)
+x3 <- gss[1:100, ] |> specify(response = hours, explanatory = c(age, college))
+x4 <- gss[1:100, ] |> specify(hours ~ age + college)
 
 test_that("get_formula helper works", {
   expect_false(has_attr(x1, "formula"))
@@ -37,7 +37,7 @@ test_that("fit_linear_model helper works", {
 
   expect_equal(
     c("character", "numeric"),
-    purrr::map_chr(x3_m, class) %>% unname()
+    purrr::map_chr(x3_m, class) |> unname()
   )
 
   expect_equal(
@@ -47,11 +47,11 @@ test_that("fit_linear_model helper works", {
 })
 
 test_that("fit.infer can handle generated objects", {
-  x3_fit <- x3 %>% fit()
+  x3_fit <- x3 |> fit()
 
-  x3_gen_fit <- x3 %>%
-    hypothesize(null = 'independence') %>%
-    generate(reps = 2, type = "permute") %>%
+  x3_gen_fit <- x3 |>
+    hypothesize(null = 'independence') |>
+    generate(reps = 2, type = "permute") |>
     fit()
 
   expect_equal(unique(x3_fit$term), unique(x3_gen_fit$term))
@@ -66,15 +66,15 @@ test_that("fit.infer can handle generated objects", {
 
 test_that("fit.infer messages informatively on excessive null", {
   expect_snapshot(
-    res_ <- gss %>%
-      specify(hours ~ age + college) %>%
-      hypothesize(null = "independence") %>%
+    res_ <- gss |>
+      specify(hours ~ age + college) |>
+      hypothesize(null = "independence") |>
       fit()
   )
 
   expect_silent(
-    gss %>%
-      specify(hours ~ age + college) %>%
+    gss |>
+      specify(hours ~ age + college) |>
       fit()
   )
 })
@@ -82,53 +82,53 @@ test_that("fit.infer messages informatively on excessive null", {
 test_that("fit.infer logistic regression works", {
   # linear regression default works
   expect_equal(
-    gss %>%
[…]

### 2025-04-25 tests/testthat/test-generate.R

@@ -1,37 +1,37 @@
-hyp_prop <- mtcars_df %>%
-  specify(response = am, success = "1") %>%
+hyp_prop <- mtcars_df |>
+  specify(response = am, success = "1") |>
   hypothesize(null = "point", p = .5)
 
-hyp_diff_in_props <- mtcars_df %>%
-  specify(am ~ vs, success = "1") %>%
+hyp_diff_in_props <- mtcars_df |>
+  specify(am ~ vs, success = "1") |>
   hypothesize(null = "independence")
 
-hyp_chisq_gof <- mtcars_df %>%
-  specify(response = cyl) %>%
+hyp_chisq_gof <- mtcars_df |>
+  specify(response = cyl) |>
   hypothesize(null = "point", p = c("4" = 1 / 3, "6" = 1 / 3, "8" = 1 / 3))
 
-hyp_chisq_ind <- mtcars_df %>%
-  specify(cyl ~ vs) %>%
+hyp_chisq_ind <- mtcars_df |>
+  specify(cyl ~ vs) |>
   hypothesize(null = "independence")
 
-hyp_mean <- mtcars_df %>%
-  specify(response = mpg) %>%
+hyp_mean <- mtcars_df |>
+  specify(response = mpg) |>
   hypothesize(null = "point", mu = 3)
 
-hyp_median <- mtcars_df %>%
-  specify(response = mpg) %>%
+hyp_median <- mtcars_df |>
+  specify(response = mpg) |>
   hypothesize(null = "point", med = 3)
 
-hyp_sd <- mtcars_df %>%
-  specify(response = mpg) %>%
+hyp_sd <- mtcars_df |>
+  specify(response = mpg) |>
   hypothesize(null = "point", sigma = 7)
 
-hyp_diff_in_means <- mtcars_df %>%
-  specify(mpg ~ vs) %>%
+hyp_diff_in_means <- mtcars_df |>
+  specify(mpg ~ vs) |>
   hypothesize(null = "independence")
 
-hyp_anova <- mtcars_df %>%
-  specify(mpg ~ cyl) %>%
+hyp_anova <- mtcars_df |>
+  specify(mpg ~ cyl) |>
   hypothesize(null = "independence")
 
 test_that("cohesion with type argument", {
@@ -76,69 +76,69 @@ test_that("sensible output", {
 })
 
 test_that("auto `type` works (generate)", {
-  one_mean <- mtcars_df %>%
[…]

### 2025-04-25 tests/testthat/test-get_confidence_interval.R

@@ -26,7 +26,7 @@ perc_def_out <- tibble::tibble(
 
 test_that("get_confidence_interval works with defaults", {
   expect_message(
-    expect_equal(test_df %>% get_confidence_interval(), perc_def_out),
+    expect_equal(test_df |> get_confidence_interval(), perc_def_out),
     "Using `level = 0.95`"
   )
 })
@@ -34,14 +34,14 @@ test_that("get_confidence_interval works with defaults", {
 test_that("get_confidence_interval works with `type = 'percentile'`", {
   expect_message(
     expect_equal(
-      test_df %>% get_confidence_interval(type = "percentile"),
+      test_df |> get_confidence_interval(type = "percentile"),
       perc_def_out
     ),
     "Using `level = 0.95`"
   )
 
   expect_equal(
-    test_df %>% get_confidence_interval(level = 0.5, type = "percentile"),
+    test_df |> get_confidence_interval(level = 0.5, type = "percentile"),
     tibble::tibble(
       lower_ci = unname(quantile(test_df[["stat"]], 0.25)),
       upper_ci = unname(quantile(test_df[["stat"]], 0.75))
@@ -53,7 +53,7 @@ test_that("get_confidence_interval works with `type = 'se'`", {
   expect_message(
     # use equivalent rather than equal as ci has attributes for se and point est
     expect_equal(
-      test_df %>%
+      test_df |>
         get_confidence_interval(type = "se", point_estimate = point),
       tibble::tibble(lower_ci = -5.653, upper_ci = 6.603),
       tolerance = 1e-3,
@@ -64,7 +64,7 @@ test_that("get_confidence_interval works with `type = 'se'`", {
 
   # use equivalent rather than equal as ci has attributes for se and point est
   expect_equal(
-    test_df %>%
+    test_df |>
       get_confidence_interval(level = 0.5, type = "se", point_estimate = point),
     tibble::tibble(lower_ci = -1.633, upper_ci = 2.583),
     tolerance = 1e-3,
@@ -75,7 +75,7 @@ test_that("get_confidence_interval works with `type = 'se'`", {
 test_that("get_confidence_interval works with `type = 'bias-corrected'`", {
   expect_message(
     expect_equal(
-      test_df %>%
+      test_df |>
         get_confidence_interval(
           type = "bias-corrected",
           point_estimate = point
[…]

### 2025-04-25 tests/testthat/test-hypothesize.R

@@ -1,47 +1,47 @@
-one_mean <- mtcars_df %>%
-  specify(response = mpg) %>% # formula alt: mpg ~ NULL
+one_mean <- mtcars_df |>
+  specify(response = mpg) |> # formula alt: mpg ~ NULL
   hypothesize(null = "point", mu = 25)
 
-one_mean_specify <- mtcars_df %>%
+one_mean_specify <- mtcars_df |>
   specify(response = mpg)
 
-one_median <- mtcars_df %>%
-  specify(response = mpg) %>% # formula alt: mpg ~ NULL
+one_median <- mtcars_df |>
+  specify(response = mpg) |> # formula alt: mpg ~ NULL
   hypothesize(null = "point", med = 26)
 
-one_prop <- mtcars_df %>%
-  specify(response = am, success = "1") %>% # formula alt: am ~ NULL
+one_prop <- mtcars_df |>
+  specify(response = am, success = "1") |> # formula alt: am ~ NULL
   hypothesize(null = "point", p = .25)
 
-one_prop_specify <- mtcars_df %>%
+one_prop_specify <- mtcars_df |>
   specify(response = am, success = "1")
 
-two_props <- mtcars_df %>%
-  specify(am ~ vs, success = "1") %>% # alt: response = am, explanatory = vs
+two_props <- mtcars_df |>
+  specify(am ~ vs, success = "1") |> # alt: response = am, explanatory = vs
   hypothesize(null = "independence")
 
-gof_chisq <- mtcars_df %>%
-  specify(cyl ~ NULL) %>% # alt: response = cyl
+gof_chisq <- mtcars_df |>
+  specify(cyl ~ NULL) |> # alt: response = cyl
   hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25))
 
-indep_chisq <- mtcars_df %>%
-  specify(cyl ~ am) %>% # alt: response = cyl, explanatory = am
+indep_chisq <- mtcars_df |>
+  specify(cyl ~ am) |> # alt: response = cyl, explanatory = am
   hypothesize(null = "independence")
 
-two_means <- mtcars_df %>%
-  specify(mpg ~ am) %>% # alt: response = mpg, explanatory = am
+two_means <- mtcars_df |>
+  specify(mpg ~ am) |> # alt: response = mpg, explanatory = am
   hypothesize(null = "independence")
 
-two_medians <- mtcars_df %>%
[…]

### 2025-04-25 tests/testthat/test-observe.R

@@ -1,18 +1,18 @@
 test_that("observe() output is equal to core verbs", {
   expect_equal(
-    gss %>%
+    gss |>
       observe(hours ~ NULL, stat = "mean"),
-    gss %>%
-      specify(hours ~ NULL) %>%
+    gss |>
+      specify(hours ~ NULL) |>
       calculate(stat = "mean")
   )
 
   expect_equal(
-    gss %>%
+    gss |>
       observe(hours ~ NULL, stat = "t", null = "point", mu = 40),
-    gss %>%
-      specify(hours ~ NULL) %>%
-      hypothesize(null = "point", mu = 40) %>%
+    gss |>
+      specify(hours ~ NULL) |>
+      hypothesize(null = "point", mu = 40) |>
       calculate(stat = "t")
   )
 
@@ -23,8 +23,8 @@ test_that("observe() output is equal to core verbs", {
       stat = "diff in means",
       order = c("degree", "no degree")
     ),
-    gss %>%
-      specify(age ~ college) %>%
+    gss |>
+      specify(age ~ college) |>
       calculate("diff in means", order = c("degree", "no degree")),
     ignore_attr = TRUE
   )
@@ -33,43 +33,43 @@ test_that("observe() output is equal to core verbs", {
 test_that("observe messages/warns/errors informatively", {
   expect_equal(
     expect_message(
-      gss %>%
+      gss |>
         observe(hours ~ NULL, stat = "mean", mu = 40)
-    ) %>%
+    ) |>
       conditionMessage(),
     expect_message(
-      gss %>%
-        specify(hours ~ NULL) %>%
-        hypothesize(null = "point", mu = 40) %>%
+      gss |>
+        specify(hours ~ NULL) |>
+        hypothesize(null = "point", mu = 40) |>
         calculate(stat = "mean")
-    ) %>%
+    ) |>
       conditionMessage()
   )
 
   expect_equal(
     expect_warning(
-      gss %>%
+      gss |>
         observe(hours ~ NULL, stat = "t")
-    ) %>%
+    ) |>
       conditionMessage(),
     expect_warning(
-      gss %>%
-        specify(hours ~ NULL) %>%
+      gss |>
+        specify(hours ~ NULL) |>
         calculate(stat = "t")
-    ) %>%
+    ) |>
       conditionMessage()
   )
 
   expect_error(
     expect_equal(
       capture.output(
-        gss %>%
+        gss |>
           observe(hours ~ age, stat = "diff in means"),
         type = "message"
[…]

### 2025-04-25 tests/testthat/test-print.R

@@ -1,8 +1,8 @@
 test_that("print works", {
   expect_output(print(
-    gss_tbl %>%
-      specify(age ~ hours) %>%
-      hypothesize(null = "independence") %>%
+    gss_tbl |>
+      specify(age ~ hours) |>
+      hypothesize(null = "independence") |>
       generate(reps = 10, type = "permute")
   ))
 })

### 2025-04-25 tests/testthat/test-shade_confidence_interval.R

@@ -73,16 +73,16 @@ test_that("shade_confidence_interval throws errors and warnings", {
   )
   expect_snapshot(
     error = TRUE,
-    res_ <- gss_viz_sim %>% shade_confidence_interval(c(-1, 1))
+    res_ <- gss_viz_sim |> shade_confidence_interval(c(-1, 1))
   )
   expect_snapshot(
     error = TRUE,
-    res_ <- gss_viz_sim %>% shade_confidence_interval(endpoints = c(-1, 1))
+    res_ <- gss_viz_sim |> shade_confidence_interval(endpoints = c(-1, 1))
   )
-  expect_snapshot(error = TRUE, res_ <- gss_viz_sim %>% shade_ci(c(-1, 1)))
+  expect_snapshot(error = TRUE, res_ <- gss_viz_sim |> shade_ci(c(-1, 1)))
   expect_snapshot(
     error = TRUE,
-    res_ <- gss_viz_sim %>% shade_ci(endpoints = c(-1, 1))
+    res_ <- gss_viz_sim |> shade_ci(endpoints = c(-1, 1))
   )
 })
 

### 2025-04-25 tests/testthat/test-specify.R

@@ -1,12 +1,12 @@
-one_nonshift_mean <- mtcars_df %>% specify(response = mpg)
+one_nonshift_mean <- mtcars_df |> specify(response = mpg)
 
-one_nonshift_prop <- mtcars_df %>% specify(response = am, success = "1")
+one_nonshift_prop <- mtcars_df |> specify(response = am, success = "1")
 
-two_means_boot <- mtcars_df %>% specify(mpg ~ am)
+two_means_boot <- mtcars_df |> specify(mpg ~ am)
 
-two_props_boot <- mtcars_df %>% specify(am ~ vs, success = "1")
+two_props_boot <- mtcars_df |> specify(am ~ vs, success = "1")
 
-slope_boot <- mtcars_df %>% specify(mpg ~ hp)
+slope_boot <- mtcars_df |> specify(mpg ~ hp)
 
 test_that("auto `type` works (specify)", {
   expect_equal(attr(one_nonshift_mean, "type"), "bootstrap")
@@ -68,8 +68,8 @@ test_that("formula argument is a formula", {
   expect_snapshot(error = TRUE, specify(mtcars, am, success = "1"))
   expect_snapshot(error = TRUE, specify(mtcars, response = am, "1"))
   expect_silent({
-    mtcars %>%
-      dplyr::mutate(am = factor(am)) %>%
+    mtcars |>
+      dplyr::mutate(am = factor(am)) |>
       specify(response = am, success = "1")
   })
 })
@@ -85,32 +85,32 @@ test_that("specify doesn't have NSE issues (#256)", {
 
 test_that("specify messages when dropping unused levels", {
   expect_snapshot(
-    res_ <- gss %>%
-      dplyr::filter(partyid %in% c("rep", "dem")) %>%
+    res_ <- gss |>
+      dplyr::filter(partyid %in% c("rep", "dem")) |>
       specify(age ~ partyid)
   )
 
   expect_snapshot(
-    res_ <- gss %>%
-      dplyr::filter(partyid %in% c("rep", "dem")) %>%
+    res_ <- gss |>
+      dplyr::filter(partyid %in% c("rep", "dem")) |>
       specify(partyid ~ age)
   )
 
   expect_snapshot(
-    res_ <- gss %>%
-      dplyr::filter(partyid %in% c("rep", "dem")) %>%
+    res_ <- gss |>
+      dplyr::filter(partyid %in% c("rep", "dem")) |>
       specify(partyid ~ NULL)
   )
 
[…]

### 2025-04-25 tests/testthat/test-utils.R

@@ -106,14 +106,14 @@ test_that("hypothesize errors out when x isn't a dataframe", {
 
 test_that("p_null supplies appropriate params", {
   expect_equal(
-    gss %>% specify(partyid ~ NULL) %>% p_null(),
+    gss |> specify(partyid ~ NULL) |> p_null(),
     c(p.dem = 0.2, p.ind = 0.2, p.rep = 0.2, p.other = 0.2, p.DK = 0.2)
   )
 })
 
 test_that("variables are standardized as expected", {
   gss_types <-
-    gss %>%
+    gss |>
     dplyr::mutate(
       age = as.integer(age),
       is_dem = dplyr::if_else(partyid == "dem", TRUE, FALSE),
@@ -144,10 +144,10 @@ test_that("group_by_replicate() helper returns correct results", {
   nrow_gss <- nrow(gss)
 
   gss_gen <-
-    gss %>%
-    specify(age ~ college) %>%
-    hypothesize(null = "independence") %>%
-    generate(reps = reps, type = "permute") %>%
+    gss |>
+    specify(age ~ college) |>
+    hypothesize(null = "independence") |>
+    generate(reps = reps, type = "permute") |>
     dplyr::ungroup()
 
   expect_equal(

### 2025-04-25 tests/testthat/test-visualize.R

@@ -2,22 +2,22 @@ library(dplyr)
 
 set.seed(42)
 
-hours_resamp <- gss_tbl %>%
-  specify(hours ~ NULL) %>%
-  hypothesize(null = "point", med = 3) %>%
-  generate(reps = 10, type = "bootstrap") %>%
+hours_resamp <- gss_tbl |>
+  specify(hours ~ NULL) |>
+  hypothesize(null = "point", med = 3) |>
+  generate(reps = 10, type = "bootstrap") |>
   calculate(stat = "median")
 
-obs_slope <- lm(age ~ hours, data = gss_tbl) %>%
-  broom::tidy() %>%
-  dplyr::filter(term == "hours") %>%
-  dplyr::select(estimate) %>%
+obs_slope <- lm(age ~ hours, data = gss_tbl) |>
+  broom::tidy() |>
+  dplyr::filter(term == "hours") |>
+  dplyr::select(estimate) |>
   dplyr::pull()
 
-obs_diff <- gss_tbl %>%
-  group_by(college) %>%
-  summarize(prop = mean(college == "no degree")) %>%
-  summarize(diff(prop)) %>%
+obs_diff <- gss_tbl |>
+  group_by(college) |>
+  summarize(prop = mean(college == "no degree")) |>
+  summarize(diff(prop)) |>
   pull()
 
 obs_z <- sqrt(
@@ -29,13 +29,13 @@ obs_z <- sqrt(
   )$statistic
 )
 
-obs_diff_mean <- gss_tbl %>%
-  group_by(college) %>%
-  summarize(mean_sepal_width = mean(hours)) %>%
-  summarize(diff(mean_sepal_width)) %>%
+obs_diff_mean <- gss_tbl |>
+  group_by(college) |>
+  summarize(mean_sepal_width = mean(hours)) |>
+  summarize(diff(mean_sepal_width)) |>
   pull()
 
-obs_t <- gss_tbl %>%
+obs_t <- gss_tbl |>
   observe(hours ~ college, order = c("no degree", "degree"), stat = "t")
 
 obs_F <- anova(
@@ -48,48 +48,48 @@ test_that("visualize warns with bad arguments", {
   # warns when supplied deprecated args in what used to be
   # a valid way
   expect_snapshot(
-    res_ <- gss_tbl %>%
-      specify(age ~ hours) %>%
-      hypothesize(null = "independence") %>%
-      generate(reps = 100, type = "permute") %>%
-      calculate(stat = "slope") %>%
[…]

### 2025-04-25 tests/testthat/test-wrappers.R

@@ -1,10 +1,10 @@
 test_that("t_test works", {
   # Two Sample
-  expect_snapshot(res_ <- gss_tbl %>% t_test(hours ~ sex))
+  expect_snapshot(res_ <- gss_tbl |> t_test(hours ~ sex))
 
   expect_snapshot(
     error = TRUE,
-    gss_tbl %>% t_test(response = "hours", explanatory = "sex")
+    gss_tbl |> t_test(response = "hours", explanatory = "sex")
   )
 
   new_way <- t_test(gss_tbl, hours ~ sex, order = c("male", "female"))
@@ -14,8 +14,8 @@ test_that("t_test works", {
     explanatory = sex,
     order = c("male", "female")
   )
-  old_way <- t.test(hours ~ sex, data = gss_tbl) %>%
-    broom::glance() %>%
+  old_way <- t.test(hours ~ sex, data = gss_tbl) |>
+    broom::glance() |>
     dplyr::select(
       statistic,
       t_df = parameter,
@@ -35,12 +35,12 @@ test_that("t_test works", {
   expect_equal(new_way[["statistic"]], -new_way2[["statistic"]])
 
   # One Sample
-  new_way <- gss_tbl %>%
+  new_way <- gss_tbl |>
     t_test(hours ~ NULL, mu = 0)
-  new_way_alt <- gss_tbl %>%
+  new_way_alt <- gss_tbl |>
     t_test(response = hours, mu = 0)
-  old_way <- t.test(x = gss_tbl$hours, mu = 0) %>%
-    broom::glance() %>%
+  old_way <- t.test(x = gss_tbl$hours, mu = 0) |>
+    broom::glance() |>
     dplyr::select(
       statistic,
       t_df = parameter,
@@ -58,15 +58,15 @@ test_that("t_test works", {
 test_that("chisq_test works", {
   # maleependence
   expect_silent(
-    gss_tbl %>%
+    gss_tbl |>
       chisq_test(college ~ partyid)
   )
-  new_way <- gss_tbl %>%
+  new_way <- gss_tbl |>
     chisq_test(college ~ partyid)
-  new_way_alt <- gss_tbl %>%
+  new_way_alt <- gss_tbl |>
     chisq_test(response = college, explanatory = partyid)
-  old_way <- chisq.test(x = table(gss_tbl$partyid, gss_tbl$college)) %>%
-    broom::glance() %>%
[…]

### 2025-04-25 README.Rmd
`usethis::use_tidy_github_actions()`
Mostly just updates GHA versions, but also renames `check-standard.yaml` to `R-CMD-check.yaml`

@@
 
-[![R-CMD-check](https://github.com/tidymodels/infer/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/tidymodels/infer/actions/workflows/check-standard.yaml)
+[![R-CMD-check](https://github.com/tidymodels/infer/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tidymodels/infer/actions/workflows/R-CMD-check.yaml)
 [![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)

### 2025-06-04 README.Rmd

@@
 [![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)
-[![Coverage Status](https://img.shields.io/codecov/c/github/tidymodels/infer/main.svg)](https://app.codecov.io/github/tidymodels/infer/?branch=main)
+[![Codecov test coverage](https://codecov.io/gh/tidymodels/infer/graph/badge.svg)](https://app.codecov.io/gh/tidymodels/infer)
 

### 2025-12-12 README.Rmd

@@
 
-If you're interested in learning more about randomization-based statistical inference generally, including applied examples of this package, we recommend checking out [Statistical Inference Via Data Science: A ModernDive Into R and the Tidyverse](https://moderndive.com/) and [Introduction to Modern Statistics](https://openintro-ims.netlify.app/).
+If you're interested in learning more about randomization-based statistical inference generally, including applied examples of this package, we recommend checking out [Statistical Inference Via Data Science: A ModernDive Into R and the Tidyverse](https://moderndive.com/v2/) and [Introduction to Modern Statistics](https://openintro-ims.netlify.app/).
 

### 2025-12-12 man-roxygen/seeds.Rmd

@@
 
-gss %>%
-  specify(age ~ college) %>%
-  hypothesize(null = "independence") %>%
-  generate(reps = 5, type = "permute") %>%
+gss |>
+  specify(age ~ college) |>
+  hypothesize(null = "independence") |>
+  generate(reps = 5, type = "permute") |>
   calculate("diff in means", order = c("degree", "no degree"))

### 2025-12-12 README.Rmd
swap hex logo
🤫

@@
 # infer R Package <img src="man/figures/logo.png" alt="A hexagonal logo.
-A silhouette of a fir tree sits atop green text, reading 'infer'.
-The logo has a white background and green border." align="right" width=280 />
+A green silhouette of a fir tree sits atop black text, reading 'infer'.
+The logo has a background in two shades of blue, resembling the Oregon license plate." align="right" width=280 />
 
